



### LEFT OFF HERE 
### correlation matrices — by category levels

_Here we explore the distribution of each SD variable (e.g. MAKER TRUST) by the different values of each categorical variable (e.g. MAKER ID). Patterns of interest are noted, which we explore further in the section **exploratory questions**._

##### MAKER ID X SD 
```{r, maker_id-sds}


df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

## CORRELATION MATRIX SPLIT BY MAKER ID  
(x <-   ggscatmat(df, columns = 1:11, color = "MAKER_ID", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="reds", direction = "1"), name = "",  guide = guide_legend(reverse = FALSE)) +   
    theme_minimal())
if(GRAPH_SAVE){ggsave(plot = x, path="figs/corr_by_group", filename =paste0("maker_id_corr_sd.png"), units = c("in"), width = 14, height = 10 )}


```
**Interesting patterns to explore further**

- When participants identify the maker as an INDIVIDUAL, the following variables show a different pattern than the other identifications: MAKER_DESIGN, MAKER_DATA, CHART INTENT
- interesting bimodal distribution on CHART INTENT for most identifications, except individuals and organizations 

##### MAKER ID X SD (abs)
```{r, maker_id-sds-abs}
if(GRAPH_SAVE){

df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

## CORRELATION MATRIX SPLIT BY MAKER ID  
(x <-   ggscatmat(df, columns = 1:11, color = "MAKER_ID", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="reds", direction = "1"), name = "",  guide = guide_legend(reverse = FALSE)) +   
    theme_minimal())
ggsave(plot = x, path="figs/corr_by_group", filename =paste0("maker_id_corr_abs.png"), units = c("in"), width = 14, height = 10 )

}
```


##### MAKER AGE X SD
```{r, maker_age-sds}
if(GRAPH_SAVE){

  df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)
  
  ## CORRELATION MATRIX SPLIT BY MAKER AGE  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_AGE", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="lightblues", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal())
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("maker_age_corr_sd.png"), units = c("in"), width = 14, height = 10 )
}
```

**Interesting patterns to explore further**

- maker_design, chart_like, chart_beauty for BOOMER vs. others
- maker_data for gen Z vs others 


##### MAKER AGE X SD (abs)
```{r, maker_age-sds-abs}
if(GRAPH_SAVE){
  
  df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

  ## CORRELATION MATRIX SPLIT BY MAKER AGE  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_AGE", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="lightblues", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal())
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("maker_age_corr_abs.png"), units = c("in"), width = 14, height = 10 )
}
```


##### MAKER GENDER X SD 
```{r, maker_gender-sds}
if(GRAPH_SAVE){
  
  df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)
  
  ## CORRELATION MATRIX SPLIT BY MAKER GENDER  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_GENDER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="smallgreens", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal() )
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("maker_gender_corr_sd.png"), units = c("in"), width = 14, height = 10 )
}
```
**Interesting patterns to explore further**
- maker-data for FEMALE

##### MAKER GENDER X SD (abs)
```{r, maker_gender-sds-abs}
if(GRAPH_SAVE){
  
  df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

  
  ## CORRELATION MATRIX SPLIT BY MAKER GENDER  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_GENDER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="smallgreens", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal() )
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("maker_gender_corr_abs.png"), units = c("in"), width = 14, height = 10 )
}
```

##### TOOL ID  X SD
```{r, tool-id-sds}
if(GRAPH_SAVE){
  
df <- df_tools %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    TOOL_ID) 
  
  ## CORRELATION MATRIX SPLIT BY TOOL ID
 (x <-  ggscatmat(df, columns = 1:11, color = "TOOL_ID", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="tools", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +
    theme_minimal() )
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("tool_id_corr_sd.png"), units = c("in"), width = 14, height = 10 )
}  
```

**Interesting patterns to explore further**
- maker data for design-basic, interesting pattern
- look closer at chart beauty
- interesting pattern across values on chart intent



##### ENCOUNTER X SD
```{r, encounter-sds}  
if(GRAPH_SAVE){
  

df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    ENCOUNTER) %>% 
    mutate(ENCOUNTER = fct_rev(ENCOUNTER))

## CORRELATION MATRIX SPLIT BY ENCOUNTER
(x <-   ggscatmat(df, columns = 1:11, color = "ENCOUNTER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="encounter", direction = "1"))+
    theme_minimal())
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("encounter_corr_sd.png"), units = c("in"), width = 14, height = 10 )
  
}  
```    
**Interesting patterns to explore further**
— no difference at ALL in maker data - interesting!
- chart beauty very diff
- chart intent intersting bimodal

##### ENCOUNTER X SD (abs)
```{r, encounter-sds-abs}  
if(GRAPH_SAVE){
  

df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    ENCOUNTER) %>% 
    mutate(ENCOUNTER = fct_rev(ENCOUNTER))

## CORRELATION MATRIX SPLIT BY ENCOUNTER
(x <-   ggscatmat(df, columns = 1:11, color = "ENCOUNTER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="encounter", direction = "1"))+
    theme_minimal())
  ggsave(plot = x, path="figs/corr_by_group", filename =paste0("encounter_corr_abs.png"), units = c("in"), width = 14, height = 10 )
  
}  
```    


##### CHART ACTION X SD
```{r, chart-action-sds}
if(GRAPH_SAVE){
  

df <- df_actions %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    CHART_ACTION) 
  
  ## CORRELATION MATRIX SPLIT BY CHART ACTION
(x <- ggscatmat(df, columns = 1:11, color = "CHART_ACTION", alpha = 0.2) + 
    scale_color_manual(values = my_palettes(name="actions", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +
    theme_minimal() )
ggsave(plot = x, path="figs/corr_by_group", filename =paste0("chart_action_corr_sd.png"), units = c("in"), width = 14, height = 10  )

}
```
**Interesting patterns to explore further**
- unfollow/block across all! 

## EXPLORATORY QUESTIONS

- When participants identify the maker as an INDIVIDUAL, the following variables show a different pattern than the other identifications: MAKER_DESIGN, MAKER_DATA, CHART INTENT
- interesting bimodal distribution on CHART INTENT for most identifications, except individuals and organizations 


### MAKER ID & Maker DATA COMPETENCY
```{r vis-maker-id-data, warning=FALSE}

df <- df_graphs 

## Does MAKER_DATA  depend on MAKER ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_DATA','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_DATA','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(count = n()) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_DATA, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", 
               vjust=+2, hjust = 0, aes( label=round(..x.., digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "DATA COMPETENCY by MAKER ID", y = "", x = "MAKER DATA COMPETENCY", caption="(mean in blue)") +
  theme_minimal() + easy_remove_legend()

```

#### model
```{r model-maker-id-data}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## SET CONTRASTS
contrasts(df$MAKER_ID) <-car::contr.Treatment(levels(df$MAKER_ID)) # intercept first group mean; coeff dif from first

## DEFINE MODEL
f <- "MAKER_DATA ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_DATA ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        value.offset = .25,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```

### Maker ID & Maker DESIGN COMPETENCY
```{r}

df <- df_graphs

## Does MAKER_DESIGN  depend on MAKER ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_DESIGN','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_DESIGN','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(count = n()) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_DESIGN, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", 
               vjust=+2, hjust = 0, aes( label=round(..x.., digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "DESIGN COMPETENCY by MAKER ID", y = "", x = "MAKER DESIGN COMPETENCY", caption="(mean in blue)") +
  theme_minimal() + easy_remove_legend()

```


#### model
```{r model-maker-id-design}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## DEFINE MODEL
f <- "MAKER_DESIGN ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_DESIGN ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```









- maker_design, chart_like, chart_beauty for BOOMER vs. others
- maker_data for gen Z vs others 
- maker-data for FEMALE


- maker data for design-basic, interesting pattern
- look closer at chart beauty
- interesting pattern across values on chart intent

— no difference at ALL in maker data - interesting!
- chart beauty very diff
- chart intent intersting bimodal

### Maker ID & Maker POLITICS
```{r, message=FALSE}

df <- df_graphs

## Does MAKER POLITICS depend on MAKER ID?
##RIDGEPLOT w/ MEAN 
answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_POLITIC','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_POLITIC','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(count = n()) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_POLITIC, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", 
               vjust=+2, hjust = 0, aes( label=round(..x.., digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "POLITICS by MAKER ID", y = "", x = "MAKER POLITICS", caption="(mean in blue)") +
  theme_minimal() + easy_remove_legend()

```

#### model
```{r model-maker-id-politics}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## DEFINE MODEL
f <- "MAKER_POLITIC ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_POLITIC ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```


### Maker ID & Maker TRUST

```{r}

df <- df_graphs

## Does MAKER_TRUST  depend on MAKER ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_TRUST','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_TRUST','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(count = n()) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_TRUST, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", 
               vjust=+2, hjust = 0, aes( label=round(..x.., digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "MAKER TRUST COMPETENCY by MAKER ID", y = "", x = "MAKER TRUST", caption="(mean in blue)") +
  theme_minimal() + easy_remove_legend()

```

#### model
```{r model-maker-id-trust}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## DEFINE MODEL
f <- "MAKER_TRUST ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_TRUST ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```


# TODO B0 SUPERPOWER ANALYSIS

## TODO MAKER

## TODO TOOL

## TODO BEHAVIOR

## TODO SEMANTIC DIFFERENTIALS

## TODO DATA MODELLING

# TODO LIMITED MODELLING

## FULL STIMULUS SET

### What predicts TRUST?

design competence? data competence? chart intent? maker id?

### What predicts BEAUTY?

### What predicts ACTION?

### Does MAKER ID predict MAKER POLITICS?

### Does MAKER ID predict CHART INTENT?

### Does MAKER AGE <predict> TOOL ID

### Does MAKER GENDER <predict> anything?

-   highlight maker_gender = female points in raincloud SD plots

### DOES TOOL ID predict DATA (VS) DESIGN competence

### DOES CHART(TYPE) <predict> MAKER(DATA COMPETENCE)

### DOES MAKER ID=individual imply TOOL(ID)=[simple]

### Worth doing any stimulus abstraction category level analysis?

#### PREDICT more abstract corresponds with low design competence (opposite for figural)

# TODO ARGUMENTS

## TODO look for examples of inconsistent relationships between TRUST and BEAUTY

## TODO look for examples of inconsistent relationships between TRUST and DATA COMPETENCE

## TODO look for patterns of reversal between CHART LIKE and CHART BEAUTY

# RESOURCES

-   custom color palettes: <https://www.r-bloggers.com/2022/06/custom-colour-palettes-for-ggplot2/>
-   lessR donuts <https://r-charts.com/part-whole/donut-chart/>
-   GGSANKEY <https://github.com/davidsjoberg/ggsankey>
-   GGALLUVIAL <https://corybrunson.github.io/ggalluvial/articles/ggalluvial.html>
-   variable standardization [variable (vs) participant] :https://cran.r-project.org/web/packages/datawizard/vignettes/standardize_data.html
- contrasts:
- UCLA:https://stats.oarc.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables
- https://phillipalday.com/stats/lazy-contrasts.html
- level naming with contrasts :https://rpubs.com/bbolker/5335
