---
title: "VIBES STUDY 2 REPORTING"
author: "ANONYMIZED"
date: "2024-08-07"
output:
  html_document:
    theme: flatly
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 5
  pdf_document:
    toc: yes
    toc_depth: '4'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe()
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates

#EDA
library(qacBase)

#VIZ
library(kableExtra) #printing tables
library(ggformula) #regression syntax viz
# library(vcd) #mosaic plots
# library(vcdExtra) #mosaic plot helpers
library(ggstatsplot) #dummies
library(GGally) #extends ggplot for EDA 
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(ggridges) #ridge plots
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(lessR) ##very pretty donuts 
library(ggsankey) ## ggplot2 sankey extension


#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer


#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
graph_render = TRUE #set to true to generate all the SD graphs and save to folders 

```

*This notebook contains code to replicate analyses reported in CHI submission*.

In VISUALIZATION VIBES project Study 2, participants completed an attitutde eliciation survey, asking questions about their attitude toward (5) stimulus images (data visualizations). Each participant was randomly assigned to one of 6 stimulus blocks, each containing 1 image from each of (4) categories (ranging from most abstract to most figural). Each participant started by responding to questions for a single 'common block' stimulus (that is thus super-powered as it was seen by all participants). Two participant recruitment pools were used: Prolific, with a smaller set of participants recruited from Tumblr (to replicate results of interview Study 1 with participants sourced from Tumblr).

# SETUP

*We start by importing data files previously wrangled in `0_VIBES_S2_wrangling.Rmd`.*

### REFS 
```{r import-refs, message=FALSE, warning = FALSE}

############## IMPORT REFERENCE FILES
ref_stimuli <- readRDS("data/input/REFERENCE/ref_stimuli.rds")
ref_surveys <- readRDS("data/input/REFERENCE/ref_surveys.rds")
```
### DATA 
```{r import-data, message=FALSE, warning = FALSE}

############## IMPORT DATA FILES
# df_data <- readRDS("data/output/df_data.rds")
df_participants <- readRDS("data/output/df_participants.rds")
# df_questions <- readRDS("data/output/df_questions.rds")
# df_sd_questions_wide <- readRDS("data/output/df_sd_questions_wide.rds")
# df_sd_questions_long <- readRDS("data/output/df_sd_questions_long.rds")
df_tools <- readRDS("data/output/df_tools.rds")
df_actions <- readRDS("data/output/df_actions.rds")
# df_graphs_full <- readRDS("data/output/df_graphs_full.rds")
df_graphs <- readRDS("data/output/df_graphs.rds")

```

### LABELS 
```{r setup-labels}

############## SETUP Graph Labels
ref_stim_id <- levels(ref_stimuli$ID)
ref_cat_questions <- c("MAKER_ID","MAKER_AGE","MAKER_GENDER")
ref_free_response <- c("MAKER_DETAIL", "MAKER_EXPLAIN", "TOOL_DETAIL", "CHART_EXPLAIN")
ref_conf_questions <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")
ref_sd_questions <- c("MAKER_DESIGN","MAKER_DATA","MAKER_POLITIC",
               "MAKER_ARGUE","MAKER_SELF","MAKER_ALIGN","MAKER_TRUST",
               "CHART_LIKE", "CHART_BEAUTY", "CHART_INTENT", "CHART_TRUST")
left <- c("professional","professional","left-leaning","confrontational",
          "altruistic","does NOT share","untrustworthy",
          "NOT at all","NOT at all", "inform", "untrustworthy")
right <- c("layperson","layperson","right-leaning","diplomatic",
           "selfish", "DOES share", "trustworthy",
           "very much", "very much", "persuade", "trusthworthy")
ref_labels <- as.data.frame(cbind(left,right))
rownames(ref_labels) <- ref_sd_questions
# ref_blocks <- c("block1", "block2", "block3", "block4", "block5", "block6")
ref_blocks <- c(1,2,3,4,5,6)
rm(left,right)


```

### COLOR 
```{r setup-pallettes}

############## SETUP Colour Palettes
#https://www.r-bloggers.com/2022/06/custom-colour-palettes-for-ggplot2/

## list of color pallettes
my_colors = list(
  politics = c("#184aff","#5238bf", "#4f4a52" ,"#84649c", "#ff0000"),
  blackred = c("black","red"),
  greens = c("#ADC69D","#81A06D","#567E39","#2D5D16","#193E0A"),
  olives = c("#CDCEA1","#B8B979","#A0A054","#78783F","#50502A","#35351C"),
  lightblues = c("#96C5D2","#61A2B2","#3C8093","#2C6378","#1F4A64"),
  darkblues = c("#7AAFE1","#3787D2","#2A73B7","#225E96","#1A4974","#133453"),
  reds = c("#D9B8BD","#CE98A2","#B17380","#954E5F","#78263E","#62151F")
)



## function for using palettes
my_palettes = function(name, n, all_palettes = my_colors, type = c("discrete","continuous"), direction = c("1","-1")) {
  palette = all_palettes[[name]]
  if (missing(n)) {
    n = length(palette)
  }
  type = match.arg(type)
  out = switch(type,
               continuous = grDevices::colorRampPalette(palette)(n),
               discrete = palette[1:n]
  )
  out = switch(direction,
               "1" = out,
               "-1" = palette[n:1])
  structure(out, name = name, class = "palette")
}

```

## GRAPHING Functions

```{r SD-GRAPHING-FUNCTIONS}


############## RETURNS SD STACKED AND COLORED BY BY X
## LOOP STYLE
multi_sd <- function (df, left, right, x, y, color) {

  # g <- ggplot(df, aes(y = .data[[x]], x = {{y}}, color = {{color}}))+
  g <- ggplot(df, aes(y = .data[[x]], x = .data[[y]], color = .data[[color]]))+
  geom_boxplot(width = 0.5) +
  geom_jitter(width = 0.1, alpha=0.5) +
    
  scale_y_continuous(limits=c(-1,101)) +
  labs(x="", y="") +
  coord_flip() +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) + theme_minimal()

  return(g)
}


############## RETURNS SINGLE SD 
## LOOP STYLE
single_sd <- function (df, left, right, x) {

  g <- ggplot(df, aes(y = {{x}}, x = ""))+
  geom_boxplot(width = 0.5) +
  geom_jitter(width = 0.1, alpha=0.5) +
  scale_y_continuous(limits=c(-1,101)) +
  labs(x="", y="") +
  coord_flip() +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) + theme_minimal()

  return(g)
}



######## RETURNS SINGLE SD
##  APPLY STYLE
# plot_sd = function (data, column, type, split, boxplot) {
# 
#   ggplot(df, aes(y = .data[[column]], x="")) +
#     {if(boxplot) geom_boxplot(width = 0.5) } +
#     geom_jitter(width = 0.1, alpha=0.3, {if(split) aes(color=Distribution)}) +
#     {if(split) facet_grid(Distribution ~ .)} +
#     scale_y_continuous(limits=c(-1,101)) +
#     labs(x="", y="") +
#     coord_flip()  +
#     {if(type == "S")
#       guides(
#         y = guide_axis_manual(labels = ref_labels[column,"left"]),
#         y.sec = guide_axis_manual(labels = ref_labels[column,"right"])
#       )} +
#     {if(type == "Q")
#       guides(
#         y = guide_axis_manual(labels = ref_labels[q,"left"]),
#         y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
#       )} +
#   theme_minimal()  +
#      labs (
#        caption = column
#      )
# }

######## RETURNS SINGLE SD
##  APPLY STYLE
plot_sd = function (data, column, type, facet, facet_by, boxplot) {

  ggplot(df, aes(y = .data[[column]], x="")) +
    {if(boxplot) geom_boxplot(width = 0.5) } +
    geom_jitter(width = 0.1, alpha=0.3, {if(facet) aes(color=.data[[facet_by]])}) +
    {if(facet) facet_grid(.data[[facet_by]] ~ .)} +
    scale_y_continuous(limits=c(-1,101)) +
    labs(x="", y="") +
    coord_flip()  +
    {if(type == "S")
      guides(
        y = guide_axis_manual(labels = ref_labels[column,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[column,"right"])
      )} +
    {if(type == "Q")
      guides(
        y = guide_axis_manual(labels = ref_labels[q,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
      )} +
  theme_minimal()  +
     labs (
       caption = column
     ) + easy_remove_legend()
}

```

# DESCRIBE SAMPLE

## Sample Demographics

```{r sample-size}

## FOR DESCRIPTIVES PARAGRAPH
# #PROLIFIC
df.p <- df_participants %>% filter(Distribution == "PROLIFIC")
desc.gender.p <- table(df.p$D_gender) %>% prop.table()
names(desc.gender.p) <- levels(df.p$D_gender)
p_participants <- nrow(df.p)

# #TUMBLR
df.t <- df_participants %>% filter(Distribution == "TUMBLR")
desc.gender.t <- table(df.t$D_gender) %>% prop.table()
names(desc.gender.t) <- levels(df.t$D_gender)
t_participants <- nrow(df.t)


```

`r p_participants` individuals from Prolific participated in Study 2, ( `r round(desc.gender.p[["Female"]],2)*100`% Female, `r round(desc.gender.p[["Male"]],2)*100`% Male, `r round(desc.gender.p[["Non-binary / third gender"]],2)*100`% Non-binary, `r (round((desc.gender.p[["Prefer not to say"]] + desc.gender.p[["Prefer to self-describe"]]),2)) * 100`% Other).

Note that a higher proportion of participants recruited from Tumblr represent identities other than cis-gender Female and cis-gender Male. `r t_participants` individuals from Tumblr participated in Study 2, ( `r round(desc.gender.t[["Female"]],2)*100`% Female, `r round(desc.gender.t[["Male"]],2)*100`% Male, `r round(desc.gender.t[["Non-binary / third gender"]],2)*100`% Non-binary, `r (round((desc.gender.t[["Prefer not to say"]] + desc.gender.t[["Prefer to self-describe"]]),2)) * 100`% Other). \*A total of `r n_tumblr + n_prolific` participants were recruited from US-located English speaking users of Tumblr (n = `r n_tumblr`) and Prolific (n = `r n_prolific`).

## Study Response Time

```{r demo-response-time}

df <- df_participants

## for descriptives paragraph
p.desc.duration <- psych::describe(df %>% filter(Distribution=="PROLIFIC") %>% pull(duration.min))
t.desc.duration <- psych::describe(df %>% filter(Distribution=="TUMBLR") %>% pull(duration.min))

```

PROLIFIC SAMPLE (n = `r p.desc.duration$n` ) participant response times ranged from `r p.desc.duration$min` to `r p.desc.duration$max` minutes, with a mean response time of `r round(p.desc.duration$mean,2)` minutes, SD = `r (round(p.desc.duration$sd,2))`.

TUMBLR SAMPLE (n = `r t.desc.duration$n` ) participant response times ranged from `r t.desc.duration$min` to `r t.desc.duration$max` minutes, with a mean response time of `r round(t.desc.duration$mean,2)` minutes, SD = `r (round(t.desc.duration$sd,2))`.

```{r demo-cleanup}
rm(df, df.p, df.t)
```

# BLOCK 2 ANALYSIS

In the interest of space, we report analysis of 1 stimulus block (stimulus block == 2; pictured in the teaser image), rather than analysis of all six blocks.

## SAMPLE

```{r block2-sample}

#block 2 participant-level data 
df_b2_p <- df_participants %>% filter(Assigned.Block ==2)

#block 2 stimulus-level data 
df_b2 <- df_graphs %>% 
  filter(str_detect(STIMULUS,"B2")) %>% 
  mutate(MAKER_ID = fct_rev(MAKER_ID),
         MAKER_AGE = fct_rev(MAKER_AGE)) # reorder factors)

```

(n = `r nrow(df_b2_p)` ) survey respondents answered questions about the (4) stimuli in block 2, yielding (r = `r nrow(df_b2)`) observations.

## TODO MAKER Donuts

```{r b2_1_maker-chars}

#### DEFINE SET 
stimulus  = "B2-1"
df <- df_graphs %>% filter(STIMULUS == stimulus)

#### GENERATE GRAPHS

  #MAKER_ID-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "reds",
         main = paste0(stimulus, " MAKER ID")) + theme_minimal()


  # #MAKER_GENDER-DONUT
  # PieChart(MAKER_GENDER, data = df,
  #        fill = "blues",
  #        main = paste0(stimulus, " MAKER GENDER")) + theme_minimal()
  # 
  # 
  # #MAKER_AGE-DONUT
  # PieChart(MAKER_AGE, data = df,
  #        fill = "olives",
  #        main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "rusts",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "olives",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "greens",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "emeralds",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "turquoises",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "aquas",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-MAKER_ID
  PieChart(MAKER_ID, data = df,
         fill = "purples",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "magentas",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "violets",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
  
  #MAKER_AGE-DONUT
  PieChart(MAKER_ID, data = df,
         fill = "grays",
         main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
# "reds"	h	0
# "rusts"	h	30
# "browns"	h	60
# "olives"	h	90
# "greens"	h	120
# "emeralds"	h	150
# "turquoises"	h	180
# "aquas"	h	210
# "blues"	h	240
# "purples"	h	270
# "violets"	h	300
# "magentas"	h	330
# "grays"

```

## MAKER ID

Participants were asked: **Who do you think is most likely responsible for having this image created?** The response is stored as `MAKER_ID`

### Maker ID by Stimulus

```{r maker-id-stimulus}

#FILTER DATASET
df <- df_b2

## A
## MAKER IDENTIFICATION BY STIMULUS AND SAMPLE
## FACETED HORIZONTAL BAR CHART 
A <- ggplot( df, aes( x = (STIMULUS), fill = MAKER_ID)) +
  geom_bar(position = "stack") +
  facet_grid( Distribution ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER ID by Stimulus and SAMPLE",
        subtitle = "", x = "") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "1")) +   
  # scale_fill_viridis(discrete=TRUE, option="viridis", direction = -1) +
  # coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()
##############################

## B
## MAKER IDENTIFICATION BY STIMULUS
## GGSTATSPLOT
#hack for consistent ordering of ggstats bar plot
dx <- df %>% mutate(MAKER_ID = fct_rev(MAKER_ID))
B <- ggbarstats( data = dx, 
            x = MAKER_ID, y = STIMULUS,
            legend.title = "MAKER ID",
            results.subtitle = FALSE)  +
    scale_fill_manual(values = my_palettes(name="reds", direction = "1")) +   
    # scale_fill_viridis(discrete=TRUE, option="viridis", direction = -1) +
    labs( title = "MAKER ID BY STIMULUS ", subtitle = "", x = "")
##############################

## S
## MAKER ID REPEATED MEASURES
## SANKEY DIAGRAM
###FILTER FOR BLOCK 2 STIM AND RESHAPE FOR SANKEY
order <- df_graphs$MAKER_ID %>% levels   #list order of factor levels
ds <- df_graphs %>% 
  filter(str_detect(STIMULUS, "B2")) %>% 
  select(STIMULUS, MAKER_ID, PID, Distribution) %>% 
#pivot wider 
  pivot_wider(
    names_from = STIMULUS, 
    values_from = MAKER_ID
  ) %>%
#prep for geom_sankey
  make_long(`B2-1`,`B2-2`,`B2-3`,`B2-4`) %>% 
  mutate(
    match = ifelse(node==next_node, 1, 0.5), # try to highlight throughflows
    node = factor(node, levels = order),
    next_node = factor(next_node, levels = order)
  ) 
#SANKEY DIAGRAM
S <- ggplot(ds, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = node, 
               ))+
  geom_alluvial(width = 0.25, flow.alpha = 0.65, node.alpha = 1, node.color = "white") +
  geom_alluvial_text(aes( x = as.numeric(x),  label = after_stat(freq)),
          size = 3, color = "white", fontface = "bold", check_overlap = TRUE) +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1")) +   
  # scale_fill_viridis(discrete=TRUE, option="viridis", drop = FALSE, alpha = 1) +
  
  labs(title = "MAKER ID by STIMULUS", 
       x = "STIMULUS", y = "(count)", fill = "MAKER ID",
       caption = "") + 
  theme_minimal()
 ##############################

# DISPLAY GRAPHS
B 
S

# CLEANUP
rm(df, ds, dx, order)

```

*To explore whether variance in maker identifications is more likely a function of participant or stimulus , we visualize the `MAKER_ID` data via an alluvial diagram. Here we see that there are **no** stable identifications (ie. paths through each stimulus with the same category) indicating that no participants had a strong preference for a particular identification category. Rather, participants seem to be identifying the maker category as a function of some features of the stimuli, rather than a trait/state inference about makers of all stimuli in general.*

### Maker ID Confidence (distribution)

Participants were asked: **Please rate your confidence in this choice.** The response is stored as `MAKER_CONF` .

```{r maker-id-confidence}

## DESCRIBE MAKER CONFIDENCE
df <- df_b2 %>% 
  select(PID, STIMULUS, MAKER_ID, MAKER_CONF) 

desc.maker_conf <- psych::describe(df$MAKER_CONF)

## H 
## Distribution of MAKER_CONF 
## GGSTATS HISTOGRAM   
H <- gghistostats(df, x = MAKER_CONF, 
              test.value = 50,
              binwidth = 5,
              centrality.plotting = TRUE,
              centrality.type = "parametric",
              bin.args = list(color = "black", fill = "grey50", alpha = 0.2)
             ) + 
  labs(title = "Distribution of Maker ID Confidence (Block 2)",
       caption = paste0("test value = 50; sd = ", round(desc.maker_conf$sd,0))) + 
  theme_minimal()
##############################

# DISPLAY GRAPHS
H

# CLEANUP 
rm(df)
```

*Across the `r nrow(df_b2)` observations, the `r nrow(df_b2_p)` participants assigned to block 2 offered confidence values [on their maker identifications] ranging from`r desc.maker_conf$min` to `r desc.maker_conf$max` , with a mean of `r round(desc.maker_conf$mean,1)`. According to (one-sample) student's t-tests, the mean of the distribution is significantly difference from both reference values of 0 (indicating no confidence) and 50% (indicating partial confidence) and 100% (indicating certainty).*

### Maker ID Confidence (by Stimulus)

```{r, maker-id-confidence-individual, fig.width = 10}

#TEMP FILTER DATAFRAME
temp  <- df_graphs %>% 
  filter(str_detect(STIMULUS, "B2")) %>% 
  select(PID, STIMULUS, MAKER_ID, MAKER_CONF) %>% 
  group_by(PID) %>% 
  summarise(
         min = min(MAKER_CONF), 
         max = max(MAKER_CONF),
         range = max-min,
         low_var = ifelse(range < 20, TRUE, FALSE)
  )

#proportion of low variance participants 
p_lowvar <- round(nrow(temp %>% filter(low_var))/ nrow(temp)*100,0)

#FILTER DATAFRAME
df <- df_graphs %>% 
  filter(str_detect(STIMULUS, "B2")) %>% 
  select(PID, STIMULUS, MAKER_ID, MAKER_CONF) %>% 
  group_by(PID) %>% 
  mutate(
         min = min(MAKER_CONF), 
         max = max(MAKER_CONF),
         range = max-min,
         low_var = ifelse(range < 20, TRUE, FALSE))
  


## I
## MAKER CONFIDENCE (REPEATED MEASURES)
## WITHIN-SUBJECTS BOXPLOT 
I <- ggplot(df, aes(STIMULUS,MAKER_CONF)) + 
  geom_boxplot(width = 0.3)+ 
  stat_summary(fun.y="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
  stat_summary(fun.y="mean", colour="blue", geom="text", fontface = "bold", show_legend = TRUE, 
               vjust=+0.5, hjust = 1.5, aes( label=round(..y.., digits=0)))+
  geom_line(aes(group = PID, color = low_var), linetype=2, size=0.25) +
  scale_color_manual(values = my_palettes(name="blackred", type = "discrete", direction="1")) +
  geom_point(aes(group=PID), size= 2 ,alpha = 0.2) + 
  labs(
    title = "Confidence in Maker ID",
    y = "MAKER ID CONFIDENCE (%)",
    x = "Stimulus",
    subtitle = paste0("Scores range from ",desc.maker_conf$min, " to ", desc.maker_conf$max, " with ", p_lowvar,"% of ",nrow(temp)," participants (red) showing little variance in confidence across stimuli"),
    caption = "lines connect observations from the same participant 
    red indicates participants with less than 20 points range between confidence scores
    (i.e. participants whose confidence is stable, invariant across stimuli)") + 
   theme_minimal() + easy_remove_legend()
##############################


# MAKER_CONFIDENCE (VANILLA)
# ggplot(df, aes( x = (STIMULUS), y = MAKER_CONF)) + 
#   geom_boxplot(width = 0.5)+
#   geom_jitter(width = 0.10, alpha = 0.4) +
#   labs (title = "",
#         x = "", y = "MAKER ID CONFIDENCE") + 
#   theme_minimal() 

# DISPLAY GRAPHS
I

# CLEANUP
rm(df, temp)


```

_To explore whether variance in confidence in maker identification differs as a function of stimulus, or as a property of an individual subject, we visualize the distribution of confidence scores for each stimulus, where connecting lines indicate responses for a single participant. Participants with less than 20 point difference between their minimum and maximum confidence scores are indicated in red, ( `r`* `p_lowvar` of the `r nrow(df_b2_p)` participants.) Note that the participants with low variance in confidence scores are clustered near the high end of the confidence scale, with the exception of two subjects near 50%. The mean confidence score for each stimulus (blue) is greater than 50%, and no participants indicated consistently low confidence across all stimuli, indicating that in general, participants were able to respond thoughtfully to the maker identification question._

### Maker ID & Confidence (by Stimulus)

```{r maker-id-confidence-stimulus}

df <- df_b2

## MC
## MAKER_CONFIDENCE by IDENTIFICATION  
## POSITION DODGE BAR PLOT
MC <- ggplot(df, aes( x = (STIMULUS), y = MAKER_CONF, color = MAKER_ID)) + 
  geom_boxplot(position=position_dodge(0.8), width = 0.5)+
  geom_jitter(position=position_jitterdodge(dodge.width = 0.8, jitter.width= 0.2, ), alpha = 0.4) +
  scale_color_manual(values = my_palettes(name="reds", direction = "1")) +   
  # scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (title = "", 
        x = "", y = "Maker ID Confidence") + 
  theme_minimal() 
###################################################


# DISPLAY GRAPHS
 (p <- ( B/MC )  + plot_annotation(
   title = 'MAKER ID & CONFIDENCE by STIMULUS',
   subtitle = '',
   caption = ''))


```

```{r maker-id-cleanup}
rm(df, A, B, S, H, I, MC, p)
rm(desc.maker_conf)
```

*Inspecting Maker ID Confidence by Maker ID category, there does not appear to be any systematic relationship between the category of Maker a participant chooses for a stimulus, and their confidence in that choice (i.e. It is not the case that identifications of `MAKER = ORGANIZATION` , for example, are made with greater or less confidence than identifications of `MAKER = INDIVIDUAL`. Statistical tests of independence (between confidence and maker id) are ill-advised because the number of observations of each maker ID vary greatly between stimuli.*

**Taken together, this analysis of correspondence between `MAKER ID` and `MAKER ID CONFIDENCE` suggests that both the inference identifying the kind of maker (and the participant's confidence in that inference) are conditioned on some features of the *stimulus* rather than more stable state/trait(s) of the participant.**

## MAKER AGE

Participants were asked: Take a moment to **imagine the person(s) responsible for creating the image**. **What generation are they most likely from? `MAKER_AGE`**

### Maker AGE by Stimulus

```{r maker-age-stimulus}

#FILTER DATASET
df <- df_b2

## A
## MAKER AGE BY STIMULUS AND SAMPLE
## FACETED HORIZONTAL BAR CHART 
A <- ggplot( df, aes( x = (STIMULUS), fill = MAKER_AGE)) +
  geom_bar(position = "stack") +
  facet_grid( Distribution ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER AGE by Stimulus and SAMPLE",
        subtitle = "", x = "") +
  scale_fill_manual(values = my_palettes(name="lightblues", direction = "1")) +   
    #scale_fill_viridis(discrete=TRUE, option="viridis", direction = -1) +
  # coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()
##############################


## B
## MAKER AGE BY STIMULUS
## GGSTATSPLOT
#hack for consistent ordering of ggstats bar plot
dx <- df %>% mutate(MAKER_AGE = fct_rev(MAKER_AGE))
B <- ggbarstats( data = dx, 
            x = MAKER_AGE, y = STIMULUS,
            legend.title = "MAKER AGE",
            results.subtitle = FALSE)  +
    scale_fill_manual(values = my_palettes(name="lightblues", direction = "1")) +   
    # scale_fill_viridis(discrete=TRUE, option="viridis", direction = -1) +
    labs( title = "MAKER AGE BY STIMULUS ", subtitle = "", x = "")
##############################

## S
## MAKER AGE REPEATED MEASURES
## SANKEY DIAGRAM
###FILTER FOR BLOCK 2 STIM AND RESHAPE FOR SANKEY
order <- df_graphs$MAKER_AGE %>% levels   #list order of factor levels
ds <- df_graphs %>% 
  filter(str_detect(STIMULUS, "B2")) %>% 
  select(STIMULUS, MAKER_AGE, PID, Distribution) %>% 
#pivot wider 
  pivot_wider(
    names_from = STIMULUS, 
    values_from = MAKER_AGE
  ) %>%
#prep for geom_sankey
  make_long(`B2-1`,`B2-2`,`B2-3`,`B2-4`) %>% 
  mutate(
    match = ifelse(node==next_node, 1, 0.5), # try to highlight throughflows
    node = factor(node, levels = order),
    next_node = factor(next_node, levels = order)
  ) 
#SANKEY DIAGRAM
S <- ggplot(ds, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = node, 
               ))+
  geom_alluvial(width = 0.25, flow.alpha = 0.65, node.alpha = 1, node.color="white") +
  geom_alluvial_text(aes( x = as.numeric(x),  label = after_stat(freq)),
          size = 3, color = "white", fontface = "bold", check_overlap = TRUE) +
  scale_fill_manual(values = my_palettes(name="lightblues", direction = "-1")) +   
  # scale_fill_viridis(discrete=TRUE, option="viridis", drop = FALSE, alpha = 1) +
  
  labs(title = "MAKER AGE by STIMULUS", 
       x = "STIMULUS", y = "(count)", fill = "MAKER AGE",
       caption = "") + 
  theme_minimal()
 ##############################

# DISPLAY GRAPHS
B 
S

# CLEANUP
rm(df, ds, dx, order)

```
### Maker AGE Confidence (distribution)

Participants were asked: **Please rate your confidence in this choice.** The response is stored as `AGE_CONF` .

```{r maker-age-confidence}

## DESCRIBE MAKER AGE CONFIDENCE
df <- df_b2 %>% 
  select(PID, STIMULUS, MAKER_AGE, AGE_CONF) 

desc.age_conf <- psych::describe(df$AGE_CONF)

## H 
## Distribution of AGE_CONF 
## GGSTATS HISTOGRAM   
H <- gghistostats(df, x = AGE_CONF, 
              test.value = 50,
              binwidth = 5,
              centrality.plotting = TRUE,
              centrality.type = "parametric",
              bin.args = list(color = "black", fill = "grey50", alpha = 0.2)
             ) + 
  labs(title = "Distribution of Maker AGE Confidence (Block 2)",
       caption = paste0("test value = 50; sd = ", round(desc.age_conf$sd,0))) + 
  theme_minimal()
##############################

# DISPLAY GRAPHS
H

# CLEANUP 
rm(df)
```

*Across the `r nrow(df_b2)` observations, the `r nrow(df_b2_p)` participants assigned to block 2 offered confidence values [on their maker age attribution] ranging from`r desc.age_conf$min` to `r desc.age_conf$max` , with a mean of `r round(desc.age_conf$mean,1)`. According to (one-sample) student's t-tests, the mean of the distribution is significantly difference from both reference values of 0 (indicating no confidence) and 50% (indicating partial confidence) and 100% (indicating certainty).*

### Maker AGE Confidence (by Stimulus)

```{r, maker-age-confidence-individual, fig.width = 10}

#TEMP FILTER DATAFRAME
temp  <- df_graphs %>% 
  filter(str_detect(STIMULUS, "B2")) %>% 
  select(PID, STIMULUS, MAKER_AGE, AGE_CONF) %>% 
  group_by(PID) %>% 
  summarise(
         min = min(AGE_CONF), 
         max = max(AGE_CONF),
         range = max-min,
         low_var = ifelse(range < 20, TRUE, FALSE)
  )

#proportion of low variance participants 
p_lowvar <- round(nrow(temp %>% filter(low_var))/ nrow(temp)*100,0)

#FILTER DATAFRAME
df <- df_graphs %>% 
  filter(str_detect(STIMULUS, "B2")) %>% 
  select(PID, STIMULUS, MAKER_AGE, AGE_CONF) %>% 
  group_by(PID) %>% 
  mutate(
         min = min(AGE_CONF), 
         max = max(AGE_CONF),
         range = max-min,
         low_var = ifelse(range < 20, TRUE, FALSE))
  


## I
## MAKER CONFIDENCE (REPEATED MEASURES)
## WITHIN-SUBJECTS BOXPLOT 
I <- ggplot(df, aes(x = STIMULUS, y = AGE_CONF)) + 
  geom_boxplot(width = 0.2) + 
  stat_summary(fun.y="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
  stat_summary(fun.y="mean", colour="blue", geom="text", fontface = "bold", show_legend = TRUE, 
               vjust=+0.5, hjust = 1.5, aes( label=round(..y.., digits=0)))+
  geom_line(aes(group = PID, color = low_var), linetype=2, size=0.25) +
  scale_color_manual(values = my_palettes(name="blackred", type = "discrete", direction="1")) +
  geom_point(aes(group=PID), size= 2 ,alpha = 0.2) +
  labs(
    title = "Confidence in Maker AGE",
    y = "MAKER AGE CONFIDENCE (%)",
    x = "Stimulus",
    subtitle = paste0("Scores range from ",desc.age_conf$min, " to ", desc.age_conf$max, " with ", p_lowvar,"% of ",nrow(temp)," participants (red) showing little variance in confidence across stimuli"),
    caption = "lines connect observations from the same participant 
    red indicates participants with less than 20 points range between confidence scores
    (i.e. participants whose confidence is stable, invariant across stimuli)") + 
   theme_minimal() + easy_remove_legend()
##############################



# MAKER_AGE CONFIDENCE (VANILLA)
# ggplot(df, aes( x = (STIMULUS), y = AGE_CONF)) + 
#   geom_boxplot(width = 0.5)+
#   geom_jitter(width = 0.10, alpha = 0.4) +
#   labs (title = "",
#         x = "", y = "MAKER AGE CONFIDENCE") + 
#   theme_minimal() 

# DISPLAY GRAPHS
I

# CLEANUP
rm(df, temp)


```

To explore whether variance in confidence in maker age differs as a function of stimulus, or as a property of an individual subject, we visualize the distribution of confidence scores for each stimulus, where connecting lines indicate responses for a single participant. Participants with less than 20 point difference between their minimum and maximum confidence scores are indicated in red, ( `r`* `p_lowvar` of the `r nrow(df_b2_p)` participants.) Note that the participants with low variance in confidence scores are clustered near the high end of the confidence scale, with the exception of (2) participants who have low variance scores clustered around 50% and (2) participants clustered around 25%. The mean confidence score for each stimulus (blue) is greater than 50%, and no participants indicated consistently low confidence across all stimuli, indicating that in general, participants were able to respond thoughtfully to the maker age question.


### Maker AGE & Confidence (by Stimulus)

```{r maker-age-confidence-stimulus}

df <- df_b2

## MC
## MAKER AGE CONFIDENCE by IDENTIFICATION  
## POSITION DODGE BAR PLOT
MC <- ggplot(df, aes( x = (STIMULUS), y = AGE_CONF, color = MAKER_AGE)) + 
  geom_boxplot(position=position_dodge(0.8), width = 0.5)+
  geom_jitter(position=position_jitterdodge(dodge.width = 0.8, jitter.width= 0.2, ), alpha = 0.4) +
  scale_color_manual(values = my_palettes(name="lightblues", direction = "1")) +   
  # scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (title = "", 
        x = "", y = "Maker Age Confidence") + 
  theme_minimal() 
###################################################


# DISPLAY GRAPHS
 (p <- ( B/MC )  + plot_annotation(
   title = 'MAKER AGE & CONFIDENCE by STIMULUS',
   subtitle = '',
   caption = ''))


```

*Inspecting Maker AGE Confidence by Maker AGE category, there does not appear to be any systematic relationship between the category of Maker AGE a participant chooses for a stimulus, and their confidence in that choice (i.e. It is not the case that identifications of `MAKER(AGE) = MILLENIAL` , for example, are made with greater or less confidence than identifications of `MAKER(AGE) = BOOMER`. Statistical tests of independence (between confidence and maker age) are ill-advised because the number of observations of each maker age vary greatly between stimuli.*

**Taken together, this analysis of correspondence between `MAKER AGE` and `MAKER AGE CONFIDENCE` suggests that both the inference identifying the age generation of maker (and the participant's confidence in that inference) are conditioned on some features of the *stimulus* rather than more stable state/trait(s) of the participant.**

```{r maker-age-cleanup}
rm(df, A, B, S, H, I, MC, p)
rm(desc.age_conf)
```


## MAKER GENDER

### Maker Gender by Stimulus

```{r maker-gender-stimulus}

#FILTER DATASET
df <- df_graphs %>% filter(Assigned.Block == 2)

#MAKER GENDER BY STIMULUS AND SAMPLE
## FACETED HORIZONTAL BAR CHART 
ggplot( df, aes( x = (STIMULUS), fill = fct_rev(MAKER_GENDER))) +
  geom_bar(position = "stack") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  labs( title = "MAKER GENDER by Stimulus",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()


#MAKER GENDER  BY STIMULUS
## HORIZONTAL BAR CHART 
ggplot( df, aes( x = fct_rev(STIMULUS), fill = fct_rev(MAKER_GENDER))) +
  geom_bar(position = "stack") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER GENDER by Stimulus",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()

#MAKER GENDER  BY STIMULUS
## GGSTATSPLOT
ggbarstats( data = df, x = "MAKER_GENDER", y = "STIMULUS",
                 legend.title = "MAKER GENDER")  +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
      labs( title = "MAKER GENDER BY STIMULUS ", subtitle = "", x = "") 



```

### Maker Gender & Confidence by Stimulus

```{r maker-gender-confidence-stimulus, message=FALSE, warning=FALSE, fig.width=10}

#FILTER DATAFRAME
df <- df_graphs %>% filter(Assigned.Block == 2)

######### MAKER GENDER AND CONFIDENCE ##############
# MAKER_GENDER by STIMULUS
a <- ggplot (df, aes( x = (STIMULUS), fill = fct_rev(MAKER_GENDER))) + 
  geom_bar(position = "fill", width = 0.8) +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# GENDER_CONFIDENCE by STIMULUS
b <- ggplot(df, aes( x = (STIMULUS), y = GENDER_CONF, color = fct_rev(MAKER_GENDER))) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_paletteer_d("awtools::a_palette", direction = 1)+
  labs (x = "STIMULUS") + 
  theme_minimal() 

# GENDER_CONFIDENCE 
c <- ggplot(df, aes( x = (STIMULUS), y = GENDER_CONF)) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(width = 0.10, alpha = 0.4) +
  labs (title = "") +
  labs (x = "") + 
  theme_minimal() 


(p <- (a / b / c )  + plot_annotation(
  title = 'MAKER GENDER & CONFIDENCE by Stimulus',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,c,p)
```

### Maker Gender by PARTICIPANT GENDER

```{r maker-gender-X-participant}

#FILTER DATAFRAME
df <- df_graphs %>% filter(Assigned.Block == 2)

#MAKER GENDER by PARTICIPANT GENDER
ggplot( df, aes( x = (STIMULUS), fill = fct_rev(MAKER_GENDER))) +
  geom_bar(position = "stack") +
  facet_grid( D_gender_collapsed ~ Distribution , scales = "free", space = "free") + 
  labs( title = "MAKER GENDER by PARTICIPANT GENDER and Stimulus",
        subtitle = "", x = "", fill = "MAKER GENDER") +
  # scale_fill_viridis(discrete=TRUE, option="viridis") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  # coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()



```

## TOOL CHOICE

### Tool ID by Stimulus

```{r toolid-stimulus}

#FILTER DATASET
df <- df_tools %>% filter( str_detect(STIMULUS, "B2"))

#TOOL ID BY STIMULUS AND SAMPLE
## FACETED HORIZONTAL BAR CHART
ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = fct_rev(STIMULUS) )) +
  geom_bar(position = "stack") +
  coord_flip() + 
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  # scale_y_continuous(labels = scales::percent) + 

  labs( title = "TOOL ID by Stimulus (grouped by Category)",
        subtitle = "", x = "") +
  easy_add_legend_title("TOOL_ID") +
  theme_minimal() 


#TOOL ID  BY STIMULUS
## HORIZONTAL BAR CHART 
ggplot( df, aes( x = fct_rev(STIMULUS), fill = fct_rev(TOOL_ID))) +
  geom_bar(position = "stack") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  labs( title = "TOOL ID by Stimulus",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()

#TOOL ID GENDER  BY STIMULUS
## GGSTATSPLOT
ggbarstats( data = df, x = "TOOL_ID", y = "STIMULUS",
                 legend.title = "TOOL ID")  +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
      labs( title = "TOOL ID BY STIMULUS ", subtitle = "", x = "") 



```

### Tool ID & Confidence by Stimulus

```{r toolid-confidence-stimulus, message=FALSE, warning=FALSE, fig.width = 10}

# FILTER DATAFRAME
df <- df_tools %>% filter( str_detect(STIMULUS, "B2"))

######### TOOL ID AND CONFIDENCE ##############
a <- ggplot (df, aes( x = (STIMULUS), fill = fct_rev(TOOL_ID))) + 
  geom_bar(position = "fill", width = 0.8) +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1) +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") +
  easy_add_legend_title("TOOL ID")+
  theme_minimal() 

# TOOL_CONFIDENCE by STIMULUS
b <- ggplot(df, aes( x = (STIMULUS), y = TOOL_CONF, color = fct_rev(TOOL_ID))) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.6)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_paletteer_d("awtools::a_palette", direction = 1) +
  labs (x = "STIMULUS") + 
  easy_add_legend_title("TOOL ID")+
  theme_minimal() 

# TOOL_CONFIDENCE 
c <- ggplot(df, aes( x = (STIMULUS), y = TOOL_CONF)) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(width = 0.10, alpha = 0.4) +
  labs (title = "") +
  labs (x = "") + 
  theme_minimal() 

(p <- (a / b / c )  + plot_annotation(
  title = 'TOOL ID & CONFIDENCE by Stimulus',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,c,p)
```

## ENCOUNTER CHOICE

### Encounter Choice by Stimulus

```{r encounter-stimulus}

#FILTER DATASET
df <- df_graphs %>% filter(Assigned.Block == 2)

# ENCOUNTER CHOICE BY STIMULUS AND SAMPLE
ggplot( df, aes( x = (STIMULUS), fill = ENCOUNTER)) +
  geom_bar(position = "stack") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  labs( title = "MAKER ENCOUNTER by Stimulus",
        subtitle = "", x = "") +
  scale_fill_brewer(palette = "Dark2") + 
  coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()

#ENCOUNTER CHOICE
## HORIZONTAL BAR CHART 
ggplot( df, aes( x = fct_rev(STIMULUS), fill = (ENCOUNTER))) +
  geom_bar(position = "stack") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  labs( title = "ENCOUNTER CHOICE by Stimulus",
        subtitle = "", x = "") +
  scale_fill_brewer(palette = "Dark2") + 
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()

#ENCOUNTER CHOICE 
## GGSTATSPLOT
ggbarstats( data = df, x = "ENCOUNTER", y = "STIMULUS",
                 legend.title = "ENCOUNTER")  +
  scale_fill_brewer(palette = "Dark2") + 
      labs( title = "ENCOUNTER BY STIMULUS ", subtitle = "", x = "") 


```

## ACTION CHOICE

### Actions Choice by Stimulus

```{r actions-stimulus}

#FILTER DATASET
df <- df_actions %>% filter( str_detect(STIMULUS, "B2"))

# ACTION CHOICE BY STIMULUS AND SAMPLE
ggplot(data = df, aes( fill = CHART_ACTION, x = fct_rev(STIMULUS) )) +
  geom_bar(position = "stack") +
  coord_flip() + 
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  # scale_y_continuous(labels = scales::percent) + 

  labs( title = "Chart Action by Stimulus",
        subtitle = "", x = "") +
  easy_add_legend_title("ACTION") +
  theme_minimal() 



# ACTION CHOICE BY STIMULUS
ggplot(data = df, aes( fill = CHART_ACTION, x = fct_rev(STIMULUS) )) +
  geom_bar(position = "stack") +
  coord_flip() + 
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  # scale_y_continuous(labels = scales::percent) + 

  labs( title = "Chart Action by Stimulus",
        subtitle = "", x = "") +
  easy_add_legend_title("ACTION") +
  theme_minimal() 

#ACTION CHOICE CHOICE BY STIMULUS
## GGSTATSPLOT
ggbarstats( data = df, x = "CHART_ACTION", y = "STIMULUS",
                 legend.title = "CHART ACTION")  +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1) +
      labs( title = "CHART ACTION BY STIMULUS ", subtitle = "", x = "") 




```

## TODO PICK UP HERE

## TODO ALSO GROUP VS. INDIVIDUAL DIFFERENCES

ie. mixed model, but also look at stability of individual choice across stimuli maybe treat individual as fixed factor and look at amount of variance explained?

## TODO CONFIDENCE

revisit ggwithin and grouped within, which require a continuous outcome

```{r}
# ggwithinstats(
#   data = df %>% filter(STIMULUS %in% c("B2-1","B2-2")),
#   x = STIMULUS,
#   y = MAKER_ID,
#   type = "robust", ## type of statistical test
#   xlab = "MAKER_ID", ## label for the x-axis
#   ylab = "MAKER_CONF", ## label for the y-axis
#   # package = "yarrr", ## package from which color palette is to be taken
#   # palette = "info2", ## choosing a different color palette
#   title = "MAKER ID BY MAKER_CONF"
# ) 
```

## CHART BEAUTY

### Chart Beauty by Stimulus and Category

```{r}

df <- df_graphs

qacBase::qstats(df, CHART_BEAUTY, STIMULUS) %>% arrange(mean)

qacBase::qstats(df, CHART_BEAUTY, STIMULUS_CATEGORY) %>% arrange(mean)

# 
# 
# ggplot(df, aes(x = CHART_BEAUTY)) + 
#   geom_histogram(bins = 20) +
#   facet_grid(BLOCK ~ STIMULUS_CATEGORY, scales = "free", space = "free", drop=TRUE) + 
#   theme_minimal()
# 
# 
# ggplot(df, aes(x = CHART_BEAUTY)) + 
#   geom_histogram(bins = 20) +
#   facet_grid( ~ fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free", drop=TRUE) + 
#   theme_minimal()
# 



##ggstatsplot BY CATEGORY
grouped_gghistostats(
  data = df_graphs %>% filter(STIMULUS != "B0-0"),
  x = CHART_BEAUTY, ## same outcome variable
  grouping.var = STIMULUS, ## grouping variable males = 1, females = 2
  type = "robust", ## robust test: one-sample percentile bootstrap
  test.value = 50, ## test value against which sample mean is to be compared
  centrality.line.args = list(color = "#D55E00", linetype = "dashed"),
  # ggtheme = ggthemes::theme_stata(), ## changing default theme
  ## turn off ggstatsplot theme layer
  ## arguments relevant for combine_plots
  annotation.args = list(
    title = "DISTRIBUTION of Chart Beauty by Cateogry",
    caption = ""
  ),
  plotgrid.args = list(nrow = 6)
)
 

#B0-0 
gghistostats(
  data = df_graphs %>% filter(STIMULUS == "B0-0"), ## data from which variable is to be taken
  x = CHART_BEAUTY, ## numeric variable
  xlab = "CHART BEAUTY", ## x-axis label
  title = "B0-0 MILLENIAL PINK PLANTS", ## title for the plot
  test.value = 50, ## test value
  caption = ""
)  


```

### Chart Trust by Stimulus and Category

```{r}

df <- df_graphs

qacBase::qstats(df, CHART_TRUST, STIMULUS) %>% arrange(mean)

qacBase::qstats(df, CHART_TRUST, STIMULUS_CATEGORY) %>% arrange(mean)


##ggstatsplot BY CATEGORY
grouped_gghistostats(
  data = df_graphs %>% filter(STIMULUS != "B0-0"),
  x = CHART_TRUST, ## same outcome variable
  grouping.var = STIMULUS, ## grouping variable males = 1, females = 2
  type = "robust", ## robust test: one-sample percentile bootstrap
  test.value = 50, ## test value against which sample mean is to be compared
  centrality.line.args = list(color = "#D55E00", linetype = "dashed"),
  # ggtheme = ggthemes::theme_stata(), ## changing default theme
  ## turn off ggstatsplot theme layer
  ## arguments relevant for combine_plots
  annotation.args = list(
    title = "DISTRIBUTION of Chart TRUST by Cateogry",
    caption = ""
  ),
  plotgrid.args = list(nrow = 6)
)
 

#B0-0 
gghistostats(
  data = df_graphs %>% filter(STIMULUS == "B0-0"), ## data from which variable is to be taken
  x = CHART_TRUST, ## numeric variable
  xlab = "CHART TRUST", ## x-axis label
  title = "B0-0 MILLENIAL PINK PLANTS", ## title for the plot
  test.value = 50, ## test value
  caption = ""
)  


```

# FISH

### bivariate combinations

```{r bivariate-demos}

if(graph_render == TRUE){





### EXPLORE ALL QUESTIONS AS EXPLAINED BY DEMOGRAPHICS
df <- df_graphs 
predictors = df %>% select(Distribution, STIMULUS_CATEGORY,
                D_gender_collapsed, D_age, D_education, D_income,
                D_politicalParty, D_politicsFiscal, D_politicsSocial) %>% colnames()

questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)

i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by demographic variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_demographics", filename =paste0(q,"_demo_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END




### EXPLORE ALL QUESTIONS AS EXPLAINED BY SD VARS
df <- df_graphs 
predictors = c(ref_sd_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by SD variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_SD", filename =paste0(q,"_sd_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g )
#####################################################END



### EXPLORE ALL QUESTIONS AS EXPLAINED BY CONF VARS
df <- df_graphs 
predictors = c(ref_conf_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by CONF variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_CONF", filename =paste0(q,"_conf_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END


### EXPLORE ALL QUESTIONS AS EXPLAINED BY CAT VARS
df <- df_graphs 
predictors = c(ref_cat_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by CATEGORICAL variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_CAT", filename =paste0(q,"_cat_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END


}

```

### DEMO-GENDER \> MAKER-GENDER?

```{r}

df <- df_graphs %>% select(PID, D_gender, MAKER_GENDER, GENDER_CONF, STIMULUS, STIMULUS_CATEGORY, BLOCK)


## ALL STIMULI
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  scale_fill_viridis(discrete=TRUE, option="viridis") + 
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
    subtitle = "(across all stimuli)",
    caption = "ARF: Attribution of maker gender does not *appear* to differ by participant \n gender identity; Each personal gender has attributions to each maker gender"
  )



## CATEGORY
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  facet_grid(.~fct_rev(STIMULUS_CATEGORY))+
  scale_fill_viridis(discrete=TRUE, option="viridis") + 
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
    subtitle = "(by stimulus category)",
    caption = "ARF: Note that across categories most attributions are male, 
    EXCEPT F (millenial pink plants) which is largely female
    HOWEVER relative proportion by participant gender looks consistent" 
  )


## STIMULUS
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  scale_fill_viridis(discrete=TRUE, option="viridis")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
    subtitle = "(by stimulus)",
    caption = "ARF: Again, relative proportions look consistent by participant gender"
  )

## B00
df <- df %>% filter(STIMULUS=="B0-0")
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  scale_fill_viridis(discrete=TRUE, option="viridis")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
   subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = "ARF: Most attributions are FEMALE but relative proportion of 
    participant gender appears comparable; difficult to detect due to low number
    of non-binary, prefer not to say, prefer to self-describe"
  )

```

### DEMO-GENDER_Q_all_stimuli

```{r GENDER-Q-FOR-ALL-STIMULI}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){

####################CREATE SD PLOTS FOR EACH QUESTION#####################

#set questions to be graphed 
questions <- ref_sd_questions  #created in wrangling block
box_s_question <- list()
rain_s_question <- list()
i = 0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  df <- df_sd_questions_wide %>% filter(QUESTION == q)

  #subset data cols 
  c <- df %>% select( all_of(ref_stimuli)) ##TODO IF NOT WORK ref_stim_id
  # plot_sd = function (data, column, type, facet, facet_by,  boxplot) {

  plots <- as.list(lapply(colnames(c), plot_sd, data = df, type = "Q", facet=TRUE, facet_by= "D_gender_collapsed", boxplot=TRUE)) 
  
  #aggregate stimulus plots into block for question
  x <- plots[[1]] / plots[[2]]  / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
        plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] /  plots[[12]] / plots[[13]] / plots[[14]] / 
        plots[[15]] /plots[[16]] /plots[[17]] /plots[[18]] /  plots[[19]] / plots[[20]] / plots[[21]] /
        plots[[22]] /plots[[23]] /plots[[24]] /plots[[25]] + 
      plot_annotation(
        title = title,
       subtitle =""
      )
  box_s_question[[i]] <- x 
  ggsave(plot = x, path="figs/GENDER_by_q_for_all_stimuli", filename =paste0(q,"_box.png"), units = c("in"), width = 10, height = 26)

  
  
  
  ############# RAINCLOUD
  # setup dataframe 
  title <- paste(q)
  df <- df_sd_questions_long %>% filter(QUESTION ==q)
    #select(1:6, QUESTION, all_of(s)) %>% filter(!is.na(s)) %>%  mutate(value = get(s))
  left <- ref_labels[q,]$left
  right <- ref_labels[q,]$right

  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(STIMULUS) , x = value, fill = fct_rev(STIMULUS))) +
      stat_slab(normalize="groups", scale = 0.7) +
      stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
    facet_grid(~D_gender_collapsed)+
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  rain_s_question[[i]] <- x
  ggsave(plot = x, path="figs/GENDER_by_q_for_all_stimuli", filename =paste0(q,"_rain.png"), units = c("in"), width = 10, height = 14  )
  

  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_s_question$MAKER_DESIGN
#ALSO plots_s_question$MAKER_DESIGN[[1]]
names(box_s_question) <- questions
names(rain_s_question) <- questions
rm(x, i, plots, left, right)

#############################################################################

}
```

### DEMO-GENDER-MILLENIAL-PLANTS-SDS

```{r GENDER-PLANTS ALL-Q-BY-STIMULUS}


#################### ALL QUESTIONS AT B00 #####################
# ONE PLOT FOR EACH STIMULUS WITH ALL QUESTIONS

#set stimuli to be graphed 
# stimuli <- ref_stimuli #created in wrangling block ##TODO IF NOT WORK ref_stim_id
stimuli <- c("B0-0")

box_stimuli <- list()
rain_stimuli <- list()
i = 0
for (s in stimuli){
  i = i+1
  
  # setup dataframe 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME) ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)
  df <- df_graphs %>% filter(STIMULUS== s)

  #subset data cols 
  cols <- df %>% select( all_of(ref_sd_questions))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type ="S", facet = TRUE, facet_by="D_gender_collapsed", boxplot=TRUE))

  #aggregate q plots into one for stimulus 
  x <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
   plot_annotation(
     title = title,
     subtitle =""
   )
  
  box_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/_millenial-pink-plants", filename =paste0(s,"_box.png"), units = c("in"), width = 10, height = 14  )
  
  
  #### RAINCLOUD PLOT
  # setup dataframe 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME) ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)
  df <- df_sd_questions_wide %>% select(1:6, D_gender_collapsed, QUESTION, all_of(s)) %>% filter(!is.na(s)) %>%  mutate(value = get(s))


  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(QUESTION), x = value, fill = fct_rev(QUESTION))) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  facet_grid(~ D_gender_collapsed)+
  guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    y = guide_axis_manual(labels = rev(ref_labels$left)),
    y.sec = guide_axis_manual(labels = rev(ref_labels$right))
  ) + 
  labs (title = title) +
  theme_minimal() 
   
  
  rain_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/_millenial-pink-plants", filename =paste0(s,"_rain.png"), units = c("in"), width = 10, height = 14  )
  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_stimulus$`B1-1`
#ALSO plots_stimulus$`B1-1`[[1]]
names(box_stimuli) <- stimuli
names(rain_stimuli) <- stimuli
rm(x, i, plots)

#############################################################################
 

```

### DEMO-GENDER-MILLENIAL-PLANTS-CATS

```{r}


#filter dataframe
df <- df_graphs %>% select(PID, D_gender_collapsed, MAKER_GENDER, GENDER_CONF, MAKER_AGE, AGE_CONF, MAKER_ID, MAKER_CONF, STIMULUS, STIMULUS_CATEGORY, BLOCK) %>% filter(STIMULUS=="B0-0")


##ID
p <- ggplot(df, aes(x = MAKER_ID, fill= D_gender_collapsed)) + 
  geom_bar(position = "fill")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER ID by participant gender (proportion)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

s <- ggplot(df, aes(x = MAKER_ID, fill= D_gender_collapsed)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER ID by participant gender (true count)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

(p/s)

##AGE
p <- ggplot(df, aes(x = MAKER_AGE, fill= D_gender_collapsed)) + 
  geom_bar(position = "fill")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER AGE by participant gender (proportion)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

s <- ggplot(df, aes(x = MAKER_AGE, fill= D_gender_collapsed)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER AGE by participant gender (true count)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

(p/s)


##GENDER
p <- ggplot(df, aes(x = MAKER_GENDER, fill= D_gender_collapsed)) + 
  geom_bar(position = "fill")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender (proportion)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = "ARF: Proportion of OTHER looks high!"
  )

s <- ggplot(df, aes(x = MAKER_GENDER, fill= D_gender_collapsed)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender (true count)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = "ARF: But count of other is very low :("
  )

(p/s)


##MAKER CONFIDENCE BY GENDER 
ggplot(df, aes(x=D_gender_collapsed, y = MAKER_CONF, color = D_gender_collapsed))+
  geom_jitter(width=0.2, height = 0) + 
  labs (title = "CONFIDENCE in MAKER_ID by Participant Gender",
        x = "participant gender")+
  theme_minimal() +
  easy_remove_legend()


##AGE CONFIDENCE BY GENDER 
ggplot(df, aes(x=D_gender_collapsed, y = AGE_CONF, color = D_gender_collapsed))+
  geom_jitter(width=0.2, height = 0) + 
  labs (title = "CONFIDENCE in MAKER_AGE by Participant Gender",
        x = "participant gender")+
  theme_minimal() +
  easy_remove_legend()


##GENDER CONFIDENCE BY GENDER 
ggplot(df, aes(x=D_gender_collapsed, y = GENDER_CONF, color = D_gender_collapsed))+
  geom_jitter(width=0.2, height = 0) + 
  labs (title = "CONFIDENCE in MAKER_GENDER by Participant Gender",
        x = "participant gender")+
  theme_minimal() +
  easy_remove_legend()

```

# B1-3 AGGRESSIVE AMERICAN FLAG

## demographics

```{r b13-demographics}

n = df_participants %>% filter(Assigned.Block == 1) %>% nrow()
print(paste(n, "participants were assigned to block 1 where they saw the 'aggressive american flag stimulus"))
```

## bar charts

```{r OMINOUS-FLAG}


df <- df_graphs %>% filter(STIMULUS == "B1-3")

#MAKER IDENTIFICATION
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) +
  geom_bar(position = "fill") +
  labs( title = "MAKER ID [B1-C]) ",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  easy_add_legend_title("") +
  theme_minimal()


#MAKER AGE
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
  geom_bar(position = "fill") +
  labs( title = "MAKER AGE [B1-C] ",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("ggsci::light_uchicago", direction = -1)+
  theme_minimal()



#MAKER GENDER
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_GENDER)) +
  geom_bar(position = "fill") +
  # facet_grid(D_gender_collapsed ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER GENDER [B1-C] ",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("ggthemes::excel_Celestial", direction = 1)+
  theme_minimal()



df <- df_tools %>% filter (STIMULUS =="B1-3")

# TOOL CHOICE BY STIMULUS
ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = fct_rev(STIMULUS) )) +
  geom_bar(position = "fill") +
  # coord_flip() + 
  # facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 
  labs( title = "TOOL ID by Stimulus (grouped by Category)",
        subtitle = "", x = "") +
  easy_add_legend_title("TOOL_ID") +
  theme_minimal() 

```

```{r angry-flag-age-by-sample}

df <- df_graphs %>% filter(STIMULUS == "B1-3")

#MAKER AGE
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
  geom_bar(position = "fill") +
  facet_grid(.~Distribution) + 
  labs( title = "MAKER AGE [B1-C] ",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("ggsci::light_uchicago", direction = -1)+
  theme_minimal()


```

## pie charts

```{r OMINOUS-FLAG}


# df <- df_graphs %>% filter(STIMULUS == "B1-3")
# 
# #MAKER IDENTIFICATION
# ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) +
#   geom_bar(position = "fill") +
#   labs( title = "MAKER ID [B1-C]) ",
#         subtitle = "", x = "") +
#   scale_fill_viridis(discrete=TRUE, option="viridis") +
#   easy_add_legend_title("") +
#   theme_minimal()
# 
# 
# #MAKER AGE
# ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
#   geom_bar(position = "fill") +
#   labs( title = "MAKER AGE [B1-C] ",
#         subtitle = "", x = "") +
#   scale_fill_paletteer_d("ggsci::light_uchicago", direction = -1)+
#   theme_minimal()
# 
# 
# 
# #MAKER GENDER
# ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_GENDER)) +
#   geom_bar(position = "fill") +
#   # facet_grid(D_gender_collapsed ~ ., scales = "free", space = "free") + 
#   labs( title = "MAKER GENDER [B1-C] ",
#         subtitle = "", x = "") +
#   scale_fill_paletteer_d("ggthemes::excel_Celestial", direction = 1)+
#   theme_minimal()
# 
# 
# 
# df <- df_tools %>% filter (STIMULUS =="B1-3")
# 
# # TOOL CHOICE BY STIMULUS
# ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = fct_rev(STIMULUS) )) +
#   geom_bar(position = "fill") +
#   # coord_flip() + 
#   # facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
#   scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
#   scale_y_continuous(labels = scales::percent) + 
#   labs( title = "TOOL ID by Stimulus (grouped by Category)",
#         subtitle = "", x = "") +
#   easy_add_legend_title("TOOL_ID") +
#   theme_minimal() 
# 
# 
# 
# 
# 
# 
# 
# 
# #### GG_LOT + GREPL
# library(ggrepel)
# df <- df_graphs %>% filter(STIMULUS == "B1-3") %>% select(STIMULUS, MAKER_ID) %>% 
#   group_by(MAKER_ID) %>% 
#   summarize(
#     value = n()
#   )
# df2 <- df %>% 
#   mutate(csum = rev(cumsum(rev(value))), 
#          pos = value/2 + lead(csum, 1),
#          pos = if_else(is.na(pos), value/2, pos))
# 
# ggplot(df, aes(x = "" , y = value, fill = fct_inorder(MAKER_ID))) +
#   geom_col(width = 1, color = 1) +
#   coord_polar(theta = "y") +
#   scale_fill_brewer(palette = "Pastel1") +
#   geom_label_repel(data = df2,
#                    aes(y = pos, label = paste0(value, "%")),
#                    size = 4.5, nudge_x = 1, show.legend = FALSE) +
#   guides(fill = guide_legend(title = "Group")) +
#   theme_void()


##GGPIESTATS MAKER_GENDER
df <- df_graphs %>% filter (STIMULUS =="B1-3") %>% 
  mutate(
    MAKER_GENDER = fct_rev(MAKER_GENDER)
  )
ggpiestats(data = df, x=MAKER_GENDER )

##GGPIESTATS MAKER_AGE
df <- df_graphs %>% filter (STIMULUS =="B1-3") %>% 
  mutate(
    MAKER_AGE = fct_rev(MAKER_AGE)
  )
ggpiestats(data = df, x=MAKER_AGE )


##GGPIESTATS MAKER_ID
df <- df_graphs %>% filter (STIMULUS =="B1-3") %>% 
  mutate(
    MAKER_ID = fct_rev(MAKER_ID)
  )
ggpiestats(data = df, x=MAKER_ID )


##DONUT WITH LESSR

library(lessR)

#MAKER_ID-DONUT
PieChart(MAKER_ID, data = df,
         fill = "reds",
         main = NULL)


#MAKER_GENDER-DONUT
PieChart(MAKER_GENDER, data = df,
         fill = "blues",
         main = NULL)


#MAKER_GENDER-DONUT
PieChart(MAKER_AGE, data = df,
         fill = "olives",
         main = NULL)


# View(paletteer::palettes_d_names)

```

## semantic differentials

```{r sd-b13, warning=FALSE}





##FILTER DATAFRAME
s = "B1-3" #stimulus code
df <- df_graphs %>% filter(STIMULUS == s)

questions = c("MAKER_POLITIC", "MAKER_ARGUE", "MAKER_SELF", "MAKER_ALIGN", "MAKER_TRUST")
# questions = ref_sd_questions
labels <- ref_labels %>% filter(row.names(ref_labels) %in% questions)

#### RAINCLOUD PLOT
  # setup dataframe 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME) ##TODO IF NOT WORK ref_stim_id
  title <- paste0(title, " [",s,"]")
  df <- df_sd_questions_wide %>% select(1:6, QUESTION, all_of(s)) %>% 
    filter(!is.na(s)) %>%  
    mutate(value = get(s)) %>% 
    filter(QUESTION %in% questions)


  #RAINCLOUD PLOT
  # x <- 
    ggplot(df, aes(y = fct_rev(QUESTION), x = value)) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  # facet_grid( .~ Distribution) +
  guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    y = guide_axis_manual(labels = rev(labels$left)),
    y.sec = guide_axis_manual(labels = rev(labels$right))
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  # rain_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/_aggressive_american_flag", filename =paste0(s,"_rain.png"), units = c("in"), width = 10, height = 14  )

```

# B0-0 MILLENIAL PINK PLANTS

### GGBIVARIATE

```{r bivariate-demos-b00}
if(graph_render == TRUE){


### EXPLORE ALL QUESTIONS AS EXPLAINED BY DEMOGRAPHICS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = df %>% select(Distribution, STIMULUS_CATEGORY,
                D_gender_collapsed, D_age, D_education, D_income,
                D_politicalParty, D_politicsFiscal, D_politicsSocial) %>% colnames()

questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)

i=0
for (q in questions){
  i = i+1
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by demographic variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_demographics", filename =paste0("B0-0_",q,"_demo_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END




### EXPLORE ALL QUESTIONS AS EXPLAINED BY SD VARS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = c(ref_sd_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by SD variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_SD", filename =paste0("B0-0_",q,"_sd_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g )
#####################################################END



### EXPLORE ALL QUESTIONS AS EXPLAINED BY CONF VARS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = c(ref_conf_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by CONF variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_CONF", filename =paste0("B0-0_",q,"_conf_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END


### EXPLORE ALL QUESTIONS AS EXPLAINED BY CAT VARS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = c(ref_cat_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by CATEGORICAL variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_CAT", filename =paste0("B0-0_",q,"_cat_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END

}
```

## PAIRPLOTS

```{r boo-pairplots}

if(graph_render == TRUE){


#####################################################PAIRPLOT_SD
df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(all_of(ref_sd_questions))
g <- ggpairs(df) 
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_sd_pairplot.png"), units = c("in"), width = 20, height = 20  )
g <- ggduo(df)
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_sd_duoplot.png"), units = c("in"), width = 20, height = 20  )

#####################################################PAIRPLOT_CAT
df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(all_of(ref_cat_questions))
g <- ggpairs(df) 
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_cat_pairplot.png"), units = c("in"), width = 20, height = 20  )
g <- ggduo(df)
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_cat_duoplot.png"), units = c("in"), width = 20, height = 20  )


#####################################################PAIRPLOT_CONF
df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(all_of(ref_conf_questions))
g <- ggpairs(df) 
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_conf_pairplot.png"), units = c("in"), width = 20, height = 20  )
g <- ggduo(df)
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_conf_duoplot.png"), units = c("in"), width = 20, height = 20  )

####################################################################################################
####################################################################################################






#####################################################PAIRPLOT_SD COLORED BY DEMO
predictors = df_graphs %>% select(Distribution, STIMULUS_CATEGORY,
                D_gender_collapsed, D_age, D_education, D_income,
                D_politicalParty) %>% colnames()

i=0
for (p in predictors){
  df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(p, all_of(ref_sd_questions))
  g <- ggpairs(df, aes(color = get(p)))   
  ggsave(plot = g, path="figs/_millenial-pink-plants/colored_pairs", filename =paste0("B00_",p,"_sd_pairplot.png"), units = c("in"), width = 40, height = 40  )  
  g <- ggduo(df, aes(color = get(p)))   
  ggsave(plot = g, path="figs/_millenial-pink-plants/colored_duos", filename =paste0("B00_",p,"_sd_duoplot.png"), units = c("in"), width = 40, height = 40  )  
  
}
rm(i,g,df)
####################################################################################################



}

```

## MODELLING

### Modelling Trust

```{r}

df <- df_graphs %>% filter(STIMULUS == "B0-0") %>%
  mutate(
    flipped_data = abs(MAKER_DATA - 100),
    flipped_design = abs(MAKER_DESIGN -100),
    flipped_intent = abs(CHART_INTENT -100),
    flipped_self = abs(MAKER_SELF -100)
  ) %>% select(
    flipped_data:flipped_self, MAKER_ARGUE, MAKER_ALIGN, CHART_LIKE, CHART_BEAUTY, CHART_TRUST, MAKER_TRUST
  )


chart_m.1 <- lm(CHART_TRUST ~ CHART_BEAUTY, data = df )
summ(chart_m.1)

chart_m.2 <- lm(CHART_TRUST ~ MAKER_ALIGN , data = df )
summ(chart_m.2)


anova(chart_m.1, chart_m.2)
compare_performance(chart_m.1, chart_m.2, rank = TRUE)


m.1 <- lm(MAKER_TRUST ~ CHART_BEAUTY, data = df )
summ(m.1)

m.2 <- lm(MAKER_TRUST ~ MAKER_ALIGN , data = df )
summ(m.2)

anova(m.1, m.2)
compare_performance(chart_m.1, chart_m.2, m.1, m.2, rank = TRUE)


m.3 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY , data = df )
summ(m.3)

m.4 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent, data = df )
summ(m.4)

m.5 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent + flipped_data, data = df )
summ(m.5)


m.6 <- lm(MAKER_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
summ(m.6)
 

m.7 <- lm(CHART_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
summ(m.7)

m <- lm(MAKER_TRUST ~ MAKER_ALIGN, data = df)
summ(m)

 
 compare_performance(m.1, m.2, m.3, m.4, m.5, m, rank = TRUE)
# 
# ## WHAT PREDICTS MAKER_TRUST?
# 
# 
# ## PLOT THE DATA 
# ggplot(df, aes(x = MAKER_ALIGN, y = MAKER_TRUST)) + 
#   geom_point() +
#   stat_smooth(method = "lm", 
#               formula = y ~ x, 
#               geom = "smooth") + 
#   labs(title = "MAKER ALIGNMENT PREDICTS TRUST?")+
#   theme_minimal()
# 
# 
# ## PLOT THE DATA 
# ggplot(df, aes(x = flipped_data, y = MAKER_TRUST)) + 
#   geom_point() +
#   stat_smooth(method = "lm", 
#               formula = y ~ x, 
#               geom = "smooth") + 
#   labs(title = "MAKER DATA PREDICTS TRUST?")+
#   theme_minimal()
# 
# 
# ## BUILD MODEL
# m.1 <- lm( MAKER_TRUST ~ MAKER_ALIGN, data = df)
# # summary(m.1)
# jtools::summ(m.1, confint = TRUE)
# # check_model(m.1)
# # report(m.1)
# 
# ## BUILD MODEL
# m.2 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data, data = df)
# # summary(m.2)
# jtools::summ(m.2, confint = TRUE)
# # check_model(m.2)
# # report(m.2)
# 
# ## BUILD MODEL
# m.3 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design , data = df)
# # summary(m.3)
# jtools::summ(m.3, confint = TRUE)
# # check_model(m.3)
# # report(m.3)
# 
# 
# ## BUILD MODEL
# m.4 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design + MAKER_POLITIC, data = df)
# # summary(m.3)
# jtools::summ(m.4, confint = TRUE)
# # check_model(m.3)
# # report(m.3)
# 
# 
# 
#   
# compare_performance(m.1, m.2, m.3, m.4, m.B,  rank = TRUE)
# 
# 
# # effect_plot(m.2, pred=MAKER_DATA, rug = TRUE, plot.points = TRUE) + 
# #   xlim(0,100) + 
# #   ylim(0,100)
# 
# 
# 
# 
# df <- df_graphs %>% filter(STIMULUS != "B0-0") %>% 
#   select(PID, STIMULUS, 
#          MAKER_ID:MAKER_TRUST, CHART_LIKE:CHART_TRUST, 
#          D_politicsFiscal, D_politicsSocial)
# 
# m.pid <- lmer( MAKER_TRUST ~  (1 | PID) , data = df, REML = FALSE)
# m.stim <- lmer( MAKER_TRUST ~ (1|STIMULUS) , data = df, REML = FALSE)
# m.r <- lmer( MAKER_TRUST ~ (1 | PID) + (1|STIMULUS), data = df, REML = FALSE)
# 
# compare_performance (m.pid, m.stim, m.r, rank = TRUE)
# 
# 
# 
# m.1 <- update( m.r, .~. + CHART_BEAUTY)
# summ(m.1)
# 
# m.2 = update(m.1, . ~ . + CHART_LIKE)
# summ(m.2)
# 
# 
# m.3 = update(m.2, . ~ . + CHART_TRUST)
# summ(m.3)
# 
# 
# compare_performance(m.r, m.1, m.2, m.3, rank = TRUE)

```

### TODO COME BACK HERE Modelling Engagement

```{r B00-ENGAGEMENT}


# df <- df_graphs %>% filter(STIMULUS == "B0-0") %>%
#   mutate(
#     flipped_data = abs(MAKER_DATA - 100),
#     flipped_design = abs(MAKER_DESIGN -100),
#     flipped_intent = abs(CHART_INTENT -100),
#     flipped_self = abs(MAKER_SELF -100),
#   ) %>% select(
#     MAKER_ARGUE, MAKER_ALIGN, CHART_LIKE, CHART_BEAUTY,
#     flipped_data:flipped_self,  CHART_TRUST, MAKER_TRUST, 
#     Distribution, D_gender, D_education, D_politicalParty, 
#     D_politicsSocial, D_politicsFiscal,
#     MAKER_ID, MAKER_AGE, MAKER_GENDER, 
#   )


## left off here !!! 
## MAKE DATAFRAME OF ACTIONS WITH OTHER STUFF 
# df_g <- df_graphs %>% filter(STIMULUS == "B0-0")
# df_a <- df_actions %>% filter(STIMULUS == "B0-0")
# df_x <- df_a %>% inner_join(x=df_a, y=df_g, by="PID",
#                            relationship = "many-to-one",
#                            multiple = "last",
#                            keep = FALSE)
# rm(df_a, df_g)
# 
# 
# df <- df_x %>% filter(STIMULUS == "B0-0") %>%
#   mutate(
#     flipped_data = abs(MAKER_DATA - 100),
#     flipped_design = abs(MAKER_DESIGN -100),
#     flipped_intent = abs(CHART_INTENT -100),
#     flipped_self = abs(MAKER_SELF -100),
#   ) %>% select(
#     MAKER_ARGUE, MAKER_ALIGN, CHART_LIKE, CHART_BEAUTY,
#     flipped_data:flipped_self,  CHART_TRUST, MAKER_TRUST,
#     Distribution, D_gender, D_education, D_politicalParty,
#     D_politicsSocial, D_politicsFiscal,
#     MAKER_ID, MAKER_AGE, MAKER_GENDER,
#   )
# 


## PLOT DISTRIBUTION OF ENGAGEMENT 
# 
# (a <- ggbarstats( data = df, x = "REV_CHART_ACTION", y = "STIMULUS",
#                  legend.title = "ENGAGEMENT")  + 
#       scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
#       labs( title = "Chart Engagement ", subtitle = "", x = "") )
#   
#         
# 
# (b <- grouped_ggbarstats( data = df_a, x = "REV_CHART_ACTION", y = "STIMULUS", 
#                     grouping.var = Distribution, 
#                     legend.title = "ENGAGEMENT",  
#                     ggplot.component = list(scale_fill_paletteer_d("awtools::a_palette", direction = 1))))
# 
# 
# 
# df <- df_a %>% mutate( REV_CHART_ACTION = fct_rev(CHART_ACTION))
# predictors = df_a %>% select(Distribution, PLATFORM, 
#                 D_gender, D_age, D_education, D_race, D_income, 
#                 D_politicalParty, D_politicsFiscal, D_politicsSocial) %>% colnames()
# 
# 
# 
# 
# 
# ## PLOT POTENTIAL BIVARIATE
# (g <- ggbivariate(df_a, outcome = "CHART_ACTION", explanatory = predictors) + 
#   scale_fill_paletteer_d("awtools::a_palette", direction = 1))
# 
# ggsave(plot = g, path="figs/modelling", filename =paste0("b00_engagement","_bivariatet.png"), units = c("in"), width = 15, height = 20  )
# 
# 
# ## PLOT EXPLANATIONS OF ENGAGEMENT
# 
# 
# 
# ##
# 
# ## Visualize Engagement with B00
# 
# # 
# # 
# # 
# # 
# # chart_m.1 <- lm(CHART_TRUST ~ CHART_BEAUTY, data = df )
# # summ(chart_m.1)
# # 
# # chart_m.2 <- lm(CHART_TRUST ~ MAKER_ALIGN , data = df )
# # summ(chart_m.2)
# # 
# # 
# # anova(chart_m.1, chart_m.2)
# # compare_performance(chart_m.1, chart_m.2, rank = TRUE)
# # 
# # 
# # m.1 <- lm(MAKER_TRUST ~ CHART_BEAUTY, data = df )
# # summ(m.1)
# # 
# # m.2 <- lm(MAKER_TRUST ~ MAKER_ALIGN , data = df )
# # summ(m.2)
# # 
# # anova(m.1, m.2)
# # compare_performance(chart_m.1, chart_m.2, m.1, m.2, rank = TRUE)
# # 
# # 
# # m.3 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY , data = df )
# # summ(m.3)
# # 
# # m.4 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent, data = df )
# # summ(m.4)
# # 
# # m.5 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent + flipped_data, data = df )
# # summ(m.5)
# # 
# # 
# # m.6 <- lm(MAKER_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
# # summ(m.6)
# #  
# # 
# # m.7 <- lm(CHART_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
# # summ(m.7)
# # 
# # m <- lm(MAKER_TRUST ~ MAKER_ALIGN, data = df)
# # summ(m)
# # 
# #  
# #  compare_performance(m.1, m.2, m.3, m.4, m.5, m, rank = TRUE)
# # # 
# # ## WHAT PREDICTS MAKER_TRUST?
# # 
# # 
# # ## PLOT THE DATA 
# # ggplot(df, aes(x = MAKER_ALIGN, y = MAKER_TRUST)) + 
# #   geom_point() +
# #   stat_smooth(method = "lm", 
# #               formula = y ~ x, 
# #               geom = "smooth") + 
# #   labs(title = "MAKER ALIGNMENT PREDICTS TRUST?")+
# #   theme_minimal()
# # 
# # 
# # ## PLOT THE DATA 
# # ggplot(df, aes(x = flipped_data, y = MAKER_TRUST)) + 
# #   geom_point() +
# #   stat_smooth(method = "lm", 
# #               formula = y ~ x, 
# #               geom = "smooth") + 
# #   labs(title = "MAKER DATA PREDICTS TRUST?")+
# #   theme_minimal()
# # 
# # 
# # ## BUILD MODEL
# # m.1 <- lm( MAKER_TRUST ~ MAKER_ALIGN, data = df)
# # # summary(m.1)
# # jtools::summ(m.1, confint = TRUE)
# # # check_model(m.1)
# # # report(m.1)
# # 
# # ## BUILD MODEL
# # m.2 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data, data = df)
# # # summary(m.2)
# # jtools::summ(m.2, confint = TRUE)
# # # check_model(m.2)
# # # report(m.2)
# # 
# # ## BUILD MODEL
# # m.3 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design , data = df)
# # # summary(m.3)
# # jtools::summ(m.3, confint = TRUE)
# # # check_model(m.3)
# # # report(m.3)
# # 
# # 
# # ## BUILD MODEL
# # m.4 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design + MAKER_POLITIC, data = df)
# # # summary(m.3)
# # jtools::summ(m.4, confint = TRUE)
# # # check_model(m.3)
# # # report(m.3)
# # 
# # 
# # 
# #   
# # compare_performance(m.1, m.2, m.3, m.4, m.B,  rank = TRUE)
# # 
# # 
# # # effect_plot(m.2, pred=MAKER_DATA, rug = TRUE, plot.points = TRUE) + 
# # #   xlim(0,100) + 
# # #   ylim(0,100)
# # 
# # 
# # 
# # 
# # df <- df_graphs %>% filter(STIMULUS != "B0-0") %>% 
# #   select(PID, STIMULUS, 
# #          MAKER_ID:MAKER_TRUST, CHART_LIKE:CHART_TRUST, 
# #          D_politicsFiscal, D_politicsSocial)
# # 
# # m.pid <- lmer( MAKER_TRUST ~  (1 | PID) , data = df, REML = FALSE)
# # m.stim <- lmer( MAKER_TRUST ~ (1|STIMULUS) , data = df, REML = FALSE)
# # m.r <- lmer( MAKER_TRUST ~ (1 | PID) + (1|STIMULUS), data = df, REML = FALSE)
# # 
# # compare_performance (m.pid, m.stim, m.r, rank = TRUE)
# # 
# # 
# # 
# # m.1 <- update( m.r, .~. + CHART_BEAUTY)
# # summ(m.1)
# # 
# # m.2 = update(m.1, . ~ . + CHART_LIKE)
# # summ(m.2)
# # 
# # 
# # m.3 = update(m.2, . ~ . + CHART_TRUST)
# # summ(m.3)
# # 
# # 
# # compare_performance(m.r, m.1, m.2, m.3, rank = TRUE)

```

```{r IXN-BOO}

df <- df_graphs_full %>% 
  filter(STIMULUS== "B0-0") 

 p <- ggplot(df, aes(x = MAKER_POLITIC, y = MAKER_CONF,
          color = MAKER_ID ,
          text = paste0("MAKER-DETAIL: ",MAKER_DETAIL, "<br>","ID: ", PID, "MAKER_EXPLAIN", MAKER_EXPLAIN)))+
      scale_color_viridis(discrete=TRUE, option="viridis")  +
      geom_point(size=0.5) +
      xlim(0,100)+
      ylim(0,100)+
      facet_grid(D_politicalParty ~ MAKER_ID) +
      theme_minimal() +
      labs(
        title = "B0-0 | MAKER Identification, Politics and Confidence",
        subtitle = "\n by Participant Confidence and Political Party",
        x = "MAKER POLITICS",
        y = "MAKER ID CONFIDENCE"
      )


ggplotly(p)
  
```

### On Confidence

```{r}


# df <- df_confidence_long %>% filter(QUESTION %nin% c("CONF", "SDIFF")) ##AVERAGE CONFIDENCE

df <- df_graphs_full %>% filter(STIMULUS== "B0-0")


ggplot(df, aes(x = MAKER_CONF, y = MAKER_TRUST, color = MAKER_ID)) + 
  geom_point() +
  scale_color_viridis(discrete=TRUE, option="viridis")  + 
  facet_grid(BLOCK ~ STIMULUS_CATEGORY) +
  theme_minimal() + 
  easy_remove_legend() 
  


ggplot(df, aes(x = MAKER_POLITIC, y = MAKER_TRUST, color = MAKER_ID)) + 
  geom_point() +
  scale_color_viridis(discrete=TRUE, option="viridis")  + 
  facet_grid(BLOCK ~ STIMULUS_CATEGORY) +
  theme_minimal() + 
  easy_remove_legend() 



```

# EDA

## PAIR PLOTS

### B0-0 MILLENIAL PINK PLANTS

```{r B00_MAKERID, message=FALSE}

#FILTER DATAFRAME
df <- df_graphs_full %>%
  filter(STIMULUS== "B0-0") %>%
  select(
    Distribution,  D_politicalParty,
    # D_gender, D_race, D_education, D_income, D_age,
    # ENCOUNTER,
    MAKER_ID,
    D_politicsSocial, D_politicsFiscal,
    MAKER_DESIGN, MAKER_DATA, MAKER_CONF, MAKER_ALIGN, MAKER_TRUST, CHART_TRUST
    # :MAKER_TRUST,
    # TOOL_CONF,CHART_LIKE:CHART_TRUST
)

# g <- ggpairs(df, color=MAKER_ID)
# ggsave(plot = g, path="figs/pairplots", filename =paste0("B0-0","_pairplot.svg"), units = c("in"), width = 20, height = 20  )
# ggplotly(g)




(boo_pair <- ggpairs(df, aes(color= MAKER_ID)) +
    scale_color_viridis(discrete=TRUE, option="viridis")+
    scale_fill_viridis(discrete=TRUE, option="viridis") +
    theme_minimal()
  )


(boo_duo <- ggduo(df, aes(color= Distribution)) +
    scale_color_viridis(discrete=TRUE, option="viridis")+
    scale_fill_viridis(discrete=TRUE, option="viridis") +
    theme_minimal()
  )



ggplotly(boo_duo) #surprisingly works! but not helpful

```

### CATEGORIES-MAKER

```{r}

df <- df_graphs %>% select(
  STIMULUS_CATEGORY, MAKER_ID, MAKER_DESIGN, MAKER_DATA, MAKER_POLITIC, MAKER_ARGUE, MAKER_ALIGN, MAKER_TRUST, CHART_TRUST, CHART_BEAUTY
)


#maker pair plot 
x <- ggduo(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("maker_category","_duoplot.png"), units = c("in"), width = 20, height = 20  )

#maker pair plot 
x <- ggpairs(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("maker_category","_pairplot.png"), units = c("in"), width = 20, height = 20  )

```

### CATEGORIES-CHART

```{r}

df <- df_graphs %>% select(
  STIMULUS_CATEGORY, MAKER_ID, CHART_LIKE, CHART_BEAUTY, CHART_INTENT, CHART_TRUST, MAKER_TRUST
)


#maker pair plot 
x <- ggduo(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("chart_category","_duoplot.png"), units = c("in"), width = 20, height = 20  )

#maker pair plot 
x <- ggpairs(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("chart_category","_pairplot.png"), units = c("in"), width = 20, height = 20  )

```

### ALL NUMERIC

```{r}

df <- df_graphs %>% select(STIMULUS_CATEGORY, where(is.numeric)) %>% 
  select(-duration.min)


#maker pair plot 
x <- ggscatmat(df, color = "STIMULUS_CATEGORY")
ggsave(plot = x, path="figs/pairplots", filename =paste0("category","_scaplot.png"), units = c("in"), width = 20, height = 20  )



```

# INTERACTIVE GRAPHS

### WIP IXN Maker ID & Politics

```{r PLOTLY}

#SETUP LISTS 
stim <- ref_stimuli##TODO IF NOT WORK ref_stim_id
plots_maker_politics <- htmltools::tagList()

### MAKE PLOTS 
# LOOP THROUGH STIMULI
i = 0
for (s in stim){
  i = i+1 #iterator hack
  
  d <- df_graphs_full %>% filter(STIMULUS == s) %>% select(PID, STIMULUS, 
                                                               MAKER_ID, MAKER_DETAIL, MAKER_CONF, MAKER_POLITIC,
                                                               D_politicalParty, D_politicsSocial, D_politicsFiscal) 
  p <- ggplot(d, aes(x = MAKER_POLITIC, y = MAKER_CONF,
          color = MAKER_ID ,
          text = paste0("MAKER-DETAIL: ",MAKER_DETAIL, "<br>","ID: ", PID)))+
      geom_point() +
      xlim(0,100)+
      ylim(0,100)+
      facet_grid(MAKER_ID  ~ D_politicalParty) +
      theme_minimal() +
      labs(
        title = paste(s," | ", "MAKER Identification, Politics and Confidence, by Participant Confidence and Political Affiliation"),
        x = "MAKER POLITICS",
        y = "MAKER CONFIDENCE"
      )

  
  plots_maker_politics[[i]] <- ggplotly(p)
  
}

names(plots_maker_politics) <- ref_stimuli ##TODO IF NOT WORK ref_stim_id


#works in console but not render 
### PRINT PLOTS
# for (s in stim){
#   print(plots_maker_politics[[s]])
# }


# ggplotly(p) #works for single

plots_maker_politics
```

# WIP QDA ANALYSIS

## MAKER ID DETAIL

```{r CODED-MAKER-ID-DETAIL}

# df <- df_graphs_coded %>% select( ID.Prolific, STIMULUS, BLOCK, STIMULUS_CATEGORY, MAKER_ID, MAKER_DETAIL, CODE_M_ID_SPECIFIC) %>% 
#   separate_longer_delim(
#     cols = CODE_M_ID_SPECIFIC,
#     delim = ","
#   ) %>% filter(
#     CODE_M_ID_SPECIFIC %nin% c("x", "X","example")
#   ) %>% mutate(
#     CODED_MAKER = str_trim(CODE_M_ID_SPECIFIC, side="left"),
#     CODED_MAKER = str_to_upper(CODED_MAKER),
#     CODED_MAKER = factor(CODED_MAKER, levels = c( "NYT",
#                                                   "WASHINGTON POST" ,
#                                                   "USA TODAY" ,
#                                                   "THE ECONOMIST" ,
#                                                   "WSJ",
#                                                   "POPULAR SCIENCE" ,
#                                                   "TIME",
#                                                   "NPR",
#                                                   "PBS",
#                                                   "ASSOCIATED PRESS"  ,
#                                                   "BBC",
#                                                   "CBS NEWS"  ,
#                                                   "ABC NEWS"  ,
#                                                   "NBC",
#                                                   "CNN",
#                                                   "FOX NEWS"  ,
#                                                   "BUZZFEED",
#                                                   "VOX",
#                                                   "VICE",
#                                                   "HUFFINGTON POST" ,
#                                                   "US DOD"  ,
#                                                   "US BUREAU OF ECONOMIC ANALYSIS",
#                                                   "US DOE"  ,
#                                                   "US CDC"  ,
#                                                   "MINISTRY OF HEALTH"  ,
#                                                   "EPA",
#                                                   "NOAA",
#                                                   "NATIONAL WEATHER SERVICE"  ,
#                                                   "WHO",
#                                                   "UN",
#                                                   "THE NATURE CONSERVANCY"  ,
#                                                   "GREENPEACE",
#                                                   "LEAF",
#                                                   "HARVARD",
#                                                   "COLUMBIA UNIVERSITY" ,
#                                                   "IAA",
#                                                   "IBM",
#                                                   "MICROSOFT",
#                                                   "GOLDMAN SACHS" ,
#                                                   "GMC",
#                                                   "TESLA",
#                                                   "GREEN PARTY OF AMERICA"  ,
#                                                   "THE DEMOCRATIC PARTY"  ,
#                                                   "THE REPUBLICAN PARTY")),
#     STIM = factor(STIMULUS, levels = c(
#       "B1-1",  "B2-1", "B3-1", "B4-1", "B5-1", "B6-1",
#       "B1-2",  "B2-2", "B3-2", "B4-2", "B5-2", "B6-2",
#       "B1-3", "B2-3", "B3-3", "B4-3", "B5-3", "B6-3",
#       "B1-4","B2-4" ,"B3-4" ,"B4-4" ,"B5-4" ,"B6-4", "B0-0"
#     ))
#   ) 
# 
# 
# 
# ggplot(df,  aes(x = MAKER_ID, fill = CODED_MAKER )) + 
#   geom_bar(position = "stack") +
#   facet_grid( rows = vars(BLOCK), cols = vars(fct_rev(STIMULUS_CATEGORY))) + 
#   theme_minimal() + 
#   labs(title = "Specific makers identified by stimulus")
# 
#                           
# ggplot(df,  aes(x = STIMULUS, fill = CODED_MAKER )) + 
#   geom_bar(position = "stack") + 
#   theme_minimal()
# 
# 
# ggplot(df,  aes(x = STIMULUS, fill = CODED_MAKER )) + 
#   geom_bar(position = "stack") + 
#   facet_wrap(~CODED_MAKER) + 
#   theme_minimal() +
#   easy_remove_x_axis() +
#   easy_remove_legend()
# 
#   
# ggplot(df,  aes(x = CODE_M_ID_SPECIFIC, fill = STIM, )) + 
#   geom_bar(position = "stack") + 
#   coord_flip() + 
#   theme_minimal() 
#   
  
      

```

# TODO

## Wrangle Participant Confidence

```{r wrangle-confidence}

# 
# ## CALCULATE AV CONFIDENCE FOR EACH SEMANTIC DIFFERENTIALS 
# df_sds <- df_sd_questions_long %>% 
#   group_by(PID, QUESTION) %>% 
#   summarize(
#     mean = mean(value), 
#     sd = sd (value)
#   ) 
# 
# df_sds_WIDE <- df_sds %>% 
#     pivot_wider(
#       names_from = QUESTION,
#       values_from = c(mean, sd)
#   )
# 
# ## CALCULATE AV CONFIDENCE ACROSS SEMANTIC DIFFERENTIALS 
# df_grandsds <- df_sd_questions_long %>% 
#   group_by(PID) %>% 
#   summarize(
#     SDIFF_mean = mean(value), 
#     SDIFF_sd = sd(value)
#   ) 
# 
# 
# df_grandsds_LONG <- df_grandsds %>% 
#   mutate(
#       QUESTION = "SDIFF", 
#       mean = SDIFF_mean, 
#       sd = SDIFF_sd
# ) %>% select(-SDIFF_mean, -SDIFF_sd)
#   
# 
# 
# ## CALCULATE AV CONFIDENCE FOR EACH CONFIDENCE
# df_confq <- df_questions %>% 
#   filter(QUESTION %in% ref_conf_questions)%>% 
#   group_by(PID, QUESTION) %>% 
#   summarize(
#     mean = mean(as.numeric(value)), 
#     sd = sd (as.numeric(value))
#   ) 
# 
# df_confq_WIDE <- df_confq %>% 
#     pivot_wider(
#       names_from = QUESTION,
#       values_from = c(mean, sd)
#   )
# 
# ## CALCULATE AV CONFIDENCE ACROSS SEMANTIC DIFFERENTIALS 
# df_grandconfs <- df_questions %>% 
#   filter(QUESTION %in% ref_conf_questions)%>% 
#   group_by(PID) %>% 
#   summarize(
#     CONF_mean = mean(as.numeric(value)), 
#     CONF_sd = sd(as.numeric(value))
#   )
# 
# 
# df_grandconfs_LONG <- df_grandconfs %>% 
#   mutate(
#       QUESTION = "CONF", 
#       mean = CONF_mean, 
#       sd = CONF_sd
# ) %>% select(-CONF_mean, -CONF_sd) 
#   
# 
# 
# 
# ## JOIN TOGETHER WIDE
# df_confidence_wide <- left_join(df_sds_WIDE, df_confq_WIDE, by="PID")
# df_confidence_wide <- left_join(df_confidence_wide, df_grandsds, by = "PID")
# df_confidence_wide <- left_join(df_confidence_wide, df_grandconfs, by = "PID")
# df_confidence_wide <- left_join(df_confidence_wide, df_participants, by = "PID")
# 
# 
# ##JOIN TOGETHER LONG
# df_confidence_long <- rbind(df_sds, df_confq, df_grandsds_LONG, df_grandconfs_LONG) %>% 
#   mutate(
#     QUESTION = factor(QUESTION)
#   ) 
# 
# df_confidence_long <- left_join(df_confidence_long, df_participants, by="PID")
# 
# rm(df_sds, df_grandsds, df_confq, df_grandconfs, df_sds_WIDE, df_grandsds_LONG, df_confq_WIDE, df_grandconfs_LONG)
# 
# print("df_confidence_wide is a participant level dataset with by question and question type mean and df per participant")
# print("df_confidence_long is a participant level dataset with by question and question type mean and df per participant")
# print("In both cases the means are over all 5 stimuli seen by each participant")

```

# STASH

wip code stash

## Alluvial Plots

```{r}
## EXAMPLE ALLUVIAL PLOT USING GGALUVIAL  (instead of GGSANKEY)
# https://corybrunson.github.io/ggalluvial/articles/ggalluvial.html

# #FILTER FOR BLOCK 2 STIM AND RESHAPE FOR SANKEY
# ds <- df_graphs %>% 
#   filter(str_detect(STIMULUS, "B2")) %>% 
#   select(STIMULUS, MAKER_ID, PID) %>% 
#   mutate(
#     MAKER_ID = fct_relevel(MAKER_ID, 
#               c("business","education","individual", "news","organization", "political" ))
#   )
# 
# ds %>% 
#   ggplot(aes( x = STIMULUS,
#               stratum = MAKER_ID,
#               label = MAKER_ID,
#               alluvium = PID)) +
#       stat_alluvium(aes(fill = MAKER_ID),
#                     width = 0,
#                     alpha = 1,
#                     geom = "flow")+
#       geom_stratum(width = 0.2, aes(fill= MAKER_ID))+
#       # geom_text(stat = "stratum", size = 5, angle = 90)+
#       scale_fill_viridis(discrete=TRUE, option="viridis", drop = FALSE,
#                      alpha = 1) +
#       theme_minimal()
```

# RESOURCES

-   custom color palettes: <https://www.r-bloggers.com/2022/06/custom-colour-palettes-for-ggplot2/>
-   lessR donuts <https://r-charts.com/part-whole/donut-chart/>
-   GGSANKEY <https://github.com/davidsjoberg/ggsankey>
-   GGALLUVIAL <https://corybrunson.github.io/ggalluvial/articles/ggalluvial.html>
