---
title: "VIBES STUDY 2 ANALYSIS — AGGREGATED DATA"
author: "ANONYMIZED"
date: "2024-08-07"
output:
  html_document:
    theme: flatly
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 5
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe()
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates

#EDA
library(qacBase)

#VIZ
library(kableExtra) #printing tables
library(ggformula) #regression syntax viz
# library(vcd) #mosaic plots
# library(vcdExtra) #mosaic plot helpers
library(ggstatsplot) #dummies
library(gghalves) #half boxplots 
library(GGally) #extends ggplot for EDA 
library(corrplot) #sophisticated correlation plots
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(ggridges) #ridge plots
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(lessR) ##very pretty donuts 
library(ggsankey) ## ggplot2 sankey extension
library(interactions) ##easier regression ixn plots.srlsy



#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer
library(equatiomatic) ## extracting model formula
library(latex2exp) ## extracting and printing model formula

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
graph_save = TRUE #set to true to generate all the SD graphs and save to folders 

```

In VISUALIZATION VIBES project Study 2, participants completed an
*attitutde eliciation* survey, asking questions about their attitude
toward (5) stimulus images (data visualizations). Each participant was
randomly assigned to one of 6 stimulus blocks, each containing 1 image
from each of (4) pseudo-categories (ranging from most abstract to most
figural). Each participant started by responding to questions for a
single 'common' stimulus (that is thus super-powered as it was seen by
all participants). Two participant recruitment pools were used:
Prolific, with a smaller set of participants recruited from Tumblr (to
replicate and compare survey results to Study 1 interviews with
participants sourced from Tumblr).

This notebook contains code to replicate quantitative analysis of data
from Study 2 reported in the CHI submission. Note that due to limited
space, we were unable to report results for *all* stimulus blocks, and
all possible analyses. A separate set of R notebooks are included in the
supplementary materials that document analysis of the other blocks not
reported here.

**This notebook includes analysis and exploration of the full data set
(i.e. data aggregated over all stimuli).**

# SETUP

*We start by importing data files previously wrangled in
`0_VIBES_S2_wrangling.Rmd`.*

## Import Data

```{r import-refs, message=FALSE, warning = FALSE}

############## IMPORT REFERENCE FILES
ref_stimuli <- readRDS("data/input/REFERENCE/ref_stimuli.rds")
ref_surveys <- readRDS("data/input/REFERENCE/ref_surveys.rds")
ref_labels <- readRDS("data/input/REFERENCE/ref_labels.rds")
ref_labels_abs <- readRDS("data/input/REFERENCE/ref_labels_abs.rds")

############## SETUP Graph Labels
ref_stim_id <- levels(ref_stimuli$ID)
ref_cat_questions <- c("MAKER_ID","MAKER_AGE","MAKER_GENDER")
ref_free_response <- c("MAKER_DETAIL", "MAKER_EXPLAIN", "TOOL_DETAIL", "CHART_EXPLAIN")
ref_conf_questions <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")
ref_sd_questions <- rownames(ref_labels)
ref_sd_questions_abs <- rownames(ref_labels_abs)
  

# ref_blocks <- c("block1", "block2", "block3", "block4", "block5", "block6")
ref_blocks <- c(1,2,3,4,5,6)

```

```{r import-data, message=FALSE, warning = FALSE}

############## IMPORT DATA FILES
# df_data <- readRDS("data/output/df_data.rds") #1 row per participant — WIDE
df_participants <- readRDS("data/output/df_participants.rds") #1 row per participant — demographic
df_questions <- readRDS("data/output/df_questions.rds") #1 row per question — LONG
df_sd_questions_wide <- readRDS("data/output/df_sd_questions_wide.rds") # only sd questions WIDE


df_tools <- readRDS("data/output/df_tools.rds") #multiselect format for tools Question
df_actions <- readRDS("data/output/df_actions.rds") # multiselect format for action Question
# # df_graphs_full <- readRDS("data/output/df_graphs_full.rds") #includes free response data

df_graphs <- readRDS("data/output/df_graphs.rds") #only categorical and numeric questions
df_sd_questions_long <- readRDS("data/output/df_sd_questions_long.rds") # only sd questions LONG

### DATA FILES WITH (VARIABLE-WISE) Z-SCORED SEMANTIC DIFFERENTIAL QS 
df_graphs_z <- readRDS("data/output/df_graphs_z.rds") #only categorical and numeric questions
df_sd_questions_long_z <- readRDS("data/output/df_sd_questions_long_z.rds") # only sd questions LONG


### DATA FILES WITH ABSOLUTE VALUE SEMANTIC DIFFERENTIAL QS 
df_graphs_abs <- readRDS("data/output/df_graphs_abs.rds") #only categorical and numeric questions
df_sd_questions_long_abs <- readRDS("data/output/df_sd_questions_long_abs.rds") # only sd questions LONG

```

## Set up Graphing

```{r setup-pallettes}

############## SETUP Colour Palettes
#https://www.r-bloggers.com/2022/06/custom-colour-palettes-for-ggplot2/

## list of color pallettes
my_colors = list(
  politics = c("#184aff","#5238bf", "#4f4a52" ,"#84649c", "#ff0000"),
  blackred = c("black","red"),
  greys = c("#707070","#999999","#C2C2C2"),
  greens = c("#ADC69D","#81A06D","#567E39","#2D5D16","#193E0A"),
  smallgreens = c("#ADC69D","#567E39","#193E0A"),
  olives = c("#CDCEA1","#B8B979","#A0A054","#78783F","#50502A","#35351C"),
  lightblues = c("#96C5D2","#61A2B2","#3C8093","#2C6378","#1F4A64"),
  darkblues = c("#7AAFE1","#3787D2","#2A73B7","#225E96","#1A4974","#133453"),
  reds = c("#D9B8BD","#CE98A2","#B17380","#954E5F","#78263E","#62151F"),
  traffic = c("#CE98A2","#81A06D","yellow"),
  questions = c("#B17380","#3787D2", "#567E39", "#EE897F"),
  tools= c("#D55662","#EE897F","#F5D0AD","#A0B79B","#499678","#2D363A"),
  encounter = c("#729B7D","#8E8E8E"),
  actions = c("#2A363B","#039876ff","#99b898ff","#fdcea8ff","#ff837bff","#e84a60ff"),
  platforms = c("#5D93EA","#FF70CD", "#3BD3F5", "#8B69B5","black"),
  amy_gradient =  c("#ac57aa", "#9e5fa4", "#90689f", "#827099", "#747894", "#66818e", "#578988", "#499183", "#3b997d", "#2da278", "#1faa72"),
  my_favourite_colours = c("#702963", "#637029",    "#296370")
                
)

## function for using palettes
my_palettes = function(name, n, all_palettes = my_colors, type = c("discrete","continuous"), direction = c("1","-1")) {
  palette = all_palettes[[name]]
  if (missing(n)) {
    n = length(palette)
  }
  type = match.arg(type)
  out = switch(type,
               continuous = grDevices::colorRampPalette(palette)(n),
               discrete = palette[1:n]
  )
  out = switch(direction,
               "1" = out,
               "-1" = palette[n:1])
  structure(out, name = name, class = "palette")
}

```

```{r SD-GRAPHING-FUNCTIONS}


############## RETURNS SD STACKED AND COLORED BY BY X
## LOOP STYLE
multi_sd <- function (data, left, right, x, y, color) {

  # g <- ggplot(df, aes(y = .data[[x]], x = {{y}}, color = {{color}}))+
  g <- ggplot(data, aes(y = .data[[x]], x = .data[[y]], color = .data[[color]]))+
  geom_boxplot(width = 0.5) +
  geom_jitter(width = 0.1, alpha=0.5) +
    
  scale_y_continuous(limits=c(-1,101)) +
  labs(x="", y="") +
  coord_flip() +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) + theme_minimal()

  return(g)
}


############## RETURNS SINGLE SD 
## LOOP STYLE
single_sd <- function (data, left, right, x) {

  g <- ggplot(data, aes(y = {{x}}, x = ""))+
  geom_boxplot(width = 0.5) +
  geom_jitter(width = 0.1, alpha=0.5) +
  scale_y_continuous(limits=c(-1,101)) +
  labs(x="", y="") +
  coord_flip() +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) + theme_minimal()

  return(g)
}


######## RETURNS SINGLE SD
##  APPLY STYLE
plot_sd = function (data, column, type, mean, facet, facet_by, boxplot) {
  
  ggplot(data, aes(y = .data[[column]], x="")) +
    {if(boxplot) geom_boxplot(width = 0.5) } +
    geom_jitter(width = 0.1, alpha=0.2, {if(facet) aes(color=.data[[facet_by]])}) +
    {if(mean) 
      stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue")
      } +
    {if(mean)
      ## assumes data has been passed in with mean column at m
      # stat_summary(fun="mean", geom="text", colour="blue",  fontface = "bold",
      #            vjust=-1.25, hjust = 0.50, aes( label=round(..y.., digits=0)))
      stat_summary(fun="mean", geom="text", colour="blue",  fontface = "bold",
                 vjust=-1.25, hjust = 0.50, aes( label=round(..y.., digits=0)))
      } +

    {if(facet) facet_grid(.data[[facet_by]] ~ .)} +
    # scale_y_continuous(limits=c(-1,101)) +
    labs(x="", y="") +
    coord_flip()  +
    {if(type == "S")
      guides(
        y = guide_axis_manual(labels = ref_labels[column,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[column,"right"])
      )} +
    {if(type == "Q")
      guides(
        y = guide_axis_manual(labels = ref_labels[q,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
      )} +
  theme_minimal()  +
     labs (
       caption = column
     ) + easy_remove_legend()
}

```

# FULL SAMPLE ANALYSIS

As we argue in our manuscript, we understand that an individual's
response to a visualization (both inferences about data, as well as any
other behaviours) will *vary* based on properties of: (1) the
visualization, (2) the data, (3) the individual, and (4) the situational
context. Thus, our survey is *not* designed to uncover *consistencies*
in behaviour, but rather, explore the nature of *variance* in behaviour
as a function of the individual and visualization.

(n = `r nrow(df_participants)` ) survey respondents answered questions
about some subset of the stimuli, (common stimulus B0-0 and 4 additional
images defined as a block), yielding (o = `r nrow(df_graphs)`)
stimulus-level observations.

## SAMPLE

### Sample Demographics

```{r sample-size}

df <- df_participants

## FOR DESCRIPTIVES PARAGRAPH
# #PROLIFIC
df.p <- df %>% filter(Distribution == "PROLIFIC")
desc.gender.p <- table(df.p$D_gender) %>% prop.table()
names(desc.gender.p) <- levels(df.p$D_gender)
p_participants <- nrow(df.p)

# #TUMBLR
df.t <- df %>% filter(Distribution == "TUMBLR")
desc.gender.t <- table(df.t$D_gender) %>% prop.table()
names(desc.gender.t) <- levels(df.t$D_gender)
t_participants <- nrow(df.t)


```

For study 2, a total of `r p_participants + t_participants` participants
were recruited from US-located English speaking users of TUMBLR (n =
`r t_participants`) and PROLIFIC (n = `r p_participants`).

`r p_participants` individuals from PROLIFIC participated in Study 2, (
`r round(desc.gender.p[["Female"]],2)*100`% Female,
`r round(desc.gender.p[["Male"]],2)*100`% Male,
`r round(desc.gender.p[["Non-binary / third gender"]],2)*100`%
Non-binary,
`r (round((desc.gender.p[["Prefer not to say"]] + desc.gender.p[["Prefer to self-describe"]]),2)) * 100`%
Other).

`r t_participants` individuals from Tumblr participated in Study 2, (
`r round(desc.gender.t[["Female"]],2)*100`% Female,
`r round(desc.gender.t[["Male"]],2)*100`% Male,
`r round(desc.gender.t[["Non-binary / third gender"]],2)*100`%
Non-binary,
`r (round((desc.gender.t[["Prefer not to say"]] + desc.gender.t[["Prefer to self-describe"]]),2)) * 100`%
Other). Note that a higher proportion of participants recruited from
TUMBLR report identities other than cis-gender Female and cis-gender
Male.

### Study Response Time

```{r demo-response-time}

df <- df_participants

## for descriptives paragraph
p.desc.duration <- psych::describe(df %>% filter(Distribution=="PROLIFIC") %>% pull(duration.min))
t.desc.duration <- psych::describe(df %>% filter(Distribution=="TUMBLR") %>% pull(duration.min))

```

PROLIFIC SAMPLE (n = `r p.desc.duration$n` ) participant response times
ranged from `r p.desc.duration$min` to `r p.desc.duration$max` minutes,
with a mean response time of `r round(p.desc.duration$mean,2)` minutes,
SD = `r (round(p.desc.duration$sd,2))`.

TUMBLR SAMPLE (n = `r t.desc.duration$n` ) participant response times
ranged from `r t.desc.duration$min` to `r t.desc.duration$max` minutes,
with a mean response time of `r round(t.desc.duration$mean,2)` minutes,
SD = `r (round(t.desc.duration$sd,2))`.

```{r demo-cleanup}
rm(df, df.p, df.t, p.desc.duration, t.desc.duration, desc.gender.p, desc.gender.t, p_participants, t_participants)
```

```{r setup-full-sample}

#full stimulus-level data
df_full <- df_graphs %>% 
  mutate(
    STUDY = "" #dummy variable for univariate visualizations
  )
# %>%
#   mutate(MAKER_ID = fct_rev(MAKER_ID))

```

## CONFIDENCE

When asking participants to identify the type, age and gender of the
maker of a visualization, we also asked participants to indicate their
confidence in these choices.

**Across all participants and all stimuli, are these (categorical)
questions answered with the same degree of confidence?**

Here we examine both the central tendency (mean) and shape of the
distribution for each confidence variable.

```{r compare-confidence}

df <- df_full %>% select(PID, Distribution, STIMULUS,MAKER_CONF, AGE_CONF, GENDER_CONF, TOOL_CONF) %>% 
  pivot_longer(
    cols = c(MAKER_CONF, AGE_CONF, GENDER_CONF, TOOL_CONF),
    names_to = "QUESTION",
    values_to = "CONFIDENCE"
  ) %>% 
  mutate(
    QUESTION = factor(QUESTION, levels=c("MAKER_CONF","AGE_CONF","GENDER_CONF","TOOL_CONF"  ) )
  ) %>% 
  group_by(QUESTION) %>% 
  mutate(
    m=round(mean(CONFIDENCE),0) #calc mean for showing in plots 
  )


## B
## CONFIDENCE ACROSS QUESTIONS (all stimuli, all Pps)
## BOXPLOT W/ JITTER
B <- df %>% 
  ggplot(aes(x=QUESTION, y= CONFIDENCE)) + 
  geom_boxplot(width = 0.5) + 
  geom_jitter(alpha = 0.25, position=position_dodge2(width = 0.25)) + 
  ## MEAN
    stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size=3,
                 vjust=+0.5, hjust = -1.5, aes( label=round(m, digits=0)))+
    stat_summary(fun=mean, geom="point", size=2, color="blue", fill="blue") +
  theme_minimal() + 
  labs(title = "Confidence by Survey Question", caption = "(mean in blue)")


## R
## CONFIDENCE ACROSS QUESTIONS (all stimuli, all Pps)
## RIDGEPLOT W/ INTERVAL MEAN
R <- df %>% 
  ggplot(aes(x=CONFIDENCE, y=fct_rev(QUESTION), fill=fct_rev(QUESTION))) + 
    geom_density_ridges(scale = 0.65, alpha = 0.75, quantile_lines = TRUE) +
    scale_x_continuous(limits = c(0,100))+
    scale_fill_manual(values = my_palettes(name="questions", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  ## MEAN
    stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size=3,
                vjust=+2.5, hjust = 0.50, aes( label=round(m, digits=0)))+
    stat_summary(fun=mean, geom="point", size=2, color="blue", fill="blue") +
  theme_minimal() + 
  labs(title = "Confidence by Survey Question", y = "QUESTION", caption =" (mean in blue)") + 
  easy_remove_legend()

(B+R)
```

**INTERPRETATION** *Aggregated across all participants and all stimuli,
the average confidence scores for each question (maker id, age, gender,
tool id) are similar, with slightly lower confidence for the GENDER
question. This tells us there is enough variance in response to each
question for the measure to be meaningful, and so we will follow up by
investigating confidence at the STIMULUS level.*

## MAKER ID

Participants were asked:

**Who do you think is most likely responsible for having this image
created?\
***options:* (select one). The response is stored as `MAKER_ID`

-   business or corporation

-   journalist or news outlet

-   educational or academic institution

-   government or political organization

-   other organization

-   an individual]\

Participants were also asked: **Please rate your confidence in this
choice.** The response is stored as `MAKER_CONF` .

```{r maker-id-confidence-full}

#FILTER DATASET
df <- df_full


## D
## MAKER IDENTIFICATION AGGREGATED (all)
## GGSTATSPLOT
##############################
#hack for consistent ordering of ggstats bar plot
dx <- df %>% mutate( MAKER_ID = fct_rev(MAKER_ID) )
S <-   ggbarstats( data = dx, x = MAKER_ID, y = STUDY,
                   legend.title = "MAKER ID") + 
    scale_fill_manual(values = my_palettes(name="reds", direction = "1")) +
    theme_minimal() +
    labs( title = "",  x = "", y="") + 
    theme(aspect.ratio = 1)
##############################


  
## H
## HALF EYE SLAB GGDIST
##############################
H <- df %>% 
  group_by(MAKER_ID) %>% 
  mutate(count = n(), m = mean(MAKER_CONF)) %>% 
  ggplot(aes(y = MAKER_CONF, x = fct_rev(MAKER_ID), fill = fct_rev(MAKER_ID))) + 
  stat_halfeye(scale=0.55, density="bounded", point_interval = "mean_qi", normalize= "all") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2,
               vjust=2.5, hjust = .5, aes( label=round(m, digits=0)))+
  stat_summary(fun=mean, geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label= paste0("n=",count) ,  y = 5), color = "black",
            size = 3, nudge_x=0.35) + 
  labs(y="Maker ID Confidence", x="") + 
  theme_minimal() + 
  easy_remove_legend()+
  coord_flip() 
##############################
  

(p <- (S + H)) + plot_annotation(
  title = "Maker ID and Confidence",
  # subtitle = "the categories of MAKER ID were chosen in similar proportion, 
  # and both the mean (in blue) and shape of distribution of confidence scores is similar across values of Maker ID",
  caption = "(blue indicates mean)"
)

```

**INTERPRETATION** *The distribution of maker types is remarkably
consitent across levels of the `MAKER_ID` variable, with the exception
of 'organization'. Howerver, as 4 of the 6 categories are specific kinds
of organizatations, this is not surprising. The believe this
distribution is likely a function of the diversity of stimuli we
selected. We will address this hypothesis in block-level analysis,
asking whether their is variance in the distribution of `MAKER_ID`
between stimuli. Notably, the confidence scores are similar (both in
mean and shape of distribution) regardless of the `MAKER_ID`, indicating
that in general, there is no particular maker identification for which
participants have less confidence.*

## MAKER AGE

Participants were asked: **Take a moment to imagine the person(s)
responsible for creating the image. What generation are they most likely
from?\
***options: (select one)* The response was saved as `MAKER_AGE`

-   *boomers (60+ years old)*

-   *Generation X (44-59 years old)*

-   *Millennials (28-43 years old)*

-   *Generation Z (12 - 27 years old]*

Participants were asked: **Please rate your confidence in this choice.**
The response is stored as `AGE_CONF` .

```{r maker-age-confidence-full}

#FILTER DATASET
df <- df_full


## D
## MAKER IDENTIFICATION AGGREGATED (all)
## GGSTATSPLOT
##############################
#hack for consistent ordering of ggstats bar plot
dx <- df %>% mutate( MAKER_AGE = fct_rev(MAKER_AGE) )
S <-   ggbarstats( data = dx, x = MAKER_AGE, y = STUDY,
                   legend.title = "MAKER AGE") + 
    scale_fill_manual(values = my_palettes(name="lightblues", direction = "1")) +
    theme_minimal() +
    labs( title = "",  x = "", y="") + 
    theme(aspect.ratio = 1)
##############################


  
## H
## HALF EYE SLAB GGDIST
##############################
H <- df %>% 
  group_by(MAKER_AGE) %>% 
  mutate(count = n(), m = mean(AGE_CONF)) %>% 
  ggplot(aes(y = AGE_CONF, x = fct_rev(MAKER_AGE), fill = fct_rev(MAKER_AGE))) + 
  stat_halfeye(scale=0.55, density="bounded", point_interval = "mean_qi", normalize= "all") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2,
               vjust=2.5, hjust = .5, aes( label=round(..y.., digits=0)))+
  stat_summary(fun=mean, geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="lightblues", direction = "-1"), guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label= paste0("n=",count) ,  y = 5), color = "black",
            size = 3, nudge_x=0.35) + 
  labs(y="Maker AGE Confidence", x="") + 
  theme_minimal() + 
  easy_remove_legend()+
  coord_flip() 
##############################


(p <- (S + H)) + plot_annotation(
  title = "Maker AGE and Confidence",
  # subtitle = "The value
  # distribution of confidence scores is similar across values of Maker AGE",
  caption = "(blue indicates mean)"
)

```

**INTERPRETATION** *The distribution of maker ages is distributed as we
would expect if participants are answering the question with some sense
of the maker's occupation in mind, thus answering with generations that
are mostly likely of working age (gen X, millennial). As with
`MAKER_ID`, confidence scores are similar (both in mean and shape of
distribution) across all levels of `MAKER_AGE`, indicating that in
general, there is no `MAKER_AGE` for which participants have less
confidence.*

## MAKER GENDER

Participants were asked: **Take a moment to imagine the person(s)
responsible for creating the image. What gender do they most likely
identify with?\
***options: [female / male / other ] (select one).* Responses were
stored as `MAKER_GENDER.`

Participants were asked: **Please rate your confidence in this choice.**
The response is stored as `GENDER_CONF` .

```{r maker-gender-confidence-full}

#FILTER DATASET
df <- df_full


## D
## MAKER IDENTIFICATION AGGREGATED (all)
## GGSTATSPLOT
##############################
#hack for consistent ordering of ggstats bar plot
dx <- df %>% mutate( MAKER_AGE = fct_rev(MAKER_AGE) )
S <-   ggbarstats( data = dx, x = MAKER_GENDER, y = STUDY,
                   legend.title = "MAKER GENDER") + 
    scale_fill_manual(values = my_palettes(name="smallgreens", direction = "1")) +
    theme_minimal() +
    labs( title = "",  x = "", y="") + 
    theme(aspect.ratio = 1)
##############################

  
## H
## HALF EYE SLAB GGDIST
##############################
H <- df %>% 
  group_by(MAKER_GENDER) %>% 
  mutate(count = n(), m = mean(GENDER_CONF)) %>% 
  ggplot(aes(y = GENDER_CONF, x = MAKER_GENDER, fill = MAKER_GENDER)) + 
  stat_halfeye(scale=0.55, density="bounded", point_interval = "mean_qi", normalize= "all") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2,
               vjust=2.5, hjust = .5, aes( label=round(..y.., digits=0)))+
  stat_summary(fun=mean, geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="greens", direction = "-1"), guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label= paste0("n=",count) ,  y = 5), color = "black",
            size = 3, nudge_x=0.35) + 
  labs(y="Maker GENDER Confidence", x="") + 
  theme_minimal() + 
  easy_remove_legend()+
  coord_flip() 
##############################

  

(p <- (S + H)) + plot_annotation(
  title = "Maker GENDER and Confidence",
  # subtitle = "The value
  # distribution of confidence scores is similar across values of Maker AGE",
  caption = "(blue indicates mean)"
)

```

**INTERPRETATION:** *The distribution of maker genders is not evenly
distributed between men and women as we might expect. We suspect it is
most likely that the 'male' category serves as a default value for the
maker gender, in the absence of any particular feature of stimulus that
viewers interpret as strongly feminine. This hypothesis is grounded in
the free response data, where respondents tend to explicitly describe
gender in the presence of a design feature consistent with modern
western stereotypes (such us pink indicating feminine, or aggressive
indicating masculine).\
*

## TOOL ID

Participants were asked: **What tools do you think were most likely used
to create this image?\
***options: (select all that apply).* The response was saved as variable
`TOOL_ID` (multi-select)

-   basic graphic design software (e.g. Canva, or similar)

-   advanced graphic design software (e.g. Adobe Illustrator, Figma, or
    similar)

-   data visualization software (e.g. Tableau, PowerBI, or similar)

-   general purpose software (e.g. MS Word/Excel, Google Sheets, or
    similar)

-   programming language (e.g. R, python, javascript, or similar)

Participants were asked: **Please rate your confidence in this choice.**
The response is stored as `TOOL_CONF` .

```{r maker-tool-confidence-full}

#FILTER DATASET
df <- df_tools %>% 
  mutate(
    STUDY = ""
  )


## D
## MAKER IDENTIFICATION AGGREGATED (all)
## GGSTATSPLOT
##############################
#hack for consistent ordering of ggstats bar plot
S <-   ggbarstats( data = df, x = TOOL_ID, y = STUDY,
                   legend.title = "TOOL ID") + 
    scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
    theme_minimal() +
    labs( title = "",  x = "", y="") + 
    theme(aspect.ratio = 1)
##############################



## H
## HALF EYE SLAB GGDIST
##############################
H <-  df %>% 
  group_by(TOOL_ID) %>% 
  mutate(count = n(), m = mean(TOOL_CONF)) %>% 
  ggplot(aes(y = TOOL_CONF, x = TOOL_ID, fill = TOOL_ID)) + 
  stat_halfeye(scale=0.55, density="bounded", point_interval = "mean_qi", normalize= "all") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2,
               vjust=2.5, hjust = .5, aes( label=round(..y.., digits=0)))+
  stat_summary(fun=mean, geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="tools", direction = "1"), guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label= paste0("n=",count) ,  y = 5), color = "black",
            size = 3, nudge_x=0.35) + 
  labs(y="Maker GENDER Confidence", x="", caption="(mean in blue) (median in red)") + 
  theme_minimal() + 
  easy_remove_legend()+
  coord_flip() 
##############################
  

(p <- (S + H)) + plot_annotation(
  title = "TOOL ID and Confidence",
  # subtitle = "The value
  # distribution of confidence scores is similar across values of Maker AGE",
  caption = "(blue indicates mean)"
)
H

```

**INTERPRETATION** *We had no expectations with respect to the
distribution of values in tool identification, but note that are roughly
even across categories (exception of 'unknown' and 'programming'), and
the confidence scores are similar.*

## ENCOUNTER CHOICE

The first question each participant saw in each stimulus block was: **As
you're scrolling through your feed, you see this image. What would you
do?**

options: keep scrolling, pause and look at the image. (select one) The
response was saved as variable `ENCOUNTER`

```{r}
## B
## ENCOUNTER  BY STIMULUS
## GGSTATSPLOT
df_full %>% 
  ggbarstats(  
            x = ENCOUNTER, y = STUDY,
            legend.title = "ENCOUNTER",
            results.subtitle = FALSE) + 
    scale_fill_manual(values = my_palettes(name="encounter", direction = "-1"))+
    theme_minimal() + 
    labs( title = "ENCOUNTER Choice ", subtitle = "", x = "")
```

**INTERPRETATION** *In roughly 10% more trials (participant + stimulus),
participants indicated they would likely engage with the image* *rather
than scroll past it.*

## ACTION CHOICE

The last question participants were asked in each stimulus block was:
**Imagine you encounter the following image while scrolling. Which of
the following are you most likely to do?**

options: (select all that apply). The response was saved as variable
`CHART_ACTION`

-   post a comment

-   share/repost

-   share/repost WITH comment

-   look up more information about the topic or source

-   unfollow/block the source

-   NOTHING—just keep scrolling

```{r}
## B
## ACTION  BY STIMULUS
## GGSTATSPLOT
#hack for consistent ordering of ggstats bar plot
df_actions %>% mutate(
  CHART_ACTION = fct_rev(CHART_ACTION),
  STUDY="") %>% 
  ggbarstats( x = CHART_ACTION, y = STUDY,
            legend.title = "CHART ACTION",
            results.subtitle = FALSE) + 
    # scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
    scale_fill_manual(values = my_palettes(name="actions", direction = "1"))+
    theme_minimal() + 
    labs( title = "ACTION Choice ", subtitle = "", x = "")
    
```

**INTERPRETATION** *A high proportion of participants answered 'nothing'
chart action, which is not surprising given the social media context. I
am surprised to see such a high proportion answering that they would
seek further information!*

## PLATFORM CHOICE

Before starting the experimental blocks, participants were asked:
**Please choose a social media platform to imagine you are engaging with
during this study**

options: (select one). The response was saved as variable `PLATFORM`

-   Twitter/X, Tumblr

-   LinkedIn

-   Instagram

-   Facebook

```{r}
## B
## PLATFORM  BY STIMULUS
## GGSTATSPLOT
#hack for consistent ordering of ggstats bar plot
df_full %>% 
  ggbarstats(  
            x = PLATFORM, y = STUDY,
            legend.title = "PLATFORM",
            results.subtitle = FALSE) + 
    scale_fill_manual(values = my_palettes(name="platforms", direction = "-1"))+
    theme_minimal() + 
    labs( title = "PLATFORM Choice ", subtitle = "", x = "")
    
```

**INTERPRETATION** *We had no expectations about the distribution of
social media platform.*

## SEMANTIC DIFFERENTIALS

Participants were also asked to rate certain characteristics of the
chart, or its maker, along a **semantic differential scale**,
implemented in Qualtrics as a continuous slider ranging from 0 -\> 100
with biploar adjectives at the end of each scale. The slider defaulted
to the center point (50), and the interface displayed the numeric value
of the slider position as a tooltip while the element had focus. Note
that on both touch and mouse devices participants could interact with
the survey element as a slider (i.e. click and and drag, or touch and
drag) *or* as a visual analogue scale (i.e. click or tap on position
along the scale).

### Full Scales

*The SD scores visualized here are in the same form as the participants'
response scale (slider from 0-100).*

#### AGGREGATED 

##### boxplot
```{r plot_boxplot_sds, fig.width=10, fig.height=14}

  #### LIST OF BLOXPLOTS + JITTER #############################################################################

  # setup dataframe 
  df <- df_graphs 
  
  #subset data cols 
  cols <- df %>% select( all_of(ref_sd_questions))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type ="S", mean=TRUE, facet = FALSE, boxplot=TRUE))
  
  #aggregate q plots into one for stimulus 
  plot_master_questions <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
   plot_annotation(
     title = "ALL STIMULI",
     subtitle ="", caption = "(point is mean)"
   )
  
if(graph_save == TRUE){  
  ggsave(plot = plot_master_questions, path="figs/level_aggregated/distributions", filename =paste0("combined_stimuli","_box.png"), units = c("in"), width = 10, height = 14  )
}

print(plot_master_questions)
  
```  
  
##### ggdist halfeye
```{r plot_halfeye_sds}



  #### GGDIST PLOT#############################################################################
  
  # setup dataframe 
  df <- df_sd_questions_long %>% select(1:8, QUESTION, STIMULUS_CATEGORY, value) 
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
               category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
  (g <- d %>%
      ggplot(aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 90, y= ref_sd_questions,size = 8, vjust=-2) +
  labs (title = "ALL STIMULI", y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
)

  if(graph_save == TRUE){ 
  ggsave(plot = g, path="figs/level_aggregated/distributions", filename =paste0("combined_stimuli","_ggdist.png"), units = c("in"), width = 10, height = 14  )
  }
  

```

##### density ridges
```{r plot_ridglines_sds}
  
#### DENSITY RIDGES#############################################################################
  # setup dataframe 
  df <- df_sd_questions_long %>% select(1:8, QUESTION, value)  
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions))%>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph
  
  
(x <-
    ggplot(d, aes(x = value, y = fct_rev(QUESTION), fill = category)) +
    geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.75, panel_scaling = TRUE) + 
    # scale_fill_manual(values = my_palettes(name="amy_gradient", direction = "1"))+ 
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+ 
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    # scale_x_continuous(limits = c(0,100))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
    labs (title = "ALL STIMULI", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions, x = 100, y= ref_sd_questions,size = 8, vjust=-2, position=position_nudge(y=-.20))  + ##raw
    # cowplot::draw_text(text = ref_sd_questions, x = -4, y= ref_sd_questions,size = 10, vjust=-2) + ##z-score
    theme_minimal() + easy_remove_legend()
)

if(graph_save == TRUE) {
    ggsave(plot = x, path="figs/level_aggregated/distributions", filename =paste0("combined_stimuli","_ridges.png"), units = c("in"), width = 10, height = 14  )
}


```    
  

#### BY STIMULUS CATEGORY
```{r sd-densities-category}  
  
#### GROUPED DENSITY RIDGES#############################################################################
  # setup dataframe 
  df <- df_sd_questions_long %>% select(1:8, QUESTION, STIMULUS_CATEGORY, value)  
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions),
          STIMULUS_CATEGORY = factor(STIMULUS_CATEGORY, levels = c("A","B","C","D","F")))%>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph
  
  
(  c <-ggplot(d, aes(x = value, y = fct_rev(QUESTION), fill=STIMULUS_CATEGORY))+ 
    geom_density_ridges(scale = 0.75, alpha = 0.5, panel_scaling = TRUE) +
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=-0.5, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=1) +
    facet_grid2(.~STIMULUS_CATEGORY)+
    # geom_density_ridges(scale = 1, quantile_lines = TRUE, alpha = 0.25) 
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
    labs(title = "by STIMULUS CATEGORY", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions, x = 40, y= ref_sd_questions, size = 6, vjust=2) + ##raw
    # # cowplot::draw_text(text = ref_sd_questions, x = -4, y= ref_sd_questions,size = 10, vjust=-2) + ##z-score
    theme_minimal() + easy_remove_legend()
)
  
if(graph_save){
    ggsave(plot = c, path="figs/level_aggregated/distributions", filename =paste0("combined_by_category","_ridges.png"), units = c("in"), width = 10, height = 14  )
}  


```

```{r plot-sd-cleanup}
rm(df, c,x,g,plot_master_questions)
```

### Absolute Values

*Here the scale of the semantic differential questions have been
collapsed, such that 0 is the midpoint of the scale (indicating
uncertainty, or not strongly indicating either of the labelled traits)
and both 100 and 0 are 50 (indicating a strong signal toward either of
the labelled traits).*

#### AGGREGATED 

##### boxplot
```{r ALL-Q-COLLAPSED-ABS, fig.width=10, fig.height=14}

  
  #### LIST OF BLOXPLOTS + JITTER #############################################################################

  # setup dataframe 
  df <- df_graphs_abs 
  
  #subset data cols 
  cols <- df %>% select( all_of(ref_sd_questions_abs))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type ="S", mean=TRUE, facet = FALSE, boxplot=TRUE))
  
  #aggregate q plots into one for stimulus 
plot_master_questions <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
   plot_annotation(
     title = "ALL STIMULI — SD (ABSOLUTE VALUE)",
     subtitle ="", caption = "(point is mean)"
   )

  
if(graph_save == TRUE){
  ggsave(plot = plot_master_questions, path="figs/level_aggregated/distributions", filename =paste0("ABS_combined_stimuli","_box.png"), units = c("in"), width = 10, height = 14  )
}
  
  print(plot_master_questions)
  
```
  
##### ggdist halfeye  
```{r plot_ggdist_sd_abs}
  
  #### GGDIST PLOT#############################################################################
  
  # setup dataframe 
  df <- df_sd_questions_long_abs %>% select(1:8, QUESTION, STIMULUS_CATEGORY, value) 
  d <- left_join( x = df, y = ref_labels_abs, 
                  by = c("QUESTION" = "ref_sd_questions_abs")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions))%>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
(  g <- ggplot(d, aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 45, y= ref_sd_questions_abs,size = 8, vjust=-2) +
  labs (title = "ALL STIMULI — SD (ABSOLUTE VALUE)", y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
) 

if(graph_save == TRUE){
  ggsave(plot = g, path="figs/level_aggregated/distributions", filename =paste0("ABS_combined_stimuli","_ggdist.png"), units = c("in"), width = 10, height = 14  )
}
  
```


##### density ridges
```{r plot_ridges_sd_abs}
  
  #### DENSITY RIDGES#############################################################################
  # setup dataframe 
  df <- df_sd_questions_long_abs %>% select(1:8, QUESTION, value)  
  d <- left_join( x = df, y = ref_labels_abs, 
                  by = c("QUESTION" = "ref_sd_questions_abs")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions))%>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph
  
  
(  x <-ggplot(d, aes(x = value, y = fct_rev(QUESTION), fill = category)) +
    geom_density_ridges(scale = 0.9,quantile_lines = TRUE, alpha = 0.75) + 
    # scale_fill_manual(values = my_palettes(name="amy_gradient", direction = "1"))+ 
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+ 
      stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
    labs(title = "ALL STIMULI — SD (ABSOLUTE VALUE)", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions, x = 45, y= ref_sd_questions_abs, size = 8, vjust=-2, position=position_nudge(y=-.20))  + ##raw
    theme_minimal() + easy_remove_legend()
)

if(graph_save == TRUE){
    ggsave(plot = x, path="figs/level_aggregated/distributions", filename =paste0("ABS_combined_stimuli","_ridges.png"), units = c("in"), width = 10, height = 14  )
}
  
```    
#### BY STIMULUS CATEGORY


```{r plot_grouped_ridges_abs}
  #### GROUPED DENSITY RIDGES#############################################################################
  # setup dataframe 
  df <- df_sd_questions_long_abs %>% select(1:8, QUESTION, STIMULUS_CATEGORY, value)  
  d <- left_join( x = df, y = ref_labels_abs, 
                  by = c("QUESTION" = "ref_sd_questions_abs")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions),
          STIMULUS_CATEGORY = factor(STIMULUS_CATEGORY, levels = c("A","B","C","D","F")))%>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph
  
  
(  c <-ggplot(d, aes(x = value, y = fct_rev(QUESTION), fill=STIMULUS_CATEGORY))+ 
    geom_density_ridges(scale = 0.75, alpha = 0.5, panel_scaling = TRUE) +
    facet_grid2(.~STIMULUS_CATEGORY)+
     ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=-0.5, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=1) +
    # geom_density_ridges(scale = 1, quantile_lines = TRUE, alpha = 0.25) 
    guides(
      y = guide_axis_manual(labels = rev(ref_labels_abs$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels_abs$right))
    ) +
    labs(title = "by STIMULUS CATEGORY (absolute value)", y = "") +
    cowplot::draw_text(text = ref_sd_questions_abs, x = 20, y= ref_sd_questions_abs, size = 6, vjust=2) + ##raw
    theme_minimal() + easy_remove_legend()
)

if(graph_save == TRUE){
    ggplot2::ggsave(plot = c, path="figs/level_aggregated/distributions", filename =paste0("ABS_combined_by_category","_ridges.png"), units = c("in"), width = 10, height = 14  )
}

```

```{r plot-sd-abs-cleanup}
rm(df, c,x,g,plot_master_questions)
```

## CORRELATIONS

### correlation matrices — semantic differential

```{r, correlation-matrices}


df <- df_graphs %>% select(
          MAKER_DESIGN, MAKER_DATA, 
          MAKER_POLITIC, MAKER_ARGUE,
          MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
          CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
          PID)

print("FULL CORRELATION NO RANDOM EFFECT")
## CALCULATE full correlations with no random effects
c <- df %>%  correlation(partial=FALSE, include_factors=FALSE)
(s <- c %>% summary(redundant = FALSE))
plot(s, show_data="point") + labs(title = "Correlation Matrix",
               subtitle="(full correlation; pearson method; Holm p-value adjustment)") + theme_minimal()



print("PARTIAL CORRELATION WITH PID AS RANDOM EFFECT")
#CALCULATE partial correlations with PID as random effect
## (this isolates correlation pairwise factoring out other variables)
c <- df %>% correlation(partial=TRUE,multilevel = TRUE)
(s <- c %>% summary(redundant = FALSE ))


###### VIS WITH CORRELATION PACKAGE
#SEE [correlation] PLOT
g <- plot(s, show_data = "point",   show_text = "label",
     stars=TRUE, show_legend=FALSE,
     show_statistic = FALSE, show_ci = FALSE) + 
     theme_minimal()+
     labs(title = "Correlation Matrix — SD Questions", 
          subtitle="(partial correlation; pearson method; Holm p-value adjustment; participant as random effect)")
     # text = list(fontface = "italic")
g
ggsave(g, scale =1, filename = "figs/level_aggregated/heatmaps/partial_correlation_all.png", width = 14, height = 6, dpi = 320, limitsize = FALSE)

#PLOT GAUSSIAN GRAPH MODEL
# plot(c)


###### VIS WITH CORRPLOT <- -- customizable but can't save to file ARGH

## GET THE MATRIX
m <- as.matrix(c)


## JUST CIRCLES
corrplot(m, method = 'circle', type = 'lower',
         order = 'original', diag = FALSE, addCoef.col = "#7A7A7A",
         tl.col = "black")






```

These plots depict the PARTIAL CORRELATION pairwise between variables
(partial correlation factors out influence of other variables), with
participant ID as a random effect. The resulting values are pearson
moment-correlation coefficients ranging of -1 (direct negative) to +1
direct positive correlation. These correlations are calculated on the
full scale semantic differential questions (i.e. with the 0 - 100 range,
where 1 and 100 are end points and 50 is the central point)

### correlation matrices — semantic differential — absolute values

```{r, correlation-matrices—abs}


df <- df_graphs_abs %>% select(
          MAKER_DESIGN, MAKER_DATA, 
          MAKER_POLITIC, MAKER_ARGUE,
          MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
          CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
          PID)

print("FULL CORRELATION NO RANDOM EFFECT")
## CALCULATE full correlations with no random effects
c <- df %>%  correlation(partial=FALSE, include_factors=FALSE)
(s <- c %>% summary(redundant = FALSE))
plot(s, show_data="point") + labs(title = "Correlation Matrix",
               subtitle="(full correlation; pearson method; Holm p-value adjustment)") + theme_minimal()


print("PARTIAL CORRELATION WITH PID AS RANDOM EFFECT")
#CALCULATE partial correlations with PID as random effect
## (this isolates correlation pairwise factoring out other variables)
c <- df %>% correlation(partial=TRUE, multilevel = TRUE)
(s <- c %>% summary(redundant = FALSE ))


###### VIS WITH CORRELATION PACKAGE
#SEE [correlation] PLOT
g <- plot(s, show_data = "point",   show_text = "label",
     stars=TRUE, show_legend=FALSE,
     show_statistic = FALSE, show_ci = FALSE) + 
     theme_minimal()+
     labs(title = "Correlation Matrix — SD Questions — absolute values", 
          subtitle="(partial correlation; pearson method; Holm p-value adjustment; participant as random effect)")
     # text = list(fontface = "italic")
g
ggsave(g, scale =1, filename = "figs/level_aggregated/heatmaps/partial_correlation_abs.png", width = 14, height = 6, dpi = 320, limitsize = FALSE)

#PLOT GAUSSIAN GRAPH MODEL
# plot(c)


###### VIS WITH CORRPLOT <- -- customizable but can't save to file ARGH

## GET THE MATRIX
m <- as.matrix(c)


## JUST CIRCLES
corrplot(m, method = 'circle', type = 'lower',
         order = 'original', diag = FALSE, addCoef.col = "#7A7A7A",
         tl.col = "black")

```

**INTERPRETATION** *These plots depict the PARTIAL CORRELATION pairwise between variables
(partial correlation factors out influence of other variables), with
participant ID as a random effect. The resulting values are pearson
moment-correlation coefficients ranging of -1 (direct negative) to +1
direct positive correlation. These correlations are calculated on the
ABSOLUTE VALUE of the semantic differential questions (i.e. with the
full scale folded in half, such that 50 now becomes 0, and the extrememe
values (0, 100) become 50). The absolute value scale allows us to
collapse for weak (near zero) vs. strong (near 50) signal in each
variable.*

### correlation matrices — by category levels

*Here we explore the distribution of each SD variable (e.g. MAKER TRUST)
by the different values of each categorical variable (e.g. MAKER ID).
Patterns of interest are noted, which we explore further in the section
**exploratory questions**.*

##### MAKER ID X SD

```{r, maker_id-sds}


df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

## CORRELATION MATRIX SPLIT BY MAKER ID  
(x <-   ggscatmat(df, columns = 1:11, color = "MAKER_ID", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="reds", direction = "1"), name = "",  guide = guide_legend(reverse = FALSE)) +   
    theme_minimal()
)
if(graph_save){
ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("maker_id_corr_sd.png"), units = c("in"), width = 14, height = 10 )
}

x


```

**Interesting patterns to explore further**

-   When participants identify the maker as an INDIVIDUAL, the following
    variables show a different pattern than the other identifications:
    MAKER_DESIGN, MAKER_DATA, CHART INTENT
-   interesting bimodal distribution on CHART INTENT for most
    identifications, except individuals and organizations

##### MAKER ID X SD (abs)

```{r, maker_id-sds-abs}


df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

## CORRELATION MATRIX SPLIT BY MAKER ID  
(x <-   ggscatmat(df, columns = 1:11, color = "MAKER_ID", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="reds", direction = "1"), name = "",  guide = guide_legend(reverse = FALSE)) +   
    theme_minimal())
    
if(graph_save){
ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("maker_id_corr_abs.png"), units = c("in"), width = 14, height = 10 )
}
x

```

##### MAKER AGE X SD

```{r, maker_age-sds}


  df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)
  
  ## CORRELATION MATRIX SPLIT BY MAKER AGE  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_AGE", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="lightblues", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal())
    
if(graph_save){    
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("maker_age_corr_sd.png"), units = c("in"), width = 14, height = 10 )
}
x  

```

**Interesting patterns to explore further**

-   maker_design, chart_like, chart_beauty for BOOMER vs. others
-   maker_data for gen Z vs others

##### MAKER AGE X SD (abs)

```{r, maker_age-sds-abs}

  
  df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

  ## CORRELATION MATRIX SPLIT BY MAKER AGE  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_AGE", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="lightblues", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal())
    
if(graph_save){
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("maker_age_corr_abs.png"), units = c("in"), width = 14, height = 10 )
}
x

```

##### MAKER GENDER X SD

```{r, maker_gender-sds}

  
  df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)
  
  ## CORRELATION MATRIX SPLIT BY MAKER GENDER  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_GENDER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="smallgreens", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal() )
    
    if(graph_save){
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("maker_gender_corr_sd.png"), units = c("in"), width = 14, height = 10 )
  }
  x

```

**Interesting patterns to explore further** - maker-data for FEMALE

##### MAKER GENDER X SD (abs)

```{r, maker_gender-sds-abs}

  
  df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                           PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                           MAKER_ID, MAKER_AGE, MAKER_GENDER)

  
  ## CORRELATION MATRIX SPLIT BY MAKER GENDER  
  (x <-   ggscatmat(df, columns = 1:11, color = "MAKER_GENDER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="smallgreens", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
    theme_minimal() )

if(graph_save){
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("maker_gender_corr_abs.png"), units = c("in"), width = 14, height = 10 )
}
  x

```

##### TOOL ID X SD

```{r, tool-id-sds}

  
df <- df_tools %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    TOOL_ID) 
  
  ## CORRELATION MATRIX SPLIT BY TOOL ID
 (x <-  ggscatmat(df, columns = 1:11, color = "TOOL_ID", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="tools", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +
    theme_minimal() )
  
  if(graph_save){
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("tool_id_corr_sd.png"), units = c("in"), width = 14, height = 10 )
  }    
  x

```

**Interesting patterns to explore further** - maker data for
design-basic, interesting pattern - look closer at chart beauty -
interesting pattern across values on chart intent

##### ENCOUNTER X SD

```{r, encounter-sds}

  

df <- df_graphs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    ENCOUNTER) %>% 
    mutate(ENCOUNTER = fct_rev(ENCOUNTER))

## CORRELATION MATRIX SPLIT BY ENCOUNTER
(x <-   ggscatmat(df, columns = 1:11, color = "ENCOUNTER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="encounter", direction = "1"))+
    theme_minimal())
if(graph_save){
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("encounter_corr_sd.png"), units = c("in"), width = 14, height = 10 )
}
  x
  
  
```

**Interesting patterns to explore further** — no difference at ALL in
maker data - interesting! - chart beauty very diff - chart intent
intersting bimodal

##### ENCOUNTER X SD (abs)

```{r, encounter-sds-abs}

  

df <- df_graphs_abs %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    ENCOUNTER) %>% 
    mutate(ENCOUNTER = fct_rev(ENCOUNTER))

## CORRELATION MATRIX SPLIT BY ENCOUNTER
(x <-   ggscatmat(df, columns = 1:11, color = "ENCOUNTER", alpha = 0.8) + 
    scale_color_manual(values = my_palettes(name="encounter", direction = "1"))+
    theme_minimal())

if(graph_save){
  ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("encounter_corr_abs.png"), units = c("in"), width = 14, height = 10 )
}
  x
  
  
```

##### CHART ACTION X SD

```{r, chart-action-sds}

  

df <- df_actions %>% select(MAKER_DESIGN, MAKER_DATA, 
                           MAKER_POLITIC, MAKER_ARGUE, MAKER_SELF, MAKER_ALIGN, MAKER_TRUST, 
                           CHART_TRUST, CHART_INTENT, CHART_LIKE, CHART_BEAUTY, 
                    PID, STIMULUS, BLOCK, STIMULUS_CATEGORY, 
                    CHART_ACTION) 
  
  ## CORRELATION MATRIX SPLIT BY CHART ACTION
(x <- ggscatmat(df, columns = 1:11, color = "CHART_ACTION", alpha = 0.2) + 
    scale_color_manual(values = my_palettes(name="actions", direction = "1"), name = "",  guide = guide_legend(reverse = TRUE)) +
    theme_minimal() )
if(graph_save){
ggsave(plot = x, path="figs/level_aggregated/pairplots", filename =paste0("chart_action_corr_sd.png"), units = c("in"), width = 14, height = 10  )
}
x


```

**Interesting patterns to explore further** - unfollow/block across all!

## EXPLORATORY QUESTIONS

-   When participants identify the maker as an INDIVIDUAL, the following
    variables show a different pattern than the other identifications:
    MAKER_DESIGN, MAKER_DATA, CHART INTENT
-   interesting bimodal distribution on CHART INTENT for most
    identifications, except individuals and organizations
    
#### DATA AND DESIGN BY CATEGORY and BLOCK



#### visualization 

```{r}

df <- df_graphs %>% 
  mutate(
    ## reverse order of MAKER_DATA, because scale ranged from 0=expert to 100=layperson
    ## we want the reverse 
    ## chose NOT to z-score data, bc we want the data in terms of the original scale 
    r_MAKER_DATA = reverse_scale(MAKER_DATA),
    STIMULUS_CATEGORY = fct_rev(STIMULUS_CATEGORY)
  ) %>% filter(STIMULUS!="B0-0")




```

#### models

```{r model-DATA-BY-CATEGORY}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs %>% 
  mutate(
    ## reverse order of MAKER_DATA, because scale ranged from 0=expert to 100=layperson
    ## we want the reverse 
    ## chose NOT to z-score data, bc we want the data in terms of the original scale 
    r_MAKER_DATA = reverse_scale(MAKER_DATA),
    STIMULUS_CATEGORY = fct_rev(STIMULUS_CATEGORY)
  ) %>% filter(STIMULUS!="B0-0")

## SET CONTRASTS
# contrasts(df$MAKER_ID) <-car::contr.Treatment(levels(df$MAKER_ID)) # intercept first group mean; coeff dif from first

## DEFINE MODEL
mr1 <-lmer(r_MAKER_DATA ~  (1|PID) , data=df)
mr2 <-lmer(r_MAKER_DATA ~  (1|PID) + (1|STIMULUS), data=df)
mm1 <-lmer(r_MAKER_DATA ~  STIMULUS +  (1|PID) , data=df)
mm2 <-lmer(r_MAKER_DATA ~  STIMULUS_CATEGORY +  (1|PID) , data=df)
mm3 <-lmer(r_MAKER_DATA ~  STIMULUS_CATEGORY*BLOCK +  (1|PID) , data=df)


compare_performance(mr1, mr2, mm1,mm2,mm3, rank=TRUE)
f <- "MAKER_DATA ~ STIMULUS_CATEGORY * BLOCK + (1|PID)"
report(mm3)
anova(mm3)

## PLOT MODEL PREDICTIONS
(p_data <- cat_plot(mm3, pred = BLOCK, modx = STIMULUS_CATEGORY,
         geom = "line", interval.geom= "linerange", 
         interval=TRUE, int.type = "confidence", int.width = 0.95, robust = TRUE,
         plot.points = FALSE) + 
    facet_wrap(~STIMULUS_CATEGORY) + 
    labs(title = "LMER Predictions | MAKER_DATA by BLOCK X CATEGORY", 
         caption = f, 
         y="MAKER_DATA \n 0(layerpson) --> 100 (professional)") + easy_remove_legend()
)

if(graph_save){
  ggsave(plot = p_data, path="figs/level_aggregated/models", filename =paste0("lmer_makerdata_by_stimulus_category","_ixn.png"), units = c("in"))
}


## PLOT MODEL PARAMETERS
plot_model(mm3, type = "est",
        # show.intercept = TRUE,
        show.values = TRUE,
        value.offset = .25,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)
```
**INTERPRETATION** *Here we see that a linear mixed effects model, predicting MAKER_DATA by the combination of STIMULUS_CATEGORY and BLOCK indicates that ratings of maker data competencies do NOT vary consistently as a function of CATEGORY (i.e. the degree of 'embellishment').  Although the degree of embellishment within a block (A,B,C,D) is the same, the ratings of maker data competency vary. This pattern is particularly salient in categories C and D (with more embellishment).  These data suggest that social inferences about a maker's data competency are not made solely based on the amount of embellishment, but rather, in response to the particular features of the visualization.  A highly embellished chart might be rated with relatively high high data competency (e.g. B3-D) or lower data competency (eg. B5-D).* 


```{r model-DESIGN-BY-CATEGORY}

df <- df_graphs %>% 
  mutate(
    ## reverse order of MAKER_DATA, because scale ranged from 0=expert to 100=layperson
    ## we want the reverse 
    ## chose NOT to z-score data, bc we want the data in terms of the original scale 
    r_MAKER_DESIGN = reverse_scale(MAKER_DESIGN),
    STIMULUS_CATEGORY = fct_rev(STIMULUS_CATEGORY)
  ) %>% filter(STIMULUS!="B0-0")

## SET CONTRASTS
# contrasts(df$MAKER_ID) <-car::contr.Treatment(levels(df$MAKER_ID)) # intercept first group mean; coeff dif from first

## DEFINE MODEL
mr1 <-lmer(r_MAKER_DESIGN ~ (1|PID) , data=df)
mr2 <-lmer(r_MAKER_DESIGN ~ (1|PID) + (1|STIMULUS), data=df)
mm1 <-lmer(r_MAKER_DESIGN ~ STIMULUS +  (1|PID) , data=df)
mm2 <-lmer(r_MAKER_DESIGN ~ STIMULUS_CATEGORY +  (1|PID) , data=df)
mm3 <-lmer(r_MAKER_DESIGN ~ STIMULUS_CATEGORY*BLOCK +  (1|PID) , data=df)


compare_performance(mr1, mr2, mm1,mm2,mm3, rank=TRUE)
f <- "MAKER_DESIGN ~ STIMULUS_CATEGORY * BLOCK + (1|PID)"
report(mm3)
anova(mm3)

(p_design <- cat_plot(mm3, pred = BLOCK, modx = STIMULUS_CATEGORY,
         geom = "line", interval.geom= "linerange", 
         interval=TRUE, int.type = "confidence", int.width = 0.95, robust = TRUE,
         plot.points = FALSE) + 
    facet_wrap(~STIMULUS_CATEGORY) + 
    labs(title = "LMER Predictions | MAKER_DESIGN by BLOCK X CATEGORY", 
         caption = f, 
         y="MAKER_DESIGN \n 0(layerpson) --> 100 (professional)") + easy_remove_legend()
)

if(graph_save){
  ggsave(plot = p_design, path="figs/level_aggregated/models", filename =paste0("lmer_makerdesign_by_stimulus_category","_ixn.png"), units = c("in"))
}



## PLOT MODEL PARAMETERS
plot_model(mm3, type = "est",
        # show.intercept = TRUE,
        show.values = TRUE,
        value.offset = .25,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)

```
**INTERPRETATION** *Here we see that a linear mixed effects model, predicting MAKER_DESIGN by the combination of STIMULUS_CATEGORY and BLOCK indicates that ratings of maker design competencies do NOT vary consistently as a function of CATEGORY (i.e. the degree of 'embellishment').  Although the degree of embellishment within a block (A,B,C,D) is the same, the ratings of maker design competency vary. This pattern is particularly salient in category C.  These data suggest that social inferences about a maker's design competency are not made solely based on the amount of embellishment, but rather, in response to the particular features of the visualization.  A highly embellished chart might be rated with relatively high design competency (e.g. B2-C) or lower data competency (eg. B5-C).*



    
    
    
### TOOL ID & DATA COMPETENCY    
    
```{r vis-tool-id-data, warning=FALSE}

df <- df_tools

## Does DATA COMPETENCY  depend on TOOL ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$TOOL_ID)
left <- rep(ref_labels['MAKER_DATA','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_DATA','right'],  length(levels(df$MAKER_ID)))

df %>% 
    group_by(TOOL_ID) %>% 
    mutate(
      md=median(MAKER_DATA),
      m=mean(MAKER_DATA),
      count = n()
    ) %>% droplevels() %>% 
  ggplot(aes(y = TOOL_ID, x= MAKER_DATA, fill = TOOL_ID)) + 
  # scale_x_continuous(limits = c(0,100))+
  # geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) +
  stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="groups") +
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "median_qi") +
  ##MEDIAN
  stat_summary(fun=median, geom="text", colour="red",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(md, digits=0)))+
  stat_summary(fun=median, geom="point", shape=20, size=3, color="red", fill="red") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(m, digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="tools", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = TOOL_ID, x = 5), color = "black",size = 3, nudge_y = 0.3) +
  cowplot::draw_text(text = toupper(answers), x = 80, y= answers, size = 10, vjust=-2, hjust=0) +
  labs (title = "DATA COMPETENCY by TOOL ID", y = "", x = "MAKER DATA COMPETENCY", caption="(mean in blue) (median in red)") +
  theme_minimal() + easy_remove_legend()

```    
#### model 




```{r}

df <- df_tools %>% 
  mutate(
    ## reverse order of MAKER_DATA, because scale ranged from 0=expert to 100=layperson
    ## we want the reverse 
    ## chose NOT to z-score data, bc we want the data in terms of the original scale 
    r_MAKER_DATA = reverse_scale(MAKER_DATA),
    STIMULUS_CATEGORY = fct_rev(STIMULUS_CATEGORY)
  ) %>% filter(STIMULUS!="B0-0")

## SET CONTRASTS
# contrasts(df$MAKER_ID) <-car::contr.Treatment(levels(df$MAKER_ID)) # intercept first group mean; coeff dif from first

## DEFINE MODEL
lm5 <-lmer(r_MAKER_DATA ~ TOOL_ID + STIMULUS_CATEGORY*BLOCK +  (1|PID) , data=df)

# ## PRINT MODEL 
# (m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(lm5)
anova(lm5)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        # show.intercept = TRUE,
        show.values = TRUE,
        value.offset = .25,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("TOOL_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="TOOL_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$TOOL_ID, y=means$Mean, label=round(means$Mean,2)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption =f, y="predicted MAKER DATA COMPETENCY \n (0=layperson, 100=expert)")

##prediced data 
plot_model(m1, type = "eff", terms = "TOOL_ID", show.p = TRUE,
           show.values = TRUE, auto.label = TRUE)

```

```{r}
### JK DO QUANTILE REGRESSION AT THE MEDIAN 
library(qrLMM)



## tau is the quantile on which to run the model 
m2 <-df %>% QRLMM( 
              y = r_MAKER_DATA, 
          r_MAKER_DATA ~ TOOL_ID, 
           random = ~ 1,
           group = PID,
           data=df, tau = 0.5)



summary(m2)
plot_model(m1)

```





### MAKER ID & Maker DATA COMPETENCY

```{r vis-maker-id-data, warning=FALSE}

df <- df_graphs 

## Does MAKER_DATA  depend on MAKER ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_DATA','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_DATA','right'],  length(levels(df$MAKER_ID)))

df %>% 
    group_by(MAKER_ID) %>% 
    mutate(
      md=median(MAKER_DATA),
      m=mean(MAKER_DATA),
      count = n()
    ) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_DATA, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  ##MEDIAN
  stat_summary(fun=median, geom="text", colour="red",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(md, digits=0)))+
  stat_summary(fun=median, geom="point", shape=20, size=3, color="red", fill="red") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(m, digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "DATA COMPETENCY by MAKER ID", y = "", x = "MAKER DATA COMPETENCY", caption="(mean in blue) (median in red)") +
  theme_minimal() + easy_remove_legend()

```

#### (YES) model

```{r model-maker-id-data}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## SET CONTRASTS
contrasts(df$MAKER_ID) <-car::contr.Treatment(levels(df$MAKER_ID)) # intercept first group mean; coeff dif from first

## DEFINE MODEL
f <- "MAKER_DATA ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_DATA ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        value.offset = .25,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```

### Maker ID & Maker DESIGN COMPETENCY

```{r}

df <- df_graphs

## Does MAKER_DESIGN  depend on MAKER ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_DESIGN','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_DESIGN','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(
    count = n(), 
    m = mean(MAKER_DESIGN),
    md = median(MAKER_DESIGN)
    ) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_DESIGN, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  ##MEDIAN
  stat_summary(fun=median, geom="text", colour="red",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(md, digits=0)))+
  stat_summary(fun=median, geom="point", shape=20, size=3, color="red", fill="red") +
  ##MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(m, digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "DESIGN COMPETENCY by MAKER ID", y = "", x = "MAKER DESIGN COMPETENCY", caption="(mean in blue) (median in red)") +
  theme_minimal() + easy_remove_legend()

```

#### (YES) model

```{r model-maker-id-design}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## DEFINE MODEL
f <- "MAKER_DESIGN ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_DESIGN ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```

-   maker_design, chart_like, chart_beauty for BOOMER vs. others

-   maker_data for gen Z vs others

-   maker-data for FEMALE

-   maker data for design-basic, interesting pattern

-   look closer at chart beauty

-   interesting pattern across values on chart intent

— no difference at ALL in maker data - interesting! - chart beauty very
diff - chart intent intersting bimodal

### Maker ID & Maker POLITICS

\*\*Is there an association between MAKER ID and MAKER POLITICS? We
hypothesize that when the MAKER ID is identified as POLITICAL, the MAKER
POLITICS score will be more strongly associated with either ends of the
semantic differential scale (ie. left leaning or right leaning). We
expect this to not be the case with the other MAKER ID values.

To test this hypothesis, we will model MAKER_ID as a predictor of
MAKER_POLITICS_ABS (the absolute value of the collapsed maker politics
sd scale), where 0 = the midpoint of the original scale, and 50 = both
the 0 and 100 pts of the original scale

```{r, message=FALSE}

df <- df_graphs_abs

## Does MAKER POLITICS depend on MAKER ID?
##RIDGEPLOT w/ MEAN 
answers <- levels(df$MAKER_ID)
left <- rep(ref_labels_abs['MAKER_POLITIC','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels_abs['MAKER_POLITIC','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(
    count = n(),
    m = mean(MAKER_POLITIC),
    md = median(MAKER_POLITIC)
  ) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_POLITIC, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,50))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  ##MEDIAN
  stat_summary(fun=median, geom="text", colour="red",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(md, digits=0)))+
  stat_summary(fun=median, geom="point", shape=20, size=3, color="red", fill="red") +
  ##MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(m, digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 50), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "POLITICS (absolute value) by MAKER ID", y = "", x = "MAKER POLITICS", caption="(mean in blue) (median in red)") +
  theme_minimal() + easy_remove_legend()

```

Once the MAKER_POLITICS score has been collapsed to the SD scale, we see
that our hypothesis is likely false, as the mean (absolute value)
maker_politics scores are nearly the same for individual, organization
and politics, with only news, education and business being slighly more
neutral.

#### (NO) model

```{r model-maker-id-politics}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs_abs

## DEFINE MODEL
f <- "MAKER_POLITIC ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_POLITIC ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```

The results of the model confirm our suspicion that our hypothesis is
not supported by the data. MAKER_ID is not a strong predictor of
MAKER_POLITICS (absolute value). Post-hoc contrasts demonstrate that the
mean values of some levels are significantly different (e.g individual
v. education, organization v. education, education v. political) however
the overall model does not indicate a good fit.

### Maker ID & Maker TRUST

\*\*Do people indicate higher TRUST in artifacts they attribute to
EDUCATION type makers?

```{r}

df <- df_graphs

## Does MAKER_TRUST  depend on MAKER ID?
##RIDGEPLOT w/ MEAN 

answers <- levels(df$MAKER_ID)
left <- rep(ref_labels['MAKER_TRUST','left'],  length(levels(df$MAKER_ID)))
right <- rep(ref_labels['MAKER_TRUST','right'],  length(levels(df$MAKER_ID)))

df %>% 
  group_by(MAKER_ID) %>% 
  mutate(
    count = n(), 
    m=mean(MAKER_TRUST),
    md=median(MAKER_TRUST)
    ) %>% 
  ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_TRUST, fill = fct_rev(MAKER_ID))) + 
  scale_x_continuous(limits = c(0,100))+
  geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
  stat_pointinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
  ##MEDIAN
  stat_summary(fun=median, geom="text", colour="red",  fontface = "bold", size = 2.5,
               vjust=+2, hjust = 0, aes( label=round(md, digits=0)))+
  stat_summary(fun=median, geom="point", shape=20, size=3, color="red", fill="red") +
  ## MEAN
  stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", size = 2.5, 
               vjust=+2, hjust = 0, aes( label=round(m, digits=0)))+
  stat_summary(fun="mean", geom="point", shape=20, size=3, color="blue", fill="blue") +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
  guides(
      y = guide_axis_manual(labels = left, title = ""),
      y.sec = guide_axis_manual(labels = right)
    ) +
  geom_text(aes(label= paste0("n=",count) ,  y = MAKER_ID, x = 100), color = "black",size = 3, nudge_y = 0.25) + 
  cowplot::draw_text(text = toupper(answers), x = 0, y= answers, size = 10, vjust=-2, hjust=0) + 
  labs (title = "MAKER TRUST  by MAKER ID", y = "", x = "MAKER TRUST", caption="(mean in blue) (median in red)") +
  theme_minimal() + easy_remove_legend()

```

#### (YES) model

```{r model-maker-id-trust}

### LINEAR MIXED EFFECTS MODEL ##################

df <- df_graphs 

## DEFINE MODEL
f <- "MAKER_TRUST ~ MAKER_ID + (1|PID) + (1|STIMULUS)"
m1 <-lmer(MAKER_TRUST ~ MAKER_ID + (1|PID) + (1|STIMULUS), data=df)

## PRINT MODEL 
(m_eq <- extract_eq(m1, use_coef = TRUE, ital_vars = TRUE, coef_digits = 1, wrap = TRUE, intercept = "beta"))

## DESCRIBE MODEL
summary(m1)
anova(m1)
performance(m1)
report(m1)

## PLOT MODEL COEFFICIENTS
coefs <- model_parameters(m1)
plot_model(m1, type = "est",
        show.intercept = TRUE,
        show.values = TRUE,
        show.p = TRUE
) + theme_minimal() + labs(caption=f)


## PLOT MODEL PREDICTIONS
means <- estimate_means(m1, at = c("MAKER_ID"))

# sjPlot::plot_model(m1, type = "pred", terms = c("MAKER_ID")) +
#     theme_minimal() + labs(caption=f)

# plot(means) + theme_minimal() + labs(caption=f) +
# geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), 
#           color="blue", position = position_nudge(x=0.25)) 


## PLOT MODEL PREDICTIONS with CONTRASTS

## contrasts
# black = estimated means and CI range; grey = CI range of the difference (as compared to the point estimate).  
(contrasts <- estimate_contrasts(m1, contrast="MAKER_ID", method="pairwise"))
plot(contrasts, means) + 
    geom_text(aes(x=means$MAKER_ID, y=means$Mean, label=round(means$Mean,1)), color="blue", position = position_nudge(x=0.25)) + 
  theme_minimal() + labs(caption = f)

```

# STASH

wip code stash


## half boxplot raincloud mean

```{r}
# ## HALF BOXPLOT + DOTPLOT + MEAN
# ##############################
# H <-  df %>% 
#   group_by(MAKER_AGE) %>% 
#   mutate(count = n(), m = mean(MAKER_CONF)) %>% 
#   ggplot(aes(y = MAKER_CONF, x = fct_rev(MAKER_AGE), color = fct_rev(MAKER_AGE))) + 
#     geom_half_boxplot(side="r", alpha = 0.5, aes(fill=fct_rev(MAKER_AGE))) + 
#     stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", 
#                vjust=-0.75, hjust = 1, aes( label=round(..y.., digits=0)))+
#     scale_color_manual(values = my_palettes(name="lightblues", direction = "-1"), 
#                        guide = guide_legend(reverse = TRUE)) + 
#     scale_fill_manual(values = my_palettes(name="lightblues", direction = "-1"), 
#                       guide = guide_legend(reverse = TRUE)) + 
#     stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, 
#                         aes(fill = fct_rev(MAKER_AGE)) , color="black",  point_interval = "mean_qi")  +
#     stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
#     geom_text(aes(label= paste0("n=",count) ,  y = 5), color = "black",
#             size = 3, nudge_x=0.35) + 
#   labs(y="Maker Age Confidence", x="") + 
#   theme_minimal() + 
#   easy_remove_legend()+
#   coord_flip() 
# ##############################
#   

```

## wip confidence modelling

```{r}
# 
# ## [test-frame] Are the confidence scores significantly different for different questions?
# ## [model-frame] Does QUESTION predict CONFIDENCE, accounting for random variance in SUBJECT and STIMULUS?
# 
# 
# ## MIXED model with random variance only at subject (not stimulus)
# mm1 <- lmer( CONFIDENCE ~ QUESTION + (1|PID), data = df)
# # summary(mm1)
# # plot(check_model(mm1))
# # pm <- model_parameters(mm1)
# # plot(pm, show_labels = TRUE, show_intercept = TRUE) + labs(title = "CONFIDENCE ~ QUESTION + (1|PID)")
# # performance(mm1)
# # report(mm1)
# 
# 
# ## MIXED model with random variance only at subject AND stimulus
# mm2 <- lmer( CONFIDENCE ~ QUESTION + (1|PID) + (1|STIMULUS), data = df)
# # summary(mm2)
# # plot(check_model(mm2))
# # pm <- model_parameters(mm2)
# # plot_model(mm2)
# # plot(pm, show_labels = TRUE, show_intercept = TRUE) + labs(title = "CONFIDENCE ~ QUESTION + (1|PID) + (1|STIMULUS)")
# # performance(mm2)
# # report(mm2)
# 
# 
# ## MIXED model with random slope for question by person and random intercept by stimulus
# mm3 <- lmer( CONFIDENCE ~ QUESTION +  (1 + QUESTION | PID) + (1|STIMULUS), data = df)
# # summary(mm3)
# # plot(check_model(mm3))
# # pm <- model_parameters(mm3)
# # plot(pm, show_labels = TRUE, show_intercept = TRUE) + labs(title = "CONFIDENCE ~ QUESTION +   (1 + QUESTION | PID) + (1|STIMULUS)")
# # performance(mm3)
# # report(mm3)
# 
# 
# ## MIXED model with STIMULUS as FIXED effect and random intercept by person
# mm4 <- lmer( CONFIDENCE ~ QUESTION + STIMULUS +  (1 | PID), data = df)
# # summary(mm4)
# # plot(check_model(mm4))
# # pm <- model_parameters(mm4)
# # plot(pm, show_labels = TRUE, show_intercept = FALSE) + labs(title = "CONFIDENCE ~ QUESTION + STIMULUS +  (1 | PID)")
# # performance(mm4)
# # report(mm4)
# 
# ## MIXED model with STIMULUS * QUESTION interaction and random intercept by person
# mm5 <- lmer( CONFIDENCE ~ QUESTION * STIMULUS +  (1 | PID), data = df)
# # summary(mm5)
# # plot(check_model(mm5))
# # pm <- model_parameters(mm5)
# # plot(pm, show_labels = TRUE, show_intercept = FALSE) + labs(title = "CONFIDENCE ~ QUESTION * STIMULUS +  (1 | PID)")
# # performance(mm5)
# # report(mm5)
# 
# 
# ## MIXED model with STIMULUS * QUESTION interaction and random intercept by person
# mmx <- lmer( CONFIDENCE ~ STIMULUS  +  (1 | PID) + (1 | QUESTION), data = df)
# # summary(mmx)
# # plot(check_model(mmx))
# # pm <- model_parameters(mmx)
# # plot(pm, show_labels = TRUE, show_intercept = FALSE) + labs(title = "CONFIDENCE ~ STIMULUS  +  (1 | PID) + (1 | QUESTION)")
# # performance(mmx)
# # report(mmx)
# 
# 
# ### COMPARE MODELS
# # compare_parameters(mm1,mm2,mm3, mm4, mm5, mmx)
# compare_performance(mm1,mm2,mm3, mm4, mm5, mmx, rank = TRUE )
# ## model 3 is the best fit, and is appropriate to the design of the study
# summary(mm3)
# report(mm3)
# # plot_model(mm3, terms = c("QUESTION", "STIMULUS"), type = "diag")
# 
# # # ## repeated measures aov
# # print("Repeated Measures ANOVA")
# # ex1 <- aov(CONFIDENCE~QUESTION+Error(PID), data=df)
# # summary(ex1)
# # report(ex1)
# 




```

## correlation plot code

```{r}
# ## SHADED CIRCLES
# corrplot(m, method = 'circle', type = 'lower', 
#          order = 'AOE', diag = FALSE,
#          insig='blank',
#          tl.col = "black")
# 
# 
# ## SHADED NUMBERS
# corrplot(m,  order = 'AOE', method = "number", 
#          diag = FALSE, type = "lower",
#          insig='blank',
#          # insig = 'label_sig', sig.level = c(0.001, 0.01, 0.05),
#          addCoef.col = '#595D60',
#          tl.pos = "ld", tl.col = "#595D60")
#          
# 
# ## SHADED SQUARED + COEFFS
# corrplot(m,  order = 'AOE', method = "circle", 
#          diag = FALSE, type = "lower",
#          insig='blank', sig.level = 0.05,
#          # insig = 'label_sig', sig.level = c(0.001, 0.01, 0.05),
#          addCoef.col = '#595D60',
#          tl.pos = "ld", tl.col = "#595D60")
#          

```

## flip some sds

```{r}



############## SETUP FOR FLIPPING SCALES ON SOME QUESTIONS TO MAKE THEM MORE READABLE
ref_sd_reordered <- c("MAKER_DATA","MAKER_DESIGN", 
                    "CHART_BEAUTY", "CHART_LIKE", 
                    "MAKER_POLITIC","MAKER_ARGUE", "MAKER_SELF", "CHART_INTENT",
                    "MAKER_ALIGN","MAKER_TRUST",
                    "CHART_TRUST")

left_reordered <- c("layperson","layperson", 
                    "NOT at all","NOT at all",
                    "left-leaning",
                    "diplomatic",
                    "altruistic",
                    "inform",    
                    "DOES share", 
                    "untrustworthy",
                    "untrustworthy")
right_reordered <- c("professional","professional",
                     "very much", "very much",          
                     "right-leaning",
                     "confrontational",
                     "selfish", 
                     "persuade",
                     "does NOT share", 
                     "trustworthy",
                     "trusthworthy")

ref_labels_reordered <- as.data.frame(cbind(left_reordered,right_reordered))
rownames(ref_labels_reordered) <- ref_sd_questions




```

## correlation matrix

```{r}
## GGALLY correlation heatmap
# ggcorr(df,
#        label = TRUE,  geom = "tile",
#        nbreaks = 5, layout.exp = 2,   
#        # label_round = 2,
#        angle = -0, hjust = 0.8, vjust = 1, size = 2.5,
#        low = "#D88585",mid = "white", high= "#6DA0D6") +
#        easy_remove_legend() + 
#   labs(title = "Correlation between SD measures", subtitle = ("pairwise; Pearson correlations"))
```

## ridgeplot with interval and mean

```{r}

# ## Does MAKER_TRUST  depend on MAKER ID?
# ##RIDGEPLOT w/ MEAN 
# answers <- levels(df$MAKER_ID)
# left <- rep(ref_labels['MAKER_TRUST','left'],  length(levels(df$MAKER_ID)))
# right <- rep(ref_labels['MAKER_TRUST','right'],  length(levels(df$MAKER_ID)))
# df %>% ggplot(aes(y = fct_rev(MAKER_ID), x= MAKER_TRUST, fill = fct_rev(MAKER_ID))) + 
#   geom_density_ridges(scale = 0.55,quantile_lines = TRUE, alpha = 0.75) + 
#   stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA, point_interval = "mean_qi") +
#   stat_summary(fun=mean, geom="text", colour="blue",  fontface = "bold", 
#                vjust=+2, hjust = 0, aes( label=round(..x.., digits=0)))+
#     stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue") +
#   scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), name = "",  guide = guide_legend(reverse = TRUE)) +   
#     guides(
#       y = guide_axis_manual(labels = left, title = ""),
#       y.sec = guide_axis_manual(labels = right)
#     ) +
#    cowplot::draw_text(text = toupper(answers), x = 10, y= answers,size = 10, vjust=-2) + 
#   labs (title = "MAKER TRUST by MAKER ID", y = "", x = "MAKER TRUST", caption="(mean in blue)") +
#   theme_minimal() + easy_remove_legend()


```

## lessR donuts

```{r b2_donuts}
##good for seeing the color schemes 
# #### DEFINE SET 
# stimulus  = "B2-1"
# df <- df_graphs %>% filter(STIMULUS == stimulus)
# 
# #### GENERATE GRAPHS
# 
#   #MAKER_ID-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "reds",
#          main = paste0(stimulus, " MAKER ID")) + theme_minimal()
# 
# 
# #MAKER_GENDER-DONUT
# PieChart(MAKER_GENDER, data = df,
#        fill = "blues",
#        main = paste0(stimulus, " MAKER GENDER")) + theme_minimal()
# 
# 
# #MAKER_AGE-DONUT
# PieChart(MAKER_AGE, data = df,
#        fill = "olives",
#        main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
# 
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "rusts",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "olives",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "greens",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "emeralds",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "turquoises",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "aquas",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-MAKER_ID
#   PieChart(MAKER_ID, data = df,
#          fill = "purples",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "magentas",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "violets",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
#   
#   #MAKER_AGE-DONUT
#   PieChart(MAKER_ID, data = df,
#          fill = "grays",
#          main = paste0(stimulus, " MAKER AGE")) + theme_minimal()
# "reds"	h	0
# "rusts"	h	30
# "browns"	h	60
# "olives"	h	90
# "greens"	h	120
# "emeralds"	h	150
# "turquoises"	h	180
# "aquas"	h	210
# "blues"	h	240
# "purples"	h	270
# "violets"	h	300
# "magentas"	h	330
# "grays"

```

## ggplot donuts

```{r}
#   df <- df_graphs %>% filter(STIMULUS== s)
# #### CATEGORICAL DONUT PLOTS
#   #subset data cols 
#   cols <- df %>% select( all_of(ref_cat_questions))
#   
#   ggplot( df, aes( x = STIMULUS, fill = MAKER_ID)) +
#   geom_bar( position = "stack", width=1) +
#   coord_radial(theta = "y", start = 0, inner.radius = 0.5, expand=FALSE) +
#   scale_fill_manual(values = my_palettes(name="reds", direction = "1"), name = "",  guide = guide_legend(reverse = FALSE)) +   
#   labs( title = paste0(s, " MAKER ID")) +
#   theme_minimal()
#   
#   
```

## Alluvial Plots

```{r}
## EXAMPLE ALLUVIAL PLOT USING GGALUVIAL  (instead of GGSANKEY)
# https://corybrunson.github.io/ggalluvial/articles/ggalluvial.html

# #FILTER FOR BLOCK 2 STIM AND RESHAPE FOR SANKEY
# ds <- df_graphs %>% 
#   filter(str_detect(STIMULUS, "B2")) %>% 
#   select(STIMULUS, MAKER_ID, PID) %>% 
#   mutate(
#     MAKER_ID = fct_relevel(MAKER_ID, 
#               c("business","education","individual", "news","organization", "political" ))
#   )
# 
# ds %>% 
#   ggplot(aes( x = STIMULUS,
#               stratum = MAKER_ID,
#               label = MAKER_ID,
#               alluvium = PID)) +
#       stat_alluvium(aes(fill = MAKER_ID),
#                     width = 0,
#                     alpha = 1,
#                     geom = "flow")+
#       geom_stratum(width = 0.2, aes(fill= MAKER_ID))+
#       # geom_text(stat = "stratum", size = 5, angle = 90)+
#       scale_fill_viridis(discrete=TRUE, option="viridis", drop = FALSE,
#                      alpha = 1) +
#       theme_minimal()
```

# RESOURCES

-   custom color palettes:
    <https://www.r-bloggers.com/2022/06/custom-colour-palettes-for-ggplot2/>
-   lessR donuts <https://r-charts.com/part-whole/donut-chart/>
-   GGSANKEY <https://github.com/davidsjoberg/ggsankey>
-   GGALLUVIAL
    <https://corybrunson.github.io/ggalluvial/articles/ggalluvial.html>
-   variable standardization [variable (vs) participant]
    :<https://cran.r-project.org/web/packages/datawizard/vignettes/standardize_data.html>
-   contrasts:
-   UCLA:<https://stats.oarc.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables>
-   <https://phillipalday.com/stats/lazy-contrasts.html>
-   level naming with contrasts :<https://rpubs.com/bbolker/5335>
-   ggdist slab normaliztion https://mjskay.github.io/ggdist/articles/thickness.html
- visualizing regression models visreg https://pbreheny.github.io/visreg/index.html
