---
title: "MAG — S0  SUMMER PILOT EDA"
author: "ANONYMIZED"
date: "2024-01-27"
output:
  html_document:
    theme: flatly
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 5
  pdf_document:
    toc: yes
    toc_depth: '4'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(tidyverse) #all the things
library(summarytools) #data quality
library(jtools) #Social Science regression utilities
library(lubridate) #dealing with dates

#VIZ
library(kableExtra) #printing tables
library(ggformula) #regression syntax viz
# library(vcd) #mosaic plots
# library(vcdExtra) #mosaic plot helpers
library(ggstatsplot) #dummies
library(ggeasy) #easy label stuff 


#MODELLING
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer

#POWER ANALYSIS
library(simr)
library(mixedpower)


options(readr.show_col_types = FALSE) #don't show coltypes on read_csv


#ARF ONLY — MANUAL RUN
# setwd("~/Code/IXN-Characterizing_Interaction/IXN-D_Characterizing_Interaction/ANALYSIS")

```

Data were exported from qualtrics to file `RAW_Vis Guise Pre-Pilot_January 27, 2024_16.57.csv` which was manually wrangled to `CLEAN_pilot_0.csv` by removing extraneous qualtrics columns and creating informative column names from question text. 

## Data Wrangling

```{r IMPORT, message=FALSE, warning=FALSE}

#DF RAW 1 ROW PER PARTICIPANT
df_raw <- read_csv("data/CLEAN_S0_pilot.csv")

#DF DATA 1 ROW PER PARTICIPANT
#PRELIM-CLEANING
df_data <- df_raw %>% filter(
  finished_survey == 'TRUE'#EXCLUDE non-finishers
) %>% filter(
  !(is.na(IPAddress)) #EXCLUDE no ip address [from survey preview]
) %>% select( #drop unecessary columns
  -StartDate, -EndDate, -IPAddress, -Progress, -finished_survey, -RecordedDate,
  -latitude, -longitude, -source, -language, -consent, -eligibility, -responseID,
  -Status
) %>% rename( #rename for consistency
  ID.PROLIFIC = prolificID,
  duration.sec = duration_sec 
) %>% mutate( #factorize 
  duration.min = round(duration.sec/60,1)
) %>% relocate(
  duration.min, .after=duration.sec
) %>% relocate(ID.PROLIFIC) 
# %>% JK DON'T FACTORIZE THIS IS GOING TO BE A PROBLEM POST PIVOT
#   mutate ( #factorize if NOT free response but IS a character
#   across(c(where(is.character),-contains("_explain"),-contains("_why")), factor)
# )  

#DF FREE 1 ROW PER PARTICIPANT
#GET ALL THE FREE RESPONSE DATA
df_free <- df_data %>% select(
  ID.PROLIFIC, duration.sec, duration.min,
  contains("_explain"), contains("_why"), contains("_who")
) 

#DF DEMOS 1 ROW PER PARTICIPANT
#WS SURVEY and DEMOGRAPHICS
df_demographics <- df_data %>% select(
  ID.PROLIFIC, duration.sec, duration.min, contains("ws_"), contains("p_")
)

#DF DATA 1 ROW PER PARTICIPANT
#DROP DEMOS and COMPREHENSION and FREE
df_data <- df_data %>% 
  select(
    -contains("ws_"), -contains("p_"), 
    -contains("_explain"), -contains("_why"), -contains("_who"),
    -contains("q1"), -contains("q2"), -contains("q3")
  )

# #DF CHART 1 ROW PER PARTICIPANT-CHART-QUESTION
# #RESHAPE 
df_graphs <- df_data  %>% 
  pivot_longer( #PIVOT ALL THE WAY LONG
    cols = v1_chart_intent:v5_author_confidence,
    names_to = c("graph","subject","question"),
    # names_pattern = "(v.)(chart.)(.)"
    names_sep = "_") %>% 
  unite( #COMBINE SUBJECT AND QUESTION
    col = "question", 
    subject:question, 
    sep="_",
    remove = TRUE) %>% 
  pivot_wider( #NOW PIVOT BACK UP ONE LEVEL
    names_from = question,
    values_from=value
  ) %>% mutate_if(#RE-FACTORIZE
    is.character,factor
  ) %>% mutate( #SET LEVELS
    chart_intent = factor (chart_intent,
      levels = c("Don't know/Can't Say","Seeking to inform","2","3","4","Seeking to persuade"),
      labels = c("?","inform","2","3","4","persuade")),
    chart_politics = factor(chart_politics,
      levels = c("Politically motivated","2","3","4","Not politically motivated","Don't know/Can't Say"),
      labels = c("political","2","3","4","not-political","?")),
    chart_bias = factor(chart_bias,
      levels = c("Biased","2","3","4","Unbiased","Don't know/Can't Say"),
      labels = c("baised","2","3","4","unbiased","?")),
    chart_complexity = factor(chart_complexity, 
      levels = c("Manipulative","2","3","4","Straightforward","Don't know/Can't Say"),
      labels = c("manipulative",  "2",  "3",  "4",  "straightforward",  "?")),
    chart_confidence = factor(chart_confidence,
      levels = c("Extremely unconfident", "Somewhat unconfident", "Neither confident nor unconfident",  
                 "Somewhat confident","Extremely confident"),
      labels = c("1","2","3","4","5")),
    author_expertise = factor(author_expertise,
      levels = c("Amateur", "2","3", "Expert","Don't know/Can't say"),
      labels = c("amateur","2","3","expert","?")),
    author_responsibility = factor(author_responsibility,
      levels = c("Responsible", "2", "3", "Irresponsible","Don't know/Can't say"),
      labels = c("responsible","2", "3","irresponsible","?")),
    author_honesty = factor(author_honesty,
      levels = c("Honest", "2", "3", "Dishonest","Don't know/Can't say"),
      labels = c("honest","2", "3","dishonest","?")),
    author_grounded = factor(author_grounded,
      levels = c("Down to earth", "2", "3", "Out of touch","Don't know/Can't say"),
      labels = c("grounded","2", "3","not-grounded","?")),
    author_alignment = factor(author_alignment,
      levels = c("Like you", "2", "3", "Unlike you","Don't know/Can't say"),
      labels = c("like-me","2", "3","unlike-me","?")),
    author_confidence = factor(author_confidence,
      levels = c("Extremely unconfident", "Somewhat unconfident", "Neither confident nor unconfident",  
                 "Somewhat confident","Extremely confident"),
      labels = c("1","2","3","4","5"))
  ) %>% mutate( genre = case_when(
    graph =="v1" ~ "news",
    graph =="v2" ~ "infographic",
    graph =="v3" ~ "infographic",
    graph =="v4" ~ "news",
    graph =="v5" ~ "infographic"
  )
) %>% mutate(
  genre = fct_relevel(genre, "news","infographic"))


```

## Visualize 

```{r vis}

library(ggeasy)
##STATSPLOT
ggbarstats(df_graphs,x = chart_intent           ,y = graph)+ easy_labs( title = "chart_intent")
ggbarstats(df_graphs,x = chart_politics         ,y = graph)+ easy_labs( title = "chart_politics")
ggbarstats(df_graphs,x = chart_complexity       ,y = graph)+ easy_labs( title = "chart_complexity")
ggbarstats(df_graphs,x = chart_bias             ,y = graph)+ easy_labs( title = "chart_bias")
ggbarstats(df_graphs,x = chart_confidence       ,y = graph)+ easy_labs( title = "chart_confidence")
ggbarstats(df_graphs,x = author_expertise       ,y = graph)+ easy_labs( title = "author_expertise")
ggbarstats(df_graphs,x = author_responsibility  ,y = graph)+ easy_labs( title = "author_responsibility")
ggbarstats(df_graphs,x = author_honesty         ,y = graph)+ easy_labs( title = "author_honesty")
ggbarstats(df_graphs,x = author_grounded        ,y = graph)+ easy_labs( title = "author_grounded")
ggbarstats(df_graphs,x = author_confidence      ,y = graph)+ easy_labs( title = "author_confidence")
# ##GGFORUULA
# gf_bar(df, ~chart_confidence) %>% gf_facet_grid(graph ~ .)
# gf_bar(df, ~author_alignment) %>% gf_facet_grid(graph ~ .)


# TODO 
# remotes::install_github('jbryer/likert')
# LIKERT VISUALIZATION

## GGALLY  --> R PAIRS PLOTS
# library(GGally)

# df <- df_graphs %>% select(contains("chart"), contains("author"),graph) %>% 
#   mutate(
#     chart_confidence = as.numeric(chart_confidence)
#   )
  
  
# ggbivariate(df, outcome = "chart_confidence", explanatory = c("chart_politics", "chart_intent","chart_complexity","graph"))
```
## Model 
```{r}
##MODEL FOR POWER ANALYSIS FOR FUTURE STUDIES 

df <- df_graphs %>% 
  select(ID.PROLIFIC, graph, genre, chart_intent, chart_politics) %>%
  mutate(
    subject = ID.PROLIFIC,
    GENRE = genre,
    intent = as.numeric(chart_intent),
    POLITICS = as.numeric(fct_rev(chart_politics))
  ) %>% select(subject, intent, GENRE, POLITICS, graph)


#visualize distribution
gf_bar(~intent, data = df) + facet_grid(.~GENRE) + 
  easy_labs(title = "Chart Intent by GENRE", 
            subtitle = "2 (to inform) --> 6 (to persuade), 1=?")
gf_bar(~POLITICS, data = df) + facet_grid(.~GENRE) + 
    easy_labs(title = "Chart Politics by GENRE", 
            subtitle = "2 (apolotical) --> 6 (political), 1=?")

gf_point(intent ~ POLITICS, color = ~GENRE, data = df) %>% gf_jitter() + 
      easy_labs(title = "CHART INTENT BY POLITICS & GENRE", 
            subtitle = "1=? higher politics -> more political; higher intent -> to persuade")

#create LMM predicting chart intent from genre
m1 <- lmer( intent ~ GENRE + (1|subject) + (1|graph), data = df)
summary(m1)
check_model(m1)
report(m1)


#create LMM predicting chart intent from genre and politics
m2 <- lmer( intent ~ GENRE + POLITICS + (1|subject) + (1|graph), data = df)
summary(m2)
check_model(m2)
report(m2)


#create LMM predicting chart intent from genre and politics with interaction term
m3 <- lmer( intent ~ GENRE * POLITICS + (1|subject) + (1|graph), data = df)
summary(m3)
check_model(m3)
report(m3)

compare_parameters(m1,m2,m3)
compare_performance(m1,m2,m3, rank=TRUE)


```

## Power Analysis with mixedpower

M3 was the best fitting model, so we use this to estimate power for subsequent studies 

```{r}

#see also  # https://lkumle.github.io/power_notebooks/Scenario3_notebook.html

## BUILD SIMULATED DATASET 

#CREATE SIMULATED DATA 
# 1. create subject IDs  
n = 10
subject_ID <- (1:n)

# 2. create stimuli IDS -> every subject should read t words
t = 5
stimuli_ID <- (1:t)

# 3. combine subject IDs and stimui IDs
df_sim <- expand.grid(subject = subject_ID, graph = stimuli_ID)

##FIXED EFFECTS 

# 4. create vector including identifier for FIXED FACTOR GENRE
#half news, half infographic
genre <- c(rep("news", (n*t)/2), rep("infographic", (n*t)/2))

# add vector to data set
df_sim["genre"] <- genre

# 5. create values for fixed factor politics
pilot_mean <- mean(df$POLITICS)
pilot_sd <- sd(df$POLITICS)
politics <- rnorm(n*t, mean = pilot_mean, sd = pilot_sd) 

# add to data frame
df_sim["politics"] <- politics # multiply by 20 (for every subject)
df_sim <- df_sim %>% mutate(
  #don't make subject and graphs factors, needs to be numeric for later power simulations
  genre = factor(genre, levels=c("news","infographic")) #have to match order of df
)


glimpse(df)
glimpse(df_sim)

####### POWER ANALYSIS

# ------------------------------------------ #
# SPECIFY BETA COEFFICIENTS FOR FIXED EFFECTS (get from pilot data model m3)
# intent ~ GENRE * POLITICS + (1|subject),
fixed_effects <-  c(1.47, -0.58, 0.37, 0.36) # order follows the order in model summary and formula

# ------------------------------------------ #
# SET RANDOM INTERCEPT VARIANCE
random_variance <- list(0.09345, 0.003284)

# ------------------------------------------ #
# SET RESIDUAL STANDARD DEVIATION
sigma <- sigma(m3)

##SIMULATE LMER 
# ------------------------------------------ #
# CREATE LMER
#m3 <- lmer( intent ~ GENRE * POLITICS + (1|subject), data = df)
sim_lmer <- makeLmer(formula = intent ~ genre * politics + (1 | subject) + (1 | graph),
                           fixef = fixed_effects, VarCorr = random_variance, sigma = sigma,
                           data = df_sim)

# lets have a look!
summary(sim_lmer)

```


```{r}

# ------------------------------------------ #
# INFORMATION ABOUT MODEL USED FOR SIMULATION

model <- sim_lmer # which model do we want to simulate power for?
data <- df_sim # data used to fit the model
fixed_effects <- c("genre", "politics") # all fixed effects specified in artificial_glmer
simvar <- "subject" # which random variable do we want to vary in the simulation?


# ------------------------------------------ #
# SIMULATION PARAMETERS
steps <- c(20,60,100,140,180) # which sample sizes do we want to look at?
critical_value <- 2 # which t/z value do we want to use to test for significance?
n_sim <- 1000 # how many single simulations should be used to estimate power?

# ------------------------------------------ #
# INCLUDE SESOI SIMULATION
# SESOI <-c(-4.3,  0.30 ,-0.34, -0.27) # specify SESOI (15% smaller betas)




# ------------------------------------------ #
# RUN SIMULATION WITH MIXEDPOWER varying SUBJECTS
subjects_power <- mixedpower(model = model, data = data,
                       fixed_effects = fixed_effects,
                       simvar = simvar, steps =steps,
                       critical_value = critical_value, n_sim = 1000
                       #, SESOI = c(-4.3,  0.30 ,-0.34, -0.27))
)

# ------------------------------------------ #
# LOOK AT RESULTS
subjects_power
saveRDS(subjects_power, file="subjects_mixedpower-simulation.RDS")
# subjects_power <- readRDS(file="subjects_mixedpower-simulation.RDS")
# ------------------------------------------ #
# PLOT THE RESULTS
multiplotPower(subjects_power)
#this run indicated 100 subjects for 5 graphs at the same effects found at summer pilot





# ------------------------------------------ #
# RUN SIMULATION WITH MIXEDPOWER — varying stimuli
graphs_power <- mixedpower(model = model, data = data,
                       fixed_effects = fixed_effects,
                       simvar = "graph", steps =c(4,6,8),
                       critical_value = critical_value, n_sim = 1000
                       #, SESOI = c(-4.3,  0.30 ,-0.34, -0.27))
)

# ------------------------------------------ #
# LOOK AT RESULTS
graphs_power
saveRDS(graphs_power, file="graphs_mixedpower-simulation.RDS")
# subjects_power <- readRDS(file="subjects_mixedpower-simulation.RDS")
# ------------------------------------------ #
# PLOT THE RESULTS
multiplotPower(graphs_power)
#this run indicated 100 subjects for 5 graphs at the same effects found at summer pilot

   




# ------------------------------------------ #
# RUN SIMULATION WITH MIXEDPOWER — varying SUBJECTS AND STIMULI
r2_power <- R2power(model = model, data = data,
                       fixed_effects = fixed_effects,
                       simvar = "subject", steps = c(20,60,100,140,180),
                       R2var="graph", R2level=30,
                       critical_value = critical_value, n_sim = 1000
                       #, SESOI = c(-4.3,  0.30 ,-0.34, -0.27))
)

# ------------------------------------------ #
# LOOK AT RESULTS
r2_power
saveRDS(r2_power, file="graphs_mixedpower-simulation.RDS")
# subjects_power <- readRDS(file="subjects_mixedpower-simulation.RDS")
# ------------------------------------------ #
# PLOT THE RESULTS
multiplotPower(r2_power)
#this run indicated only 20 subjects are needed? very confused

   

```

## Power Analysis with powerSim
```{r}


# ------------------------------------------ #
# POWER ANALYSIS WITH SIMR
power_simr <- powerSim(sim_lmer, test= fcompare(intent~politics),  nsim=100)
print(power_simr)
model_ext_subject <- extend(sim_lmer, along="subject", n=20)
sim_treat_subject <- powerSim(model_ext_subject, test= fcompare(intent~politics),  nsim=100)
print(sim_treat_subject)
p_curve_treat <- powerCurve(model_ext_subject, test=fcompare(intent~politics), along="subject")
plot(p_curve_treat)
# savePlot(plot(p_curve_treat), file = "summer-pilot-intent-politics-powerCurve.png")
saveRDS(p_curve_treat, file = "summer-pilot-intent-politics-powerCurve.RDS")



##_________________OBSERVED MODEL
# actual_simr_politics <- powerSim(m3, test=fcompare(intent~POLITICS), nsim=100)
# print(actual_simr_politics)
# model_extend_sub <- extend(sim_lmer, along="subject", n=20)
# sim_treat_subject <- powerSim(model_extend_sub, test=fcompare(intent~POLITICS), nsim=100)
# p_curve_treat <- powerCurve(sim_treat_subject, test=fcompare(intent~POLITICS), along="subject")



```



```



