---
title: "MAG — S2 Exploratory Data Analysis"
author: "ANONYMIZED"
date: "2024-02-04"
output:
  html_document:
    theme: flatly
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 5
  pdf_document:
    toc: yes
    toc_depth: '4'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe()
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates

#EDA
library(qacBase)

#VIZ
library(kableExtra) #printing tables
library(ggformula) #regression syntax viz
# library(vcd) #mosaic plots
# library(vcdExtra) #mosaic plot helpers
library(ggstatsplot) #dummies
library(GGally) #extends ggplot for EDA 
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(ggridges) #ridge plots
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(lessR) ##easy donuts 


#GEO-VIS
library(tigris)
options(tigris_use_cache = TRUE)

#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer

#ARF ONLY — MANUAL RUN
# setwd("~/Code/IXN-Characterizing_Interaction/IXN-D_Characterizing_Interaction/ANALYSIS")

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
graph_render = TRUE #set to true to generate all the SD graphs and save to folders 

```


# WRANGLING

Initial pilot data were collected via Qualtrics surveys named `MAG_S2_PROLIFIC-DATACOLLAR_0` and `MAG_S2_PROLIFIC-DATACOLLAR_0`, each presenting participants with one common graph ("block 0", `STIMULUS = B0-0`) and four subsequent graphs in random order ("block 1").

Subsequently we made minor alterations to the question wording and respose wording, and the remaining stimuli were organized in 6 blocks. Each block was collected via PROLIFIC using independent Qualtrics surveys, with the exception of a sample of respondents directly recruited from Tumblr, using a single Qualtrics surveys with randomization logic to assign each Tumblr participant to one of the six stimulus blocks.

Participants were excluded from the sample for the following reasons

-   **abandoned**; Finished = False and Progress \< 100%
-   **fails consent or pre-screening**, Finished = TRUE, Progress = 100%, Q_TerminateFlag = "Screened"
-   **didnot-follow-instructions** free responses indicate they misinterpred the question (most commonly they describe the graph rather than their reactions/judgements/impressions of it)
-   **illegible-english** free responses text is largely illegible

Following wrangling, there should be 6 blocks of stimuli, each containing responses from 40 participants from prolific, and TODO responses directly from Tumblr.


### Import Configuration Files
```{r setup-stimuli, message=FALSE, warning = FALSE}

############## IMPORT STIMULI FILE
df_stimuli <- read_csv("data/input/stimuli.csv", col_names = TRUE) %>% 
  mutate(
    BLOCK = as.factor(BLOCK), 
    STIMULUS_CATEGORY = as.factor(CATEGORY),
    ID = as.factor(ID),
    MAKER_ID = as.factor(MAKER_ID)
  )

############## BUILD LABELS
ref_stimuli <- levels(df_stimuli$ID)
ref_cat_questions <- c("MAKER_ID","MAKER_AGE","MAKER_GENDER")
ref_free_response <- c("MAKER_DETAIL", "MAKER_EXPLAIN", "TOOL_DETAIL", "CHART_EXPLAIN")
ref_conf_questions <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")
ref_sd_questions <- c("MAKER_DESIGN","MAKER_DATA","MAKER_POLITIC",
               "MAKER_ARGUE","MAKER_SELF","MAKER_ALIGN","MAKER_TRUST",
               "CHART_LIKE", "CHART_BEAUTY", "CHART_INTENT", "CHART_TRUST")
left <- c("professional","professional","left-leaning","confrontational",
          "altruistic","does NOT share","untrustworthy",
          "NOT at all","NOT at all", "inform", "untrustworthy")
right <- c("layperson","layperson","right-leaning","diplomatic",
           "selfish", "DOES share", "trustworthy",
           "very much", "very much", "persuade", "trusthworthy")
ref_labels <- as.data.frame(cbind(left,right))
rownames(ref_labels) <- ref_sd_questions
ref_blocks <- c("block1", "block2", "block3", "block4", "block5", "block6")
rm(left,right)

############## STUDY ID FILE
#most blocks were run as separate qualtrics surveys with diffferent recruitments in Prolific
#Tumblr was run with all blocks and randomization
df_studies <- read_csv("data/input/studies.csv", col_names = TRUE) %>%
  mutate(
    ID.Study = as.factor(ID.Study),
    Assigned.Block = as.factor(Assigned.Block),
    Distribution = as.factor(Distribution),
    Prolific.Name = as.factor(Prolific.Name),
    Qualtrics.URL = as.factor(Qualtrics.URL),
    Qualtrics.Survey = as.factor(Qualtrics.Survey),
    Sample = as.factor(Sample),
    Scope = as.factor(Scope)
)

```


### Import Data Files
```{r WRANGLE-INPUT, message=FALSE, warning=FALSE}

#1. IMPORT RAW DATA FILES ########################################################
#### RAW DATA ####################################################################
# will always be the unaltered version of imported data
# 1 row per subject 
df_raw_datacollar <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_datacollarpilot_B1.csv", col_names = TRUE)
df_raw_bluecollar <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_bluecollarpilot_B1.csv", col_names = TRUE)
df_raw_b1 <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_GENERAL_B1.csv", col_names = TRUE)
df_raw_b2 <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_GENERAL_B2.csv", col_names = TRUE)
df_raw_b3 <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_GENERAL_B3.csv", col_names = TRUE)
df_raw_b4 <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_GENERAL_B4.csv", col_names = TRUE)
df_raw_b5 <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_GENERAL_B5.csv", col_names = TRUE)
df_raw_b6 <- read_csv("data/input/CLEAN_MAG_S2_PROLIFIC_GENERAL_B6.csv", col_names = TRUE)
df_raw_tumblr_paid <- read_csv("data/input/CLEAN_MAG_S2_TUMBLR_PAID_ALL.csv", col_names = TRUE)
df_raw_tumblr_free <- read_csv("data/input/CLEAN_MAG_S2_TUMBLR_FREE_ALL.csv", col_names = TRUE)

# drop first two rows (qualtrics_specs)
df_raw_datacollar <- df_raw_datacollar[-c(1:2),]
df_raw_bluecollar <- df_raw_bluecollar[-c(1:2),]
df_raw_b1 <- df_raw_b1[-c(1:2),]
df_raw_b2 <- df_raw_b2[-c(1:2),]
df_raw_b3 <- df_raw_b3[-c(1:2),]
df_raw_b4 <- df_raw_b4[-c(1:2),]
df_raw_b5 <- df_raw_b5[-c(1:2),]
df_raw_b6 <- df_raw_b6[-c(1:2),]
df_raw_tumblr_paid <- df_raw_tumblr_paid[-c(1:2),]
df_raw_tumblr_free <- df_raw_tumblr_free[-c(1:2),]

# ADD DUMMY COLS TO DATA/BLUE COLLAR PILOT DATA 
# necessary b/c pilot (block 1) did not have chart_action behavioural question
# x <- compare_df_cols(df_raw_b2, df_raw_pilot)
df_raw_pilot <- rbind(df_raw_datacollar, df_raw_bluecollar) %>% 
  mutate(
    '0_Q_B0_CHART_ACTION' = NA,
    '1_Q_B1_CHART_ACTION' = NA,
    '1_Q_B2_CHART_ACTION' = NA,
    '1_Q_B3_CHART_ACTION' = NA,
    '1_Q_B4_CHART_ACTION' = NA,
    '1_Q_B5_CHART_ACTION' = NA,
    '1_Q_B6_CHART_ACTION' = NA,
    '2_Q_B1_CHART_ACTION' = NA,
    '2_Q_B2_CHART_ACTION' = NA,
    '2_Q_B3_CHART_ACTION' = NA,
    '2_Q_B4_CHART_ACTION' = NA,
    '2_Q_B5_CHART_ACTION' = NA,
    '2_Q_B6_CHART_ACTION' = NA,
    '3_Q_B1_CHART_ACTION' = NA,
    '3_Q_B2_CHART_ACTION' = NA,
    '3_Q_B3_CHART_ACTION' = NA,
    '3_Q_B4_CHART_ACTION' = NA,
    '3_Q_B5_CHART_ACTION' = NA,
    '3_Q_B6_CHART_ACTION' = NA,
    '4_Q_B1_CHART_ACTION' = NA,
    '4_Q_B2_CHART_ACTION' = NA,
    '4_Q_B3_CHART_ACTION' = NA,
    '4_Q_B4_CHART_ACTION' = NA,
    '4_Q_B5_CHART_ACTION' = NA,
    '4_Q_B6_CHART_ACTION' = NA
  )

# BIND COLUMNS RAW prolific datasets 
df_raw_prolific <- rbind(df_raw_pilot, df_raw_b1, df_raw_b2, df_raw_b3, df_raw_b4, df_raw_b5, df_raw_b6)

# RETROFIT SOME COLNAMES FOR COMPATIBILITY WITH TUMBLR 
df_raw_prolific <- df_raw_prolific %>% 
  #drop T_BROWSER cols [these are blank]
  select(-contains("T_BROWSER"), -T_EMAIL) %>% 
  mutate(
    Q_RelevantIDDuplicate = NA, 
    Q_RelevantIDDuplicateScore = NA, 
    Q_RelevantIDFraudScore = NA, 
    Q_RelevantIDLastStartDate = NA, 
    RANDOM_BLOCK = NA
  ) %>% rename_with(
    stringr::str_replace, 
      pattern = "P_BROWSER", replacement = "BROWSER",
  ) %>% 
  dplyr::rename(
    BROWSER_OS = `BROWSER_Operating System`
  ) %>% mutate_all(funs(str_replace(., "millenial", "millennial")))


# BIND COLUMNS RAW prolific datasets 
df_raw_tumblr <- rbind(df_raw_tumblr_paid, df_raw_tumblr_free)

# RETROFIT SOME TUMBLR COLNAMES FOR MERGING WITH PROLIFIC 
df_raw_tumblr <- df_raw_tumblr %>% 
  select( - t_example_question1, -t_example_question2, -D_email) %>% 
  mutate(
    #add empty browser cols; didn't collect these in tumblr qualtrics
    BROWSER_Browser = NA,
    BROWSER_OS = NA,
    BROWSER_Resolution = NA,
    BROWSER_Version = NA, 
    ID_PROLIFIC = "TUMBLR",
    ID_SESSION = "TUMBLR",
    ID_STUDY = "TUMBLR"
  ) %>% mutate_all(funs(str_replace(., "millenial", "millennial")))

#dataframe column comparisons 
# x <- janitor::compare_df_cols(df_raw_prolific, df_raw_tumblr)

# JOINT PROLIFIC AND TUMBLR DATAFRAMES
df_raw <- rbind(df_raw_prolific, df_raw_tumblr)

df_raw <- df_raw %>% 
  #reorder 
  select( RANDOM_BLOCK, 
          End_State,
          StartDate:randomize_common, 
          ID_PROLIFIC:ID_SESSION, 
          D_gender:FEEDBACK, 
          PROLIFIC_PID: FL_14_DO,
          Q_RelevantIDDuplicate: Q_RelevantIDLastStartDate, 
          `0_Q_B0_ENCOUNTER`: `0_Q_B0_CHART_LATENCY_Click Count`, 
          `0_Q_B0_CHART_ACTION`, 
          `1_Q_B1_loop-number` : `1_Q_B1_CHART_LATENCY_Click Count`,
          `1_Q_B1_CHART_ACTION`, 
          `2_Q_B1_loop-number` : `2_Q_B1_CHART_LATENCY_Click Count`,
          `2_Q_B1_CHART_ACTION`, 
          `3_Q_B1_loop-number` : `3_Q_B1_CHART_LATENCY_Click Count`,
          `3_Q_B1_CHART_ACTION`, 
          `4_Q_B1_loop-number` : `4_Q_B1_CHART_LATENCY_Click Count`,
          `4_Q_B1_CHART_ACTION`, 
          `1_Q_B2_loop-number` : `1_Q_B2_CHART_LATENCY_Click Count`,
          `1_Q_B2_CHART_ACTION`, 
          `2_Q_B2_loop-number` : `2_Q_B2_CHART_LATENCY_Click Count`,
          `2_Q_B2_CHART_ACTION`, 
          `3_Q_B2_loop-number` : `3_Q_B2_CHART_LATENCY_Click Count`,
          `3_Q_B2_CHART_ACTION`, 
          `4_Q_B2_loop-number` : `4_Q_B2_CHART_LATENCY_Click Count`,
          `4_Q_B2_CHART_ACTION`, 
          `1_Q_B3_loop-number` : `1_Q_B3_CHART_LATENCY_Click Count`,
          `1_Q_B3_CHART_ACTION`, 
          `2_Q_B3_loop-number` : `2_Q_B3_CHART_LATENCY_Click Count`,
          `2_Q_B3_CHART_ACTION`, 
          `3_Q_B3_loop-number` : `3_Q_B3_CHART_LATENCY_Click Count`,
          `3_Q_B3_CHART_ACTION`, 
          `4_Q_B3_loop-number` : `4_Q_B3_CHART_LATENCY_Click Count`,
          `4_Q_B3_CHART_ACTION`, 
          `1_Q_B4_loop-number` : `1_Q_B4_CHART_LATENCY_Click Count`,
          `1_Q_B4_CHART_ACTION`, 
          `2_Q_B4_loop-number` : `2_Q_B4_CHART_LATENCY_Click Count`,
          `2_Q_B4_CHART_ACTION`, 
          `3_Q_B4_loop-number` : `3_Q_B4_CHART_LATENCY_Click Count`,
          `3_Q_B4_CHART_ACTION`, 
          `4_Q_B4_loop-number` : `4_Q_B4_CHART_LATENCY_Click Count`,
          `4_Q_B4_CHART_ACTION`, 
          `1_Q_B5_loop-number` : `1_Q_B5_CHART_LATENCY_Click Count`,
          `1_Q_B5_CHART_ACTION`, 
          `2_Q_B5_loop-number` : `2_Q_B5_CHART_LATENCY_Click Count`,
          `2_Q_B5_CHART_ACTION`, 
          `3_Q_B5_loop-number` : `3_Q_B5_CHART_LATENCY_Click Count`,
          `3_Q_B5_CHART_ACTION`, 
          `4_Q_B5_loop-number` : `4_Q_B5_CHART_LATENCY_Click Count`,
          `4_Q_B5_CHART_ACTION`, 
          `1_Q_B6_loop-number` : `1_Q_B6_CHART_LATENCY_Click Count`,
          `1_Q_B6_CHART_ACTION`, 
          `2_Q_B6_loop-number` : `2_Q_B6_CHART_LATENCY_Click Count`,
          `2_Q_B6_CHART_ACTION`, 
          `3_Q_B6_loop-number` : `3_Q_B6_CHART_LATENCY_Click Count`,
          `3_Q_B6_CHART_ACTION`, 
          `4_Q_B6_loop-number` : `4_Q_B6_CHART_LATENCY_Click Count`,
          `4_Q_B6_CHART_ACTION`
          #df_raw 937 vars           
  ) 



#DROP WIP DATAFRAMES 
rm(df_raw_datacollar, df_raw_bluecollar, df_raw_b1, df_raw_b2, df_raw_b3, df_raw_b4, df_raw_b5, df_raw_b6, df_raw_pilot, df_raw_prolific, df_raw_tumblr, df_raw_tumblr_free, df_raw_tumblr_paid)

```


### Clean Data 
```{r WRANGLE-CLEANING}

#2. CLEAN MASTER PARTICIPANT-LEVEL DF  #########################################################
################################################################################################
#### MASTER WIDE FORMAT DATA FRAME [1 row / qualtrics submission] ################

df_data <- df_raw %>% 
  select(
    -EndDate, -IPAddress, -RecordedDate,
    -RecipientLastName, -RecipientFirstName, -RecipientEmail,
    -ExternalReference, -LocationLatitude, -LocationLongitude, 
    -DistributionChannel, -UserLanguage, -Q_RecaptchaScore,
    -BROWSER_Version, -BROWSER_Resolution, 
    -CONSENT, -ELIGIBILITY, 
    -randomize_common,
    #hidden q that controls common stimulus url
    -stimulus_common, 
    #not actually randomization order
    -FL_14_DO, 
    -contains("First Click"), -contains("Last Click"), -contains("Click Count"),
    -D_politicalParty_DO, 
    -ID_PROLIFIC, -ID_STUDY, -ID_SESSION #redundant to other cols 
  ) %>% 
  dplyr::rename(
    duration.sec = `Duration (in seconds)`,
    EndState = End_State, 
    TerminateFlag = Q_TerminateFlag,
    Source = Status, #where the survey originated from (should not be preview or test)
    PLATFORM = Q_PLATFORM,
    ID.Qualtrics = ResponseId,
    ID.Prolific = PROLIFIC_PID,
    ID.Study = STUDY_ID,
    ID.Session = SESSION_ID,
    # P_BROWSER_OS = `P_BROWSER_Operating System`,
    # T_BROWSER_OS = `T_BROWSER_Operating System`,
    SCREEN_workFunction_TEXT = SCREEN_workFunction_22_TEXT, 
    SCREEN_socialMedia_TEXT = SCREEN_socialMedia_18_TEXT,
    D_politicalParty_OTHER = D_politicalParty_4_TEXT,
    D_politicsSocial = D_politicsSocial_1,
    D_politicsFiscal = D_politicsFiscal_2
 ) %>% 
  mutate(
    #SET FACTORS 
    D_politicsSocial = as.numeric(D_politicsSocial),
    D_politicsFiscal = as.numeric(D_politicsFiscal),
    ID.Study = factor(ID.Study),
    ID.Qualtrics = factor(ID.Qualtrics),
    ID.Prolific = factor(ID.Prolific),
    ID.Session = factor(ID.Session),
    PLATFORM = factor(PLATFORM),
    Source = factor(Source),
    Finished = as.logical(Finished),
    TerminateFlag = factor(TerminateFlag),
    EndState = factor(EndState), 
    D_gender = factor(D_gender), 
    D_gender_collapsed = fct_collapse(D_gender, 
                                female = "Female", 
                                male = "Male", 
                                other = c("Non-binary / third gender", "Prefer not to say", "Prefer to self-describe")),
    D_age = factor(D_age), 
    D_income = factor(D_income, 
                      levels = c(
                        "Prefer not to say",
                        "Less than $25,000",
                        "$25,000-$49,999"  ,
                        "$50,000-$74,999"  ,
                        "$75,000-$99,999"  ,
                        "$100,000-$149,999",
                        "$150,000 or more" 
                      )),
    D_employmentStatus = factor(D_employmentStatus),
    duration.sec = as.numeric(duration.sec), #weird booleans should only be for the test generator
    duration.min = round(duration.sec/60,2),
    Progress = as.numeric(Progress), 
    D_education = forcats::fct_na_value_to_level( D_education, level="NA"),
    D_education = forcats::fct_collapse( D_education,
                                no_data = "NA",
                                less_high_school = c("Some high school or less"),
                                high_school = c("High school diploma or GED"),
                                some_college = c("Some college, but no degree", "Some college, no degree"),
                                associates =c( "Associates or technical degree"),
                                undergrad = c("Bachelor’s degree","Bachelor's degree"),
                                grad = c("Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS etc.)",
                                         "Graduate or professional degree (MA, MS, MBA, PhD, JD, MD, DDS, etc)")
    ),
    D_education = factor(D_education, 
                                       levels = c("no_data", "less_high_school","high_school", "some_college",
                                         "associates", "undergrad", "grad"), 
                                       labels = c("NA", "some high school or less","high school diploma or GED ", 
                                                  "some college", "associates or technical degree", 
                                                  "undergradudate degree", "graduate or professional degree"), 
                                       ),
    D_politicalParty = factor(D_politicalParty, levels = c("No preference", "Other", "Independent", "Republican", "Democrat")),
    D_age = factor(D_age, 
                   levels = c("18-24 years old" ,
                              "25-34 years old" ,
                              "35-44 years old" ,
                              "45-54 years old" ,
                              "55-64 years old" ,
                              "65+ years old"   ), 
                   labels = c("18-24", "25-34","35-44","45-54","55-64","65+ years"))
  ) %>%
  #REPLACE RANDOM TRAILING _1 AND _65 FROM QUALTRICS
  rename_with( .cols = contains('_65'), .fn = ~str_replace(.,  pattern = '_65', replacement = '')) %>% 
  rename_with( .cols = contains('_1'), .fn = ~str_replace(.,  pattern = '_1', replacement = '')) %>% 
  #RM _PAGE Submit from LATENCY
  rename_with( .cols = contains('_Page Submit'), .fn = ~str_replace(.,  pattern = '_Page Submit', replacement = '')) %>% 
  #CHANGE DETAIL QUESTION DELIMITER FOR PIVOT PURPOSES 
  rename_with( .cols = contains('_CHART_'), .fn = ~str_replace(.,  pattern = '_CHART_', replacement = '_CHART-')) %>% 
  #CHANGE DETAIL QUESTION DELIMITER FOR PIVOT PURPOSES 
  rename_with( .cols = contains('_MAKER_'), .fn = ~str_replace(.,  pattern = '_MAKER_', replacement = '_MAKER-')) %>% 
  #CHANGE DETAIL QUESTION DELIMITER FOR PIVOT PURPOSES 
  rename_with( .cols = contains('_AGE_'), .fn = ~str_replace(.,  pattern = '_AGE_', replacement = '_AGE-')) %>% 
  #CHANGE DETAIL QUESTION DELIMITER FOR PIVOT PURPOSES 
  rename_with (.cols = contains('_GENDER_'), .fn = ~str_replace(., pattern = '_GENDER_', replacement = '_GENDER-')) %>% 
  #CHANGE DETAIL QUESTION DELIMITER FOR PIVOT PURPOSES 
  rename_with (.cols = contains('_TOOL_'), .fn = ~str_replace(., pattern = '_TOOL_', replacement = '_TOOL-')) %>% 
  select(
    #reordering
    RANDOM_BLOCK:Progress, 
    Finished, EndState, TerminateFlag, 
    Q_RelevantIDDuplicate:Q_RelevantIDLastStartDate,
    ID.Qualtrics, 
    ID.Prolific : ID.Session, 
    duration.sec, duration.min,
    BROWSER_Browser : BROWSER_OS, 
    D_gender_collapsed, D_gender:D_politicsFiscal,
    SCREEN_workMethod: SCREEN_socialMedia_TEXT, 
    PURPOSE, FEEDBACK, PLATFORM,
    `0_Q_B0_ENCOUNTER`: `4_Q_B6_CHART-ACTION`
  ) 

##### JOIN STUDY-LEVEL DATA 
df_data <- dplyr::left_join(df_data, df_studies, by="ID.Study") 

#SET IDS AND ASSIGNED BLOCK TO HANDLE PROLIFIC AND TUMBLR 
df_data <- df_data %>% 
  mutate(
    # SET ASSIGNMENT BLOCK FOR TUMBLR
    Assigned.Block = if_else( (Distribution =="TUMBLR"), RANDOM_BLOCK, Assigned.Block),
    Assigned.Block = factor(Assigned.Block), 
    # PID = if_else( (Distribution =="TUMBLR"), ID.Qualtrics, ID.Prolific),
    PID = factor(ID.Qualtrics)
  ) %>% #DROP RANDOM_BLOC COLUMNS
  select (-RANDOM_BLOCK) %>% 
  select(
    #REORDER
    PID, 
    Distribution, 
    Assigned.Block,
    ID.Qualtrics:ID.Session,
    EndState,
    StartDate: Q_RelevantIDLastStartDate, 
    Prolific.Name, Qualtrics.Survey,  Qualtrics.URL, Description, Sample, Scope, 
    duration.sec:PLATFORM,
    `0_Q_B0_ENCOUNTER` : `4_Q_B6_CHART-ACTION`
  )


#2B CLEAN MASTER PARTICIPANT-LEVEL DF  #########################################
#### SEGREGATE PARTICIPANTS WHO DID NOT COMPLETE ###############################
## [1 row / qualtrics submission] ################
## NOTE it is common for prolific participants to fail the 
## screening verification, and then try again but change their 
## screening verification answers (ie. one prolific ID for multiple qualrics IDs)
df_exclude <- df_data %>% 
  filter( 
    !is.na(TerminateFlag) | Finished == FALSE | EndState != "COMPLETE"  
  ) %>% 
  select(
    PID, Distribution, ID.Qualtrics, ID.Prolific, ID.Study, Assigned.Block, Scope, Source, Progress, 
    Finished, TerminateFlag, EndState,StartDate, duration.min, 
    D_gender:D_politicsFiscal, SCREEN_workMethod:FEEDBACK, Prolific.Name:Scope
  )  %>% 
  mutate(
    EndState = if_else( (Progress < 100), "abandoned", EndState),
    EndState = if_else( (str_detect(EndState,"screen")), "screened", EndState),
    EndState = if_else( (TerminateFlag == "Screened" & is.na(EndState)), "screened", EndState),
    EndState = factor(EndState)
  )

#### MASTER VALID DATA [WIDE] 1 row per qualtrics entry #########################
## [1 row / qualtrics submission] ################
df_data <- df_data %>% filter(
  PID %nin% df_exclude$PID
  # (Finished == TRUE ) & is.na(TerminateFlag)
) %>% mutate(
  EndState = droplevels(EndState),
  ID.Prolific = droplevels(ID.Prolific),
  ID.Qualtrics = droplevels(ID.Qualtrics), 
  PID = droplevels((PID))
  
)

#sanity check === SHOULD BE O
#no qualtrics surveys in good data that weren't finished
print("Number of PID entries in df_data AND nofinish/excluded? [should be 0]")
sum(df_data$PID %in% df_exclude$PID)

#sanity check === SHOULD BE O
#no duplicated PROLIFIC ids in good data 
print("Number of PIDs duplicated in df_data print [should be 0]")
sum(duplicated(df_data$PID))


## save participant-level data file for qda validation 
## note that this DOES contain pilot data 
## this does NOT contain excluded participants 
write.csv(df_data, file = "data/output/df_participants.csv", na="")


#3 CREATE TRIAL LEVEL DFS FOR QDA ###############################################
#### CHART LEVEL DATA FRAME (LONG) FOR QDA (incl demographics) ##################
#### INCLUDES PILOT DATA FROM DATACOLLAR BLUECOLLAR PROLIFIC RECRUITMENT ########
# 1 ROW / participant X GRAPH including demographics 
# UNRAVEL TO QUESTIONS
df_qda_input <- df_data %>% 
  # select(
  # ID.Qualtrics:ID.Study, PLATFORM,
  # contains("_Q_"), contains("loop")
# ) %>% 
  pivot_longer( #PIVOT ON stimulus
  cols = contains("_Q_"),
  names_to = c("stimulus","dummy","BLOCK","QUESTION"),
  values_to = c("value"),
  names_sep = "_"
) %>% select(-dummy) %>% 
  unite(
   BLOCK:stimulus, col="STIMULUS", sep="-", remove=FALSE
) %>% 
  mutate(
    BLOCK = factor(BLOCK),
    STIMULUS = factor(STIMULUS),
    QUESTION = str_replace_all(QUESTION,"-","_"),
    QUESTION = factor(QUESTION),
    STIMULUS_CATEGORY = str_remove(STIMULUS,"B.-"),
    STIMULUS_CATEGORY = factor(STIMULUS_CATEGORY,
                  levels=c("0","4","3","2","1"),
                  labels= c("F","D","C","B","A"))
) %>% 
  select(-stimulus) %>% 
# RE-RAVEL UP TO STIMULI
  filter(!is.na(value)) %>% 
   pivot_wider(
    names_from = QUESTION,
    values_from = value 
  ) %>%  
  tidyr::unnest() %>%  # handle r coerces values to lists
  mutate(
    across(contains("MAKER_ID") | contains("MAKER_GENDER") | contains("MAKER_AGE"), factor),
    across(contains("_CONF") | contains("_LATENCY"), as.numeric),
    across(MAKER_DESIGN:MAKER_TRUST, as.numeric),
    across(CHART_LIKE:CHART_TRUST, as.numeric),
    ENCOUNTER = factor(ENCOUNTER),
    # loop_number = as.numeric(loop_number),
    # loop_number = ifelse(is.na(loop_number), 0, loop_number),
    MAKER_LATENCY = round(MAKER_LATENCY/60,2), #CHANGE TO MINS
    CHART_LATENCY = round(CHART_LATENCY/60,2) #CHANGE TO MINS
  )
#WRITE A CSV FILE AS THE BASIS FOR THE QUALITATIVE DATA ANALYSIS
write.csv(df_qda_input, file = "data/output/df_qda_input.csv", na="")


#### REMOVE PILOT DATA FROM DF_DATA 
## pilot data IS not included QDA file, but not in quant analysis 
df_data <- df_data %>% 
  filter(Scope != "pilot") %>% 
  mutate(
    ID.Study = droplevels(ID.Study), 
    ID.Prolific = droplevels(ID.Prolific),
    ID.Qualtrics = droplevels(ID.Qualtrics),
    PID = droplevels(PID)
  ) 

########## CHECK BLOCK COUNTS 
# title = "Participants by Condition and Data Collection Modality"
# cols = c("Control Condition","Impasse Condition","Total for Period")


title = "Number of abandoned/screened/rejected attempts "
cols = c("Block","pilot","study2","sum")
cont <- table(df_exclude$Assigned.Block, df_exclude$Scope)
cont %>% addmargins() %>% kbl(caption = title, col.names = cols) %>%  kable_classic()

title = "Number of abandoned/screened/rejected attempts by type"
cols = c("Rejection Type", "Sum")
cont <- table(df_exclude$EndState)
cont %>% addmargins() %>% kbl(caption = title, col.names = cols) %>%  kable_classic()

title = "Number of successful surveys"
cols = c("Assigned.Block", "Sum")
cont <- table(df_data$Assigned.Block)
cont %>% addmargins() %>% kbl(caption = title, col.names = cols) %>%  kable_classic()

title = "Number of successful surveys by distribution"
cols = c("Sampling Platform", "Sum")
cont <- table(df_data$Distribution)
cont %>% addmargins() %>% kbl(caption = title, col.names = cols) %>%  kable_classic()




title = "Number of successful surveys by distribution and block"
cols = c("Sampling Platform", "Block-1","Block-2","Block-3","Block-4","Block-5","Block-6", "Sum")
cont <- table(df_data$Distribution, df_data$Assigned.Block)
cont %>% addmargins() %>% kbl(caption = title, col.names = cols) %>%  kable_classic()


##### CREATE PARTICIPANT LEVEL SIMPLFIFLIED DATAFRAME 
df_participants <- df_data %>% 
  select(
    PID:Assigned.Block, 
    EndState, Sample, Scope, 
    duration.sec, duration.min, 
    contains("D_"), 
    contains("SCREEN_")
  )

# END WRANGLE MASTER WIDE PARTICIPANT LEVEL DATA FRAME 
################################################################################################
################################################################################################

print("df_data represents full set of valid complete participants [wide]")
print("df_participants represents full set of valid complete participants [simplified]")

```

### Wrangle Question and Trial Level 
```{r WRANGLE-QUESTION-LEVEL}

#4 CREATE QUESTION LEVEL DFS ###################################################################
#### QUESTION LEVEL DATA FRAME (LONG) ##########################
# unravel ALL the way down to questions 
# 1 row per participant-graph-question
df_questions <- df_data %>% 
  select(
  PID, duration.min,  Assigned.Block,
  Sample, Scope, Distribution, PLATFORM, 
  D_gender_collapsed:D_politicsFiscal, 
  contains("_Q_"), contains("loop"), 
) %>% 
  pivot_longer( #PIVOT ON stimulus
  cols = contains("_Q_"),
  names_to = c("stimulus","dummy","BLOCK","QUESTION"),
  values_to = c("value"),
  names_sep = "_"
) %>% select(-dummy) %>% 
  unite(
   BLOCK:stimulus, col="STIMULUS", sep="-", remove=FALSE
) %>% 
  mutate(
    BLOCK = factor(BLOCK),
    STIMULUS = factor(STIMULUS),
    QUESTION = str_replace_all(QUESTION,"-","_"),
    QUESTION = factor(QUESTION, 
                      levels = c(
                        "ENCOUNTER",    
                        "MAKER_ID",        
                        "MAKER_DETAIL", 
                        "MAKER_CONF",
                        "MAKER_AGE", 
                        "AGE_CONF",
                        "MAKER_GENDER",
                        "GENDER_CONF",
                        "MAKER_DESIGN",  
                        "MAKER_DATA",    
                        "MAKER_POLITIC",
                        "MAKER_ARGUE",  
                        "MAKER_SELF",   
                        "MAKER_ALIGN",    
                        "MAKER_TRUST", 
                        "MAKER_EXPLAIN",
                        "MAKER_LATENCY", 
                        "TOOL_ID",     
                        "TOOL_CONF",     
                        "TOOL_DETAIL",   
                        "CHART_LIKE",    
                        "CHART_BEAUTY",  
                        "CHART_INTENT", 
                        "CHART_TRUST",   
                        "CHART_TYPE",    
                        "CHART_ACTION",  
                        "CHART_EXPLAIN", 
                        "CHART_LATENCY", 
                        "loop_number" )),
    STIMULUS_CATEGORY = str_remove(STIMULUS,"B.-"),
    STIMULUS_CATEGORY = factor(STIMULUS_CATEGORY,
                  levels=c("0","4","3","2","1"),
                  labels= c("F","D","C","B","A"))
) %>% 
  select(-stimulus) %>% filter(!is.na(value))


#### SD QUESTION LEVEL DATA FRAME (wide-stim) ##########################
# ravel up one level from questions
# 1 row per participant-question with all blocks as cols for SD qs
df_sd_questions_wide <- df_questions %>%
  select(-BLOCK,-STIMULUS_CATEGORY) %>% #drop block in order to work at stimulus level
  filter(QUESTION %in% ref_sd_questions) %>% 
  pivot_wider(
    names_from = STIMULUS,
    values_from = value 
  ) %>%  
  tidyr::unnest() %>%  # handle r coerces values to lists
  mutate(
    across(contains("-") , as.numeric),
    QUESTION = droplevels(QUESTION)
  )



### SD QUESTIONS LEVEL DATA FRAME (LONG) #####################
df_sd_questions_long <- df_questions %>% 
  filter(QUESTION %in% ref_sd_questions) %>% 
  mutate(
    QUESTION = droplevels(QUESTION),
    value = as.numeric(value)
  )


#5 SPECIAL DFS FOR MULTISELECT QS  #####################################################
#### MULTI-SELECT QUESTIONS  ##########################

## DF_TOOLS 
# 1 ROW per PARTICIPANT X STIMULUS X tool_id selection 
# tool_id is a multiselect field 
df_tools <- df_questions %>% 
  # select(ID.Prolific, QUESTION, value) %>%
  filter(QUESTION  %in% c("TOOL_ID", "TOOL_CONF")) %>% 
  mutate(QUESTION = fct_drop(QUESTION)) %>% 
  pivot_wider(
    names_from = QUESTION,
    values_from = value 
  ) %>% 
  separate_longer_delim(
    cols = TOOL_ID,
    delim = ","
  ) %>% 
  mutate(TOOL_ID = factor(TOOL_ID, 
                             levels = c("?", "design_basic","design_advanced", "viz_basic", "viz_advanced", "programming")),
         PID = droplevels(PID),
         TOOL_CONF = as.numeric(TOOL_CONF)
         ) 

## DF_ACTIONS 
# 1 ROW per PARTICIPANT X STIMULUS X chart_action selection 
# chart_action is a multiselect field 
df_actions <- df_questions %>% 
  filter(QUESTION == "CHART_ACTION") %>% 
  mutate(QUESTION = fct_drop(QUESTION)) %>% 
  separate_longer_delim(
    cols = value,
    delim = ","
  ) %>% 
  mutate(CHART_ACTION = factor(value, 
                                  levels =  c("NOTHING — just keep scrolling",
                                              "unfollow / block the source",
                                              "post a comment",
                                              "share / repost",
                                              "share / repost WITH comment",
                                              "look up more information about the topic or source"),
                                  labels =  c("nothing",
                                              "unfollow/block",
                                              "comment",  
                                              "share",
                                              "share w/ comment",
                                              "seek information")),
         PID = droplevels(PID)) %>% 
  select(-value,-QUESTION)


#6 DFS FOR TRIAL LEVEL ANALYSIS   ######################################################
#### CHART LEVEL DATA FRAME (LONG) #####################################################
# roll partway back up from questions 
# 1 row per participant X graph 
# unnest https://stackoverflow.com/questions/58035452/pivot-wider-outputs-s3-vctrs-list-of-objects
df_graphs_full <- df_questions %>% 
  pivot_wider(
    names_from = QUESTION,
    values_from = value 
  ) %>%  
  tidyr::unnest() %>%  # handle r coerces values to lists
  mutate(
    across(contains("MAKER_ID") | contains("MAKER_GENDER") | contains("MAKER_AGE"), factor),
    across(contains("_CONF") | contains("_LATENCY"), as.numeric),
    across(MAKER_DESIGN:MAKER_TRUST, as.numeric),
    across(CHART_LIKE:CHART_TRUST, as.numeric),
    ENCOUNTER = factor(ENCOUNTER),
    # loop_number = as.numeric(loop_number),
    # loop_number = ifelse(is.na(loop_number), 0, loop_number),
    MAKER_LATENCY = round(MAKER_LATENCY/60,2), #CHANGE TO MINS
    CHART_LATENCY = round(CHART_LATENCY/60,2), #CHANGE TO MINS
    MAKER_ID = factor( MAKER_ID,levels = c("business", "political", "education","news","organization","individual"))
  )

#7 DFS FOR TRIAL LEVEL ANALYSIS w/o free response ######################################################
#### CHART LEVEL DATA FRAME (LONG) ##########################
## SUBSET OF COLUMNS EXCLUDING THE FREE RESPONSES and MULTISELECT
df_graphs <- df_graphs_full %>% 
  select( !where(is.character))

print("df_graphs_full is trial level dataset; df_graphs is trial level quantitative data only")

```
## Wrangle  Participant Confidence 
```{r wrangle-confidence}


## CALCULATE AV CONFIDENCE FOR EACH SEMANTIC DIFFERENTIALS 
df_sds <- df_sd_questions_long %>% 
  group_by(PID, QUESTION) %>% 
  summarize(
    mean = mean(value), 
    sd = sd (value)
  ) 

df_sds_WIDE <- df_sds %>% 
    pivot_wider(
      names_from = QUESTION,
      values_from = c(mean, sd)
  )

## CALCULATE AV CONFIDENCE ACROSS SEMANTIC DIFFERENTIALS 
df_grandsds <- df_sd_questions_long %>% 
  group_by(PID) %>% 
  summarize(
    SDIFF_mean = mean(value), 
    SDIFF_sd = sd(value)
  ) 


df_grandsds_LONG <- df_grandsds %>% 
  mutate(
      QUESTION = "SDIFF", 
      mean = SDIFF_mean, 
      sd = SDIFF_sd
) %>% select(-SDIFF_mean, -SDIFF_sd)
  


## CALCULATE AV CONFIDENCE FOR EACH CONFIDENCE
df_confq <- df_questions %>% 
  filter(QUESTION %in% ref_conf_questions)%>% 
  group_by(PID, QUESTION) %>% 
  summarize(
    mean = mean(as.numeric(value)), 
    sd = sd (as.numeric(value))
  ) 

df_confq_WIDE <- df_confq %>% 
    pivot_wider(
      names_from = QUESTION,
      values_from = c(mean, sd)
  )

## CALCULATE AV CONFIDENCE ACROSS SEMANTIC DIFFERENTIALS 
df_grandconfs <- df_questions %>% 
  filter(QUESTION %in% ref_conf_questions)%>% 
  group_by(PID) %>% 
  summarize(
    CONF_mean = mean(as.numeric(value)), 
    CONF_sd = sd(as.numeric(value))
  )


df_grandconfs_LONG <- df_grandconfs %>% 
  mutate(
      QUESTION = "CONF", 
      mean = CONF_mean, 
      sd = CONF_sd
) %>% select(-CONF_mean, -CONF_sd) 
  



## JOIN TOGETHER WIDE
df_confidence_wide <- left_join(df_sds_WIDE, df_confq_WIDE, by="PID")
df_confidence_wide <- left_join(df_confidence_wide, df_grandsds, by = "PID")
df_confidence_wide <- left_join(df_confidence_wide, df_grandconfs, by = "PID")
df_confidence_wide <- left_join(df_confidence_wide, df_participants, by = "PID")


##JOIN TOGETHER LONG
df_confidence_long <- rbind(df_sds, df_confq, df_grandsds_LONG, df_grandconfs_LONG) %>% 
  mutate(
    QUESTION = factor(QUESTION)
  ) 

df_confidence_long <- left_join(df_confidence_long, df_participants, by="PID")

rm(df_sds, df_grandsds, df_confq, df_grandconfs, df_sds_WIDE, df_grandsds_LONG, df_confq_WIDE, df_grandconfs_LONG)

print("df_confidence_wide is a participant level dataset with by question and question type mean and df per participant")
print("df_confidence_long is a participant level dataset with by question and question type mean and df per participant")
print("In both cases the means are over all 5 stimuli seen by each participant")

```

### Vibe Check

```{r vibe-search}

#special search for the word "vibe" .... because... vibes 

#get purpose and feedback questions and format as long
df_purpose <- df_data %>% 
  select(
    PID, PURPOSE, FEEDBACK
) %>% mutate(
  STIMULUS = "NONE"
) %>% pivot_longer(
  cols = c("PURPOSE", "FEEDBACK"), 
  names_to = "QUESTION",
  values_to = "value"
)

#get free response questions in long format 
df_free <- df_questions %>% 
  select(
    PID, STIMULUS, QUESTION, value
  ) %>% 
  filter(
    QUESTION %in% ref_free_response
  )


#join these dataframes 
df_vibes <- rbind(df_purpose, df_free)
##6992

#SEARCH FOR VIBES! 
df_vibes <- df_vibes %>% 
  filter(
    str_detect(value, regex(
      "vibe",
      ignore_case=TRUE, 
      multiline = TRUE,
      dotall = TRUE))
  )

## ADD PARTICIPANT DATA 
df_vibes <- left_join(df_vibes, df_participants, by="PID")

## WRITE VIBE DATA 
write.csv(df_vibes, file = "data/output/df_vibes.csv", na="")







#special search for the word "core" .... because... tumblr-core
#join these dataframes 
df_core <- rbind(df_purpose, df_free)
##6992

#SEARCH FOR VIBES! 
df_core <- df_core %>% 
  filter(
    str_detect(value, regex(
      "core",
      ignore_case=TRUE, 
      multiline = TRUE,
      dotall = TRUE))
  )

## ADD PARTICIPANT DATA 
df_core <- left_join(df_core, df_participants, by="PID")

## WRITE VIBE DATA 
write.csv(df_core, file = "data/output/df_core.csv", na="")

rm(df_free, df_purpose)

```


### TODO Wrangle QDA 
```{r WRANGLE-QDA}
#8 TRIAL LEVEL DATA INCLUDING QDA CODING ############################################################
#### CHART LEVEL DATA FRAME (LONG) ##########################




# ### TODO PICK UP HERE
# 
# 
# # import coded QDA data
# # participant X chart level
# df_coded <- read_csv("data/input/QDA/s2_qda_maker.csv", col_names = TRUE)
# # create unique key for join
# df_coded <- df_coded %>% filter(
#   Scope != "pilot"   #filter out pilot data
# ) %>% mutate(
#   TRIAL = paste0(STIMULUS,"_",ID.Prolific)
# ) %>% select(
#   #TODO ADD CODED DATA THEY ARE ADDED
#   TRIAL, CODE_M_ID_SPECIFIC
# )
# 
# # create base dataframe
# df_graphs_coded <- df_graphs_full %>% mutate(
#   TRIAL = paste0(STIMULUS,"_",ID.Prolific)
# )
# 
# ##SANITY CHECK
# print("coded df & trials df have same num rows")
# nrow(df_coded) == nrow(df_graphs_coded)
# 
# df_graphs_coded <- dplyr::left_join(df_graphs_coded, df_coded, by="TRIAL") %>%
#   select(
#   #reorder cols
#   duration.min:D_politicsFiscal, BLOCK:MAKER_ID, MAKER_CONF:CHART_ACTION, STIMULUS, ID.Prolific,  TRIAL, MAKER_DETAIL, CODE_M_ID_SPECIFIC
# )
# 
# ##SANITY CHECK
# print("coded df & trials df have same num rows")
# nrow(df_graphs) == nrow(df_graphs_coded)
# 
# #####################################################################################
# ################ SANITY CHECKS ######################################################
# #CHECK BLOCKS PER PARTICIPANT
# # every participant should have 2 blocks
# check_subject_blocks <- df_questions %>%
#   group_by(ID.Prolific) %>% summarise(
#     n_block = length(unique(BLOCK))
#   )
# print("every participant should have two blocks, [block 0 + randomly assigned block]")
# all(check_subject_blocks$n_block==2)
# 
# 
# #CHECK STIMULI PER PARTICIPANT
# # every participant should have 5 graphs
# check_subject_graphs <- df_questions %>%
#   group_by(ID.Prolific) %>%summarise(
#     n_graphs = length(unique(STIMULUS))
#   ) #each participant should have five graphs
# print("every participant should have five stimuli [B0 + 4 stimuli in a block]]")
# all(check_subject_graphs$n_graphs==5)
# 
# 
# 
# 
# 
# 
# 
# 
# #CLEANUP
# rm(check_subject_blocks, check_subject_graphs, df_graphs_qda, df_coded)

```

## Graphing Functions

```{r SD-GRAPHING-FUNCTIONS}


############## RETURNS SD STACKED AND COLORED BY BY X
## LOOP STYLE
multi_sd <- function (df, left, right, x, y, color) {

  # g <- ggplot(df, aes(y = .data[[x]], x = {{y}}, color = {{color}}))+
  g <- ggplot(df, aes(y = .data[[x]], x = .data[[y]], color = .data[[color]]))+
  geom_boxplot(width = 0.5) +
  geom_jitter(width = 0.1, alpha=0.5) +
  scale_y_continuous(limits=c(-1,101)) +
  labs(x="", y="") +
  coord_flip() +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) + theme_minimal()

  return(g)
}


############## RETURNS SINGLE SD 
## LOOP STYLE
single_sd <- function (df, left, right, x) {

  g <- ggplot(df, aes(y = {{x}}, x = ""))+
  geom_boxplot(width = 0.5) +
  geom_jitter(width = 0.1, alpha=0.5) +
  scale_y_continuous(limits=c(-1,101)) +
  labs(x="", y="") +
  coord_flip() +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) + theme_minimal()

  return(g)
}



######## RETURNS SINGLE SD
##  APPLY STYLE
# plot_sd = function (data, column, type, split, boxplot) {
# 
#   ggplot(df, aes(y = .data[[column]], x="")) +
#     {if(boxplot) geom_boxplot(width = 0.5) } +
#     geom_jitter(width = 0.1, alpha=0.3, {if(split) aes(color=Distribution)}) +
#     {if(split) facet_grid(Distribution ~ .)} +
#     scale_y_continuous(limits=c(-1,101)) +
#     labs(x="", y="") +
#     coord_flip()  +
#     {if(type == "S")
#       guides(
#         y = guide_axis_manual(labels = ref_labels[column,"left"]),
#         y.sec = guide_axis_manual(labels = ref_labels[column,"right"])
#       )} +
#     {if(type == "Q")
#       guides(
#         y = guide_axis_manual(labels = ref_labels[q,"left"]),
#         y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
#       )} +
#   theme_minimal()  +
#      labs (
#        caption = column
#      )
# }


# # ##  APPLY STYLE
plot_sd = function (data, column, type, facet, facet_by, boxplot) {

  ggplot(df, aes(y = .data[[column]], x="")) +
    {if(boxplot) geom_boxplot(width = 0.5) } +
    geom_jitter(width = 0.1, alpha=0.3, {if(facet) aes(color=.data[[facet_by]])}) +
    {if(facet) facet_grid(.data[[facet_by]] ~ .)} +
    scale_y_continuous(limits=c(-1,101)) +
    labs(x="", y="") +
    coord_flip()  +
    {if(type == "S")
      guides(
        y = guide_axis_manual(labels = ref_labels[column,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[column,"right"])
      )} +
    {if(type == "Q")
      guides(
        y = guide_axis_manual(labels = ref_labels[q,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
      )} +
  theme_minimal()  +
     labs (
       caption = column
     ) + easy_remove_legend()
}

```

```{r}

df_p <- df_participants


df_t <- df_qda_input
df_t <- df_t %>% select(
  -PURPOSE, -FEEDBACK
)


write.csv(df_p, file = "data/output/clean_participants.csv", na="")
write.csv(df_t, file = "data/output/clean_trials.csv", na="")

```




# PROFILING

## Descriptives

```{r summarytools-profile, results='asis'}


dfSummary(df_data %>% select(PID, duration.min, Distribution, Assigned.Block, PLATFORM, 
                             contains("D_"), Prolific.Name:Scope, contains("SCREEN_")), 
          headings = TRUE,
          plain.ascii  = FALSE,
          style        = 'grid',
          graph.magnif = 0.85,
          varnumbers = FALSE,
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")


```

## Plotting the dataframe

```{r plot-dataframe}

# print("Explore shapes of the prepared dataframes")
# 
# qacBase::df_plot(df_graphs)
# qacBase::df_plot(df_questions)
# qacBase::df_plot(df_sd_questions_long)
# qacBase::df_plot(df_sd_questions_wide)
# qacBase::barcharts(df_participants)

```


## Demographics


### Participant Sample

```{r}

df <- df_participants

tab(df_participants, Distribution)


```


### Total Response Time
```{r demo-response-time}

df <- df_data

## BOXPLOT — SURVEY RESPONSE TIME 
ggplot(df_data, aes(x=fct_rev(Assigned.Block), y=duration.min, color=Assigned.Block))+
  geom_boxplot(position=position_dodge(0.9))+
  geom_jitter(position=position_jitterdodge(), alpha = 0.3) +
  facet_grid(Distribution ~.) + 
  coord_flip() + 
  labs( y = "Survey Response Time (mins)", x="",
        title = "TOTAL Response Time by Sample",
        subtitle = "(distributions of response times are similar across samples, as expected)") +
  theme_minimal() + theme(legend.position = "none") 

## RIDGEPLOT — SURVEY RESPONSE TIME 
ggplot(df, aes(x = duration.min, y = fct_rev(Assigned.Block), fill = fct_rev(Assigned.Block))) +
  geom_density_ridges(scale=0.8) +
  # geom_boxplot()+
  stat_pointinterval()+
  theme_ridges() +
  scale_fill_discrete(direction=-1)+
  facet_grid(Distribution ~.) + 
  theme_minimal() + 
  theme(legend.position = "none") +
    labs( x = "Survey Response Time (mins)", y="",
        title = "TOTAL Response Time by Sample",
        subtitle = "(distributions of response times are similar across samples, as expected)") 



p.desc.duration <- psych::describe(df_data %>% filter(Distribution=="PROLIFIC") %>% pull(duration.min))
t.desc.duration <- psych::describe(df_data %>% filter(Distribution=="TUMBLR") %>% pull(duration.min))

``` 


PROLIFIC SAMPLE (n = `r p.desc.duration$n` ) participant response times ranged from `r p.desc.duration$min` to `r p.desc.duration$max` minutes, with a mean response time of `r round(p.desc.duration$mean,2)` minutes, SD = `r (round(p.desc.duration$sd,2))`.

TUMBLR SAMPLE (n = `r t.desc.duration$n` ) participant response times ranged from `r t.desc.duration$min` to `r t.desc.duration$max` minutes, with a mean response time of `r round(t.desc.duration$mean,2)` minutes, SD = `r (round(t.desc.duration$sd,2))`.

### Age

```{r demo-age, message=FALSE}
 
# AGE by SAMPLE
ggplot(data = df_data, aes( x = Assigned.Block, fill = fct_rev(D_age) )) +
  geom_bar(position = "stack") +
  facet_grid(Distribution ~ .) + 
  labs( title = "AGE by Sample", subtitle = "Expect similiar across samples", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
  theme_minimal() +
  easy_add_legend_title("")


# OVERALL AGE
ggstatsplot::ggbarstats(df_data, x= D_age, y=Distribution,
                          results.subtitle = FALSE) +
    theme_minimal() +
    scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
    easy_add_legend_title("Age") + 
    labs (title = "Participant Age")



```

### Gender

```{r demo-gender, message=FALSE}
 
# GENDER by SAMPLE
ggplot(data = df_data, aes( x = Assigned.Block, fill = fct_rev(D_gender) )) +
  geom_bar(position = "stack") +
  facet_grid(Distribution ~ .) + 
  labs( title = "Gender by Sample", subtitle = "Expect similiar across samples", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
  theme_minimal() 
  # easy_add_legend_title("")


# OVERALL GENDER
ggstatsplot::ggbarstats(df_data, x= D_gender, y=Distribution, 
                        results.subtitle = FALSE) +
    theme_minimal() +
    scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
    easy_add_legend_title("Gender") + 
    labs (title = "Participant Gender")


# COLLAPSED GENDER
ggstatsplot::ggbarstats(df_data, x= D_gender_collapsed, y=Distribution,
                        results.subtitle = FALSE) +
    theme_minimal() +
    scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
    easy_add_legend_title("Gender") + 
    labs (title = "Participant Gender (Collapsed)")


#PROLIFIC
df.p <- df_data %>% filter(Distribution == "PROLIFIC")
desc.gender.p <- table(df.p$D_gender) %>% prop.table() 
names(desc.gender.p) <- levels(df.p$D_gender)
p_participants <- nrow(df.p)


#TUMBLR
df.t <- df_data %>% filter(Distribution == "TUMBLR")
desc.gender.t <- table(df.t$D_gender) %>% prop.table() 
names(desc.gender.t) <- levels(df.t$D_gender)
t_participants <- nrow(df.t)


title = "Participant Gender — Self Describe"
cols = c("Text","Count")
cont <- table(df_data$D_gender_4_TEXT)
cont %>% addmargins() %>% kbl(caption = title, col.names = cols) %>%  kable_classic()


round(prop.table(table(df_participants$Distribution, df_participants$D_gender), margin=1),3)

```


`r p_participants` individuals from Prolific participated in Study 2, ( `r round(desc.gender.p[["Female"]],2)*100`% Female, `r round(desc.gender.p[["Male"]],2)*100`% Male, `r round(desc.gender.p[["Non-binary / third gender"]],2)*100`% Non-binary, `r (round((desc.gender.p[["Prefer not to say"]] + desc.gender.p[["Prefer to self-describe"]]),2)) * 100`% Other).


Note that a higher proportion of participants recruited from Tumblr represent identities other than cis-gender Female and cis-gender Male.   `r t_participants` individuals from Tumblr participated in Study 2, ( `r round(desc.gender.t[["Female"]],2)*100`% Female, `r round(desc.gender.t[["Male"]],2)*100`% Male, `r round(desc.gender.t[["Non-binary / third gender"]],2)*100`% Non-binary, `r (round((desc.gender.t[["Prefer not to say"]] + desc.gender.t[["Prefer to self-describe"]]),2)) * 100`% Other).

### Education
```{r demo-education, message=FALSE}

df <- df_data

# EDUCATION by SAMPLE
ggplot(data = df, aes( x = Assigned.Block, fill = D_education )) +
  geom_bar(position = "stack") +
  facet_grid(Distribution ~ .)+
  scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
  labs( title = "EDUCATION by Sample",
        subtitle = "Expect similiar across samples") +
  theme_minimal() +
  easy_add_legend_title("Education")


# INCOME BY EDUCATION
ggstatsplot::ggbarstats(df_data, x= D_education, y=D_income) +
    theme_minimal() +
    scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) +
    labs (title = "INCOME by EDUCATION")


```



### Political Values

```{r, demo-political-values, warning=FALSE}

df <- df_graphs

# FISCAL POLITICAL SAMPLE

leftside <- rep("left-leaning", length(ref_blocks))
rightside <- rep("right-leaning", length(ref_blocks))
g <- ggplot(df_data, aes(x=fct_rev(Assigned.Block), y=D_politicsFiscal, color=Assigned.Block)) +
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.3) +
  facet_grid(Distribution ~ .)+
  labs( title = "FISCAL VALUES by Sample",
        subtitle = "(expect similar values across samples)",
         y = "Fiscal Politics", x = "") +
  # easy_add_legend_title("Sample") +
  theme_minimal() +
  coord_flip()
g + guides(
  y = guide_axis_manual(
  breaks = ref_blocks,
  labels = leftside
  ),
  y.sec = guide_axis_manual(
  breaks = ref_blocks,
  labels = rightside
))

# SOCIAL POLITICAL SAMPLE

leftside <- rep("left-leaning", length(ref_blocks))
rightside <- rep("right-leaning", length(ref_blocks))
g <- ggplot(df_data, aes(x=fct_rev(Assigned.Block), y=D_politicsSocial, color=Assigned.Block)) +
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.3) +
  facet_grid(Distribution ~ .)+
  labs( title = "SOCIAL VALUES by Sample",
        subtitle = "(expect similar values across samples)",
         y = "Social Politics", x = "") +
  # easy_add_legend_title("Sample") +
  theme_minimal() +
  coord_flip()
g + guides(
  y = guide_axis_manual(
  breaks = ref_blocks,
  labels = leftside
  ),
  y.sec = guide_axis_manual(
  breaks = ref_blocks,
  labels = rightside
))

r_politics <- nrow(df_data %>% filter(D_politicsSocial >= 50)) / nrow(df_data)
l_politics <- nrow(df_data %>% filter(D_politicsSocial < 50)) / nrow(df_data)
r_fiscal <- nrow(df_data %>% filter(D_politicsFiscal >= 50)) / nrow(df_data)
l_fiscal <- nrow(df_data %>% filter(D_politicsFiscal < 50)) / nrow(df_data)
 
rm(g)



#PROLIFIC
df.p <- df_data %>% filter(Distribution == "PROLIFIC")
desc.fiscal.p <- psych::describe(df.p$D_politicsFiscal)
desc.social.p <- psych::describe(df.p$D_politicsSocial)


#TUMBLR
df.t <- df_data %>% filter(Distribution == "TUMBLR")
desc.fiscal.t <- psych::describe(df.t$D_politicsFiscal)
desc.social.t <- psych::describe(df.t$D_politicsSocial)

  
```


For the `r nrow(df.p)` participants recruited from Prolific, a spectrum of Social Political values [ranging from 0 (left-leaning) to 100 (right-leaning)] ranged from `r desc.social.p$min` to `r desc.social.p$max`, with a mean value of `r round(desc.social.p$mean,2)`, SD = `r (round(desc.social.p$sd,2))`.  A spectrum of Fiscal Political values [ranging from 0 (left-leaning) to 100 (right-leaning)] ranged from `r desc.fiscal.p$min` to `r desc.fiscal.p$max`, with a mean value of `r round(desc.fiscal.p$mean,2)`, SD = `r (round(desc.fiscal.p$sd,2))`.   

For the `r nrow(df.t)` participants recruited from Tumblr, a spectrum of Social Political values [ranging from 0 (left-leaning) to 100 (right-leaning)] ranged from `r desc.social.t$min` to `r desc.social.t$max`, with a mean value of `r round(desc.social.t$mean,2)`, SD = `r (round(desc.social.t$sd,2))`.  A spectrum of Fiscal Political values [ranging from 0 (left-leaning) to 100 (right-leaning)] ranged from `r desc.fiscal.t$min` to `r desc.fiscal.t$max`, with a mean value of `r round(desc.fiscal.t$mean,2)`, SD = `r (round(desc.fiscal.t$sd,2))`.   

Overall, `r round(l_politics*100,2)`% of respondents identify with left-leaning social values (vs) `r round(r_politics*100,2)`% identifying as right-leaning; while `r round(l_fiscal*100,2)`% of respondents reported left-leaning fiscal values (vs) `r round(r_fiscal*100,2)`% identify as right-leaning. 


### Political Values — Relationship

```{r demo-plot-political-grid,  fig.width = 10}

df <- df_graphs %>% select(PID, Assigned.Block, Distribution, D_politicsSocial, D_politicsFiscal, D_politicalParty) %>% 
  mutate(
    d_social = D_politicsSocial,
    d_fiscal = D_politicsFiscal
  )

ggplot(df, aes(x = d_social, y = d_fiscal, color = D_politicalParty)) + 
  geom_point() + 
  geom_hline(yintercept = 50) +
  geom_vline(xintercept = 50) + 
  facet_grid(Distribution~D_politicalParty)+
  labs(
    title = "Social and Fiscal Political Values by Political Party Affiliation",
    x = "Social Values", y = "Fiscal Values"
  )+
  theme_minimal() + 
  easy_remove_legend() + 
  easy_remove_axes()



```


### Politcal Affiliation


```{r demo-political-party}
# POLITICAL PARTY
ggplot(data = df_data, aes( fill = D_politicalParty, x = Assigned.Block )) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .) + 
  scale_fill_viridis(discrete=TRUE, option="viridis", direction=-1) + 
  labs( title = "POLITICAL PARTY by Sample",
        subtitle = "Expect similiar across samples", x = "") +
  theme_minimal() +
  easy_add_legend_title("")

ggbarstats( data = df_data, x = "D_politicalParty", y = "Progress")  
```



### Platform Choice

```{r platform-choice}

#PLATFORM CHOICE
ggplot( df_data, aes( x = Assigned.Block, fill = PLATFORM)) +
  geom_bar(position = "stack") +
  facet_grid(Distribution ~ .) + 
  labs( title = "PLATFORM CHOICE by Sample",
        subtitle = "Expect similiar across samples", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") + 
  easy_add_legend_title("") +
  theme_minimal()


```


### Confidence

How confident are participants in their attributions? We want to explore this from several perspectives, including: participant-level differences, question-level differences, and stimulus-level differences

#### Distribution of Confidence

```{r inspect-confidence, message=FALSE}


## QUESTION LEVEL CONFIDENCE 
df <- df_questions %>%
  filter(QUESTION %in% ref_conf_questions) %>% 
  mutate(value= as.numeric(value))


(g <- ggplot(df, aes(x = value, fill = QUESTION)) + 
  geom_histogram() + 
  facet_wrap(. ~ QUESTION) +  #, scales = "free", space = "free", drop = TRUE
  theme_minimal() + 
  labs(title = "Distrubtion of Confidence by Question") + 
  easy_remove_legend())


ggsave(plot = g, path="figs/histograms", filename =paste0("confidence_","histograms.png"), units = c("in"))

```


```{r demo-scales}

## QUESTION LEVEL CONFIDENCE 
df <- df_questions %>%
  filter(QUESTION %in% ref_sd_questions) %>% 
  mutate(value= as.numeric(value))


(g <- ggplot(df, aes(x = value, fill = QUESTION)) + 
  geom_histogram() + 
  facet_grid( STIMULUS~ QUESTION) + 
  theme_minimal() + 
  labs(title = "Distrubtion of SEMANTIC DIFFERENTIAL SCALES by Question") + 
  easy_remove_legend())



ggsave(plot = g, path="figs/histograms", filename =paste0("sd_scales_by_question_stimulus","histograms.png"), units = c("in"), width = 20, height = 30)

```

```{r demo-scales-category}

## QUESTION LEVEL CONFIDENCE 
df <- df_questions %>%
  filter(QUESTION %in% ref_sd_questions) %>% 
  mutate(value= as.numeric(value))


(g <- ggplot(df, aes(x = value, fill = STIMULUS_CATEGORY)) + 
  geom_histogram() + 
  facet_grid( STIMULUS_CATEGORY~ QUESTION) + 
  theme_minimal() + 
  labs(title = "Distrubtion of SEMANTIC DIFFERENTIAL SCALES by Question") + 
  easy_remove_legend())

ggsave(plot = g, path="figs/histograms", filename =paste0("sd_scales_by_question_category","histograms.png"), units = c("in"), width = 20, height = 20)

```


```{r}

## STIMULUS LEVEL CONFIDENCE 

df <- df_questions %>%
  filter(QUESTION %in% ref_conf_questions) %>% 
  mutate(value= as.numeric(value)) 

(g <- ggplot(df, aes(x = value, fill = fct_rev(STIMULUS_CATEGORY))) + 
  geom_histogram() + 
  facet_grid(rows = vars(BLOCK),
             cols = vars(fct_rev(STIMULUS_CATEGORY)), scales = "free_y", space = "free", drop = TRUE) +
  theme_minimal()+  
  labs(title = "Distrubtion of Confidence by Stimulus"))

ggsave(plot = g, path="figs/histograms", filename =paste0("confidence_matrix_","histograms.png"), units = c("in"), width = 20, height = 20)
```


#### Individual Participant Confidence

```{r message=FALSE}

df <- df_questions %>%
  filter(QUESTION %in% c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")) %>% 
  mutate(value= as.numeric(value)) %>% 
  group_by(PID, QUESTION) %>% 
  summarise(
    mean_conf = mean(value),
    sd_conf = sd(value),
    var_conf = var(value)
  )


ggplot(df, aes( x = mean_conf)) +
  geom_histogram() +
  facet_wrap( ~ QUESTION) + 
  labs(
    title = "Mean Participant confidence by Question",
    subtitle = "(averaging across all 5 stimuli per participant)"
  ) + 
  theme_minimal()
  
  
ggplot(df, aes( x = sd_conf)) +
  geom_histogram() +
  facet_wrap( ~ QUESTION) + 
  labs(
    title = "Standard Deviation of Participant confidence by Question",
    subtitle = "(averaging across all 5 stimuli per participant)"
  ) +
  theme_minimal()  
  
```
```{r message=FALSE, warning=FALSE}
## BY PARTICIPANT
df <- df_questions %>%
  filter(QUESTION %in% c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")) %>% 
  mutate(value= as.numeric(value)) %>% 
  group_by(PID) %>% 
  summarise(
    mean_conf = mean(value),
    sd_conf = sd(value),
    var_conf = var(value)
  )

ggplot(df, aes( x = mean_conf)) +
  geom_histogram(binwidth = 2) +
  
  labs(
    title = "Mean Participant Confidence ",
    subtitle = "(averaging across 4 confidence questions and all 5 stimuli per participant)"
  ) +
  theme_minimal()  


ggplot(df, aes( x = sd_conf)) +
  geom_histogram(binwidth = 2) +
  xlim(0,100)+
  labs(
    title = "Standard Deviation of Participant Confidence ",
    subtitle = "(averaging across 4 confidence questions and all 5 stimuli per participant)"
  ) +
  theme_minimal()  

```

#### Predicting Confidence 

```{r predict-confidence}

df <- df_graphs %>% left_join(df_confidence_wide, by="PID") %>% 
  select(-contains(".y")) %>% 
  rename_with(
    stringr::str_replace, 
      pattern = ".x", replacement = ""
  )


## maker confidence by age
(m <- ggplot(df, aes( color = CONF_mean, x = D_age, y = MAKER_CONF, text = PID)) + 
  geom_jitter(size = 0.5, width = .2, height = 0) + 
  scale_colour_paletteer_c("ggthemes::Red-Black Diverging", direction = -1)+
  labs (
    title = "Confidence in MAKER_ID by Participant Age",
    subtitle = "color by average participant confidence: red HIGH, black LOW",
    x = "participant age"
  ) + theme_minimal() )


# ggplotly(m)

## age maker confidence by age
(a <- ggplot(df, aes( color = CONF_mean, x = D_age, y = AGE_CONF, text = PID)) + 
  geom_jitter(size = 0.5, width = .2, height = 0) + 
  scale_colour_paletteer_c("ggthemes::Red-Black Diverging", direction = -1)+
  labs (
    title = "Confidence in MAKER_AGE by Participant Age",
    subtitle = "color by average participant confidence: red HIGH, black LOW",
    x = "participant age"
  ) + theme_minimal() )


# ggplotly(a)

## age maker confidence by age
(a <- ggplot(df, aes( color = CONF_mean, x = D_age, y = GENDER_CONF, text = PID)) + 
  geom_jitter(size = 0.5, width = .2, height = 0) + 
  scale_colour_paletteer_c("ggthemes::Red-Black Diverging", direction = -1)+
  labs (
    title = "Confidence in MAKER_GENDER by Participant Age",
    subtitle = "color by average participant confidence: red HIGH, black LOW",
    x = "participant age"
  ) + theme_minimal() )


# ggplotly(a)

```



# ATTRIBUTIONS

## MAKER ID

### Maker ID by Stimulus

```{r maker-id-stimulus}

df <- df_graphs 

#MAKER IDENTIFICATION
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) +
  geom_bar(position = "fill") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  labs( title = "MAKER ID by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()



#MAKER IDENTIFICATION
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) +
  geom_bar(position = "fill") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER ID by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()

```

### Maker ID by Category

```{r maker-id-category}

df <- df_graphs 

#MAKER IDENTIFICATION
ggplot( df, aes( x = STIMULUS_CATEGORY, fill = MAKER_ID)) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .) + 
  labs( title = "MAKER ID by Stimulus Category",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()

#MAKER IDENTIFICATION
ggplot( df, aes( x = STIMULUS_CATEGORY, fill = MAKER_ID)) +
  geom_bar(position = "fill") +
  labs( title = "MAKER ID by Stimulus Category",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  coord_flip()+
  easy_add_legend_title("") +
  theme_minimal()

```




### Maker ID & Confidence by Stimulus


```{r maker-id-confidence-stimulus, fig.width = 10}

#FILTER DATAFRAME
df <- df_graphs 

######### MAKER ID AND CONFIDENCE ##############
# MAKER_ID by Sample and BEHAVIOR 
a <- ggplot (df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) + 
  # geom_bar(width = 0.5, position = position_dodge(0.5)) +
  geom_bar(position = "fill", width = 0.8) + 
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# MAKER_CONFIDENCE by IDENTIFICATION  
b <- ggplot(df, aes( x = fct_rev(STIMULUS), y = MAKER_CONF, color = MAKER_ID)) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.4) +
  scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (title = "") +
  labs (x = "") + 
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'MAKER ID & CONFIDENCE by Stimulus',
  subtitle = '',
  caption = ''))

###################################################
rm(a,b,p)
```


### Maker ID & Confidence

```{r, maker-id-confidence-category, message=FALSE, warning=FALSE}

#FILTER DATAFRAME
df <- df_graphs 

######### MAKER ID AND CONFIDENCE ##############
# MAKER_ID by Sample and BEHAVIOR 
a <- ggplot (df, aes( x = fct_rev(STIMULUS_CATEGORY), fill = MAKER_ID)) + 
  geom_bar(position = "fill") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# MAKER_CONFIDENCE by IDENTIFICATION  
b <- ggplot(df, aes( x = fct_rev(STIMULUS_CATEGORY), y = MAKER_CONF, color = MAKER_ID)) + 
  geom_boxplot(position=position_dodge(0.9))+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_viridis(discrete=TRUE, option="viridis") +
  # labs (title = "MAKER-ID-CONFIDENCE") +
  labs (x = "STIMULUS CATEGORY") + 
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'MAKER ID & CONFIDENCE',
  subtitle = '',
  caption = ''))

rm(a,b,p)

###################################################
```






## MAKER AGE

### Maker Age by Stimulus

```{r maker-age-stimulus}

df <- df_graphs 

#MAKER AGE
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
  geom_bar(position = "fill") +
  #SCALES & SPACE FREE SUPPRESSES EMPTY ROWS
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  labs( title = "MAKER AGE by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()

```

### Maker Age by Category

```{r maker-age-category}

df <- df_graphs 

#MAKER AGE
ggplot( df, aes( x = STIMULUS_CATEGORY, fill = MAKER_AGE)) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .) + 
  labs( title = "MAKER AGE by Stimulus Category",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid(rows= vars(D_age)) +
  coord_flip()+
  theme_minimal()

```

### Maker Age & Confidence by Stimulus

```{r maker-age-confidence-stimulus, message=FALSE, warning=FALSE, fig.width=10}

#FILTER DATAFRAME
df <- df_graphs 

######### MAKER ID AND CONFIDENCE ##############
# MAKER_ID by Sample and BEHAVIOR 
a <- ggplot (df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) + 
  geom_bar(position = "fill", width = 0.8) +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# MAKER_CONFIDENCE by IDENTIFICATION  
b <- ggplot(df, aes( x = fct_rev(STIMULUS), y = MAKER_CONF, color = MAKER_AGE)) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (title = "") +
  labs (x = "STIMULUS CATEGORY") + 
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'MAKER AGE & CONFIDENCE by Category',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,p)
```
### Maker Age & Confidence by Category

```{r maker-age-confidence-category, message=FALSE, warning=FALSE}

#FILTER DATAFRAME
df <- df_graphs 

######### MAKER ID AND CONFIDENCE ##############
# MAKER_AGE by Sample and BEHAVIOR 
a <- ggplot (df, aes( x = fct_rev(STIMULUS_CATEGORY), fill = MAKER_AGE)) + 
  geom_bar(position = "fill") + #dodge
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# MAKER_CONFIDENCE by IDENTIFICATION  
b <- ggplot(df, aes( x = fct_rev(STIMULUS_CATEGORY), y = AGE_CONF, color = MAKER_AGE)) + 
  geom_boxplot(position=position_dodge(0.9))+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (x = "STIMULUS CATEGORY") + 
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'MAKER AGE & CONFIDENCE by Category',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,p)
```


## MAKER GENDER

### Maker Gender by Stimulus
```{r maker-gender-stimulus}

df <- df_graphs 

#MAKER GENDER
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_GENDER)) +
  geom_bar(position = "fill") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  labs( title = "MAKER GENDER by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  # scale_fill_viridis(discrete=TRUE, option="viridis") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()


#MAKER GENDER
ggplot( df, aes( x = fct_rev(STIMULUS), fill = fct_rev(MAKER_GENDER))) +
  geom_bar(position = "fill") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER GENDER by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  # scale_fill_viridis(discrete=TRUE, option="viridis") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()


#MAKER GENDER
ggplot( df, aes( x = fct_rev(STIMULUS), fill = fct_rev(MAKER_GENDER))) +
  geom_bar(position = "fill") +
  facet_grid(.~fct_rev(STIMULUS_CATEGORY) , scales = "free", space = "free") + 
  labs( title = "MAKER GENDER by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  # scale_fill_viridis(discrete=TRUE, option="viridis") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  # coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()


#MAKER GENDER

ggbarstats( data = df, x = "MAKER_GENDER", y = "STIMULUS",
                 legend.title = "MAKER_GENDER")  +
      scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
      labs( title = "MAKER_GENDER ", subtitle = "", x = "") 






```
### Maker Gender by Category

```{r maker-gender-category}

df <- df_graphs 

#MAKER GENDER
ggplot( df, aes( x = STIMULUS_CATEGORY, fill = MAKER_GENDER)) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .)+
  labs( title = "MAKER GENDER by Stimulus Category",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid(rows= vars(D_age)) +
  coord_flip()+
  theme_minimal()

```

### Maker Gender & Confidence by Stimulus

```{r maker-gender-confidence-stimulus, message=FALSE, warning=FALSE, fig.width=10}

#FILTER DATAFRAME
df <- df_graphs 

######### MAKER GENDER AND CONFIDENCE ##############
# MAKER_GENDER by STIMULUS
a <- ggplot (df, aes( x = fct_rev(STIMULUS), fill = MAKER_GENDER)) + 
  geom_bar(position = "fill", width = 0.8) +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# GENDER_CONFIDENCE by STIMULUS
b <- ggplot(df, aes( x = fct_rev(STIMULUS), y = GENDER_CONF, color = MAKER_GENDER)) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.5)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (x = "STIMULUS") + 
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'MAKER GENDER & CONFIDENCE by Stimulus',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,p)
```

### Maker Gender & Confidence by Category

```{r maker-gender-confidence-category, message=FALSE, warning=FALSE}

#FILTER DATAFRAME
df <- df_graphs 

######### MAKER GENDER AND CONFIDENCE ##############
a <- ggplot (df, aes( x = fct_rev(STIMULUS_CATEGORY), fill = MAKER_GENDER)) + 
  geom_bar(position = "fill") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  theme_minimal() 

# GENDER_CONFIDENCE by GENDER  
b <- ggplot(df, aes( x = fct_rev(STIMULUS_CATEGORY), y = GENDER_CONF, color = MAKER_GENDER)) + 
  geom_boxplot(position=position_dodge(0.9))+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_viridis(discrete=TRUE, option="viridis") +
  labs (x = "STIMULUS CATEGORY") + 
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'MAKER GENDER & CONFIDENCE by Category',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,p)
```

## TOOL CHOICE

### Tool ID by Stimulus

```{r toolid-stimulus}

df <- df_tools 

# TOOL CHOICE BY STIMULUS
ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = fct_rev(STIMULUS) )) +
  geom_bar(position = "fill") +
  coord_flip() + 
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 

  labs( title = "TOOL ID by Stimulus (grouped by Category)",
        subtitle = "", x = "") +
  easy_add_legend_title("TOOL_ID") +
  theme_minimal() 


```

### Tool ID by Category

```{r toolid-category}

df <- df_tools 

# TOOL CHOICE BY STIMULUS
ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = STIMULUS_CATEGORY )) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .) + 
  coord_flip() + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 
  labs( title = "TOOL ID by Category",
        subtitle = "", x = "") +
  easy_add_legend_title("TOOL_ID") +
  theme_minimal() 


```

### Tool ID & Confidence by Stimulus

```{r toolid-confidence-stimulus, message=FALSE, warning=FALSE, fig.width = 10}

#FILTER DATAFRAME
df <- df_tools 

######### TOOL ID AND CONFIDENCE ##############
a <- ggplot (df, aes( x = fct_rev(STIMULUS), fill = fct_rev(TOOL_ID))) + 
  geom_bar(position = "fill", width = 0.8) +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1) +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") +
  easy_add_legend_title("TOOL ID")+
  theme_minimal() 

# TOOL_CONFIDENCE by STIMULUS
b <- ggplot(df, aes( x = fct_rev(STIMULUS), y = TOOL_CONF, color = fct_rev(TOOL_ID))) + 
  geom_boxplot(position=position_dodge(0.9), width = 0.6)+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_paletteer_d("awtools::a_palette", direction = 1) +
  labs (x = "STIMULUS") + 
  easy_add_legend_title("TOOL ID")+
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'TOOL ID & CONFIDENCE by Stimulus',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,p)
```

### Tool ID & Confidence by Category

```{r toolid-confidence-category, message=FALSE, warning=FALSE}

#FILTER DATAFRAME
df <- df_tools 

######### TOOL ID AND CONFIDENCE ##############
a <- ggplot (df, aes( x = fct_rev(STIMULUS_CATEGORY), fill = fct_rev(TOOL_ID))) + 
  geom_bar(position = "fill") +
  scale_fill_paletteer_d("awtools::a_palette", direction = 1) +
  # facet_grid( df$ENCOUNTER) + 
  labs (x = "") + 
  easy_add_legend_title("TOOL ID")+
  theme_minimal() 

# TOOL CONF 
b <- ggplot(df, aes( x = fct_rev(STIMULUS_CATEGORY), y = TOOL_CONF, color = fct_rev(TOOL_ID))) + 
  geom_boxplot(position=position_dodge(0.9))+
  geom_jitter(position=position_jitterdodge(), alpha = 0.2) + 
  scale_color_paletteer_d("awtools::a_palette", direction = 1) +
  labs (x = "STIMULUS CATEGORY") + 
  easy_add_legend_title("TOOL ID")+
  theme_minimal() 

(p <- (a / b )  + plot_annotation(
  title = 'TOOL ID & CONFIDENCE by Category',
  subtitle = '',
  caption = ''))

###################################################

rm(a,b,p)
```





## ENCOUNTER CHOICE

### Encounter Choice by Stimulus
```{r encounter-stimulus}

df <- df_graphs 

#MAKER IDENTIFICATION
ggplot( df, aes( x = fct_rev(STIMULUS), fill = ENCOUNTER)) +
  geom_bar(position = "fill") +
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  labs( title = "MAKER ENCOUNTER by Stimulus (grouped by CATEGORY) ",
        subtitle = "", x = "") +
  scale_fill_brewer(palette = "Dark2") + 
  # scale_fill_viridis(discrete=TRUE, option="viridis", direction = -1) +
  coord_flip()+
  # easy_add_legend_title("") +
  theme_minimal()

```


### Encounter Choice by Category

```{r encounter-category}

df <- df_graphs 

#MAKER IDENTIFICATION
ggplot( df, aes( x = STIMULUS_CATEGORY, fill = ENCOUNTER)) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .) + 
  labs( title = "ENCOUNTER by Stimulus Category (grouped by CATEGORY)",
        subtitle = "", x = "") +
  scale_fill_brewer(palette = "Dark2") + 
  coord_flip()+
  theme_minimal()

```







## ENGAGEMENT CHOICE

### Actions Choice by Stimulus

```{r actions-stimulus}

df <- df_actions 

# ACTION CHOICE BY STIMULUS
ggplot(data = df, aes( fill = CHART_ACTION, x = fct_rev(STIMULUS) )) +
  geom_bar(position = "fill") +
  coord_flip() + 
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 

  labs( title = "Chart Action by Stimulus (grouped by Category)",
        subtitle = "", x = "") +
  easy_add_legend_title("ACTION") +
  theme_minimal() 



# ACTION CHOICE BY STIMULUS
ggplot(data = df, aes( fill = CHART_ACTION, x = fct_rev(STIMULUS) )) +
  geom_bar(position = "fill") +
  coord_flip() + 
  facet_grid(fct_rev(STIMULUS_CATEGORY) ~ ., scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 

  labs( title = "Chart Action by Stimulus (grouped by Category)",
        subtitle = "", x = "") +
  easy_add_legend_title("ACTION") +
  theme_minimal() 



```

### Actions Choice by Category

```{r actions-category}

df <- df_actions 

# ACTION CHOICE BY STIMULUS
ggplot(data = df, aes( fill = CHART_ACTION, x = STIMULUS_CATEGORY )) +
  geom_bar(position = "fill") +
  facet_grid(Distribution ~ .) + 
  coord_flip() + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 
  labs( title = "CHART ACTION by Category",
        subtitle = "", x = "") +
  easy_add_legend_title("ACTION") +
  theme_minimal() 


```






## CHART BEAUTY

### Chart Beauty by Stimulus and Category
```{r}

df <- df_graphs

qacBase::qstats(df, CHART_BEAUTY, STIMULUS) %>% arrange(mean)

qacBase::qstats(df, CHART_BEAUTY, STIMULUS_CATEGORY) %>% arrange(mean)

# 
# 
# ggplot(df, aes(x = CHART_BEAUTY)) + 
#   geom_histogram(bins = 20) +
#   facet_grid(BLOCK ~ STIMULUS_CATEGORY, scales = "free", space = "free", drop=TRUE) + 
#   theme_minimal()
# 
# 
# ggplot(df, aes(x = CHART_BEAUTY)) + 
#   geom_histogram(bins = 20) +
#   facet_grid( ~ fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free", drop=TRUE) + 
#   theme_minimal()
# 



##ggstatsplot BY CATEGORY
grouped_gghistostats(
  data = df_graphs %>% filter(STIMULUS != "B0-0"),
  x = CHART_BEAUTY, ## same outcome variable
  grouping.var = STIMULUS, ## grouping variable males = 1, females = 2
  type = "robust", ## robust test: one-sample percentile bootstrap
  test.value = 50, ## test value against which sample mean is to be compared
  centrality.line.args = list(color = "#D55E00", linetype = "dashed"),
  # ggtheme = ggthemes::theme_stata(), ## changing default theme
  ## turn off ggstatsplot theme layer
  ## arguments relevant for combine_plots
  annotation.args = list(
    title = "DISTRIBUTION of Chart Beauty by Cateogry",
    caption = ""
  ),
  plotgrid.args = list(nrow = 6)
)
 

#B0-0 
gghistostats(
  data = df_graphs %>% filter(STIMULUS == "B0-0"), ## data from which variable is to be taken
  x = CHART_BEAUTY, ## numeric variable
  xlab = "CHART BEAUTY", ## x-axis label
  title = "B0-0 MILLENIAL PINK PLANTS", ## title for the plot
  test.value = 50, ## test value
  caption = ""
)  


```

### Chart Trust by Stimulus and Category
```{r}

df <- df_graphs

qacBase::qstats(df, CHART_TRUST, STIMULUS) %>% arrange(mean)

qacBase::qstats(df, CHART_TRUST, STIMULUS_CATEGORY) %>% arrange(mean)


##ggstatsplot BY CATEGORY
grouped_gghistostats(
  data = df_graphs %>% filter(STIMULUS != "B0-0"),
  x = CHART_TRUST, ## same outcome variable
  grouping.var = STIMULUS, ## grouping variable males = 1, females = 2
  type = "robust", ## robust test: one-sample percentile bootstrap
  test.value = 50, ## test value against which sample mean is to be compared
  centrality.line.args = list(color = "#D55E00", linetype = "dashed"),
  # ggtheme = ggthemes::theme_stata(), ## changing default theme
  ## turn off ggstatsplot theme layer
  ## arguments relevant for combine_plots
  annotation.args = list(
    title = "DISTRIBUTION of Chart TRUST by Cateogry",
    caption = ""
  ),
  plotgrid.args = list(nrow = 6)
)
 

#B0-0 
gghistostats(
  data = df_graphs %>% filter(STIMULUS == "B0-0"), ## data from which variable is to be taken
  x = CHART_TRUST, ## numeric variable
  xlab = "CHART TRUST", ## x-axis label
  title = "B0-0 MILLENIAL PINK PLANTS", ## title for the plot
  test.value = 50, ## test value
  caption = ""
)  


```


# FISH

### bivariate combinations 
```{r bivariate-demos}

if(graph_render == TRUE){





### EXPLORE ALL QUESTIONS AS EXPLAINED BY DEMOGRAPHICS
df <- df_graphs 
predictors = df %>% select(Distribution, STIMULUS_CATEGORY,
                D_gender_collapsed, D_age, D_education, D_income,
                D_politicalParty, D_politicsFiscal, D_politicsSocial) %>% colnames()

questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)

i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by demographic variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_demographics", filename =paste0(q,"_demo_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END




### EXPLORE ALL QUESTIONS AS EXPLAINED BY SD VARS
df <- df_graphs 
predictors = c(ref_sd_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by SD variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_SD", filename =paste0(q,"_sd_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g )
#####################################################END



### EXPLORE ALL QUESTIONS AS EXPLAINED BY CONF VARS
df <- df_graphs 
predictors = c(ref_conf_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by CONF variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_CONF", filename =paste0(q,"_conf_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END


### EXPLORE ALL QUESTIONS AS EXPLAINED BY CAT VARS
df <- df_graphs 
predictors = c(ref_cat_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0(q, " as explained by CATEGORICAL variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/bivariate/bivariate_CAT", filename =paste0(q,"_cat_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END


}

```


### DEMO-GENDER > MAKER-GENDER?

```{r}

df <- df_graphs %>% select(PID, D_gender, MAKER_GENDER, GENDER_CONF, STIMULUS, STIMULUS_CATEGORY, BLOCK)


## ALL STIMULI
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  scale_fill_viridis(discrete=TRUE, option="viridis") + 
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
    subtitle = "(across all stimuli)",
    caption = "ARF: Attribution of maker gender does not *appear* to differ by participant \n gender identity; Each personal gender has attributions to each maker gender"
  )



## CATEGORY
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  facet_grid(.~fct_rev(STIMULUS_CATEGORY))+
  scale_fill_viridis(discrete=TRUE, option="viridis") + 
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
    subtitle = "(by stimulus category)",
    caption = "ARF: Note that across categories most attributions are male, 
    EXCEPT F (millenial pink plants) which is largely female
    HOWEVER relative proportion by participant gender looks consistent" 
  )


## STIMULUS
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  scale_fill_viridis(discrete=TRUE, option="viridis")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
    subtitle = "(by stimulus)",
    caption = "ARF: Again, relative proportions look consistent by participant gender"
  )

## B00
df <- df %>% filter(STIMULUS=="B0-0")
ggplot(df, aes(x = MAKER_GENDER, fill= D_gender)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  scale_fill_viridis(discrete=TRUE, option="viridis")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender",
   subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = "ARF: Most attributions are FEMALE but relative proportion of 
    participant gender appears comparable; difficult to detect due to low number
    of non-binary, prefer not to say, prefer to self-describe"
  )

```
### DEMO-GENDER_Q_all_stimuli
```{r GENDER-Q-FOR-ALL-STIMULI}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){

####################CREATE SD PLOTS FOR EACH QUESTION#####################

#set questions to be graphed 
questions <- ref_sd_questions  #created in wrangling block
box_s_question <- list()
rain_s_question <- list()
i = 0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  df <- df_sd_questions_wide %>% filter(QUESTION == q)

  #subset data cols 
  c <- df %>% select( all_of(ref_stimuli))
  # plot_sd = function (data, column, type, facet, facet_by,  boxplot) {

  plots <- as.list(lapply(colnames(c), plot_sd, data = df, type = "Q", facet=TRUE, facet_by= "D_gender_collapsed", boxplot=TRUE)) 
  
  #aggregate stimulus plots into block for question
  x <- plots[[1]] / plots[[2]]  / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
        plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] /  plots[[12]] / plots[[13]] / plots[[14]] / 
        plots[[15]] /plots[[16]] /plots[[17]] /plots[[18]] /  plots[[19]] / plots[[20]] / plots[[21]] /
        plots[[22]] /plots[[23]] /plots[[24]] /plots[[25]] + 
      plot_annotation(
        title = title,
       subtitle =""
      )
  box_s_question[[i]] <- x 
  ggsave(plot = x, path="figs/GENDER_by_q_for_all_stimuli", filename =paste0(q,"_box.png"), units = c("in"), width = 10, height = 26)

  
  
  
  ############# RAINCLOUD
  # setup dataframe 
  title <- paste(q)
  df <- df_sd_questions_long %>% filter(QUESTION ==q)
    #select(1:6, QUESTION, all_of(s)) %>% filter(!is.na(s)) %>%  mutate(value = get(s))
  left <- ref_labels[q,]$left
  right <- ref_labels[q,]$right

  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(STIMULUS) , x = value, fill = fct_rev(STIMULUS))) +
      stat_slab(normalize="groups", scale = 0.7) +
      stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
    facet_grid(~D_gender_collapsed)+
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  rain_s_question[[i]] <- x
  ggsave(plot = x, path="figs/GENDER_by_q_for_all_stimuli", filename =paste0(q,"_rain.png"), units = c("in"), width = 10, height = 14  )
  

  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_s_question$MAKER_DESIGN
#ALSO plots_s_question$MAKER_DESIGN[[1]]
names(box_s_question) <- questions
names(rain_s_question) <- questions
rm(x, i, plots, left, right)

#############################################################################

}
```

### DEMO-GENDER-MILLENIAL-PLANTS-SDS
```{r GENDER-PLANTS ALL-Q-BY-STIMULUS}


#################### ALL QUESTIONS AT B00 #####################
# ONE PLOT FOR EACH STIMULUS WITH ALL QUESTIONS

#set stimuli to be graphed 
# stimuli <- ref_stimuli #created in wrangling block
stimuli <- c("B0-0")

box_stimuli <- list()
rain_stimuli <- list()
i = 0
for (s in stimuli){
  i = i+1
  
  # setup dataframe 
  title <- df_stimuli %>% filter(ID == s) %>% select(NAME) 
  title <- paste(s,"|",title)
  df <- df_graphs %>% filter(STIMULUS== s)

  #subset data cols 
  cols <- df %>% select( all_of(ref_sd_questions))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type ="S", facet = TRUE, facet_by="D_gender_collapsed", boxplot=TRUE))

  #aggregate q plots into one for stimulus 
  x <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
   plot_annotation(
     title = title,
     subtitle =""
   )
  
  box_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/_millenial-pink-plants", filename =paste0(s,"_box.png"), units = c("in"), width = 10, height = 14  )
  
  
  #### RAINCLOUD PLOT
  # setup dataframe 
  title <- df_stimuli %>% filter(ID == s) %>% select(NAME) 
  title <- paste(s,"|",title)
  df <- df_sd_questions_wide %>% select(1:6, D_gender_collapsed, QUESTION, all_of(s)) %>% filter(!is.na(s)) %>%  mutate(value = get(s))


  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(QUESTION), x = value, fill = fct_rev(QUESTION))) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  facet_grid(~ D_gender_collapsed)+
  guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    y = guide_axis_manual(labels = rev(ref_labels$left)),
    y.sec = guide_axis_manual(labels = rev(ref_labels$right))
  ) + 
  labs (title = title) +
  theme_minimal() 
   
  
  rain_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/_millenial-pink-plants", filename =paste0(s,"_rain.png"), units = c("in"), width = 10, height = 14  )
  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_stimulus$`B1-1`
#ALSO plots_stimulus$`B1-1`[[1]]
names(box_stimuli) <- stimuli
names(rain_stimuli) <- stimuli
rm(x, i, plots)

#############################################################################
 

```


### DEMO-GENDER-MILLENIAL-PLANTS-CATS
```{r}


#filter dataframe
df <- df_graphs %>% select(PID, D_gender_collapsed, MAKER_GENDER, GENDER_CONF, MAKER_AGE, AGE_CONF, MAKER_ID, MAKER_CONF, STIMULUS, STIMULUS_CATEGORY, BLOCK) %>% filter(STIMULUS=="B0-0")


##ID
p <- ggplot(df, aes(x = MAKER_ID, fill= D_gender_collapsed)) + 
  geom_bar(position = "fill")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER ID by participant gender (proportion)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

s <- ggplot(df, aes(x = MAKER_ID, fill= D_gender_collapsed)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER ID by participant gender (true count)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

(p/s)

##AGE
p <- ggplot(df, aes(x = MAKER_AGE, fill= D_gender_collapsed)) + 
  geom_bar(position = "fill")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER AGE by participant gender (proportion)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

s <- ggplot(df, aes(x = MAKER_AGE, fill= D_gender_collapsed)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER AGE by participant gender (true count)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = ""
  )

(p/s)


##GENDER
p <- ggplot(df, aes(x = MAKER_GENDER, fill= D_gender_collapsed)) + 
  geom_bar(position = "fill")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender (proportion)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = "ARF: Proportion of OTHER looks high!"
  )

s <- ggplot(df, aes(x = MAKER_GENDER, fill= D_gender_collapsed)) + 
  geom_bar(position = "stack")  + 
  facet_grid(BLOCK~fct_rev(STIMULUS_CATEGORY), scales = "free", space = "free")+
  theme_minimal() + 
  labs(
    title = "MAKER GENDER by participant gender (true count)",
    subtitle = "B0-0 MILLENIAL PINK PLANTS",
    caption = "ARF: But count of other is very low :("
  )

(p/s)


##MAKER CONFIDENCE BY GENDER 
ggplot(df, aes(x=D_gender_collapsed, y = MAKER_CONF, color = D_gender_collapsed))+
  geom_jitter(width=0.2, height = 0) + 
  labs (title = "CONFIDENCE in MAKER_ID by Participant Gender",
        x = "participant gender")+
  theme_minimal() +
  easy_remove_legend()


##AGE CONFIDENCE BY GENDER 
ggplot(df, aes(x=D_gender_collapsed, y = AGE_CONF, color = D_gender_collapsed))+
  geom_jitter(width=0.2, height = 0) + 
  labs (title = "CONFIDENCE in MAKER_AGE by Participant Gender",
        x = "participant gender")+
  theme_minimal() +
  easy_remove_legend()


##GENDER CONFIDENCE BY GENDER 
ggplot(df, aes(x=D_gender_collapsed, y = GENDER_CONF, color = D_gender_collapsed))+
  geom_jitter(width=0.2, height = 0) + 
  labs (title = "CONFIDENCE in MAKER_GENDER by Participant Gender",
        x = "participant gender")+
  theme_minimal() +
  easy_remove_legend()

```

# B1-3 AGGRESSIVE AMERICAN FLAG

## demographics

```{r b13-demographics}

n = df_participants %>% filter(Assigned.Block == 1) %>% nrow()
print(paste(n, "participants were assigned to block 1 where they saw the 'aggressive american flag stimulus"))
```

## bar charts 

```{r OMINOUS-FLAG}


df <- df_graphs %>% filter(STIMULUS == "B1-3")

#MAKER IDENTIFICATION
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) +
  geom_bar(position = "fill") +
  labs( title = "MAKER ID [B1-C]) ",
        subtitle = "", x = "") +
  scale_fill_viridis(discrete=TRUE, option="viridis") +
  easy_add_legend_title("") +
  theme_minimal()


#MAKER AGE
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
  geom_bar(position = "fill") +
  labs( title = "MAKER AGE [B1-C] ",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("ggsci::light_uchicago", direction = -1)+
  theme_minimal()



#MAKER GENDER
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_GENDER)) +
  geom_bar(position = "fill") +
  # facet_grid(D_gender_collapsed ~ ., scales = "free", space = "free") + 
  labs( title = "MAKER GENDER [B1-C] ",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("ggthemes::excel_Celestial", direction = 1)+
  theme_minimal()



df <- df_tools %>% filter (STIMULUS =="B1-3")

# TOOL CHOICE BY STIMULUS
ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = fct_rev(STIMULUS) )) +
  geom_bar(position = "fill") +
  # coord_flip() + 
  # facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
  scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
  scale_y_continuous(labels = scales::percent) + 
  labs( title = "TOOL ID by Stimulus (grouped by Category)",
        subtitle = "", x = "") +
  easy_add_legend_title("TOOL_ID") +
  theme_minimal() 

```
```{r angry-flag-age-by-sample}

df <- df_graphs %>% filter(STIMULUS == "B1-3")

#MAKER AGE
ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
  geom_bar(position = "fill") +
  facet_grid(.~Distribution) + 
  labs( title = "MAKER AGE [B1-C] ",
        subtitle = "", x = "") +
  scale_fill_paletteer_d("ggsci::light_uchicago", direction = -1)+
  theme_minimal()


```

## pie charts 

```{r OMINOUS-FLAG}


# df <- df_graphs %>% filter(STIMULUS == "B1-3")
# 
# #MAKER IDENTIFICATION
# ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_ID)) +
#   geom_bar(position = "fill") +
#   labs( title = "MAKER ID [B1-C]) ",
#         subtitle = "", x = "") +
#   scale_fill_viridis(discrete=TRUE, option="viridis") +
#   easy_add_legend_title("") +
#   theme_minimal()
# 
# 
# #MAKER AGE
# ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_AGE)) +
#   geom_bar(position = "fill") +
#   labs( title = "MAKER AGE [B1-C] ",
#         subtitle = "", x = "") +
#   scale_fill_paletteer_d("ggsci::light_uchicago", direction = -1)+
#   theme_minimal()
# 
# 
# 
# #MAKER GENDER
# ggplot( df, aes( x = fct_rev(STIMULUS), fill = MAKER_GENDER)) +
#   geom_bar(position = "fill") +
#   # facet_grid(D_gender_collapsed ~ ., scales = "free", space = "free") + 
#   labs( title = "MAKER GENDER [B1-C] ",
#         subtitle = "", x = "") +
#   scale_fill_paletteer_d("ggthemes::excel_Celestial", direction = 1)+
#   theme_minimal()
# 
# 
# 
# df <- df_tools %>% filter (STIMULUS =="B1-3")
# 
# # TOOL CHOICE BY STIMULUS
# ggplot(data = df, aes( fill = fct_rev(TOOL_ID), x = fct_rev(STIMULUS) )) +
#   geom_bar(position = "fill") +
#   # coord_flip() + 
#   # facet_grid(fct_rev(STIMULUS_CATEGORY) ~ Distribution, scales = "free", space = "free") + 
#   scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
#   scale_y_continuous(labels = scales::percent) + 
#   labs( title = "TOOL ID by Stimulus (grouped by Category)",
#         subtitle = "", x = "") +
#   easy_add_legend_title("TOOL_ID") +
#   theme_minimal() 
# 
# 
# 
# 
# 
# 
# 
# 
# #### GG_LOT + GREPL
# library(ggrepel)
# df <- df_graphs %>% filter(STIMULUS == "B1-3") %>% select(STIMULUS, MAKER_ID) %>% 
#   group_by(MAKER_ID) %>% 
#   summarize(
#     value = n()
#   )
# df2 <- df %>% 
#   mutate(csum = rev(cumsum(rev(value))), 
#          pos = value/2 + lead(csum, 1),
#          pos = if_else(is.na(pos), value/2, pos))
# 
# ggplot(df, aes(x = "" , y = value, fill = fct_inorder(MAKER_ID))) +
#   geom_col(width = 1, color = 1) +
#   coord_polar(theta = "y") +
#   scale_fill_brewer(palette = "Pastel1") +
#   geom_label_repel(data = df2,
#                    aes(y = pos, label = paste0(value, "%")),
#                    size = 4.5, nudge_x = 1, show.legend = FALSE) +
#   guides(fill = guide_legend(title = "Group")) +
#   theme_void()


##GGPIESTATS MAKER_GENDER
df <- df_graphs %>% filter (STIMULUS =="B1-3") %>% 
  mutate(
    MAKER_GENDER = fct_rev(MAKER_GENDER)
  )
ggpiestats(data = df, x=MAKER_GENDER )

##GGPIESTATS MAKER_AGE
df <- df_graphs %>% filter (STIMULUS =="B1-3") %>% 
  mutate(
    MAKER_AGE = fct_rev(MAKER_AGE)
  )
ggpiestats(data = df, x=MAKER_AGE )


##GGPIESTATS MAKER_ID
df <- df_graphs %>% filter (STIMULUS =="B1-3") %>% 
  mutate(
    MAKER_ID = fct_rev(MAKER_ID)
  )
ggpiestats(data = df, x=MAKER_ID )


##DONUT WITH LESSR

library(lessR)

#MAKER_ID-DONUT
PieChart(MAKER_ID, data = df,
         fill = "reds",
         main = NULL)


#MAKER_GENDER-DONUT
PieChart(MAKER_GENDER, data = df,
         fill = "blues",
         main = NULL)


#MAKER_GENDER-DONUT
PieChart(MAKER_AGE, data = df,
         fill = "olives",
         main = NULL)


# View(paletteer::palettes_d_names)

```
## semantic differentials
```{r sd-b13, warning=FALSE}





##FILTER DATAFRAME
s = "B1-3" #stimulus code
df <- df_graphs %>% filter(STIMULUS == s)

questions = c("MAKER_POLITIC", "MAKER_ARGUE", "MAKER_SELF", "MAKER_ALIGN", "MAKER_TRUST")
# questions = ref_sd_questions
labels <- ref_labels %>% filter(row.names(ref_labels) %in% questions)

#### RAINCLOUD PLOT
  # setup dataframe 
  title <- df_stimuli %>% filter(ID == s) %>% select(NAME) 
  title <- paste0(title, " [",s,"]")
  df <- df_sd_questions_wide %>% select(1:6, QUESTION, all_of(s)) %>% 
    filter(!is.na(s)) %>%  
    mutate(value = get(s)) %>% 
    filter(QUESTION %in% questions)


  #RAINCLOUD PLOT
  # x <- 
    ggplot(df, aes(y = fct_rev(QUESTION), x = value)) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  # facet_grid( .~ Distribution) +
  guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    y = guide_axis_manual(labels = rev(labels$left)),
    y.sec = guide_axis_manual(labels = rev(labels$right))
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  # rain_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/_aggressive_american_flag", filename =paste0(s,"_rain.png"), units = c("in"), width = 10, height = 14  )

```



# B0-0 MILLENIAL PINK PLANTS
### GGBIVARIATE
```{r bivariate-demos-b00}
if(graph_render == TRUE){


### EXPLORE ALL QUESTIONS AS EXPLAINED BY DEMOGRAPHICS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = df %>% select(Distribution, STIMULUS_CATEGORY,
                D_gender_collapsed, D_age, D_education, D_income,
                D_politicalParty, D_politicsFiscal, D_politicsSocial) %>% colnames()

questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)

i=0
for (q in questions){
  i = i+1
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by demographic variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_demographics", filename =paste0("B0-0_",q,"_demo_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END




### EXPLORE ALL QUESTIONS AS EXPLAINED BY SD VARS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = c(ref_sd_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by SD variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_SD", filename =paste0("B0-0_",q,"_sd_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g )
#####################################################END



### EXPLORE ALL QUESTIONS AS EXPLAINED BY CONF VARS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = c(ref_conf_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by CONF variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_CONF", filename =paste0("B0-0_",q,"_conf_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END


### EXPLORE ALL QUESTIONS AS EXPLAINED BY CAT VARS
df <- df_graphs %>% filter(STIMULUS=="B0-0")
predictors = c(ref_cat_questions)
questions = c(ref_sd_questions, ref_conf_questions, ref_cat_questions)
i=0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  g <- ggbivariate(df, outcome = q, explanatory = predictors) + labs(
    title = paste0("B0-0 ",q, " as explained by CATEGORICAL variables")
  )+ theme_minimal()
  ggsave(plot = g, path="figs/_millenial-pink-plants/bivariate/bivariate_CAT", filename =paste0("B0-0_",q,"_cat_ggbivariate.png"), units = c("in"), width = 10, height = 25)
}
rm(i,g)
#####################################################END

}
```


## PAIRPLOTS

```{r boo-pairplots}

if(graph_render == TRUE){


#####################################################PAIRPLOT_SD
df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(all_of(ref_sd_questions))
g <- ggpairs(df) 
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_sd_pairplot.png"), units = c("in"), width = 20, height = 20  )
g <- ggduo(df)
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_sd_duoplot.png"), units = c("in"), width = 20, height = 20  )

#####################################################PAIRPLOT_CAT
df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(all_of(ref_cat_questions))
g <- ggpairs(df) 
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_cat_pairplot.png"), units = c("in"), width = 20, height = 20  )
g <- ggduo(df)
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_cat_duoplot.png"), units = c("in"), width = 20, height = 20  )


#####################################################PAIRPLOT_CONF
df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(all_of(ref_conf_questions))
g <- ggpairs(df) 
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_conf_pairplot.png"), units = c("in"), width = 20, height = 20  )
g <- ggduo(df)
ggsave(plot = g, path="figs/_millenial-pink-plants", filename =paste0("B00","_conf_duoplot.png"), units = c("in"), width = 20, height = 20  )

####################################################################################################
####################################################################################################






#####################################################PAIRPLOT_SD COLORED BY DEMO
predictors = df_graphs %>% select(Distribution, STIMULUS_CATEGORY,
                D_gender_collapsed, D_age, D_education, D_income,
                D_politicalParty) %>% colnames()

i=0
for (p in predictors){
  df <- df_graphs %>% filter(STIMULUS=="B0-0") %>% select(p, all_of(ref_sd_questions))
  g <- ggpairs(df, aes(color = get(p)))   
  ggsave(plot = g, path="figs/_millenial-pink-plants/colored_pairs", filename =paste0("B00_",p,"_sd_pairplot.png"), units = c("in"), width = 40, height = 40  )  
  g <- ggduo(df, aes(color = get(p)))   
  ggsave(plot = g, path="figs/_millenial-pink-plants/colored_duos", filename =paste0("B00_",p,"_sd_duoplot.png"), units = c("in"), width = 40, height = 40  )  
  
}
rm(i,g,df)
####################################################################################################



}

```

## MODELLING

### Modelling Trust

```{r}

df <- df_graphs %>% filter(STIMULUS == "B0-0") %>%
  mutate(
    flipped_data = abs(MAKER_DATA - 100),
    flipped_design = abs(MAKER_DESIGN -100),
    flipped_intent = abs(CHART_INTENT -100),
    flipped_self = abs(MAKER_SELF -100)
  ) %>% select(
    flipped_data:flipped_self, MAKER_ARGUE, MAKER_ALIGN, CHART_LIKE, CHART_BEAUTY, CHART_TRUST, MAKER_TRUST
  )


chart_m.1 <- lm(CHART_TRUST ~ CHART_BEAUTY, data = df )
summ(chart_m.1)

chart_m.2 <- lm(CHART_TRUST ~ MAKER_ALIGN , data = df )
summ(chart_m.2)


anova(chart_m.1, chart_m.2)
compare_performance(chart_m.1, chart_m.2, rank = TRUE)


m.1 <- lm(MAKER_TRUST ~ CHART_BEAUTY, data = df )
summ(m.1)

m.2 <- lm(MAKER_TRUST ~ MAKER_ALIGN , data = df )
summ(m.2)

anova(m.1, m.2)
compare_performance(chart_m.1, chart_m.2, m.1, m.2, rank = TRUE)


m.3 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY , data = df )
summ(m.3)

m.4 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent, data = df )
summ(m.4)

m.5 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent + flipped_data, data = df )
summ(m.5)


m.6 <- lm(MAKER_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
summ(m.6)
 

m.7 <- lm(CHART_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
summ(m.7)

m <- lm(MAKER_TRUST ~ MAKER_ALIGN, data = df)
summ(m)

 
 compare_performance(m.1, m.2, m.3, m.4, m.5, m, rank = TRUE)
# 
# ## WHAT PREDICTS MAKER_TRUST?
# 
# 
# ## PLOT THE DATA 
# ggplot(df, aes(x = MAKER_ALIGN, y = MAKER_TRUST)) + 
#   geom_point() +
#   stat_smooth(method = "lm", 
#               formula = y ~ x, 
#               geom = "smooth") + 
#   labs(title = "MAKER ALIGNMENT PREDICTS TRUST?")+
#   theme_minimal()
# 
# 
# ## PLOT THE DATA 
# ggplot(df, aes(x = flipped_data, y = MAKER_TRUST)) + 
#   geom_point() +
#   stat_smooth(method = "lm", 
#               formula = y ~ x, 
#               geom = "smooth") + 
#   labs(title = "MAKER DATA PREDICTS TRUST?")+
#   theme_minimal()
# 
# 
# ## BUILD MODEL
# m.1 <- lm( MAKER_TRUST ~ MAKER_ALIGN, data = df)
# # summary(m.1)
# jtools::summ(m.1, confint = TRUE)
# # check_model(m.1)
# # report(m.1)
# 
# ## BUILD MODEL
# m.2 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data, data = df)
# # summary(m.2)
# jtools::summ(m.2, confint = TRUE)
# # check_model(m.2)
# # report(m.2)
# 
# ## BUILD MODEL
# m.3 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design , data = df)
# # summary(m.3)
# jtools::summ(m.3, confint = TRUE)
# # check_model(m.3)
# # report(m.3)
# 
# 
# ## BUILD MODEL
# m.4 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design + MAKER_POLITIC, data = df)
# # summary(m.3)
# jtools::summ(m.4, confint = TRUE)
# # check_model(m.3)
# # report(m.3)
# 
# 
# 
#   
# compare_performance(m.1, m.2, m.3, m.4, m.B,  rank = TRUE)
# 
# 
# # effect_plot(m.2, pred=MAKER_DATA, rug = TRUE, plot.points = TRUE) + 
# #   xlim(0,100) + 
# #   ylim(0,100)
# 
# 
# 
# 
# df <- df_graphs %>% filter(STIMULUS != "B0-0") %>% 
#   select(PID, STIMULUS, 
#          MAKER_ID:MAKER_TRUST, CHART_LIKE:CHART_TRUST, 
#          D_politicsFiscal, D_politicsSocial)
# 
# m.pid <- lmer( MAKER_TRUST ~  (1 | PID) , data = df, REML = FALSE)
# m.stim <- lmer( MAKER_TRUST ~ (1|STIMULUS) , data = df, REML = FALSE)
# m.r <- lmer( MAKER_TRUST ~ (1 | PID) + (1|STIMULUS), data = df, REML = FALSE)
# 
# compare_performance (m.pid, m.stim, m.r, rank = TRUE)
# 
# 
# 
# m.1 <- update( m.r, .~. + CHART_BEAUTY)
# summ(m.1)
# 
# m.2 = update(m.1, . ~ . + CHART_LIKE)
# summ(m.2)
# 
# 
# m.3 = update(m.2, . ~ . + CHART_TRUST)
# summ(m.3)
# 
# 
# compare_performance(m.r, m.1, m.2, m.3, rank = TRUE)

```
### TODO COME BACK HERE Modelling Engagement

```{r B00-ENGAGEMENT}


# df <- df_graphs %>% filter(STIMULUS == "B0-0") %>%
#   mutate(
#     flipped_data = abs(MAKER_DATA - 100),
#     flipped_design = abs(MAKER_DESIGN -100),
#     flipped_intent = abs(CHART_INTENT -100),
#     flipped_self = abs(MAKER_SELF -100),
#   ) %>% select(
#     MAKER_ARGUE, MAKER_ALIGN, CHART_LIKE, CHART_BEAUTY,
#     flipped_data:flipped_self,  CHART_TRUST, MAKER_TRUST, 
#     Distribution, D_gender, D_education, D_politicalParty, 
#     D_politicsSocial, D_politicsFiscal,
#     MAKER_ID, MAKER_AGE, MAKER_GENDER, 
#   )


## left off here !!! 
## MAKE DATAFRAME OF ACTIONS WITH OTHER STUFF 
# df_g <- df_graphs %>% filter(STIMULUS == "B0-0")
# df_a <- df_actions %>% filter(STIMULUS == "B0-0")
# df_x <- df_a %>% inner_join(x=df_a, y=df_g, by="PID",
#                            relationship = "many-to-one",
#                            multiple = "last",
#                            keep = FALSE)
# rm(df_a, df_g)
# 
# 
# df <- df_x %>% filter(STIMULUS == "B0-0") %>%
#   mutate(
#     flipped_data = abs(MAKER_DATA - 100),
#     flipped_design = abs(MAKER_DESIGN -100),
#     flipped_intent = abs(CHART_INTENT -100),
#     flipped_self = abs(MAKER_SELF -100),
#   ) %>% select(
#     MAKER_ARGUE, MAKER_ALIGN, CHART_LIKE, CHART_BEAUTY,
#     flipped_data:flipped_self,  CHART_TRUST, MAKER_TRUST,
#     Distribution, D_gender, D_education, D_politicalParty,
#     D_politicsSocial, D_politicsFiscal,
#     MAKER_ID, MAKER_AGE, MAKER_GENDER,
#   )
# 


## PLOT DISTRIBUTION OF ENGAGEMENT 
# 
# (a <- ggbarstats( data = df, x = "REV_CHART_ACTION", y = "STIMULUS",
#                  legend.title = "ENGAGEMENT")  + 
#       scale_fill_paletteer_d("awtools::a_palette", direction = 1)+
#       labs( title = "Chart Engagement ", subtitle = "", x = "") )
#   
#         
# 
# (b <- grouped_ggbarstats( data = df_a, x = "REV_CHART_ACTION", y = "STIMULUS", 
#                     grouping.var = Distribution, 
#                     legend.title = "ENGAGEMENT",  
#                     ggplot.component = list(scale_fill_paletteer_d("awtools::a_palette", direction = 1))))
# 
# 
# 
# df <- df_a %>% mutate( REV_CHART_ACTION = fct_rev(CHART_ACTION))
# predictors = df_a %>% select(Distribution, PLATFORM, 
#                 D_gender, D_age, D_education, D_race, D_income, 
#                 D_politicalParty, D_politicsFiscal, D_politicsSocial) %>% colnames()
# 
# 
# 
# 
# 
# ## PLOT POTENTIAL BIVARIATE
# (g <- ggbivariate(df_a, outcome = "CHART_ACTION", explanatory = predictors) + 
#   scale_fill_paletteer_d("awtools::a_palette", direction = 1))
# 
# ggsave(plot = g, path="figs/modelling", filename =paste0("b00_engagement","_bivariatet.png"), units = c("in"), width = 15, height = 20  )
# 
# 
# ## PLOT EXPLANATIONS OF ENGAGEMENT
# 
# 
# 
# ##
# 
# ## Visualize Engagement with B00
# 
# # 
# # 
# # 
# # 
# # chart_m.1 <- lm(CHART_TRUST ~ CHART_BEAUTY, data = df )
# # summ(chart_m.1)
# # 
# # chart_m.2 <- lm(CHART_TRUST ~ MAKER_ALIGN , data = df )
# # summ(chart_m.2)
# # 
# # 
# # anova(chart_m.1, chart_m.2)
# # compare_performance(chart_m.1, chart_m.2, rank = TRUE)
# # 
# # 
# # m.1 <- lm(MAKER_TRUST ~ CHART_BEAUTY, data = df )
# # summ(m.1)
# # 
# # m.2 <- lm(MAKER_TRUST ~ MAKER_ALIGN , data = df )
# # summ(m.2)
# # 
# # anova(m.1, m.2)
# # compare_performance(chart_m.1, chart_m.2, m.1, m.2, rank = TRUE)
# # 
# # 
# # m.3 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY , data = df )
# # summ(m.3)
# # 
# # m.4 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent, data = df )
# # summ(m.4)
# # 
# # m.5 <- lm(CHART_TRUST ~ MAKER_TRUST + MAKER_ALIGN + CHART_BEAUTY + flipped_intent + flipped_data, data = df )
# # summ(m.5)
# # 
# # 
# # m.6 <- lm(MAKER_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
# # summ(m.6)
# #  
# # 
# # m.7 <- lm(CHART_TRUST ~ CHART_BEAUTY + MAKER_ALIGN + flipped_intent + flipped_data + flipped_design, data = df )
# # summ(m.7)
# # 
# # m <- lm(MAKER_TRUST ~ MAKER_ALIGN, data = df)
# # summ(m)
# # 
# #  
# #  compare_performance(m.1, m.2, m.3, m.4, m.5, m, rank = TRUE)
# # # 
# # ## WHAT PREDICTS MAKER_TRUST?
# # 
# # 
# # ## PLOT THE DATA 
# # ggplot(df, aes(x = MAKER_ALIGN, y = MAKER_TRUST)) + 
# #   geom_point() +
# #   stat_smooth(method = "lm", 
# #               formula = y ~ x, 
# #               geom = "smooth") + 
# #   labs(title = "MAKER ALIGNMENT PREDICTS TRUST?")+
# #   theme_minimal()
# # 
# # 
# # ## PLOT THE DATA 
# # ggplot(df, aes(x = flipped_data, y = MAKER_TRUST)) + 
# #   geom_point() +
# #   stat_smooth(method = "lm", 
# #               formula = y ~ x, 
# #               geom = "smooth") + 
# #   labs(title = "MAKER DATA PREDICTS TRUST?")+
# #   theme_minimal()
# # 
# # 
# # ## BUILD MODEL
# # m.1 <- lm( MAKER_TRUST ~ MAKER_ALIGN, data = df)
# # # summary(m.1)
# # jtools::summ(m.1, confint = TRUE)
# # # check_model(m.1)
# # # report(m.1)
# # 
# # ## BUILD MODEL
# # m.2 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data, data = df)
# # # summary(m.2)
# # jtools::summ(m.2, confint = TRUE)
# # # check_model(m.2)
# # # report(m.2)
# # 
# # ## BUILD MODEL
# # m.3 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design , data = df)
# # # summary(m.3)
# # jtools::summ(m.3, confint = TRUE)
# # # check_model(m.3)
# # # report(m.3)
# # 
# # 
# # ## BUILD MODEL
# # m.4 <- lm( MAKER_TRUST ~ MAKER_ALIGN + flipped_data + flipped_design + MAKER_POLITIC, data = df)
# # # summary(m.3)
# # jtools::summ(m.4, confint = TRUE)
# # # check_model(m.3)
# # # report(m.3)
# # 
# # 
# # 
# #   
# # compare_performance(m.1, m.2, m.3, m.4, m.B,  rank = TRUE)
# # 
# # 
# # # effect_plot(m.2, pred=MAKER_DATA, rug = TRUE, plot.points = TRUE) + 
# # #   xlim(0,100) + 
# # #   ylim(0,100)
# # 
# # 
# # 
# # 
# # df <- df_graphs %>% filter(STIMULUS != "B0-0") %>% 
# #   select(PID, STIMULUS, 
# #          MAKER_ID:MAKER_TRUST, CHART_LIKE:CHART_TRUST, 
# #          D_politicsFiscal, D_politicsSocial)
# # 
# # m.pid <- lmer( MAKER_TRUST ~  (1 | PID) , data = df, REML = FALSE)
# # m.stim <- lmer( MAKER_TRUST ~ (1|STIMULUS) , data = df, REML = FALSE)
# # m.r <- lmer( MAKER_TRUST ~ (1 | PID) + (1|STIMULUS), data = df, REML = FALSE)
# # 
# # compare_performance (m.pid, m.stim, m.r, rank = TRUE)
# # 
# # 
# # 
# # m.1 <- update( m.r, .~. + CHART_BEAUTY)
# # summ(m.1)
# # 
# # m.2 = update(m.1, . ~ . + CHART_LIKE)
# # summ(m.2)
# # 
# # 
# # m.3 = update(m.2, . ~ . + CHART_TRUST)
# # summ(m.3)
# # 
# # 
# # compare_performance(m.r, m.1, m.2, m.3, rank = TRUE)

```


```{r IXN-BOO}

df <- df_graphs_full %>% 
  filter(STIMULUS== "B0-0") 

 p <- ggplot(df, aes(x = MAKER_POLITIC, y = MAKER_CONF,
          color = MAKER_ID ,
          text = paste0("MAKER-DETAIL: ",MAKER_DETAIL, "<br>","ID: ", PID, "MAKER_EXPLAIN", MAKER_EXPLAIN)))+
      scale_color_viridis(discrete=TRUE, option="viridis")  +
      geom_point(size=0.5) +
      xlim(0,100)+
      ylim(0,100)+
      facet_grid(D_politicalParty ~ MAKER_ID) +
      theme_minimal() +
      labs(
        title = "B0-0 | MAKER Identification, Politics and Confidence",
        subtitle = "\n by Participant Confidence and Political Party",
        x = "MAKER POLITICS",
        y = "MAKER ID CONFIDENCE"
      )


ggplotly(p)
  
```


### On Confidence

```{r}


# df <- df_confidence_long %>% filter(QUESTION %nin% c("CONF", "SDIFF")) ##AVERAGE CONFIDENCE

df <- df_graphs_full %>% filter(STIMULUS== "B0-0")


ggplot(df, aes(x = MAKER_CONF, y = MAKER_TRUST, color = MAKER_ID)) + 
  geom_point() +
  scale_color_viridis(discrete=TRUE, option="viridis")  + 
  facet_grid(BLOCK ~ STIMULUS_CATEGORY) +
  theme_minimal() + 
  easy_remove_legend() 
  


ggplot(df, aes(x = MAKER_POLITIC, y = MAKER_TRUST, color = MAKER_ID)) + 
  geom_point() +
  scale_color_viridis(discrete=TRUE, option="viridis")  + 
  facet_grid(BLOCK ~ STIMULUS_CATEGORY) +
  theme_minimal() + 
  easy_remove_legend() 



```










# EDA

##  PAIR PLOTS

### B0-0 MILLENIAL PINK PLANTS 

```{r B00_MAKERID, message=FALSE}

#FILTER DATAFRAME
df <- df_graphs_full %>%
  filter(STIMULUS== "B0-0") %>%
  select(
    Distribution,  D_politicalParty,
    # D_gender, D_race, D_education, D_income, D_age,
    # ENCOUNTER,
    MAKER_ID,
    D_politicsSocial, D_politicsFiscal,
    MAKER_DESIGN, MAKER_DATA, MAKER_CONF, MAKER_ALIGN, MAKER_TRUST, CHART_TRUST
    # :MAKER_TRUST,
    # TOOL_CONF,CHART_LIKE:CHART_TRUST
)

# g <- ggpairs(df, color=MAKER_ID)
# ggsave(plot = g, path="figs/pairplots", filename =paste0("B0-0","_pairplot.svg"), units = c("in"), width = 20, height = 20  )
# ggplotly(g)




(boo_pair <- ggpairs(df, aes(color= MAKER_ID)) +
    scale_color_viridis(discrete=TRUE, option="viridis")+
    scale_fill_viridis(discrete=TRUE, option="viridis") +
    theme_minimal()
  )


(boo_duo <- ggduo(df, aes(color= Distribution)) +
    scale_color_viridis(discrete=TRUE, option="viridis")+
    scale_fill_viridis(discrete=TRUE, option="viridis") +
    theme_minimal()
  )



ggplotly(boo_duo) #surprisingly works! but not helpful

```

### CATEGORIES-MAKER
```{r}

df <- df_graphs %>% select(
  STIMULUS_CATEGORY, MAKER_ID, MAKER_DESIGN, MAKER_DATA, MAKER_POLITIC, MAKER_ARGUE, MAKER_ALIGN, MAKER_TRUST, CHART_TRUST, CHART_BEAUTY
)


#maker pair plot 
x <- ggduo(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("maker_category","_duoplot.png"), units = c("in"), width = 20, height = 20  )

#maker pair plot 
x <- ggpairs(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("maker_category","_pairplot.png"), units = c("in"), width = 20, height = 20  )

```


### CATEGORIES-CHART
```{r}

df <- df_graphs %>% select(
  STIMULUS_CATEGORY, MAKER_ID, CHART_LIKE, CHART_BEAUTY, CHART_INTENT, CHART_TRUST, MAKER_TRUST
)


#maker pair plot 
x <- ggduo(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("chart_category","_duoplot.png"), units = c("in"), width = 20, height = 20  )

#maker pair plot 
x <- ggpairs(df, aes(color = STIMULUS_CATEGORY))
ggsave(plot = x, path="figs/pairplots", filename =paste0("chart_category","_pairplot.png"), units = c("in"), width = 20, height = 20  )

```



### ALL NUMERIC
```{r}

df <- df_graphs %>% select(STIMULUS_CATEGORY, where(is.numeric)) %>% 
  select(-duration.min)


#maker pair plot 
x <- ggscatmat(df, color = "STIMULUS_CATEGORY")
ggsave(plot = x, path="figs/pairplots", filename =paste0("category","_scaplot.png"), units = c("in"), width = 20, height = 20  )



```



# INTERACTIVE GRAPHS


### WIP IXN Maker ID & Politics
```{r PLOTLY}

#SETUP LISTS 
stim <- ref_stimuli
plots_maker_politics <- htmltools::tagList()

### MAKE PLOTS 
# LOOP THROUGH STIMULI
i = 0
for (s in stim){
  i = i+1 #iterator hack
  
  d <- df_graphs_full %>% filter(STIMULUS == s) %>% select(PID, STIMULUS, 
                                                               MAKER_ID, MAKER_DETAIL, MAKER_CONF, MAKER_POLITIC,
                                                               D_politicalParty, D_politicsSocial, D_politicsFiscal) 
  p <- ggplot(d, aes(x = MAKER_POLITIC, y = MAKER_CONF,
          color = MAKER_ID ,
          text = paste0("MAKER-DETAIL: ",MAKER_DETAIL, "<br>","ID: ", PID)))+
      geom_point() +
      xlim(0,100)+
      ylim(0,100)+
      facet_grid(MAKER_ID  ~ D_politicalParty) +
      theme_minimal() +
      labs(
        title = paste(s," | ", "MAKER Identification, Politics and Confidence, by Participant Confidence and Political Affiliation"),
        x = "MAKER POLITICS",
        y = "MAKER CONFIDENCE"
      )

  
  plots_maker_politics[[i]] <- ggplotly(p)
  
}

names(plots_maker_politics) <- ref_stimuli


#works in console but not render 
### PRINT PLOTS
# for (s in stim){
#   print(plots_maker_politics[[s]])
# }


# ggplotly(p) #works for single

plots_maker_politics
```


# WIP QDA ANALYSIS

## MAKER ID DETAIL 

```{r CODED-MAKER-ID-DETAIL}

# df <- df_graphs_coded %>% select( ID.Prolific, STIMULUS, BLOCK, STIMULUS_CATEGORY, MAKER_ID, MAKER_DETAIL, CODE_M_ID_SPECIFIC) %>% 
#   separate_longer_delim(
#     cols = CODE_M_ID_SPECIFIC,
#     delim = ","
#   ) %>% filter(
#     CODE_M_ID_SPECIFIC %nin% c("x", "X","example")
#   ) %>% mutate(
#     CODED_MAKER = str_trim(CODE_M_ID_SPECIFIC, side="left"),
#     CODED_MAKER = str_to_upper(CODED_MAKER),
#     CODED_MAKER = factor(CODED_MAKER, levels = c( "NYT",
#                                                   "WASHINGTON POST" ,
#                                                   "USA TODAY" ,
#                                                   "THE ECONOMIST" ,
#                                                   "WSJ",
#                                                   "POPULAR SCIENCE" ,
#                                                   "TIME",
#                                                   "NPR",
#                                                   "PBS",
#                                                   "ASSOCIATED PRESS"  ,
#                                                   "BBC",
#                                                   "CBS NEWS"  ,
#                                                   "ABC NEWS"  ,
#                                                   "NBC",
#                                                   "CNN",
#                                                   "FOX NEWS"  ,
#                                                   "BUZZFEED",
#                                                   "VOX",
#                                                   "VICE",
#                                                   "HUFFINGTON POST" ,
#                                                   "US DOD"  ,
#                                                   "US BUREAU OF ECONOMIC ANALYSIS",
#                                                   "US DOE"  ,
#                                                   "US CDC"  ,
#                                                   "MINISTRY OF HEALTH"  ,
#                                                   "EPA",
#                                                   "NOAA",
#                                                   "NATIONAL WEATHER SERVICE"  ,
#                                                   "WHO",
#                                                   "UN",
#                                                   "THE NATURE CONSERVANCY"  ,
#                                                   "GREENPEACE",
#                                                   "LEAF",
#                                                   "HARVARD",
#                                                   "COLUMBIA UNIVERSITY" ,
#                                                   "IAA",
#                                                   "IBM",
#                                                   "MICROSOFT",
#                                                   "GOLDMAN SACHS" ,
#                                                   "GMC",
#                                                   "TESLA",
#                                                   "GREEN PARTY OF AMERICA"  ,
#                                                   "THE DEMOCRATIC PARTY"  ,
#                                                   "THE REPUBLICAN PARTY")),
#     STIM = factor(STIMULUS, levels = c(
#       "B1-1",  "B2-1", "B3-1", "B4-1", "B5-1", "B6-1",
#       "B1-2",  "B2-2", "B3-2", "B4-2", "B5-2", "B6-2",
#       "B1-3", "B2-3", "B3-3", "B4-3", "B5-3", "B6-3",
#       "B1-4","B2-4" ,"B3-4" ,"B4-4" ,"B5-4" ,"B6-4", "B0-0"
#     ))
#   ) 
# 
# 
# 
# ggplot(df,  aes(x = MAKER_ID, fill = CODED_MAKER )) + 
#   geom_bar(position = "stack") +
#   facet_grid( rows = vars(BLOCK), cols = vars(fct_rev(STIMULUS_CATEGORY))) + 
#   theme_minimal() + 
#   labs(title = "Specific makers identified by stimulus")
# 
#                           
# ggplot(df,  aes(x = STIMULUS, fill = CODED_MAKER )) + 
#   geom_bar(position = "stack") + 
#   theme_minimal()
# 
# 
# ggplot(df,  aes(x = STIMULUS, fill = CODED_MAKER )) + 
#   geom_bar(position = "stack") + 
#   facet_wrap(~CODED_MAKER) + 
#   theme_minimal() +
#   easy_remove_x_axis() +
#   easy_remove_legend()
# 
#   
# ggplot(df,  aes(x = CODE_M_ID_SPECIFIC, fill = STIM, )) + 
#   geom_bar(position = "stack") + 
#   coord_flip() + 
#   theme_minimal() 
#   
  
      

```




# MODELLING






```{r, message=FALSE}

##STATSPLOT
# grouped_ggwithinstats(
#   data  = df_graphs,
#   x     = STIMULUS,
#   y     = CHART_TRUST,
#   grouping.var = ID.Study
# ) 

# grouped_ggscatterstats(
#   data = df_graphs, ## data frame from which variables are taken
#   x = CHART_BEAUTY, ## predictor/independent variable
#   y = CHART_TRUST, ## dependent variable
#   grouping.var = ID.Study,
#   xlab = "CHART BEAUTY", ## label for the x-axis
#   ylab = "CHART TRUST", ## label for the y-axis
#   # label.expression = rating < 5 & budget > 100, ## expression for deciding which points to label
#   point.label.args = list(alpha = 0.7, size = 4, color = "grey50"),
#   xfill = "#CC79A7", ## fill for marginals on the x-axis
#   yfill = "#009E73" ## fill for marginals on the y-axis
#   # title = "CHART TRUST (VS) MAKER TRUST",
#   # caption = ""
# )
# 
# gf_point( data = df_graphs, CHART_TRUST~MAKER_TRUST, color = ~STIMULUS) %>% gf_facet_wrap(~STIMULUS)
# 
# 
# grouped_ggscatterstats(
#   data = df_graphs, ## data frame from which variables are taken
#   x = MAKER_TRUST, ## predictor/independent variable
#   y = CHART_TRUST, ## dependent variable
#   grouping.var = ID.Study,
#   xlab = "MAKER TRUST", ## label for the x-axis
#   ylab = "CHART TRUST", ## label for the y-axis
#   # label.expression = rating < 5 & budget > 100, ## expression for deciding which points to label
#   point.label.args = list(alpha = 0.7, size = 4, color = "grey50"),
#   xfill = "#CC79A7", ## fill for marginals on the x-axis
#   yfill = "#009E73" ## fill for marginals on the y-axis
#   # title = "CHART TRUST (VS) MAKER TRUST",
#   # caption = ""
# )
# 
# gf_point( data = df_graphs, MAKER_TRUST~CHART_TRUST, color = ~STIMULUS) %>% gf_facet_wrap(~STIMULUS)
# 
# 
# 
# grouped_ggscatterstats(
#   data = df_graphs, ## data frame from which variables are taken
#   x = CHART_BEAUTY, ## predictor/independent variable
#   y = MAKER_ALIGN, ## dependent variable
#   grouping.var = ID.Study,
#   xlab = "CHART BEAUTY", ## label for the x-axis
#   ylab = "MAKER ALIGN", ## label for the y-axis
#   # label.expression = rating < 5 & budget > 100, ## expression for deciding which points to label
#   point.label.args = list(alpha = 0.7, size = 4, color = "grey50"),
#   xfill = "#CC79A7", ## fill for marginals on the x-axis
#   yfill = "#009E73" ## fill for marginals on the y-axis
#   # title = "CHART TRUST (VS) MAKER TRUST",
#   # caption = ""
# )
# 
# 
# gf_point( data = df_graphs, MAKER_ALIGN~CHART_BEAUTY, color = ~STIMULUS) %>% gf_facet_wrap(~STIMULUS)
# 
# 
# 
# 
# 
# 
# ggscatterstats(
#   data = df_graphs %>% filter(STIMULUS=="B0-0"), ## data frame from which variables are taken
#   x = CHART_BEAUTY, ## predictor/independent variable
#   y = MAKER_TRUST, ## dependent variable
#   xlab = "CHART BEAUTY", ## label for the x-axis
#   ylab = "MAKER TRUST", ## label for the y-axis
#   # label.expression = rating < 5 & budget > 100, ## expression for deciding which points to label
#   point.label.args = list(alpha = 0.7, size = 4, color = "grey50"),
#   xfill = "#CC79A7", ## fill for marginals on the x-axis
#   yfill = "#009E73" ## fill for marginals on the y-axis
#   # title = "CHART TRUST (VS) MAKER TRUST",
#   # caption = ""
# )
# 
# gf_point( data = df_graphs %>% filter(STIMULUS=="B0-0"), CHART_TRUST~CHART_BEAUTY, color = ~STIMULUS) %>% gf_facet_wrap(~STIMULUS)
# 
# gf_point( data = df_graphs %>% filter(STIMULUS=="B0-0"), MAKER_TRUST~CHART_BEAUTY, color = ~STIMULUS) %>% gf_facet_wrap(~STIMULUS)


```

```{r}
# 
# 
# #TODO CENTERING AND NORMALIZING
# 
# ### little model
# df <- df_graphs %>% filter(STIMULUS == "B0-0")
# m <- lm( CHART_TRUST ~ CHART_BEAUTY,data = df)
# summary(m)
# ggnostic(m) #GGALLY MODEL CHECKS
# check_model(m) #EASY STATS MODEL CHECKS 
# 
# report(m)
```

```{r}
### MORE COMPLEX MODEL
# df <- df_graphs %>% filter(STIMULUS != "B0-0")
# m1 <- lmer(CHART_TRUST ~ CHART_BEAUTY + (1|ID.Qualtrics), data = df)
# m2 <- lmer(CHART_TRUST ~ CHART_BEAUTY + (1|STIMULUS), data = df)
# m3 <- lmer(CHART_TRUST ~ CHART_BEAUTY + (1 | STIMULUS) + (1 | ID.Qualtrics), data = df)
# summary(m1)
# summary(m2)
# summary(m3)
# compare_parameters(m1,m2,m3)
# compare_performance(m1,m2,m3, rank = TRUE)
# 
# 
# m <- lmer(CHART_TRUST ~ CHART_BEAUTY + MAKER_TRUST + (1 | STIMULUS) ,  data = df)
# mi <- lmer(CHART_TRUST ~ CHART_BEAUTY * MAKER_TRUST + (1 | STIMULUS) , data = df)
# summary(m)
# summary(mi)
# 
# compare_performance(m3,m,mi, rank = TRUE)
# 
# report(m)
#todo see https://yury-zablotski.netlify.app/post/mixed-effects-models-2/ about fitting with ML vs REML for model comparison 
```

```{r}
# #TODO WALK THROUGH THIS 
# #https://yury-zablotski.netlify.app/post/mixed-models/#multiple-random-slope-model
# 
# #load example data
# data("sleepstudy")
# 
# #fit the model
# m_slp <- lmer(Reaction ~ Days + (Days | Subject), sleepstudy)
# 
# #the next line put all the estimated intercept and slope per subject into a dataframe
# reaction_slp <- as.data.frame(t(apply(ranef(m_slp)$Subject, 1,function(x) fixef(m_slp) + x)))
# 
# #to get the predicted regression lines we need one further step, writing the linear equation: Intercept + Slope*Days with different coefficient for each subject
# pred_slp <- melt(apply(reaction_slp,1,function(x) x[1] + x[2]*0:9), value.name = "Reaction")
# 
# #some re-formatting for the plot
# names(pred_slp)[1:2] <- c("Days","Subject")
# pred_slp$Days <- pred_slp$Days - 1
# pred_slp$Subject <- as.factor(pred_slp$Subject)
# 
# #plot with actual data 
# ggplot(pred_slp,aes(x=Days,y=Reaction,color=Subject))+
#   geom_line()+
#   geom_point(data=sleepstudy,aes(x=Days,y=Reaction))+
#   facet_wrap(~Subject,nrow=3)

```



# GENERATE SEMANTIC DIFFERENTIAL GRAPHS

NOTE: the following blocks run if the `graph_render` var is set to `TRUE` in the header block. Graphs are generated (takes a long time) and written to the figs folder. Only do this data are are added or excluded 

## ALL QUESTIONS

### MASTER — ALL STIMULI

```{r ALL-Q-COLLAPSED}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){


  
  plot_sd = function (data, column, type, facet, facet_by, boxplot) {

  ggplot(df, aes(y = .data[[column]], x="")) +
    {if(boxplot) geom_boxplot(width = 0.5) } +
    geom_jitter(width = 0.1, alpha=0.3, {if(facet) aes(color=.data[[facet_by]])}) +
    {if(facet) facet_grid(.data[[facet_by]] ~ .)} +
    scale_y_continuous(limits=c(-1,101)) +
    labs(x="", y="") +
    coord_flip()  +
    {if(type == "S")
      guides(
        y = guide_axis_manual(labels = ref_labels[column,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[column,"right"])
      )} +
    {if(type == "Q")
      guides(
        y = guide_axis_manual(labels = ref_labels[q,"left"]),
        y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
      )} +
  theme_minimal()  +
     labs (
       caption = column
     ) + easy_remove_legend()
  }
  
#################### ALL QUESTIONS across ALL STIMULUS #####################

  df <- df_graphs 

  #subset data cols 
  cols <- df %>% select( all_of(ref_sd_questions))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type ="S", facet = FALSE, boxplot=TRUE))
  
  #aggregate q plots into one for stimulus 
  plot_master_questions <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
   plot_annotation(
     title = "ALL STIMULI",
     subtitle =""
   )
  
  ggsave(plot = plot_master_questions, path="figs/_master", filename =paste0("combined_stimuli","_box.png"), units = c("in"), width = 10, height = 14  )
  
  
  #### RAINCLOUD PLOT#############################################################################
  # setup dataframe 
  df <- df_sd_questions_long %>% select(1:8, QUESTION, value) 

  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(QUESTION), x = value, fill = fct_rev(QUESTION))) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    y = guide_axis_manual(labels = rev(ref_labels$left)),
    y.sec = guide_axis_manual(labels = rev(ref_labels$right))
  ) + 
  labs (title = "ALL STIMULI") +
  theme_minimal() 
   
  
  ggsave(plot = x, path="figs/_master", filename =paste0("combined_stimuli","_rain.png"), units = c("in"), width = 10, height = 14  )


  
  
  #### DENSITY RIDGES#############################################################################
  # setup dataframe 
  
  magic_colors = list(
  amy_gradient =  c("#ac57aa", "#9e5fa4", "#90689f", "#827099", "#747894", "#66818e", "#578988", "#499183", "#3b997d", "#2da278", "#1faa72"),
  my_favourite_colours = c("#702963", "#637029",    "#296370")
)
  
  
  magic_palettes = function(name, n, all_palettes = magic_colors, type = c("discrete", "continuous")) {
  palette = all_palettes[[name]]
  if (missing(n)) {
    n = length(palette)
  }
  type = match.arg(type)
  out = switch(type,
               continuous = grDevices::colorRampPalette(palette)(n),
               discrete = palette[1:n]
  )
  structure(out, name = name, class = "palette")
}
  

  
  df <- df_sd_questions_long %>% select(1:8, QUESTION, value) 
  
  
 (x <-  ggplot(df, aes(x = value, y = fct_rev(QUESTION), fill = fct_rev(QUESTION))) +
    geom_density_ridges(scale = 1.5,quantile_lines = TRUE, alpha = 0.75) + 
    # scale_fill_paletteer_d("colorBlindness::SteppedSequential5Steps")+ #don't hate this
    # scale_fill_paletteer_d("dichromat::SteppedSequential_5", direction = 1)+  #don't hate this
    # scale_fill_paletteer_d("ggthemes::Hue_Circle", direction = 1)+  #LOVE THIS
    # scale_fill_paletteer_d("ggthemes::Classic_Cyclic", direction = 1)+  #LOVE THIS
    ggplot2::scale_fill_manual(values = magic_palettes("amy_gradient"))+
    theme_minimal() +
    guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    # y = guide_axis_manual(labels = paste(rev(levels(df$QUESTION)))),
    y = guide_axis_manual(labels = rev(ref_labels$left)),
    y.sec = guide_axis_manual(labels = rev(ref_labels$right))
  ) + labs(
    title = "ALL STIMULI — SD questions"
  ))
  
  ggsave(plot = x, path="figs/_master", filename =paste0("combined_stimuli","_ridges.png"), units = c("in"), width = 10, height = 14  )

  
  
}
  






```



### ALL Q BY STIMULUS

```{r ALL-Q-BY-STIMULUS}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){


#################### ALL QUESTIONS AT STIMULUS #####################
# ONE PLOT FOR EACH STIMULUS WITH ALL QUESTIONS

#set stimuli to be graphed 
stimuli <- ref_stimuli #created in wrangling block
# stimili <- c("B0-0","B2-1" ,"B2-2", "B2-3", "B2-4")

box_stimuli <- list()
rain_stimuli <- list()
i = 0
for (s in stimuli){
  i = i+1
  
  # setup dataframe 
  title <- df_stimuli %>% filter(ID == s) %>% select(NAME) 
  title <- paste(s,"|",title)
  df <- df_graphs %>% filter(STIMULUS== s)

  #subset data cols 
  cols <- df %>% select( all_of(ref_sd_questions))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type ="S", facet = FALSE, boxplot=TRUE))

  #aggregate q plots into one for stimulus 
  x <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
   plot_annotation(
     title = title,
     subtitle =""
   )
  
  box_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/all_q_by_stimulus", filename =paste0(s,"_box.png"), units = c("in"), width = 10, height = 14  )
  
  
  #### RAINCLOUD PLOT
  # setup dataframe 
  title <- df_stimuli %>% filter(ID == s) %>% select(NAME) 
  title <- paste(s,"|",title)
  df <- df_sd_questions_wide %>% select(1:6, QUESTION, all_of(s)) %>% filter(!is.na(s)) %>%  mutate(value = get(s))


  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(QUESTION), x = value, fill = fct_rev(QUESTION))) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  guides(
    # y = guide_axis_manual(labels = paste(levels(df$QUESTION),ref_labels$left)),
    y = guide_axis_manual(labels = rev(ref_labels$left)),
    y.sec = guide_axis_manual(labels = rev(ref_labels$right))
  ) + 
  labs (title = title) +
  theme_minimal() 
   
  
  rain_stimuli[[i]] <- x
  ggsave(plot = x, path="figs/all_q_by_stimulus", filename =paste0(s,"_rain.png"), units = c("in"), width = 10, height = 14  )
  
  
  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_stimulus$`B1-1`
#ALSO plots_stimulus$`B1-1`[[1]]
names(box_stimuli) <- stimuli
names(rain_stimuli) <- stimuli
rm(x, i, plots)

#############################################################################
} 

```



### ALL Q BY CATEGORY

```{r ALL-Q-BY-CATEGORY}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){

#################### ALL QUESTIONS AT CATEGORY #####################
# ONE PLOT FOR EACH CATEGORY WITH ALL QUESTIONS

#set questions to be graphed 
categories <- unique(df_graphs$STIMULUS_CATEGORY)#created in wrangling block
box_category <- list()
rain_category <- list()

i = 0
for (c in categories){
  i = i+1

  # setup dataframe
  title <- paste("STIMULUS CATEGORY ", c)
  df <- df_graphs %>% filter(STIMULUS_CATEGORY == c)
  
  #subset data cols
  cols <- df %>% select( all_of(ref_sd_questions))
  plots <- as.list(lapply(colnames(cols), plot_sd, data = df, type = "S", facet = FALSE, boxplot=TRUE))
  
  #aggregate stimulus plots into block for question
  x <- plots[[1]] / plots[[2]]  / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
        plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] +
      plot_annotation(
        title = title,
       subtitle =""
      )

  box_category[[i]] <- x
  ggsave(plot = x, path="figs/all_q_by_category", filename =paste0(c,"_box.png"), units = c("in"), width = 10, height = 26)
  
  
  
  
  #### RAINCLOUD PLOT
  # setup dataframe 
  title <- paste("STIMULUS CATEGORY ", c)
  df <- df_sd_questions_long %>% filter(STIMULUS_CATEGORY == c) %>% select(STIMULUS_CATEGORY, QUESTION, value, PID, Assigned.Block) 
  
  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(QUESTION), x = value, fill = fct_rev(QUESTION))) +
  stat_slab(normalize="groups", trim = TRUE, scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  guides(
    y = guide_axis_manual(labels = paste(rev(levels(df$QUESTION)),rev(ref_labels$left))),
    y = guide_axis_manual(labels = rev(ref_labels$left)),
    y.sec = guide_axis_manual(labels = rev(ref_labels$right))
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  rain_category[[i]] <- x
  ggsave(plot = x, path="figs/all_q_by_category", filename =paste0(c,"_rain.png"), units = c("in"), width = 10, height = 26  )
  
  
}  

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_category$A
#ALSO plots_category$A[[1]]
names(box_category) <- categories
names(rain_category) <- categories
rm(x, i, plots)

}

```

## BY QUESTION

### Q for ALL STIMULI

```{r Q-FOR-ALL-STIMULI}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){

####################CREATE SD PLOTS FOR EACH QUESTION#####################

#set questions to be graphed 
questions <- ref_sd_questions  #created in wrangling block
box_s_question <- list()
rain_s_question <- list()
i = 0
for (q in questions){
  i = i+1
  
  # setup dataframe 
  title <- paste(q)
  df <- df_sd_questions_wide %>% filter(QUESTION == q)

  #subset data cols 
  c <- df %>% select( all_of(ref_stimuli))
  plots <- as.list(lapply(colnames(c), plot_sd, data = df, type = "Q", facet = FALSE, boxplot=TRUE))
  
  #aggregate stimulus plots into block for question
  x <- plots[[1]] / plots[[2]]  / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
        plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] /  plots[[12]] / plots[[13]] / plots[[14]] / 
        plots[[15]] /plots[[16]] /plots[[17]] /plots[[18]] /  plots[[19]] / plots[[20]] / plots[[21]] /
        plots[[22]] /plots[[23]] /plots[[24]] /plots[[25]] + 
      plot_annotation(
        title = title,
       subtitle =""
      )
  box_s_question[[i]] <- x 
  ggsave(plot = x, path="figs/by_q_for_all_stimuli", filename =paste0(q,"_box.png"), units = c("in"), width = 10, height = 26)

  
  
  
  ############# RAINCLOUD
  # setup dataframe 
  title <- paste(q)
  df <- df_sd_questions_long %>% filter(QUESTION ==q)
    #select(1:6, QUESTION, all_of(s)) %>% filter(!is.na(s)) %>%  mutate(value = get(s))
  left <- ref_labels[q,]$left
  right <- ref_labels[q,]$right

  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = fct_rev(STIMULUS) , x = value, fill = fct_rev(STIMULUS))) +
      stat_slab(normalize="groups", scale = 0.7) +
      stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  rain_s_question[[i]] <- x
  ggsave(plot = x, path="figs/by_q_for_all_stimuli", filename =paste0(q,"_rain.png"), units = c("in"), width = 10, height = 14  )
  

  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_s_question$MAKER_DESIGN
#ALSO plots_s_question$MAKER_DESIGN[[1]]
names(box_s_question) <- questions
names(rain_s_question) <- questions
rm(x, i, plots, left, right)

#############################################################################

}
```

### Q for ALL CATEGORIES

```{r Q-FOR-ALL-CATEGORIES}

##ONLY RENDER GRAPHS IF SET TO TRUE
if(graph_render == TRUE){
  
####################SD PLOTS QUESTION BY CATEGORY #####################

#set grouping column 
g = "STIMULUS_CATEGORY" #string name of column to group by 

#set questions to be graphed 
questions <- ref_sd_questions#created in wrangling block
box_c_question <- list()
rain_c_question <- list()
i = 0
for (q in questions){
  i = i+1
  left <-   ref_labels[q,]$left
  right <-  ref_labels[q,]$right
  
  # setup dataframe 
  title <- paste(q," BY CATEGORY")
  df <- df_graphs 
  
  x <- multi_sd(df, left, right, x = q, y = g, color = g) + 
      labs(title  = q) 
 
  box_c_question[[i]] <- x
  ggsave(plot = x, path="figs/by_q_for_all_categories", filename =paste0(q,"_box.png"))
  
  
  
  ############RAINCLOUDS
  # setup dataframe 
  title <- paste(q," BY CATEGORY")
  df <- df_sd_questions_long %>% filter(QUESTION ==q)
  left <-   ref_labels[q,]$left
  right <-  ref_labels[q,]$right

  #RAINCLOUD PLOT
  x <- ggplot(df, aes(y = STIMULUS_CATEGORY , x = value, fill = STIMULUS_CATEGORY)) +
      stat_slab(normalize="groups", scale = 0.7) +
      stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  guides(
    y = guide_axis_manual(labels = left),
    y.sec = guide_axis_manual(labels = right)
  ) +
  labs (title = title) +
  theme_minimal() 
   
  
  rain_c_question[[i]] <- x
  ggsave(plot = x, path="figs/by_q_for_all_categories", filename =paste0(q,"_rain.png"), units = c("in"), width = 10, height = 14  )

  
}

#GIVE NAMES TO LIST
#NOW CAN ACCESS plots by plots_c_question$MAKER_DESIGN
#ALSO plots_c_question$MAKER_DESIGN[[1]]
names(box_c_question) <- questions
names(rain_c_question) <- questions
rm(x, i, right, left, df)
  
#############################################################################

}

```



# STASH

wip code stash

### COLOR palettes

```{r}

#DISPLAY COLOR PALETTE
#display.brewer.pal(n = 8, name = 'Dark2')

#DISPLAY COLOR PALETTE
# paletteer_d("Redmonder::dPBIPuGn")

```

### DISTRIBUTION plots
```{r stash-SAMPLE-DISTRIBUTION-PLOTS}

# #SET UP DATAFRAME
# df <- df_data
# 
# ## DENSITY HISTOGRAPH
# ggplot(data = df_data, aes( x = duration.min, fill = Assigned.Block)) +
#   geom_density(alpha = 0.5) +
#   facet_grid(rows = vars(Assigned.Block)) +
#   labs( x = "Survey Response Time (mins)",
#         title = "TOTAL Response Time by Sample",
#         subtitle = "(expect similiar across samples)") +
#   easy_add_legend_title("Sample") +
#   theme_minimal()
# 
# 
# ## RAINCLOUD
# ggplot(df, aes(x = duration.min, y = fct_rev(Assigned.Block), fill = fct_rev(Assigned.Block))) +
#   stat_slab(aes(thickness = after_stat(pdf*n), alpha=0.5), scale = 0.7) +
#   stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
#   scale_fill_discrete(direction=-1)+
#   xlim(0,225) +
#   labs( x = "Survey Response Time (mins)", y="",
#         title = "TOTAL Response Time by Sample",
#         subtitle = "(expect similiar across samples)") +
#   theme_minimal() +
#   easy_remove_legend()
# 
# 
# ##RIDGEPLOT
# ggplot(df, aes(x = duration.min, y = fct_rev(Assigned.Block), fill = fct_rev(Assigned.Block))) +
#   geom_density_ridges(scale=0.9) +
#   # geom_boxplot()+
#   stat_pointinterval()+
#   theme_ridges() +
#   scale_fill_discrete(direction=-1)+
#   theme(legend.position = "none") +
#     labs( x = "Survey Response Time (mins)", y="",
#         title = "TOTAL Response Time by Sample",
#         subtitle = "(expect similiar across samples)")


```

### all-q for stimulus
```{r stash-SAMPLE-ALLQ-BY-STIMULUS}

# s = "B0-0" #stimulus code
# t = "STIMULUS B0 — MILLENIAL PINK PLANTS" #STIMULUS TITLE
# 
# #FILTER DATAFRAME
# df <- df_graphs %>% filter(STIMULUS == s)
# 
# 
# #BUILD SEMANTIC DIFFERENTIALS
# m_design <- single_sd(df, "professional", "layperson", x = MAKER_DESIGN) +
#       labs(title  = "MAKER-DESIGN") +
#       easy_remove_legend()
# 
# m_data <- single_sd(df, "professional", "layperson", x = MAKER_DATA) +
#       labs(title  = "MAKER-DATA") +
#       easy_remove_legend()
# 
# m_politics <- single_sd(df, "left-leaning", "right-leaning", x = MAKER_POLITIC) +
#       labs(title  = "MAKER-POLITICS") +
#       easy_remove_legend()
# 
# m_argue <- single_sd(df, "confrontational", "diplomatic", x = MAKER_ARGUE) +
#       labs(title  = "MAKER-ARGUE") +
#       easy_remove_legend()
# 
# m_selfish <- single_sd(df, "altruistic", "selfish", x = MAKER_SELF) +
#       labs(title  = "MAKER-SELFISH") +
#       easy_remove_legend()
# 
# m_align <- single_sd(df, "does NOT share", "does share", x = MAKER_ALIGN) +
#       labs(title  = "MAKER-ALIGNMENT") +
#       easy_remove_legend()
# 
# m_trust <- single_sd(df, "untrustworthy", "trustworthy", x = MAKER_TRUST) +
#       labs(title  = "MAKER-TRUST") +
#       easy_remove_legend()
# 
# 
# #BUILD MASTER PLOT
# PLOT_maker <- (m_design / m_data / m_politics / m_argue / m_selfish / m_align / m_trust) +
#   plot_annotation(
#     title = t,
#     subtitle =""
#   )
# 
# PLOT_maker

```

### all-q for stimulus - grouped
```{r stash-SAMPLE-ALLQ-BY-STIMULUS-GROUPED}

#  s = "B0-0" #stimulus code
#  t = "STIMULUS B0 — MILLENIAL PINK PLANTS" #STIMULUS TITLE
#  g = "Assigned.Block"
#  ##can also use y and color to split by additional variable 
#  
#  #FILTER DATAFRAME
#  df <- df_graphs %>% filter(STIMULUS == s)
# 
#  #BUILD SEMANTIC DIFFERENTIALS
#  m_design <- multi_sd(df, "professional", "layperson", x = "MAKER_DESIGN", y = g, color = g) +
#        labs(title  = "MAKER-DESIGN") +
#        easy_remove_legend()
# 
#  m_data <- multi_sd(df, "professional", "layperson", x = "MAKER_DATA", y = g, color = g) +
#        labs(title  = "MAKER-DATA") +
#        easy_remove_legend()
# 
#  m_politics <- multi_sd(df, "left-leaning", "right-leaning", x = "MAKER_POLITIC", y = g, color = g) +
#        labs(title  = "MAKER-POLITICS") +
#        easy_remove_legend()
# 
#  m_argue <- multi_sd(df, "confrontational", "diplomatic", x = "MAKER_ARGUE", y = g, color = g) +
#        labs(title  = "MAKER-ARGUE") +
#        easy_remove_legend()
# 
#  m_selfish <- multi_sd(df, "altruistic", "selfish", x = "MAKER_SELF", y = g, color = g) +
#        labs(title  = "MAKER-SELFISH") +
#        easy_remove_legend()
# 
#  m_align <- multi_sd(df, "does NOT share", "does share", x = "MAKER_ALIGN", y = g, color = g) +
#        labs(title  = "MAKER-ALIGNMENT") +
#        easy_remove_legend()
# 
#  m_trust <- multi_sd(df, "untrustworthy", "trustworthy", x = "MAKER_TRUST", y = g, color = g) +
#        labs(title  = "MAKER-TRUST") 
# 
# 
#  #BUILD MASTER PLOT
#  PLOT_maker <- (m_design / m_data / m_politics / m_argue / m_selfish / m_align / m_trust) +
#    plot_annotation(
#      title = t,
#      subtitle =""
#    )
# 
#  PLOT_maker
```

### across Blocks
```{r stash-across-blocks}
######### MAKER ATTRIBUTES ########################
# vals = c("datacollar", "bluecollar")
# leftside <- rep ("PROFESSIONAL",n_blocks )
# rightside <-rep ("LAYPERSON",n_blocks ) 
# b00_m_design <- ggplot(df, aes(y = MAKER_DESIGN, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-DESIGN")

# b00_m_data <- ggplot(df, aes(y = MAKER_DATA, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-DATA")


# leftside <- rep ("LEFT-WING",n_blocks )
# rightside <-rep ("RIGHT-WING",n_blocks ) 
# b00_m_politics <- ggplot(df, aes(y = MAKER_POLITIC, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-POLITICS")
  

# leftside <- rep ("CONFRONTATIONAL",n_blocks )
# rightside <-rep ("DIPLOMATIC",n_blocks ) 
# b00_m_argue <- ggplot(df, aes(y = MAKER_ARGUE, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-ARGUE")
  
# leftside <- rep ("ALTRUSITC",n_blocks )
# rightside <-rep ("SELFISH",n_blocks ) 
# b00_m_selfish <- ggplot(df, aes(y = MAKER_SELF, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-SELFISH")

# 
# leftside <- rep ("Does NOT",n_blocks )
# rightside <-rep ("DOES",n_blocks ) 
# b00_m_align <- ggplot(df, aes(y = MAKER_ALIGN, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-SHARES-MY-VALUES")

# leftside <- rep ("UNTRUSTWORTHY",n_blocks )
# rightside <-rep ("TRUSTWORTHY",n_blocks ) 
# b00_m_trust <- ggplot(df, aes(y = MAKER_TRUST, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   # easy_remove_legend() +
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-TRUST")
# 
# PLOT_b0_maker <- (b00_m_design / b00_m_data / b00_m_politics / b00_m_argue / b00_m_selfish / b00_m_align / b00_m_trust) + 
#   plot_annotation(
#     title = "STIMULUS B0 — MILLENIAL PINK PLANTS",
#     subtitle =""
#   )
# 
# PLOT_b0_maker
###################################################
```

### single Block
```{r stash-single-block}

# #FILTER DATAFRAME
# df <- df_graphs %>% filter(STIMULUS == "B0-0")
# 
# ######### MAKER ATTRIBUTES ########################
# vals = c("datacollar", "bluecollar")
# leftside <- rep ("PROFESSIONAL",1 )
# rightside <-rep ("LAYPERSON",1 ) 
# b_m_design <- ggplot(df, aes(y = MAKER_DESIGN, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-DESIGN")
# 
# b_m_data <- ggplot(df, aes(y = MAKER_DATA, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-DATA")
# 
# 
# leftside <- rep ("LEFT-WING",1 )
# rightside <-rep ("RIGHT-WING",1 ) 
# b_m_politics <- ggplot(df, aes(y = MAKER_POLITIC, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-POLITICS")
#   
# 
# leftside <- rep ("CONFRONTATIONAL",1 )
# rightside <-rep ("DIPLOMATIC",1 ) 
# b_m_argue <- ggplot(df, aes(y = MAKER_ARGUE, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-ARGUE")
#   
# leftside <- rep ("ALTRUSITC",1 )
# rightside <-rep ("SELFISH",1 ) 
# b_m_selfish <- ggplot(df, aes(y = MAKER_SELF, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-SELFISH")
# 
# 
# leftside <- rep ("Does NOT",1 )
# rightside <-rep ("DOES",1 ) 
# b_m_align <- ggplot(df, aes(y = MAKER_ALIGN, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-SHARES-MY-VALUES")
# 
# leftside <- rep ("UNTRUSTWORTHY",1 )
# rightside <-rep ("TRUSTWORTHY",1 ) 
# b_m_trust <- ggplot(df, aes(y = MAKER_TRUST, x = ""))+
#   geom_boxplot(width = 0.5) +
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-TRUST")
# 
# 
# PLOT_b_maker <- (b_m_design / b_m_data / b_m_politics / b_m_argue / b_m_selfish / b_m_align / b_m_trust) + 
#   plot_annotation(
#     title = paste(unique(df$STIMULUS), "MAKER")
#   )
# 
# PLOT_b_maker
###################################################
```

### single Block grouped
```{r stash-single-block-grouped}
# 
# #FILTER DATAFRAME
# df <- df_graphs %>% filter(STIMULUS == "B0-0")
# 
# ######### MAKER ATTRIBUTES ########################
# vals = c("datacollar", "bluecollar")
# leftside <- rep ("PROFESSIONAL",1 )
# rightside <-rep ("LAYPERSON",1 ) 
# b_m_design <- ggplot(df, aes(y = MAKER_DESIGN, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-DESIGN")
# 
# b_m_data <- ggplot(df, aes(y = MAKER_DATA, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-DATA")
# 
# 
# leftside <- rep ("LEFT-WING",1 )
# rightside <-rep ("RIGHT-WING",1 ) 
# b_m_politics <- ggplot(df, aes(y = MAKER_POLITIC, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-POLITICS")
#   
# 
# leftside <- rep ("CONFRONTATIONAL",1 )
# rightside <-rep ("DIPLOMATIC",1 ) 
# b_m_argue <- ggplot(df, aes(y = MAKER_ARGUE, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-ARGUE")
#   
# leftside <- rep ("ALTRUSITC",1 )
# rightside <-rep ("SELFISH",1 ) 
# b_m_selfish <- ggplot(df, aes(y = MAKER_SELF, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-SELFISH")
# 
# 
# leftside <- rep ("Does NOT",1 )
# rightside <-rep ("DOES",1 ) 
# b_m_align <- ggplot(df, aes(y = MAKER_ALIGN, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-SHARES-MY-VALUES")
# 
# leftside <- rep ("UNTRUSTWORTHY",1 )
# rightside <-rep ("TRUSTWORTHY",1 ) 
# b_m_trust <- ggplot(df, aes(y = MAKER_TRUST, x = ID.Study, color = ID.Study))+
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   labs(x="", y="") +
#   coord_flip() + 
#   theme_minimal() + 
#   easy_remove_legend() + 
#   guides(
#   y = guide_axis_manual(
#   #breaks = vals, 
#   labels = leftside  
#   ),
#   y.sec = guide_axis_manual(
#   #breaks = vals, 
#   labels = rightside
# )) + 
#   labs(title  = "MAKER-TRUST")
# 
# 
# PLOT_b_maker <- (b_m_design / b_m_data / b_m_politics / b_m_argue / b_m_selfish / b_m_align / b_m_trust) + 
#   plot_annotation(
#     title = paste(unique(df$STIMULUS), "MAKER")
#   )
# 
# PLOT_b_maker
# ###################################################
```

### graph matrix
```{r stash-graph-matrix}




# #### 
# q = "MAKER_DESIGN"
# df <- df_questions %>% filter(QUESTION == q) %>% 
#   mutate(
#     value = as.numeric(value),
#     STIMULUS_CATEGORY = str_remove(STIMULUS,"B.-"),
#     STIMULUS_CATEGORY = factor(STIMULUS_CATEGORY,
#                   levels=c("0","1","2","3","4"),
#                   labels= c("F","A","B","C","D"))
# )
# 
# 
# g <- ggplot(df, aes(y = value, x="", color = STIMULUS_CATEGORY)) +
#     geom_boxplot(width = 0.5)+
#     geom_jitter(width = 0.1, alpha=0.3) + 
#     scale_y_continuous(limits=c(-1,101)) +
#     labs(x="", y="") +
#     coord_flip()  +
#     facet_grid(df$STIMULUS_CATEGORY ~ .) + 
#     labs(title=df$STIMULUS_CATEGORY) + 
#     guides(
#         y = guide_axis_manual(labels = ref_labels[q,"left"]),
#         y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
#       ) +  
#   theme_minimal()  + 
#   labs (title = q)
# 
# g
# left <- rep(ref_labels[q,"left"], length(unique(df$STIMULUS_CATEGORY)))
# right <- rep(ref_labels[q,"left"], length(unique(df$STIMULUS_CATEGORY)))
# a <- multi_sd(df, x = value, y = QUESTION, color = STIMULUS_CATEGORY, left=, right=right)
# 
# 
# multi_sd <- function (df, x, y, color, left,right) { 
#   
#   g <- ggplot(df, aes(y = {{x}}, x = {{y}}, color = {{color}}))+
#   geom_boxplot(width = 0.5) + 
#   geom_jitter(width = 0.1, alpha=0.5) + 
#   scale_y_continuous(limits=c(-1,101)) +
#   facet_grid(rows=vars({{color}})) +
#   labs(x="", y="") +
#   coord_flip() + 
#   guides(
#     y = guide_axis_manual(labels = left),
#     y.sec = guide_axis_manual(labels = right)
#   ) + theme_minimal() 
#   
#   return(g)
# }




# ## GROUPED PLOTSD FUNCTION 
# grouped_plotsd = function (data, x, type, q, boxplot) {
#   ggplot(df, aes(y = .data[[x]], x="")) +
#     {if(boxplot) geom_boxplot(width = 0.5) } +
#     geom_jitter(width = 0.1, alpha=0.3) + 
#     scale_y_continuous(limits=c(-1,101)) +
#     labs(x="", y="") +
#     coord_flip()  +
#     {if(type == "Q")
#       guides(
#         y = guide_axis_manual(labels = ref_labels[q,"left"]),
#         y.sec = guide_axis_manual(labels = ref_labels[q,"right"])
#       )} +  
#   theme_minimal()  + 
#      labs (
#        caption = column
#      )
# }


#####################################################################

# # stim <- "B1-1"
# 
# # setup dataframe 
# title <- df_stimuli %>% filter(ID ==stim) %>% select(NAME) 
# title <- paste(stim,"|",title)
# df <- df_graphs %>% filter(STIMULUS==stim)
# 
# #subset data cols 
# d <- df %>% select( all_of(questions))
# plots <- as.list(lapply(colnames(d), plotsd, data = df, boxplot=TRUE))
# 
# ## PICK UP HERE, FIGURE OUT HOW TO LOOP OVER STIM
# 
# x <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] / plots[[7]] /
#   plots[[8]] /plots[[9]] /plots[[10]] /plots[[11]] + 
#   plot_annotation(
#     title = title,
#     subtitle =""
#   )
# x
# ggsave(plot = x, filename =paste(stim,".png"), units = c("in"), width = 10, height = 14  )




#CREATE MATRIX 
# m <- matrix(nrow = length(stim), ncol = length(questions)) 
# rownames(m) <- stim
# colnames(m) <- questions

##END OF FILE

```



## TEMP JOB TALK STUFF

```{r}
data(iris)
library(ggpubr)
# Scatter plot colored by groups ("Species")
sp <- ggscatter(iris, x = "Sepal.Length", y = "Sepal.Width",
                color = "Species",
                size = 2, alpha = 0.6)+
  border()                                         
# Marginal density plot of x (top panel) and y (right panel)
xplot <- ggdensity(iris, "Sepal.Length", fill = "Species")
yplot <- ggdensity(iris, "Sepal.Width", fill = "Species")+
  rotate()
# Cleaning the plots
yplot <- yplot + clean_theme() 
xplot <- xplot + clean_theme()
# Arranging the plot
ggarrange(xplot, NULL, sp, yplot, 
          ncol = 2, nrow = 2,  align = "hv", 
          widths = c(2, 1), heights = c(1, 2),
          common.legend = TRUE)

```

```{r}
# library
library(ggplot2)
library(ggExtra)
library(palmerpenguins) 


p <- ggplot(penguins, aes(x = bill_length_mm, y=bill_depth_mm, colour = species)) +
  geom_point() + theme(legend.position = "bottom") 

ggMarginal(p, groupColour = TRUE, groupFill = TRUE)  


p <- ggplot(penguins, aes(x = bill_length_mm, y=bill_depth_mm, colour = species)) +
  geom_point() + theme_minimal() + theme(legend.position = "bottom") +
  scale_color_viridis(discrete=TRUE, option="viridis", direction=-1) 

ggMarginal(p, groupColour = TRUE, groupFill = TRUE)  

```
