---
title: "VIBES STUDY 2 ANALYSIS — CHI REPORTING"
author: "ANONYMIZED"
date: "2024-08-07"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
# font-family: DejaVu Sans
# mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

In VISUALIZATION VIBES project Study 2, participants completed an
*attribution eliciation* survey, asking questions about their social inferences drawn from  (5) stimulus images (data visualizations). Each participant was
randomly assigned to one of 6 stimulus blocks, each containing 1 image
from each of (4) 'embellishment categories' (ranging from most abstract
to most figural). Each participant started by responding to questions
for a single 'common' stimulus (B0-0). Two participant recruitment pools
were used: Prolific, with a smaller set of participants recruited from
Tumblr (to replicate and compare survey results to Study 1 interviews
with participants sourced from Tumblr).

This notebook contains code to replicate quantitative analysis of data
from Study 2 reported in CHI submission #5584.

# SETUP

### Import Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe()
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates
library(tinytable) ##sparkline tables 
library(webshot2) ##saving sparkline tables

#EDA
library(qacBase)

#VIZ
library(ggformula) #regression syntax viz
library(ggstatsplot) #dummies
library(gghalves) #half boxplots 
library(GGally) #extends ggplot for EDA 
library(corrplot) #sophisticated correlation plots
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(interactions) ##easier regression ixn plots.srlsy
library(tidygraph)



#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer
# library(mixed) ## utilities for glmers 
library(jmv) ## jamovi EFA


#STATISTICAL TESTS 
library(kSamples) #AD K-SAMPLE TEST (for distribution comparison)
library(rstatix) #FRIEDMAN'S TESTS and effect sizes 

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
GRAPH_SAVE = FALSE #set to true to generate all the SD graphs and save to folders (note this will overwrite existing graphs)

```

### Setup Graphing

```{r setup-pallettes}


# Custom ggplot theme to make pretty plots
# Get the font at https://fonts.google.com/specimen/Barlow+Semi+Condensed
theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA))
}

set_theme(base = theme_clean())



############## SETUP Colour Palettes
#https://www.r-bloggers.com/2022/06/custom-colour-palettes-for-ggplot2/

## list of color pallettes
my_colors = list(
  politics = c("#184aff","#5238bf", "#4f4a52" ,"#84649c", "#ff0000"),
  blackred = c("black","red"),
  greys = c("#707070","#999999","#C2C2C2"),
  greens = c("#ADC69D","#81A06D","#567E39","#2D5D16","#193E0A"),
  smallgreens = c("#ADC69D","#567E39","#193E0A"), ## MALE FEMALE OTHER
  olives = c("#CDCEA1","#B8B979","#A0A054","#78783F","#50502A","#35351C"),
  lightblues = c("#96C5D2","#61A2B2","#3C8093","#2C6378","#1F4A64"),
  darkblues = c("#7AAFE1","#3787D2","#2A73B7","#225E96","#1A4974","#133453"),
  reds = c("#D9B8BD","#CE98A2","#B17380","#954E5F","#78263E","#62151F"),
  traffic = c("#CE98A2","#81A06D","yellow"),
  questions = c("#B17380","#3787D2", "#567E39", "#EE897F"),
  tools= c("#D55662","#EE897F","#F5D0AD","#A0B79B","#499678","#2D363A"), #? ... design.....vis...... programming
  encounter = c("#8E8E8E","#729B7D"), ##SCROLL ENGAGE
  actions2 = c("#8E8E8E","#729B7D"),
  actions4 = c("#8E8E8E", "#A3A3A3","#729B7D","#499678"),
  actions3 = c("#8E8E8E","#99b898ff","#fdcea8ff"),
  actions = c("#8E8E8E","#2A363B","#99b898ff","#fdcea8ff","#ff837bff","#e84a60ff"),
  
  platforms = c("#5D93EA","#FF70CD", "#3BD3F5", "#8B69B5","black"),
  amy_gradient =  c("#ac57aa", "#9e5fa4", "#90689f", "#827099", "#747894", "#66818e", "#578988", "#499183", "#3b997d", "#2da278", "#1faa72"),
  my_favourite_colours = c("#702963", "#637029",    "#296370")
)

## function for using palettes
my_palettes = function(name, n, all_palettes = my_colors, type = c("discrete","continuous"), direction = c("1","-1")) {
  palette = all_palettes[[name]]
  if (missing(n)) {
    n = length(palette)
  }
  type = match.arg(type)
  out = switch(type,
               continuous = grDevices::colorRampPalette(palette)(n),
               discrete = palette[1:n]
  )
  out = switch(direction,
               "1" = out,
               "-1" = palette[n:1])
  structure(out, name = name, class = "palette")
}

```

```{r SD-GRAPHING-FUNCTIONS}

# ######## RETURNS SINGLE SD
# ##  APPLY STYLE
plot_sd = function (data, column, type, mean, facet, facet_by, boxplot, labels) {

  ggplot(data, aes(y = .data[[column]], x="")) +
    {if(boxplot) geom_boxplot(width = 0.5) } +
    geom_jitter(width = 0.1, alpha=0.2, {if(facet) aes(color=.data[[facet_by]])}) +
    {if(mean)
      stat_summary(fun="mean", geom="point", shape=20, size=5, color="blue", fill="blue")
      } +
    {if(mean)
      ## assumes data has been passed in with mean column at m
      # stat_summary(fun="mean", geom="text", colour="blue",  fontface = "bold",
      #            vjust=-1.25, hjust = 0.50, aes( label=round(..y.., digits=0)))
      stat_summary(fun="mean", geom="text", colour="blue",  fontface = "bold",
                 vjust=-1.25, hjust = 0.50, aes( label=round(..y.., digits=0)))
      } +

    {if(facet) facet_grid(.data[[facet_by]] ~ .)} +
    # scale_y_continuous(limits=c(-1,101)) +
    labs(x="", y="") +
    coord_flip()  +
    {if(type == "S")
      guides(
        y = guide_axis_manual(labels = labels[column,"left"]),
        y.sec = guide_axis_manual(labels = labels[column,"right"])
      )} +
    {if(type == "Q")
      guides(
        y = guide_axis_manual(labels = labels[q,"left"]),
        y.sec = guide_axis_manual(labels = labels[q,"right"])
      )} +
  theme_minimal()  +
     labs (
       caption = column
     ) + easy_remove_legend()
}

```

### Import References

```{r import-refs, message=FALSE, warning = FALSE}

############## IMPORT REFERENCE FILES
ref_stimuli <- readRDS("data/input/REFERENCE/ref_stimuli.rds")
# ref_surveys <- readRDS("data/input/REFERENCE/ref_surveys.rds")
ref_labels <- readRDS("data/input/REFERENCE/ref_labels.rds")
# ref_labels_abs <- readRDS("data/input/REFERENCE/ref_labels_abs.rds")

############## SETUP Graph Labels
ref_stim_id <- levels(ref_stimuli$ID)
ref_cat_questions <- c("MAKER_ID","MAKER_AGE","MAKER_GENDER")
ref_free_response <- c("MAKER_DETAIL", "MAKER_EXPLAIN", "TOOL_DETAIL", "CHART_EXPLAIN")
ref_conf_questions <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")
ref_sd_questions <- rownames(ref_labels)
ref_sd_questions_abs <- rownames(ref_labels_abs)
  

# ref_blocks <- c("block1", "block2", "block3", "block4", "block5", "block6")
ref_blocks <- c(1,2,3,4,5,6)

```

### Import Data

```{r import-data, message=FALSE, warning = FALSE}

############## IMPORT DATA FILES
df_participants <- readRDS("data/output/df_participants.rds") #1 row per participant — demographic
df_graphs <- readRDS("data/output/df_graphs.rds") #only categorical and numeric questions
df_sd_questions_long <- readRDS("data/output/df_sd_questions_long.rds") # only sd questions LONG

```

# AGGREGATED DATA

## (5.1.2) Survey Response Time

```{r demo-response-time}

df <- df_participants

## for descriptives paragraph
a.desc.duration <- psych::describe(df %>% pull(duration.min))

```

**As Reported in Section 5.1.2 Procedure :**

Across the entire sample, responses from (n = `r a.desc.duration$n` )
participants ranged from `r round(a.desc.duration$min,0)` to
`r round(a.desc.duration$max,0)` minutes, with a mean response time of
`r round(a.desc.duration$mean,0)` minutes, SD =
`r (round(a.desc.duration$sd,0))`.

```{r demo-cleanup}
rm(df, a.desc.duration)
```

## (5.1.4) Participants

```{r demo-sample-size}

df <- df_participants

## FOR DESCRIPTIVES PARAGRAPH
# #PROLIFIC
df.p <- df %>% filter(Distribution == "PROLIFIC")
desc.gender.p <- table(df.p$D_gender) %>% prop.table()
names(desc.gender.p) <- levels(df.p$D_gender)
p_participants <- nrow(df.p)

# #TUMBLR
df.t <- df %>% filter(Distribution == "TUMBLR")
desc.gender.t <- table(df.t$D_gender) %>% prop.table()
names(desc.gender.t) <- levels(df.t$D_gender)
t_participants <- nrow(df.t)


```

**As Reported in Section 5.1.4 Participants :**

For Study 2, a total of `r p_participants + t_participants` participants
were recruited from US-located English speaking users of TUMBLR (n =
`r t_participants`) and PROLIFIC (n = `r p_participants`).

`r t_participants` individuals from Tumblr participated in Study 2, (
`r round(desc.gender.t[["Female"]],2)*100`% Female,
`r round(desc.gender.t[["Male"]],2)*100`% Male,
`r round(desc.gender.t[["Non-binary / third gender"]],2)*100`%
Non-binary, `r round(desc.gender.t[["Prefer to self-describe"]],2)*100`%
Prefer to Self Describe,
`r round(desc.gender.t[["Prefer not to say"]],2)*100`% Prefer Not to
Say. Other).

`r p_participants` individuals from PROLIFIC participated in Study 2, (
`r round(desc.gender.p[["Female"]],2)*100`% Female,
`r round(desc.gender.p[["Male"]],2)*100`% Male,
`r round(desc.gender.p[["Non-binary / third gender"]],2)*100`%
Non-binary, `r round(desc.gender.p[["Prefer not to say"]],2)*100` %
Prefer Not to Say,
`r round(desc.gender.p[["Prefer to self-describe"]],2)*100`% Prefer to
Self Describe).

```{r demo-sample-cleanup}
rm(df, df.p, desc.gender.p, p_participants, df.t, desc.gender.t, t_participants)
```

## (5.1.4) Participants per Block

**As Reported in Section 5.1.4 Participants, there were \~ 53
participants per stimulus block**

```{r participant-block}

df <- df_participants
table(df$Assigned.Block)
# cols = c("Block", "n")
# %>% kable(col.names = cols)

```

## (FIG 5) Survey Question Distributions

**As Reported in Figure 5, descriptive statistics for in-scope survey
questions.**

```{r sparktable}

# # library(tinytable)
# # library(webshot2)

#### CUSTOM HORIZONTAL STACKED BARPLOT
g <- function(d, ...){

  p <- d$pal %>% unique
  ggplot(d, aes(x="", fill=value)) +
    geom_bar(stat="count", position = "stack") +
    scale_fill_manual(values=my_colors[[p]]) +
    coord_flip() + theme_void() + easy_remove_axes() + easy_remove_legend()
}


## SETUP LIST OF NUMERIC DATAFRAMES
all_q <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", ref_sd_questions)

# ## SETUP NUMERIC DATAFRAME
df_num <- df_graphs %>% select(all_of(all_q))

## CALC MEANS
### MEANS
m <- sapply(df_num, FUN=mean)
m <- round(m,1)
m <- paste0("M=",m)
sd <- sapply(df_num, FUN=sd)
sd <- round(sd,1)
sd <- paste0("SD=",sd)
stat <- paste0(m," ",sd)


### CREATE LIST OF CATEGORICAL DATAFRAMES
id = df_graphs %>% select(MAKER_ID) %>%
  pivot_longer(cols=1)%>% mutate(pal="reds") %>% as.data.frame()
age = df_graphs %>% select(MAKER_AGE) %>%
  pivot_longer(cols=1)%>% mutate(pal="lightblues") %>% as.data.frame()
gender = df_graphs %>% select(MAKER_GENDER) %>%
  pivot_longer(cols=1)%>% mutate(pal="smallgreens") %>% as.data.frame()

df_cat <- list()
df_cat[["MAKER_ID"]] <- id
df_cat[["MAKER_AGE"]] <- age
df_cat[["MAKER_GENDER"]] <- gender

## CALC CAT PROPORTIONS
n <- nrow(id)
m_id <- table(id) %>% as.data.frame() %>% mutate(prop = round(Freq/n, 2)*100) %>% map_df(rev) #reverse reading order
stat_id <- paste0(m_id$value, "(", m_id$prop,"%)") %>%  unlist() %>% paste0(collapse=''," ")

n <- nrow(age)
m_age <- table(age) %>% as.data.frame() %>% mutate(prop = round(Freq/n, 2)*100)%>% map_df(rev)
stat_age <- paste0(m_age$value, "(", m_age$prop,"%)") %>%  unlist() %>% paste0(collapse=''," ")

n <- nrow(gender)
m_gender <- table(gender) %>% as.data.frame() %>% mutate(prop = round(Freq/n, 2)*100)%>% map_df(rev)
stat_gender <- paste0(m_gender$value, "(", m_gender$prop,"%)")%>%  unlist() %>% paste0(collapse=''," ")

## SETUP QUESTIONS
questions <- c(ref_cat_questions, "MAKER_CONF", "AGE_CONF", "GENDER_CONF", ref_sd_questions) 


#### SETUP TABLE
tab <- data.frame(
  VARIABLE = questions,
  DISTRIBUTION = "",
  STATISTICS = c(stat_id, stat_age, stat_gender, stat)
)

### RENDER TABLE
t <- tinytable::tt(tab, theme = "void") %>%
  plot_tt(j=2, i= 1:3, fun=g, data = df_cat, height = 1.5) %>%
  plot_tt(j=2, i= 4:17, fun="density", data = df_num, color="darkgrey") %>%
  style_tt(j=2, align="c")

t
if(GRAPH_SAVE){
  save_tt(t, output="figs/SUPPLEMENTALS/fig_5_descriptives.png", overwrite = TRUE)
}
```

## (FIG 6) Exploratory Factor Analysis

**As Reported in Section 5.3, Figure 6, here we conduct an exploratory factor analysis of the semantic differential scale questions.**

We use a parallel analysis method, verified by inspection of the scree plot to determine (4) factors, and see that both the KMO measure and Bartlett's test of sphericity meet the necessary pre-requisites to support this analysis.  The resultant factor loadings are described below. 


```{r efa, message=FALSE}

jmv::efa(
    data = df_graphs,
    vars = as.vector(ref_sd_questions),
    nFactors = 4,
    extraction = "ml",
    sortLoadings = TRUE,
    screePlot = TRUE,
    eigen = FALSE,
    factorCor = TRUE,
    factorSummary = FALSE,
    modelFit = TRUE,
    kmo = TRUE,
    bartlett = TRUE)

```

# BLOCK 2 DATA

## (5.4) Design Features Index Social Attributions

**As Reported in Section 5.4, here we visualize the semantic
differential scale survey questions for each stimulus in randomization
block #2**

```{r plot_halfeye_sds_BLOCK2, warning=FALSE}


#DEFINE BLOCK 2 STIMULI
stimuli <- c("B2-1" ,"B2-2", "B2-3", "B2-4")
graphs <- list()

## LOOP THROUGH EACH STIMULUS IN LIST
i = 0

for (s in stimuli){
  i = i+1
  
  # setup titles 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME)  ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)

  # setup dataframe
  df <- df_sd_questions_long %>% select(1:8, STIMULUS, QUESTION, STIMULUS_CATEGORY, value) %>% filter(STIMULUS == s)
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
               category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
  (g <- d %>%
      ggplot(aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 90, y= ref_sd_questions,size = 8, vjust=-2) +
  labs (title = title, y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
)
  
  graphs[[i]] <- g

  if(GRAPH_SAVE == TRUE){ 
  ggsave(plot = g, path="figs/SUPPLEMENTALS/", filename =paste0("fig_7_",s,"_ggdist.png"), units = c("in"), width = 10, height = 14,bg='#ffffff'   )
  }


} ## END LOOP 

graphs
```

# PREDICTING TRUST

## (5.5) Social Inferences & Trust: Makers Matter

**As reported in Section 5.5**

What predicts CHART-TRUST? Recent work in psychology (Lin & Thorton,
2021) suggests that beauty is a strong predictor of trust. However, from
our free response data, we have reason to believe the relationship is
not this simple. For example, some participants explained that very
aesthetically pleasing images were likely meant to be persuasive and thus were
less trustworthy. Similarly, we observed that participants frequently
talked about a maker's data competency in relation to their
trustworthiness. On this basis, we expect that in predicting
`CHART_TRUST`: (1) there will be a significant interaction between
`CHART_BEAUTY` and `CHART_INTENT`, and (2) that `MAKER_DATA`
(competency) will also be a significant predictor.

We test this hypothesis by fitting a series of linear mixed effects
models, with `PID` (participant unique identifier) as a random intercept
to account for repeated measures. All continuous measures were
originally taken on a (0-100) scale. In these models, all continuous
predictors are first z-scored. We compare model fit via ChiSquared
difference tests and likelihood ratio tests (for nested models).

#### Setup Data

```{r hypo-trust_beauty_intent-data}

df <- df_graphs %>%
  ## FILTER OUT B0-0 COMMON STIMULUS (so cells can be balanced)
  # filter(STIMULUS != "B0-0") %>% 
  select(PID, STIMULUS,STIMULUS_CATEGORY, MAKER_ID, MAKER_TRUST, CHART_TRUST, CHART_BEAUTY, CHART_INTENT, MAKER_DATA) %>% 
  mutate(
    TRUST_Z = datawizard::standardise(CHART_TRUST),
    BEAUTY_Z = datawizard::standardise(CHART_BEAUTY),
    INTENT_Z = datawizard::standardise(CHART_INTENT),
    DATA_Z = datawizard::standardise(MAKER_DATA)
  ) %>% 
  droplevels()
```

#### M1 \| TRUST \~ BEAUTY

We begin by fitting a linear mixed effects, model predicting
`CHART_TRUST` by `CHART_BEAUTY` to see whether our data support the
claims made by Lin & Thorton, 2021.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

```{r, m1}

################## FIT MODEL
f.B <-  "TRUST ~ BEAUTY + (1|PID)"
mm.B <- lmer(TRUST_Z ~ BEAUTY_Z + (1|PID), data = df)
summary(mm.B)
car::Anova(mm.B, type=2)
performance(mm.B)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.B, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.B, type = "pred", terms = "BEAUTY_Z") +  theme_minimal()
(g <- (e+p) + plot_annotation(title = f.B))

```

A model predicting `CHART-TRUST` by `CHART_BEAUTY` explains 30% variance
in `CHART_TRUST`, with 22% variance explained by a significant main
effect of `CHART_BEAUTY` ($t(1586) = 21.59, p <
.001$). The model coefficient indicates that for every 1 standard
deviation increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average
by 0.47 SD.

**Model 1 supports the argument of Lin & Thorton (2021) that graphs
judged to be more attractive are also judged as more trustworthy.**

#### M2 \| TRUST \~ BEAUTY + INTENT

Here we fit add a main effect term `CHART_INTENT` as a predictor to the
previous model and compare fit with Model 1, to determine whether a
social attribution (in this case inference about the chart's intent) is
also predictive of `CHART_TRUST`.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

-   (`CHART_INTENT` 0 = to *inform* , 100 = *persuade*)

```{r m2}

################## FIT MODEL
f.BI <-  "TRUST ~ BEAUTY + INTENT + (1|PID)"
mm.BI <- lmer(TRUST_Z ~ BEAUTY_Z + INTENT_Z + (1|PID), data = df)
summary(mm.BI)
car::Anova(mm.BI, type=2)

################## COMPARE MODEL
compare_performance(mm.BI, mm.B, rank = TRUE)
anova(mm.BI, mm.B)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.BI, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.BI, type = "pred", terms = c("BEAUTY_Z", "INTENT_Z")) + theme_minimal()
(g <- (e+p) + plot_annotation(title = f.B, caption="low intent = inform, high intent = persuade"))

```

A model predicting `CHART-TRUST` by a linear combination of
`CHART_BEAUTY` and `CHART_INTENT` explains 49% variance in
`CHART_TRUST`, with 41% variance explained by fixed effects alone:

1.  A significant main effect of `CHART_BEAUTY`
    ($t(1531) = 22.04, p <.001$), and

2.  A significant main effect of `CHART_INTENT`
    ($t(1580) = -22.83, p <.001$).

    The model coefficients indicates that for every 1 standard deviation
    increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average by
    0.47 SD (more beauty corresponds to more trust). For every 1
    standard deviation increase in `CHART_INTENT`, (where LOW values
    correspond to intent to INFORM and high values correspond to intent
    to PERSUADE) `CHART-TRUST` decreases by 0.44 SD (more persuasive
    corresponds to less trust).

Further, model comparisons indicate that MODEL 2 (including
`CHART_INTENT`) is a significantly better fit to the data
($\chi^2(1)=448 , p < 0.001$) than MODEL 1 including `CHART_BEAUTY` alone. 

**Model 2 supports our claim that social attributions (in this case, an
inference about the communicative intent of the chart) *also* predict
beauty, above and beyond the beauty-centric argument of Lin & Thorton
(2021) that graphs judged to be more attractive are also judged as more
trustworthy.**

#### M3 \| TRUST \~ BEAUTY X INTENT

Here we fit a model with `CHART_INTENT` as an **interaction** with
`CHART_BEAUTY` and compare with the previous model to determine whether
the social attribution of `CHART_INTENT` **moderates** the effect of
`CHART_BEAUTY` on `CHART_TRUST`.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

-   (`CHART_INTENT` 0 = to *inform* , 100 = *persuade*)

```{r m3}

################## FIT MODEL
f.BxI <-  "TRUST ~ BEAUTY X INTENT + (1|PID)"
mm.BxI <- lmer(TRUST_Z ~ BEAUTY_Z * INTENT_Z + (1|PID), data = df)
summary(mm.BxI)
car::Anova(mm.BxI, type=2)

################## COMPARE MODEL
compare_performance(mm.BxI, mm.BI, rank = TRUE)
anova(mm.BxI, mm.BI)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.BxI, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.BxI, type = "int", terms = c("INTENT_Z","BEAUTY_Z"),mdrt.values = "all") + theme_minimal()
(g <- (e+p) + plot_annotation(title = f.BxI, caption="low intent = inform, high intent = persuade", subtitle = f.BxI))

```

A model predicting `CHART-TRUST` by a linear **interaction** of
`CHART_BEAUTY` and `CHART_INTENT` explains 51% variance in
`CHART_TRUST`, with 42% variance explained by fixed effects alone:

1.  A significant main effect of `CHART_BEAUTY`
    ($t(1526) = 22.07, p <.001$)

2.  A significant main effect of `CHART_INTENT`
    ($t(1581) = -22.4, p <.001$)

3.  A significant interaction between `CHART_BEAUTY` and `CHART_INTENT`
    ($t(1559) = 7.01, p <.001$).

    The model coefficients indicates that for every 1 standard deviation
    increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average by
    0.47 SD (more beauty corresponds to more trust). For every 1
    standard deviation increase in `CHART_INTENT`, (where LOW values
    correspond to intent to INFORM and high values correspond to intent
    to PERSUADE) `CHART-TRUST` decreases on average by 0.42 SD (more
    persuasive corresponds to less trust). The significant interaction
    term indicates the difference in slope between the two main effects,
    that is to say, that the effect of `CHART_BEAUTY` on `CHART_TRUST`
    is **moderated** such that the effect of `CHART_BEAUTY` is
    *minimized* when `CHART_INTENT` is attributed as more informative
    (lower values of chart_intent) than persuasive (higher values of
    chart_intent)

Further, model comparisons indicate that MODEL 3 (an interaction rather
than MODEL 2 with a linear combination of `CHART_BEAUTY` and `CHART_INTENT`) is a
significantly better fit to the data ($\chi^2(1)=48.5 , p < 0.001$).

**Model 3 supports our claim that social attributions (in this case, an
inference about the communicative intent of the chart) *also* predict
beauty, and infact can change (moderate) the effect of beauty on
trust.**

#### M4 \| TRUST \~ BEAUTY X INTENT + MAKER_DATA

Here we add `MAKER_DATA` competency to our previous model to determine
whether a viewer's inferences about the data analysis ability of the
chart's maker affect assesments of the chart's trustworthiness.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

-   (`CHART_INTENT` 0 = to *inform* , 100 = *persuade*)

-   (`MAKER_DATA` 0 = *professional* in data analysis , 100 =
    *layperson* in data analysis)

```{r, m4}

################## FIT MODEL
f.BxID <-  "TRUST ~ BEAUTY X INTENT + DATA (1|PID)"
mm.BxID <- lmer(TRUST_Z ~ BEAUTY_Z * INTENT_Z + DATA_Z + (1|PID), data = df)
summary(mm.BxID)
car::Anova(mm.BxID, type=2)

################## COMPARE MODEL
compare_performance(mm.BxID, mm.BxI, rank = TRUE)
anova(mm.BxID, mm.BxI)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.BxID, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.BxID, type = "pred", terms = c("INTENT_Z", "BEAUTY_Z", "DATA_Z")) + theme_minimal()
(g <- (e/p) + plot_annotation(title = f.BxID, caption="low intent = inform, high intent = persuade; low data = professional, high data = layperson", subtitle = f.BxID))

if(GRAPH_SAVE){
 ggsave(g, scale =1, filename = "figs/SUPPLEMENTALS/fig_9_mm.BxID.png", width = 14, height = 6, dpi = 320, limitsize = FALSE,bg='#ffffff')
 tab_model(mm.BxID, file = "figs/SUPPLEMENTALS/fig_9_mm.BxID_table.html")
}


```

A model predicting `CHART-TRUST` by a linear **interaction** of
`CHART_BEAUTY` and `CHART_INTENT` as well as a main effect of
`MAKER_DATA` competency explains 54% variance in `CHART_TRUST`, with 45%
variance explained by fixed effects alone:

1.  A significant main effect of `CHART_BEAUTY`
    ($t(1520) = 20.72, p <.001$),

2.  A significant main effect of `CHART_INTENT`
    ($t(1580) = -18.81, p <.001$),

3.  A significant main effect of `MAKER_DATA`
    ($t(1564) = -9.56, p <.001$),

4.  A significant interaction between `CHART_BEAUTY` and `CHART_INTENT`
    ($t(1556) = 6.63, p <.001$).

    The model coefficients indicates that for every 1 standard deviation
    increase in `MAKER_DATA`, `CHART-TRUST` decreases on average by
    0.19 SD (more layperson corresponds to less trust).For every 1 standard deviation
    increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average by
    0.38 SD (more beauty corresponds to more trust). For every 1
    standard deviation increase in `CHART_INTENT`, (where LOW values
    correspond to intent to INFORM and high values correspond to intent
    to PERSUADE) `CHART-TRUST` decreases on average by 0.37 SD (more
    persuasive corresponds to less trust). The significant interaction
    term indicates the difference in slope between the two main effects,
    that is to say, that the effect of `CHART_BEAUTY` on `CHART_TRUST`
    is **moderated** such that the effect of `CHART_BEAUTY` is
    *minimized* when `CHART_INTENT` is attributed as more informative
    (lower values of chart_intent) than persuasive (higher values of
    chart_intent)

Further, model comparisons indicate that MODEL 4 (adding a simple main effect of `MAKER_DATA`) is a
significantly better fit to the data than the prio model ($\chi^2(1)=89.1 , p < 0.001$) than MODEL 3 without the `MAKER_DATA` fixed effect. 

**Model 4 supports our claim that social attributions (in this case, _both_ an
inference about the communicative intent of the chart and inference about the data analysis skill of the maker) *also* predict
beauty, and infact can change (in the case of intent, moderate) the effect of beauty on
trust.**


#### (FIG 9) Predicting Trust

```{r best-fit-model}

################## PLOT MODEL
p + plot_annotation(title = f.BxID, caption="low intent = inform, high intent = persuade; low data = professional, high data = layperson", subtitle = f.BxID)

################## PRINT MODEL
tab_model(mm.BxID)

```

# ADDITIONAL BLOCKS

**In addition to the descriptive analysis of stimuli in Block 2 that is
reported in the manuscript, here we create visualize the semantic
differential scale for *each* stimulus in Study 2.**

## SD questions for each stimulus

```{r plot_halfeye_sdsplot_ALL, warning=FALSE}


#DEFINE STIMULI
df <- df_graphs
stimuli <- levels(df$STIMULUS)
graphs <- list()


## LOOP THROUGH EACH STIMULUS IN LIST
i = 0

for (s in stimuli){
  i = i+1
  
  # setup titles 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME)  ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)

  # setup dataframe
  df <- df_sd_questions_long %>% select(1:8, STIMULUS, QUESTION, STIMULUS_CATEGORY, value) %>% filter(STIMULUS == s)
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
               category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
  (g <- d %>%
      ggplot(aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 90, y= ref_sd_questions,size = 8, vjust=-2) +
  labs (title = title, y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
)

  graphs[[i]] <- g
  
  if(GRAPH_SAVE == TRUE){ 
  ggsave(plot = g, path="figs/SUPPLEMENTALS/other_blocks/", filename =paste0(s,"_ggdist.png"), units = c("in"), width = 10, height = 14,  bg='#ffffff'  )}
  

  
  
} ## END LOOP 

graphs
```

# SESSION

```{r session}
sessionInfo()
```
