---
title: "MVP ANALYSES"
author: "ANONYMIZED"
date: "2024-02-24"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

# TODO 

# SETUP

### Import Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe() & efa
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates
library(tinytable) ##sparkline tables 
library(webshot2) ##saving sparkline tables

#EDA
library(qacBase)

#VIZ
library(ggformula) #regression syntax viz
library(ggstatsplot) #dummies
library(gghalves) #half boxplots 
library(GGally) #extends ggplot for EDA 
library(corrplot) #sophisticated correlation plots
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(interactions) ##easier regression ixn plots.srlsy
library(tidygraph)

#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer
# library(mixed) ## utilities for glmers 
library(jmv) ## jamovi EFA


#STATISTICAL TESTS 
library(kSamples) #AD K-SAMPLE TEST (for distribution comparison)
library(rstatix) #FRIEDMAN'S TESTS and effect sizes 

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
GRAPH_SAVE = TRUE #set to true to generate all the SD graphs and save to folders 
source("graphing_functions.R") #import graphing palettes and custom functions

```

### Import References

```{r import-refs, message=FALSE, warning = FALSE}

############## IMPORT REFERENCE FILES
ref_stimuli <- readRDS("data/input/REFERENCE/ref_stimuli.rds")
ref_labels <- readRDS("data/input/REFERENCE/ref_labels.rds")


############## SETUP Graph Labels
ref_stim_id <- levels(ref_stimuli$ID)
ref_cat_questions <- c("MAKER_ID","MAKER_AGE","MAKER_GENDER")
ref_free_response <- c("MAKER_DETAIL", "MAKER_EXPLAIN", "TOOL_DETAIL", "CHART_EXPLAIN")
ref_conf_questions <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")
ref_sd_questions <- rownames(ref_labels)
ref_blocks <- c(1,2,3,4,5,6)


############## FULL QUESTION SET FOR S1_3
ref_sd_questions <- c("MAKER_DESIGN","MAKER_DATA",
                      "MAKER_POLITIC", "MAKER_ARGUE","MAKER_SELF","MAKER_ALIGN","MAKER_TRUST",
                      "CHART_TRUST", "CHART_INTENT", "CHART_LIKE", "CHART_BEAUTY")

ref_sd_questions_z <- c("MAKER_DESIGN_z","MAKER_DATA_z",
                      "MAKER_POLITIC_z", "MAKER_ARGUE_z","MAKER_SELF_z","MAKER_ALIGN_z","MAKER_TRUST_z",
                      "CHART_TRUST_z", "CHART_INTENT_z", "CHART_LIKE_z", "CHART_BEAUTY_z")


############## MINIMAL QUESTION SET FOR STUDY 4
ref_min_sd_questions <-  c("DESIGN","DATA","POLITICS", "TRUST","ALIGN","BEAUTY","INTENT")
ref_min_sd_questions_z <-  c("DESIGN_z","DATA_z","POLITICS_z", "TRUST_z","ALIGN_z","BEAUTY_z","INTENT_z")



```

### Import Data

```{r import-data, message=FALSE, warning = FALSE}

############## IMPORT Study 1_3 DATA FILES
df_participants <- readRDS("data/output/Study_1_2_3/df_participants.rds") #1 row per participant — demographic
df_graphs <- readRDS("data/output/Study_1_2_3/df_graphs.rds") #only categorical and numeric questions
df_graphs_z <- readRDS("data/output/Study_1_2_3/df_graphs_z.rds") #only categorical and numeric questions
df_sd_questions_long <- readRDS("data/output/Study_1_2_3/df_sd_questions_long.rds") # only sd questions LONG


############## IMPORT Study 4 DATA FILES



############## IMPORT COMBINED DATA FILES
df_graphs_all <- readRDS("data/output/COMBINED/df_graphs_ALL.rds") 
```



# ANALYSES (Study 1, Study 2)

## (1) EFA | Exploratory Factor Analysis (S1,S2 minimal vars)

**As Reported in Section TODO, Figure TODO, here we conduct an exploratory factor analysis of the semantic differential scale questions.**

This analysis was performed on the combined dataset from Study 1 (Tumblr) and Study 2 (Prolific). Both studies were run on all 6 stimulus blocks, meaning the data are balanced across all stimuli. 

We use a parallel analysis method, verified by inspection of the scree plot to determine (f=4) factors, and see that both the KMO measure and Bartlett's test of sphericity meet the necessary pre-requisites to support this analysis.  The resultant factor loadings are described below.

```{r efa}

## SETUP DATA
df <- df_graphs_all %>% 
  filter(Study %in% c("Study1","Study3")) 
  # %>% filter(STIMULUS !="B0-0") ## filtering out B0-0 doesn't change factors
  
x <- ref_min_sd_questions_z
print("Dataset for EFA")
addmargins(table(df$Study, df$Assigned.Block)/5)


## RUN EFA JAMOVI STYLE
jmv::efa(
    data = df,
    vars = as.vector(x),
    # nFactors = 3,
    extraction = "ml",
    sortLoadings = FALSE,
    screePlot = TRUE,
    eigen = FALSE,
    factorCor = TRUE,
    factorSummary = TRUE,
    modelFit = TRUE,
    kmo = TRUE,
    bartlett = TRUE)


## RUN EFA PSYCH PACKAGE
# df <- df_graphs_all %>% select(all_of(ref_min_sd_questions_z))
# 
# # EFA using Maximum Likelihood extraction and Oblimin rotation
# efa_result <- fa(df, 
#                  nfactors = 3, 
#                  rotate = "oblimin", 
#                  fm = "ml")
# 
# # View the entire EFA output
# print(efa_result, cut = 0.3)
# # View entire result w/o cutoff
# # efa_result
# # Optional: visualize factor diagram
# fa.diagram(efa_result)

```


## (2) MODELLING | Predicting TRUST


# SESSION

```{r session}
sessionInfo()
```
