---
title: "SUBMISSION 1006 — DATA WRANGLING"
author: "ANONYMIZED"
date: "2025-02-24"
output:
  html_document:
    theme: flatly
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 5
  pdf_document:
    toc: yes
    toc_depth: '4'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe()
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(lubridate) #dealing with dates
library(kableExtra) #printing tables

#EXPLORATORY DATA ANALYSIS
library(summarytools) #data quality
library(qacBase) #EDA

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6 #number of stimulus blocks in study design

```

*This notebook contains code to combine data from Study 1, Study 2, Study 3, and Study 4 of the MAGIC-VIS project to a single single normalized dataset of (valid) participant responses.* The file only includes questions included in all four versions of the attitude elictation survey




## IMPORT Configuration Files

*Import files with reference information for stimuli `ref_stimuli` and qualtrics surveys `ref_surveys`.*

```{r setup-references, message=FALSE, warning = FALSE}

############## IMPORT STIMULI FILE
#contains data for each stimulus used 
ref_stimuli <- read_csv("data/input/REFERENCE/stimuli.csv", col_names = TRUE) %>% 
  mutate(
    BLOCK = as.factor(BLOCK), 
    STIMULUS_CATEGORY = as.factor(CATEGORY),
    ID = as.factor(ID),
    MAKER_ID = as.factor(MAKER_ID)) %>% 
  select(-CATEGORY)



############## STUDY ID FILE
#most blocks were run as separate qualtrics surveys with diffferent recruitments in Prolific
ref_surveys <- read_csv("data/input/REFERENCE/studies.csv", col_names = TRUE) %>%
  mutate(
    ID.Study = as.factor(ID.Study),
    Assigned.Block = as.factor(Assigned.Block),
    Distribution = as.factor(Distribution),
    Prolific.Name = as.factor(Prolific.Name),
    Qualtrics.URL = as.factor(Qualtrics.URL),
    Qualtrics.Survey = as.factor(Qualtrics.Survey),
    Sample = as.factor(Sample),
    Study = as.factor(Study)
)


```

## DEFINE Labels

*Define labels used in survey questions and response options; used to generate labels for graphs and filtering of datasets in analysis files.*

```{r setup-labels}

############## BUILD LABELS
ref_stim_id <- levels(ref_stimuli$ID)

### SD questions on Studies S1, S2, S3
ref_sd_questions <- c("MAKER_DESIGN","MAKER_DATA",
                      "MAKER_POLITIC", "MAKER_ARGUE","MAKER_SELF","MAKER_ALIGN","MAKER_TRUST",
                      "CHART_TRUST", "CHART_INTENT", "CHART_LIKE", "CHART_BEAUTY")
ref_sd_questions_z <- c("MAKER_DESIGN_z","MAKER_DATA_z",
                      "MAKER_POLITIC_z", "MAKER_ARGUE_z","MAKER_SELF_z","MAKER_ALIGN_z","MAKER_TRUST_z",
                      "CHART_TRUST_z", "CHART_INTENT_z", "CHART_LIKE_z", "CHART_BEAUTY_z")


## SD questions on Study4
ref_min_sd_questions <-  c("DESIGN","DATA","POLITICS", "TRUST","ALIGN","BEAUTY","INTENT")
ref_min_sd_questions_z <-  c("DESIGN_z","DATA_z","POLITICS_z", "TRUST_z","ALIGN_z","BEAUTY_z","INTENT_z")


```

## IMPORT Wrangled Data

We want to include in this dataset only responses from participants who saw _message-obscured_ stimuli. Thus we include participants from Studies 1-3, and for Study 4, on the _pre-test_ scores, which reflect answers to questions when participants viewed the message-obscured version of the graph. 
```{r import-wrangled}

## IMPORT STUDIES 1-3 FILES
df_graphs_s13 <- readRDS("data/output/Study_1_2_3/df_graphs_z.rds")
df_sd_questions_long_s13 <- readRDS("data/output/Study_1_2_3/df_sd_questions_long.rds")
df_sd_questions_long_s13_z <- readRDS("data/output/Study_1_2_3/df_sd_questions_long_z.rds")


## IMPORT STUDY 4 FILES
df_graphs_s4 <- readRDS("data/output/Study_4/df_graphs_z_S4.rds")
df_sd_questions_long_s4 <- readRDS("data/output/Study_4/df_sd_questions_long_S4.rds")
df_sd_questions_long_s4_z <- readRDS("data/output/Study_4/df_sd_questions_long_z_S4.rds")
```


## TODO JOIN PARTICIPANT level files


## JOIN GRAPH level Files 

```{r join-graphs}

## WRANGLE STUDIES 1_3, 
df1 <- df_graphs_s13 %>% 
  # Retain only cols needed for modelling
  select(PID, Assigned.Block, Study, Sample, D_politicsSocial, D_politicsFiscal, 
         STIMULUS_CATEGORY, STIMULUS, BLOCK, ENCOUNTER, MAKER_ID, MAKER_AGE, MAKER_GENDER, 
         MAKER_DESIGN_z:CHART_TRUST_z) %>% 
  # Filter out questions dropped from Study 4
  select(-c("MAKER_ARGUE_z","MAKER_SELF_z","CHART_LIKE_z","CHART_TRUST_z"))  %>% 
  # Rename questions to match Study 4 and get rid of magicwizard transform for raw z value
  mutate(
    DESIGN_z = as.numeric(MAKER_DESIGN_z),
    DATA_z = as.numeric(MAKER_DATA_z),
    POLITICS_z = as.numeric(MAKER_POLITIC_z),
    ALIGN_z = as.numeric(MAKER_ALIGN_z),
    TRUST_z = as.numeric(MAKER_TRUST_z),
    BEAUTY_z = as.numeric(CHART_BEAUTY_z),
    INTENT_z = as.numeric(CHART_INTENT_z)) %>% 
  rename(
    ID = MAKER_ID,
    AGE = MAKER_AGE,
    GENDER = MAKER_GENDER
  ) %>% 
  # Drop old columns
  select(-c(MAKER_DESIGN_z:CHART_INTENT_z)) %>% 
  # Drop levels
  droplevels()

## STUDY 4, RETAIN ONLY COLUMNS NECESSARY FOR MODELLING, and only TIME=PRE
df4 <- df_graphs_s4%>% 
  # Retail only cols needed for modelling
  select(PID, Assigned.Block, Study, Sample, D_politicsSocial, D_politicsFiscal, 
        STIMULUS_CATEGORY, STIMULUS, BLOCK, 
        # only keep pre-test columns
        contains("PRE")) %>% 
  # drop confidence 
  select(-contains("CONF")) %>%  
  # drop latency
  select(-contains("LATENCY"))%>% 
  # drop non-zscore cols 
  select(-c(PRE_DESIGN: PRE_INTENT)) %>% 
  # rename categoricals
  rename(
    ENCOUNTER = PRE_ENCOUNTER,
    ID = PRE_ID,
    AGE = PRE_AGE,
    GENDER = PRE_GENDER
  ) %>% 
  #get rid of magicwizard transform for raw z value
  mutate(
    DESIGN_z = as.numeric(PRE_DESIGN_z),
    DATA_z = as.numeric(PRE_DATA_z),
    POLITICS_z = as.numeric(PRE_POLITICS_z),
    ALIGN_z = as.numeric(PRE_ALIGN_z),
    TRUST_z = as.numeric(PRE_TRUST_z),
    BEAUTY_z = as.numeric(PRE_BEAUTY_z),
    INTENT_z = as.numeric(PRE_INTENT_z)) %>% 
  # drop old columns
  select(-c(PRE_DESIGN_z: PRE_INTENT_z)) %>% 
  droplevels()
  
## JOIN STUDIES
df <- rbind(df1, df4)

table(df$Study, df$STIMULUS)

## WRITE FILE
saveRDS(df, file = "data/output/COMBINED/df_graphs_ALL.rds")

## CLEANUP
rm(df, df1, df4)

```



## JOIN SD QUESTION LONG Files

```{r join-sds}

## WRANGLE STUDIES 1_3, 
df1 <- df_sd_questions_long_s13 %>% 
  # Retain only cols needed for modelling
  select(PID, Assigned.Block, Study, Sample, D_politicsSocial, D_politicsFiscal, 
         STIMULUS_CATEGORY, STIMULUS, BLOCK, QUESTION, value) %>% 
  # Filter out questions dropped from Study 4
  filter(QUESTION %nin% c("MAKER_ARGUE","MAKER_SELF","CHART_LIKE","CHART_TRUST")) %>% 
  # Rename questions to match Study 4
  mutate(
    QUESTION = str_replace(QUESTION, "MAKER_",""), #strip MAKER_ prefix
    QUESTION = str_replace(QUESTION, "CHART_",""), #strip CHART_ prefix
    QUESTION = str_replace(QUESTION, "POLITIC","POLITICS"), 
    QUESTION = factor(QUESTION, levels = ref_min_sd_questions) #set factor order
  ) %>% 
  # Drop levels
  droplevels()

## STUDY 4, RETAIN ONLY COLUMNS NECESSARY FOR MODELLING, and only TIME=PRE
df4 <- df_sd_questions_long_s4 %>% 
  #Retail only cols needed for modelling
  select(PID, Assigned.Block, Study, Sample, D_politicsSocial, D_politicsFiscal, 
        STIMULUS_CATEGORY, STIMULUS, BLOCK, QUESTION, value, TIME) %>% 
  # Filter out responses from the POST test
  filter(TIME=="PRE") %>% 
  # Drop time
  select(-TIME) %>% 
  # Drop levels
  droplevels()

## JOIN STUDIES
df <- rbind(df1, df4)

table(df$Study, df$STIMULUS)


## WRITE FILE
saveRDS(df, file = "data/output/COMBINED/df_sd_questions_long_ALL.rds")

## CLEANUP
rm(df, df1, df4)

```

## JOIN SD QUESTION LONG Files (Z-SCORED)

```{r join-sds-z}

## WRANGLE STUDIES 1_3, 
df1 <- df_sd_questions_long_s13_z %>% 
  # Retain only cols needed for modelling
  select(PID, Assigned.Block, Study, Sample, D_politicsSocial, D_politicsFiscal, 
         STIMULUS_CATEGORY, STIMULUS, BLOCK, QUESTION, value) %>% 
  # Filter out questions dropped from Study 4
  filter(QUESTION %nin% c("MAKER_ARGUE_z","MAKER_SELF_z","CHART_LIKE_z","CHART_TRUST_z"))  %>% 
  # Rename questions to match Study 4
  mutate(
    QUESTION = str_replace(QUESTION, "MAKER_",""), #strip MAKER_ prefix
    QUESTION = str_replace(QUESTION, "CHART_",""), #strip CHART_ prefix
    QUESTION = str_replace(QUESTION, "POLITIC","POLITICS"), 
    QUESTION = factor(QUESTION, levels = ref_min_sd_questions_z) #set factor order
  ) %>% 
  # Drop levels
  droplevels()

## STUDY 4, RETAIN ONLY COLUMNS NECESSARY FOR MODELLING, and only TIME=PRE
df4 <- df_sd_questions_long_s4_z %>% 
  #Retail only cols needed for modelling
  select(PID, Assigned.Block, Study, Sample, D_politicsSocial, D_politicsFiscal, 
        STIMULUS_CATEGORY, STIMULUS, BLOCK, QUESTION, value, TIME) %>% 
  # Filter out responses from the POST test
  filter(TIME=="PRE") %>% 
  # Drop time
  select(-TIME) %>% 
  # Drop levels
  droplevels()

## JOIN STUDIES
df <- rbind(df1, df4)

table(df$Study, df$STIMULUS)


## WRITE FILE
saveRDS(df, file = "data/output/COMBINED/df_sd_questions_long_ALL_z.rds")

```

