---
title: "WIP ANALYSIS"
author: "ANONYMIZED"
date: "2024-02-24"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---


# SETUP

### Import Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe() & efa
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates
library(tinytable) ##sparkline tables 
library(webshot2) ##saving sparkline tables

#EDA
library(qacBase)

#VIZ
library(ggformula) #regression syntax viz
library(ggstatsplot) #dummies
library(gghalves) #half boxplots 
library(GGally) #extends ggplot for EDA 
library(corrplot) #sophisticated correlation plots
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(interactions) ##easier regression ixn plots.srlsy
library(tidygraph)



#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer
# library(mixed) ## utilities for glmers 
library(jmv) ## jamovi EFA


#STATISTICAL TESTS 
library(kSamples) #AD K-SAMPLE TEST (for distribution comparison)
library(rstatix) #FRIEDMAN'S TESTS and effect sizes 

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
GRAPH_SAVE = TRUE #set to true to generate all the SD graphs and save to folders 
source("graphing_functions.R") #import graphing palettes and custom functions

```

### Import References

```{r import-refs, message=FALSE, warning = FALSE}

############## IMPORT REFERENCE FILES
ref_stimuli <- readRDS("data/input/REFERENCE/ref_stimuli.rds")
ref_labels <- readRDS("data/input/REFERENCE/ref_labels.rds")


############## SETUP Graph Labels
ref_stim_id <- levels(ref_stimuli$ID)
ref_cat_questions <- c("MAKER_ID","MAKER_AGE","MAKER_GENDER")
ref_free_response <- c("MAKER_DETAIL", "MAKER_EXPLAIN", "TOOL_DETAIL", "CHART_EXPLAIN")
ref_conf_questions <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", "TOOL_CONF")
ref_sd_questions <- rownames(ref_labels)
ref_blocks <- c(1,2,3,4,5,6)

############## MINIMAL QUESTION SET FOR STUDY 4
ref_min_sd_questions <-  c("DESIGN","DATA","POLITICS", "TRUST","ALIGN","BEAUTY","INTENT")
ref_min_sd_questions_z <-  c("DESIGN_z","DATA_z","POLITICS_z", "TRUST_z","ALIGN_z","BEAUTY_z","INTENT_z")


```

### Import Data

```{r import-data, message=FALSE, warning = FALSE}

############## IMPORT Study 1_3 DATA FILES
df_participants <- readRDS("data/output/Study_1_2_3/df_participants.rds") #1 row per participant — demographic
df_graphs <- readRDS("data/output/Study_1_2_3/df_graphs.rds") #only categorical and numeric questions
df_sd_questions_long <- readRDS("data/output/Study_1_2_3/df_sd_questions_long.rds") # only sd questions LONG


############## IMPORT Study 4 DATA FILES



############## IMPORT COMBINED DATA FILES
df_graphs_all <- readRDS("data/output/COMBINED/df_graphs_ALL.rds") 
```

# NEW


```{r}


```

## EXPLORATORY FACTOR ANALYSIS 

### REPLICATE CHI (FIG 6) Exploratory Factor Analysis

**As Reported in Section 5.3, Figure 6, here we conduct an exploratory factor analysis of the semantic differential scale questions.**

We use a parallel analysis method, verified by inspection of the scree plot to determine (4) factors, and see that both the KMO measure and Bartlett's test of sphericity meet the necessary pre-requisites to support this analysis.  The resultant factor loadings are described below. 

(EFA on [not-zscored] SD questions from studies 1 and 3 [study 2 pilot was excluded, but included here]; changes numeric results slightly, but not the factor grouping)

```{r chi-efa, message=FALSE}

jmv::efa(
    data = df_graphs,
    vars = as.vector(ref_sd_questions),
    nFactors = 4,
    extraction = "ml",
    sortLoadings = TRUE,
    screePlot = TRUE,
    eigen = FALSE,
    factorCor = TRUE,
    factorSummary = FALSE,
    modelFit = TRUE,
    kmo = TRUE,
    bartlett = TRUE)

```







### EFA STUDY 1-4 (all blocks)

Exploratory Factor Analysis of data combined from Studies 1 through 4(pre-test only), including all (z-scored) semantic differential questions asked on all surveys. 

We use a parallel analysis method, verified by inspection of the scree plot to determine (4) factors, and see that both the KMO measure and Bartlett's test of sphericity meet the necessary pre-requisites to support this analysis.  The resultant factor loadings are described below. 

#### Jamovi EFA

```{r minimal-q-efa_S14, message=FALSE}

df <- df_graphs_all
table(df$Study)/5

jmv::efa(
    data = df_graphs_all,
    vars = as.vector(ref_min_sd_questions_z),
    nFactors = 4,
    extraction = "ml",
    sortLoadings = TRUE,
    screePlot = TRUE,
    eigen = FALSE,
    factorCor = TRUE,
    factorSummary = FALSE,
    modelFit = TRUE,
    kmo = TRUE,
    bartlett = TRUE)



```


#### Psych EFA

```{r minimal-q-efa-psychS14}



df <- df_graphs_all %>% select(all_of(ref_min_sd_questions_z))

# EFA using Maximum Likelihood extraction and Oblimin rotation
efa_result <- fa(df, nfactors = 3, rotate = "oblimin", fm = "ml")

# View communalities
efa_result$communality

# View the entire EFA output
print(efa_result, cut = 0.3)

# Optional: visualize factor diagram
fa.diagram(efa_result)


efa_result

```


### EFA STUDY 1-4 (block1)

Exploratory Factor Analysis of data combined from Studies 1 through 4(pre-test only), including all (z-scored) semantic differential questions asked on all surveys, but only data from block 1

We use a parallel analysis method, verified by inspection of the scree plot to determine (4) factors, and see that both the KMO measure and Bartlett's test of sphericity meet the necessary pre-requisites to support this analysis.  The resultant factor loadings are described below. 

#### Jamovi EFA

```{r minimal-q-efa_block1, message=FALSE}

## DEFINE DATA
df <- df_graphs_all %>% filter(Assigned.Block==1) %>% droplevels()
table(df$Assigned.Block, df$Study)/5


## RUN EFA
jmv::efa(
    data = df,
    vars = as.vector(ref_min_sd_questions_z),
    nFactors = 3,
    extraction = "ml",
    sortLoadings = TRUE,
    screePlot = TRUE,
    eigen = FALSE,
    factorCor = TRUE,
    factorSummary = FALSE,
    modelFit = TRUE,
    kmo = TRUE,
    bartlett = TRUE)



```


#### Psych EFA

```{r minimal-q-efa-psych_block1}


## DEFINE DATA
df <- df_graphs_all %>% filter(Assigned.Block==1) %>% droplevels()
table(df$Assigned.Block, df$Study)/5

df <- df %>% select(all_of(ref_min_sd_questions_z))

# EFA using Maximum Likelihood extraction and Oblimin rotation
efa_result <- fa(df, nfactors = 3, rotate = "oblimin", fm = "ml")

# View communalities
efa_result$communality

# View the entire EFA output
print(efa_result, cut = 0.3)

# Optional: visualize factor diagram
fa.diagram(efa_result)


efa_result

```




## MFA Multiple Factor Analysis (Combines PCA & MCA to essentially do an EFA using continuous and categorical data)
https://chatgpt.com/c/67d0e6ec-540c-8002-86ee-46536c59a368

#### WORKING WORKING BLOCK 1 NUMERICAL VARS
```{r}

library(FactoMineR)
library(factoextra)


################################### DEFINE DATA just block 1 NUMERIC
df_b1 <- df_graphs %>% 
  # replace - in stimlus index to _
  mutate(
    STIMULUS= str_replace(STIMULUS,"-","_"),
    STIMULUS = factor(STIMULUS)
  ) %>% 
  # keep only common stimulus
  filter(Assigned.Block==1) %>% 
  # drop cols we're not going to use
  select(-contains("LATENCY")) %>% 
  select(-contains("CONF"))  %>% 
  select(-c(duration.min:D_politicsFiscal)) %>% 
  select(-c(BLOCK, STIMULUS_CATEGORY)) %>% 
  select(-c(ENCOUNTER:MAKER_GENDER))
  

## PIVOT to wide dataframe (1 row per participant)
df_wide_b1 <- df_b1 %>% 
  pivot_wider(
    names_from = STIMULUS , 
    values_from = c(MAKER_DESIGN:CHART_TRUST)
  )  %>% 
  select(-PID)





################################## CALC. GROUP STRUCTURE

## get image ids
# Extract unique image identifiers from the original dataset
image_ids <- unique(df_b1$STIMULUS) %>% droplevels()
# Print to verify
print(image_ids)

# Assign columns to images
group_list <- lapply(image_ids, function(img) {
  which(grepl(paste0("_", img, "$"), colnames(df_wide_b1)))  # Match all variables for this image
})
# Name groups using image identifiers
names(group_list) <- image_ids

#compute group sizes
group_sizes <- sapply(group_list, length)

# Print for verification
print(group_sizes)  # Should sum to ncol(df_wide_b1)

# Verify group assignments
print_group_columns <- function(group_indices, group_name) {
  if (length(group_indices) == 0) {
    cat("\n", group_name, "has no assigned columns!\n")
  } else {
    cat("\n", group_name, "Column Names:\n")
    print(colnames(df_wide_b1)[group_indices])
  }
}

# Print columns for each group
lapply(seq_along(group_list), function(i) {
  print_group_columns(group_list[[i]], names(group_list)[i])
})



################## RUN THE MFA
mfa_block <- MFA(
  df_wide_b1, 
  group = group_sizes, 
  type = rep("c", length(group_sizes)),  
  graph = TRUE
)






```








#### NOT WORKING WORKING BLOCK 1 ALL VARS
```{r}

library(FactoMineR)
library(factoextra)


################################### DEFINE DATA just block 1
df_b1 <- df_graphs %>% 
  # replace - in stimlus index to _
  mutate(
    STIMULUS= str_replace(STIMULUS,"-","_"),
    STIMULUS = factor(STIMULUS)
  ) %>% 
  # keep only common stimulus
  filter(Assigned.Block==1) %>% 
  # drop cols we're not going to use
  select(-contains("LATENCY")) %>% 
  select(-contains("CONF"))  %>% 
  select(-c(duration.min:D_politicsFiscal)) %>% 
  select(-c(BLOCK, STIMULUS_CATEGORY))
  

## PIVOT to wide dataframe (1 row per participant)
df_wide_b1 <- df_b1 %>% 
  pivot_wider(
    names_from = STIMULUS , 
    values_from = c(ENCOUNTER:CHART_TRUST)
  )  %>% 
  select(-PID)


################################## CALC. GROUP STRUCTURE

## get image ids
# Extract unique image identifiers from the original dataset
image_ids <- unique(df_b1$STIMULUS) %>% droplevels()
# Print to verify
print(image_ids)

# Assign columns to images
group_list <- lapply(image_ids, function(img) {
  which(grepl(paste0("_", img, "$"), colnames(df_wide_b1)))  # Match all variables for this image
})
# Name groups using image identifiers
names(group_list) <- image_ids

#compute group sizes
group_sizes <- sapply(group_list, length)

# Print for verification
print(group_sizes)  # Should sum to ncol(df_wide_b1)

# Verify group assignments
print_group_columns <- function(group_indices, group_name) {
  if (length(group_indices) == 0) {
    cat("\n", group_name, "has no assigned columns!\n")
  } else {
    cat("\n", group_name, "Column Names:\n")
    print(colnames(df_wide_b1)[group_indices])
  }
}

# Print columns for each group
lapply(seq_along(group_list), function(i) {
  print_group_columns(group_list[[i]], names(group_list)[i])
})





mfa_block <- MFA(
  df_wide_b1, 
  group = group_sizes, 
  type = rep("FAMD", length(group_sizes)),  
  graph = FALSE
)




### TROUBLESHOOT 123
print("Checking group_sizes:")
print(group_sizes)  # Should be a numeric vector
print(paste("Sum of group_sizes:", sum(group_sizes)))
print(paste("Number of columns in df_wide_b1:", ncol(df_wide_b1)))
print(sum(group_sizes) == ncol(df_wide_b1))  # Should return TRUE

### TROUBLESHOOT 124
assigned_columns <- unlist(group_list)  # All column indices assigned to groups
all_columns <- 1:ncol(df_wide_b1)  # All columns in the dataset

# Find unassigned columns
unassigned_columns <- setdiff(all_columns, assigned_columns)
print("Unassigned Columns:")
print(colnames(df_wide_b1)[unassigned_columns])  # Should return an empty list

### TROUBLESHOOT 125
print(is.numeric(group_sizes))  # Should return TRUE


### TROUBLESHOOT 126
mfa_test <- tryCatch({
  print("Running MFA with:")
  print(paste("Number of columns in df_wide_b1:", ncol(df_wide_b1)))
  print(paste("Group sizes:", toString(group_sizes)))
  print(paste("Sum of group sizes:", sum(group_sizes)))

  MFA(
    df_wide_b1, 
    group = group_sizes, 
    type = rep("FAMD", length(group_sizes)), 
    graph = FALSE
  )
}, error = function(e) {
  print("MFA Failed! Here is the error message:")
  print(e)
  return(NULL)
})


## 126
str(df_wide_b1)  # Check all variable types
#127
df_wide_b1 <- as.data.frame(df_wide_b1)


mfa_block <- MFA(
  df_wide_b1, 
  group = group_sizes, 
  type = rep("FAMD", length(group_sizes)),  
  graph = FALSE
)

#make sure names are null
names(group_sizes) <- NULL
types <- rep("FAMD", length(group_sizes))
type2 <- rep("m",length(group_sizes))
# ## DEBUG MODE
debugonce(MFA)  # Opens MFA for interactive debugging

mfa_test <- MFA(
  base = df_wide_b1, 
  group = group_sizes,  
  type = type2,
  graph = FALSE
)





```





##### ONLY BLOCK 1

```{r block_1_mfa}

library(FactoMineR)
library(factoextra)


################################### DEFINE DATA just block 1
df_b1 <- df_graphs %>% 
  # replace - in stimlus index to _
  mutate(
    STIMULUS= str_replace(STIMULUS,"-","_"),
    STIMULUS = factor(STIMULUS)
  ) %>% 
  # keep only common stimulus
  filter(Assigned.Block==1) %>% 
  # drop cols we're not going to use
  select(-contains("LATENCY")) %>% 
  select(-contains("CONF"))  %>% 
  select(-c(duration.min:D_politicsFiscal)) %>% 
  select(-c(BLOCK, STIMULUS_CATEGORY))
  

## PIVOT to wide dataframe (1 row per participant)
df_wide_b1 <- df_b1 %>% 
  pivot_wider(
    names_from = STIMULUS , 
    values_from = c(ENCOUNTER:CHART_TRUST)
  )  %>% 
  select(-PID)


################################# DEFINE GROUPS BY IMAGE
group_list <- list(
  grep("_B0_0$", colnames(df_wide_b1)),  # All responses for B0_0
  grep("_B1_1$", colnames(df_wide_b1)),  # All responses for B1_1
  grep("_B1_2$", colnames(df_wide_b1)),  # All responses for B1_2
  grep("_B1_3$", colnames(df_wide_b1)),  # All responses for B1_3
  grep("_B1_4$", colnames(df_wide_b1))   # All responses for B1_4
)

# Compute group sizes
group_sizes <- sapply(group_list, length)
print(sum(group_sizes)) ==ncol(df_wide_b1)  # Should sum to ncol(data_mfa_block)


## VERIFY
# Function to print column names instead of indices
print_group_columns <- function(group_indices, group_name) {
  if (length(group_indices) == 0) {
    cat("\n", group_name, "has no assigned columns!\n")
  } else {
    cat("\n", group_name, "Column Names:\n")
    print(colnames(df_wide_b1)[group_indices])
  }
}

# Print column names for each image block
print_group_columns(group_list[[1]], "Image B0_0")
print_group_columns(group_list[[2]], "Image B1_1")
print_group_columns(group_list[[3]], "Image B1_2")
print_group_columns(group_list[[4]], "Image B1_3")
print_group_columns(group_list[[5]], "Image B1_4")



################################ RUN THE MFA
mfa_block <- MFA(
  df_wide_b1, 
  group = group_sizes, 
  type = rep("FAMD", length(group_sizes)), 
  graph = FALSE
)

mfa_test <- MFA(
  df_wide_b1[, 1:10],  # Minimal dataset
  group = c(5, 5),  # Two groups
  type = rep("FAMD", 2), 
  graph = FALSE
)

### TROUBLESHOOT FACTOMINE
print("Structure of df_wide_b1:")
str(df_wide_b1)  # Print detailed structure

print("First few rows of df_wide_b1:")
print(head(df_wide_b1, 5))  # Print first few rows

print("Group sizes being passed to MFA:")
print(group_sizes)

print("Sum of group_sizes:")
print(sum(group_sizes))

print("Number of columns in df_wide_b1:")
print(ncol(df_wide_b1))

print("Matching sum(group_sizes) and ncol(df_wide_b1):")
print(sum(group_sizes) == ncol(df_wide_b1))

## FORCE DEBUGGING
mfa_test <- tryCatch({
  print("Running MFA with:")
  print(paste("Number of columns in df_wide_b1:", ncol(df_wide_b1)))
  print(paste("Group sizes:", toString(group_sizes)))
  print(paste("Sum of group sizes:", sum(group_sizes)))
  
  MFA(
    df_wide_b1, 
    group = group_sizes, 
    type = rep("FAMD", length(group_sizes)), 
    graph = FALSE
  )
}, error = function(e) {
  print("MFA Failed! Here is the error message:")
  print(e)
  return(NULL)
})


## VARS w/ zero variance?
zero_variance_vars <- sapply(df_wide_b1, function(col) length(unique(na.omit(col))) == 1)
print(names(zero_variance_vars[zero_variance_vars == TRUE]))  # Should return an empty list


### try numeric datat only
numeric_data <- df_wide_b1 %>% select(where(is.numeric))

mfa_numeric <- MFA(
  numeric_data, 
  group = rep(ncol(numeric_data), 1),  # One group containing all numeric variables
  type = "c",  # "c" means continuous numeric data
  graph = FALSE
)

##verify numeric_data
print(ncol(numeric_data))  # Should be > 0
print(colnames(numeric_data))  # Should list the numeric variables


mfa_numeric <- MFA(
  numeric_data, 
  group = ncol(numeric_data),  # Single group containing all numeric variables
  type = "c",  # "c" means continuous numeric data
  graph = FALSE
)
pca_numeric <- PCA(numeric_data, graph = FALSE)
mfa_tiny <- MFA(
  numeric_data[, 1:5],  # Only first 5 variables
  group = c(5),  # One group with 5 variables
  type = "c", 
  graph = FALSE
)

print(dim(numeric_data[, 1:5]))  # Should return something like [95, 5]
print(str(numeric_data[, 1:5]))  # Should confirm it contains <dbl> values
numeric_subset <- as.data.frame(numeric_data[, 1:5])  # Ensure it is a dataframe
mfa_test <- MFA(
  as.data.frame(numeric_data[, 1:5]),  # Force it to be a dataframe
  group = c(5),  # One group of 5 variables
  type = "c",  
  graph = FALSE
)



```
```{r synthetic-data}
library(FactoMineR)

# Create a small, artificial dataset with numeric variables
set.seed(123)
synthetic_data <- data.frame(
  Var1 = rnorm(100),
  Var2 = rnorm(100),
  Var3 = rnorm(100),
  Var4 = rnorm(100),
  Var5 = rnorm(100)
)

# Define a simple group structure
synthetic_groups <- c(2, 3)  # Two groups: first 2 vars, last 3 vars

# Run MFA on synthetic data
mfa_synthetic <- MFA(
  synthetic_data, 
  group = synthetic_groups, 
  type = rep("c", length(synthetic_groups)), 
  graph = TRUE
)




###### TROUBLESHOOT MY DATA
print("Structure of synthetic_data:")
str(synthetic_data)

print("Structure of numeric_data:")
str(numeric_data)
numeric_data <- as.data.frame(numeric_data)


## try again
# mfa_numeric <- MFA(
#   numeric_data, 
#   group = ncol(numeric_data),  # Single group containing all numeric variables
#   type = "c",  # "c" means continuous numeric data
#   graph = FALSE
# )
# 
# ## check for extremems
# summary(numeric_data)
# 
# 
# ## DEBUG MODE
# debugonce(MFA)  # This will open an interactive debugger when MFA runs
# 
# mfa_numeric <- MFA(
#   numeric_data,
#   group = ncol(numeric_data),
#   type = "c",
#   graph = FALSE
# )


##TRACE MODE
# trace(MFA, edit = TRUE)  # This will allow us to modify MFA before running it
# 
# mfa_numeric <- MFA(
#   numeric_data, 
#   group = ncol(numeric_data),  
#   type = "c",  
#   graph = FALSE
# )


####### FIX GROUPS
image_names <- unique(df_b1$STIMULUS) %>% droplevels()  # Get unique image names
print(image_names)  # Verify it contains B0_0, B1_1, B1_2, B1_3, B1_4

group_list <- lapply(image_names, function(img) {
  which(grepl(paste0("_", img, "$"), colnames(numeric_data)))  # Find all columns related to each image
})

# Convert to a named list for clarity
names(group_list) <- image_names


group_sizes <- sapply(group_list, length)
print(group_sizes)  # Should sum to ncol(numeric_data)

print_group_columns <- function(group_indices, group_name) {
  if (length(group_indices) == 0) {
    cat("\n", group_name, "has no assigned columns!\n")
  } else {
    cat("\n", group_name, "Column Names:\n")
    print(colnames(numeric_data)[group_indices])
  }
}

lapply(seq_along(group_list), function(i) {
  print_group_columns(group_list[[i]], names(group_list)[i])
})

mfa_block <- MFA(
  numeric_data, 
  group = group_sizes, 
  type = rep("c", length(group_sizes)),  
  graph = TRUE
)


```



##### ONLY B0-0



```{r}

library(FactoMineR)
library(factoextra)


################################### DEFINE DATA just b0_0
df_0 <- df_graphs %>% 
  # replace - in stimlus index to _
  mutate(
    STIMULUS= str_replace(STIMULUS,"-","_"),
    STIMULUS = factor(STIMULUS)
  ) %>% 
  # keep only common stimulus
  filter(STIMULUS=="B0_0") %>% 
  # drop cols we're not going to use
  select(-contains("LATENCY")) %>% 
  select(-contains("CONF"))  

## PIVOT to wide dataframe (1 row per participant)
data_wide_0 <- df_0 %>% 
  pivot_wider(
    names_from = STIMULUS , 
    values_from = c(ENCOUNTER:CHART_TRUST)
  ) %>% 
  select(-c(PID:STIMULUS_CATEGORY))
  # #move supp vars to end
  # relocate(
  #   PID:STIMULUS_CATEGORY, .after = CHART_TRUST_B0_0 
  # )

group_sizes <- 1  # All variables belong to one group


##########################

################################### DEFINE ALL
df <- df_graphs %>% 
  # replace - in stimlus index to _
  mutate(
    STIMULUS= str_replace(STIMULUS,"-","_"),
    STIMULUS = factor(STIMULUS)
  ) %>% 
  # drop cols we're not going to use
  select(-contains("LATENCY")) %>% 
  select(-contains("CONF"))  

## PIVOT to wide dataframe (1 row per participant)
data_wide <- df %>% 
  pivot_wider(
    names_from = STIMULUS , 
    values_from = c(ENCOUNTER:CHART_TRUST)
  ) %>% 
  select(-c(PID:STIMULUS_CATEGORY))
  # #move supp vars to end
  # relocate(
  #   PID:STIMULUS_CATEGORY, .after = CHART_TRUST_B0_0 
  # )



##########################

## RUN THE MFA WITH NO GROUPING STRUCTURE B/C JUST 1 IMAGE AND NO
## PLAUSIBLY MEAININGFUL GROUPS
mfa_common <- MFA(
  data_wide_0, 
  group = group_sizes,  # Treating all variables as a single group
  type = "FAMD",  # Allows both numeric & categorical variables
  graph = FALSE
)

print("Group sizes being passed to MFA:")
print(group_sizes)


```

```{r troubleshoot-factominer}

# Select only numeric variables (PCA does not support factors)
numeric_mfa <- data_wide %>% select(where(is.numeric))
pca_test <- PCA(numeric_mfa, graph = TRUE)
## RUNS CORRECTLY


famd_test <- FAMD(data_wide_0, graph = TRUE)
famd_test <- FAMD(data_wide, graph = TRUE)
## RUNS ON THE B0_O ONLY, BUT NOT DATA_WIDE


## 54 check infinite values
print(any(sapply(data_wide, function(col) any(is.infinite(col), na.rm = TRUE))))  # Should return FALSE
## 55 check missing data
na_counts <- colSums(is.na(data_wide))
na_percentage <- na_counts / nrow(data_wide) * 100
print(na_percentage[na_percentage > 50])  # Show columns where >50% of data is missing

##lots of missing data so



# ## do imputations
# 
# install.packages("missMDA")  # Install if not already installed
# library(missMDA)
# 
# # Perform PCA-based imputation for missing data
# imputed_data <- imputePCA(data_wide, method = "Regularized", ncp = 2)$completeObs


```

##### ATTEMPS WITH TOO MUCH MISSING DATA
```{r mfa}


library(FactoMineR)
library(factoextra)


################################### DEFINE DATA 
df <- df_graphs %>% 
  # replace - in stimlus index to _
  mutate(
    STIMULUS= str_replace(STIMULUS,"-","_"),
    STIMULUS = factor(STIMULUS)
  )

## PIVOT to wide dataframe (1 row per participant)
data_wide <- df %>% 
  # drop cols we're not going to use
  select(-contains("LATENCY")) %>% 
  select(-contains("CONF"))  %>% 
  pivot_wider(
    names_from = STIMULUS , 
    values_from = c(ENCOUNTER:CHART_TRUST)
  ) %>% 
  #move supp vars to end
  relocate(
    PID:STIMULUS_CATEGORY, .after = `CHART_TRUST_B6_4` 
  )



################################# DEFINE GROUPS
#### structure by embellishment categories, 
####b/c structure by block was too sparse and wouldn't run

### Step 1: Extract Unique Image-Category Mapping from df

# Extract unique STIMULUS (image number) to STIMULUS_CATEGORY (embellishment category) mapping
# Extract the last character (which indicates the category)
stimulus_mapping <- df %>%
  select(STIMULUS, STIMULUS_CATEGORY) %>%
  distinct() %>%
  mutate(
    Stimulus_Number = as.numeric(str_extract(STIMULUS, "\\d+$"))  # Extract last digit
  )

# Print to verify
print(stimulus_mapping)

### Step 2: Identify Images in Each Category

# Extract image numbers for each embellishment category
common_image <- stimulus_mapping$STIMULUS[stimulus_mapping$STIMULUS_CATEGORY == "F"]
category_A_images <- stimulus_mapping$STIMULUS[stimulus_mapping$STIMULUS_CATEGORY == "A"]
category_B_images <- stimulus_mapping$STIMULUS[stimulus_mapping$STIMULUS_CATEGORY == "B"]
category_C_images <- stimulus_mapping$STIMULUS[stimulus_mapping$STIMULUS_CATEGORY == "C"]
category_D_images <- stimulus_mapping$STIMULUS[stimulus_mapping$STIMULUS_CATEGORY == "D"]

# Print to check if the correct images are assigned
print(common_image)
print(category_A_images)
print(category_B_images)
print(category_C_images)
print(category_D_images)



### Step 3: Extract Column Names in data_wide
# Convert STIMULUS into valid image indices
stimulus_to_index <- setNames(1:25, stimulus_mapping$STIMULUS)

# Map category images to their respective indices
common_image_indices <- stimulus_to_index[common_image]
category_A_indices <- stimulus_to_index[category_A_images]
category_B_indices <- stimulus_to_index[category_B_images]
category_C_indices <- stimulus_to_index[category_C_images]
category_D_indices <- stimulus_to_index[category_D_images]

# Function to print column names
print_category_columns <- function(image_indices, category_name) {
  if (length(image_indices) == 0) {
    cat("\n", category_name, "has no assigned images!\n")
  } else {
    cat("\n", category_name, "Column Names:\n")
    valid_indices <- unlist(lapply(image_indices, function(img) seq(img, 15 * 25, by = 25)))  
    print(colnames(data_wide)[valid_indices])
  }
}

# Print column names for each category
print_category_columns(common_image_indices, "Common Image")
print_category_columns(category_A_indices, "Category A")
print_category_columns(category_B_indices, "Category B")
print_category_columns(category_C_indices, "Category C")
print_category_columns(category_D_indices, "Category D")
#######


################### DEFINE SUPPLEMENTARY VARIABLES

## 1. Remove vars not going to be used
data_mfa <- data_wide %>% 
  select(-c(PID,duration.min,Assigned.Block,D_gender,D_education, D_employmentStatus,D_income,BLOCK)) 
  


supplementary_vars <- c("Sample","Study","Distribution","PLATFORM","D_gender_collapsed","D_education_collapsed","D_age","D_politicalParty","D_politicsSocial","D_politicsFiscal","STIMULUS_CATEGORY")

# Get indices of supplementary columns
sup_vars_indices <- which(colnames(data_mfa) %in% supplementary_vars)

####### TEMP JUST DROP THE SUPP VARS
data_mfa <- data_wide %>% 
  select(-c(PID:STIMULUS_CATEGORY))


###################### RUN MFA
mfa_result <- MFA(
  data_mfa, 
  group = list(common_image_indices, category_A_indices, category_B_indices, category_C_indices, category_D_indices), 
  type = rep("FAMD", 5),  # Since all groups contain mixed data
  graph = FALSE
)

# Scree plot to check variance explained
fviz_screeplot(mfa_result, addlabels = TRUE)

# Factor contributions
fviz_contrib(mfa_result, "var", axes = 1)
fviz_contrib(mfa_result, "var", axes = 2)

# Factor map to visualize how embellishment categories relate to latent dimensions
fviz_mfa_var(mfa_result, "group", repel = TRUE)

# Individual factor map (participants)
fviz_mfa_ind(mfa_result, repel = TRUE)






```

```{r}

## MFA TROUBLESHOOTING


## 1 check group list, should be list of 5, each with numeric indices
group_list <- list(common_image_indices, category_A_indices, category_B_indices, category_C_indices, category_D_indices)
print(group_list)

##save
g <- group_list

## 2 Are indices numeric?
print(sapply(group_list, is.numeric))  # Should return TRUE for all


## 3 Ensure no NA values
print(any(is.na(unlist(group_list))))  # Should return FALSE

## 4 Ensure indices exist in data_Wide
max_col <- ncol(data_mfa)  # Total number of columns
valid_indices <- all(unlist(group_list) > 0 & unlist(group_list) <= max_col)
print(valid_indices)  # Should return TRUE

## 5 Run with verified groups
# mfa_result <- MFA(
#   data_mfa,
#   group = group_list,
#   type = rep("FAMD", length(group_list)),
#   graph = FALSE
# )
#Error in 1:group[1] : NA/NaN argument

## 6 debug how mfa sees group
str(group_list)
#### RETURNED
# List of 5
#  $ : Named int 1
#   ..- attr(*, "names")= chr "B0_0"
#  $ : Named int [1:6] 2 6 10 14 18 22
#   ..- attr(*, "names")= chr [1:6] "B1_1" "B2_1" "B3_1" "B4_1" ...
#  $ : Named int [1:6] 3 7 11 15 19 23
#   ..- attr(*, "names")= chr [1:6] "B1_2" "B2_2" "B3_2" "B4_2" ...
#  $ : Named int [1:6] 4 8 12 16 20 24
#   ..- attr(*, "names")= chr [1:6] "B1_3" "B2_3" "B3_3" "B4_3" ...
#  $ : Named int [1:6] 5 9 13 17 21 25
#   ..- attr(*, "names")= chr [1:6] "B1_4" "B2_4" "B3_4" "B4_4" ...
##FIX
group_list <- lapply(group_list, unlist)  # Flatten nested lists
str(group_list)

### !!!!!! THIS fixed the. group list issue
group_list <- lapply(group_list, function(g) as.numeric(unname(g)))
str(group_list)

## TRY TO RUN
# mfa_result <- MFA(
#   data_mfa,
#   group = group_list,
#   type = rep("FAMD", length(group_list)),
#   graph = FALSE
# )


## check group list again
print(group_list)  # Check its structure
print(length(group_list))  # Should return 5 (since there are 5 groups)
print(sapply(group_list, length))  # Should return the number of columns in each group

## check group_list nas
any(is.na(unlist(group_list)))  # Should return FALSE

## check group_list contains column counts not indices
group_sizes <- sapply(group_list, length)  # Convert from indices to counts
print(group_sizes)  # Verify that this prints numbers summing to ncol(data_mfa)

## NOW TRY MFA with group sizes instead of group list
# mfa_result <- MFA(
#   data_mfa, 
#   group = group_sizes,  # Group sizes instead of raw indices
#   type = rep("FAMD", length(group_sizes)), 
#   graph = FALSE
# )

# Error in names(list.type.var[[1]]) <- colnames(base)[1:group[1]] : 
#   attempt to set an attribute on NULL


##1 Verify no empty groups
print(group_sizes)  # Should print 5 numbers > 0
print(any(group_sizes == 0))  # Should return FALSE

## check group_sizes matches ncol(data_mfa)
print(sum(group_sizes))  # Should equal ncol(data_mfa)
print(ncol(data_mfa))  # Should match sum(group_sizes)
## ^^ THIS WAS A PROBLEM


## 1. Fix group_sizes to capture columns
group_sizes <- sapply(group_list, function(g) length(g) * 15)  # Multiply by 15 questions per image
print(sum(group_sizes))  # Should return 375
print(ncol(data_mfa))  # Should also return 375

### now run
# mfa_result <- MFA(
#   data_mfa, 
#   group = group_sizes,  # Now correctly reflecting column counts
#   type = rep("FAMD", length(group_sizes)), 
#   graph = FALSE
# )


# 1 confirm no missing cols
print(ncol(data_mfa))  # Should be 375
print(colnames(data_mfa))  # Check if column names look correct


#### VERIFY QUESTIONS
unique_questions <- unique(gsub("_B\\d+_\\d+", "", colnames(data_mfa)))
print(unique_questions)


#### 2 ADJUST GROUP LIST BASED ON QUESTIONS
# Get question prefixes
question_prefixes <- unique(gsub("_B\\d+_\\d+", "", colnames(data_mfa)))

# Create new group list based on actual column names
group_list <- lapply(question_prefixes, function(prefix) {
  grep(paste0("^", prefix), colnames(data_mfa))  # Find all columns matching each question prefix
})

# Verify the structure of the new groups
print(group_list)

###### 3 ENSURE group sizes match new groups
group_sizes <- sapply(group_list, length)  # Get column counts per question type
print(sum(group_sizes))  # Should return 375
print(ncol(data_mfa))  # Should also return 375



##### 4 RUN MFA AGAIN
# mfa_result <- MFA(
#   data_mfa, 
#   group = group_sizes,  # Corrected groups based on actual question types
#   type = rep("FAMD", length(group_sizes)), 
#   graph = FALSE
# )

## try only one grup
# mfa_test <- MFA(
#   data_mfa, 
#   group = c(group_sizes[1]),  # Only the first group
#   type = "FAMD", 
#   graph = FALSE
# )

### CHECK PROBLEMS WITH data_mfa


### 1. data type
str(data_mfa)  # Print data types of each column
glimpse(data_mfa)

###2. nulls
any(sapply(data_mfa, is.null))  # Should return FALSE

###3. no NA onlys
print(any(rowSums(is.na(data_mfa)) == ncol(data_mfa)))  # Should return FALSE
print(any(colSums(is.na(data_mfa)) == nrow(data_mfa)))  # Should return FALSE

## 4. group sizes match
group_sizes <- sapply(group_list, function(g) sum(colnames(data_mfa) %in% colnames(data_mfa)[g]))
print(sum(group_sizes))  # Should match ncol(data_mfa)
print(ncol(data_mfa))

## try again
# mfa_result <- MFA(
#   data_mfa, 
#   group = group_sizes, 
#   type = rep("FAMD", length(group_sizes)), 
#   graph = FALSE
# )

print("Group sizes:")
print(group_sizes)

print("First few rows of data_mfa:")
print(head(data_mfa[, 1:10]))  # Print first 10 columns

print(any(is.na(group_sizes)))  # Should return FALSE
print(any(group_sizes == 0))  # Should return FALSE

print(sum(group_sizes))
print(ncol(data_mfa))


```

```{r troubleshoot-factors}
#summary(data_mfa)  # Check how factors are structured
##^^ COME BACK TO THAT

all_factors <- all(sapply(data_mfa, is.factor))
print(all_factors)  # Should return FALSE (meaning there are some numeric variables)


#### try numeric mfa
numeric_mfa <- data_mfa %>% select(where(is.numeric))

# mfa_test <- MFA(
#   numeric_mfa, 
#   group = group_sizes, 
#   type = rep("FAMD", length(group_sizes)), 
#   graph = FALSE
# )


## any factors with only one level?
single_level_factors <- sapply(data_mfa, function(col) if(is.factor(col)) length(unique(col)) else NA)
print(single_level_factors[single_level_factors == 1])  # Should return an empty list



## 20
na_factors <- sapply(data_mfa, function(col) if(is.factor(col)) all(is.na(col)) else FALSE)
print(names(na_factors[na_factors == TRUE]))  # This should return the names of any fully NA factors

##21
single_level_factors <- sapply(data_mfa, function(col) if(is.factor(col)) length(unique(na.omit(col))) else NA)
print(single_level_factors[single_level_factors == 1])  # Should return an empty list

#21
single_level_factors <- sapply(data_mfa, function(col) {
  if (is.factor(col)) length(unique(na.omit(col))) else NA
})

print(single_level_factors)  # Now it should return actual numbers



na_counts <- colSums(is.na(data_mfa))
total_rows <- nrow(data_mfa)

na_percentage <- na_counts / total_rows * 100
print(na_percentage[na_percentage > 50])  # Show columns where >50% of values are NA


```

```{r not_working_mfa_too_sparse}
################### PREPARE GROUPS

# Define parameters
num_questions <- 15  # Number of survey questions
num_images <- 25     # Total images

# Generate column indices for each image
image_groups <- lapply(1:num_images, function(img) {
  seq(img, num_questions * num_images, by = num_images)
})

# Define MFA groups: 1 group for the common image, 6 groups for the image blocks
common_image_group <- image_groups[[1]]  # Img1 (common image)
block_1_group <- unlist(image_groups[2:5])   # Images 2-5
block_2_group <- unlist(image_groups[6:9])   # Images 6-9
block_3_group <- unlist(image_groups[10:13]) # Images 10-13
block_4_group <- unlist(image_groups[14:17]) # Images 14-17
block_5_group <- unlist(image_groups[18:21]) # Images 18-21
block_6_group <- unlist(image_groups[22:25]) # Images 22-25

# Create the final MFA group list
groups <- list(common_image_group, block_1_group, block_2_group, 
               block_3_group, block_4_group, block_5_group, block_6_group)


# Sanity check grouping
# Loop through each group and print the corresponding column names
for (i in seq_along(groups)) {
  cat("\nGroup", i, "Column Names:\n")
  print(colnames(d)[groups[[i]]])  # Extract column names using indices
}



################### DEFINE SUPPLEMENTARY VARIABLES

## 1. Remove vars not going to be used
data_mfa <- data_wide %>% 
  select(-c(PID,duration.min,Assigned.Block,D_gender,D_education, D_employmentStatus,D_income,BLOCK)) %>% 
  droplevels()


supplementary_vars <- c("Sample","Study","Distribution","PLATFORM","D_gender_collapsed","D_education_collapsed","D_age","D_politicalParty","D_politicsSocial","D_politicsFiscal","STIMULUS_CATEGORY")

# Get indices of supplementary columns
sup_vars_indices <- which(colnames(data_mfa) %in% supplementary_vars)


################### RUN MFA
mfa_result <- MFA(
  data_mfa, 
  group = groups, 
  type = rep("FAMD", length(groups)), 
  ind.sup = sup_vars_indices,  # Specify supplementary individual variables
  graph = FALSE
)


###### TROUBLESHOOTING
# ERROR: Error in 1:group[1] : NA/NaN argument
## 1790 rows, 386 columns
colSums(is.na(data_mfa))  # Count NAs per column #shouldn't have any cols with all NA
rowSums(is.na(data_mfa))  # Count NAs per participant # shouldn't have any rows with all NA

## run on subset
mfa_test <- MFA(
  data_mfa[1:50, ], 
  group = groups, 
  type = rep("FAMD", length(groups)), 
  graph = FALSE
)

##check how nas are stored
sum(data_mfa == "NA", na.rm = TRUE)  # Count "NA" stored as text
sum(is.na(data_mfa))  # Count actual NA values




# Remove participants who have more than 50% missing values
data_mfa_subset <- data_mfa[rowMeans(is.na(data_mfa)) < 0.5, ]

# Check how many rows remain
print(dim(data_mfa_subset))


```

# AGGREGATED DATA

## (5.1.2) Survey Response Time

```{r demo-response-time}

df <- df_participants

# #TUMBLR
df.t <- df %>% filter(Distribution == "TUMBLR")
t.desc.duration <- psych::describe(df.t %>% pull(duration.min))

# #PROLIFIC
df.p <- df %>% filter(Distribution == "PROLIFIC")
p.desc.duration <- psych::describe(df.p %>% pull(duration.min))

## COMBINED for descriptives paragraph
a.desc.duration <- psych::describe(df %>% pull(duration.min))


```

**As Reported in Section 5.1.2 Procedure :**

STUDY 1, TUMBLR Across the TUMBLR sample (S1), responses from (n = `r t.desc.duration$n` )
participants ranged from `r round(t.desc.duration$min,0)` to
`r round(t.desc.duration$max,0)` minutes, with a mean response time of
`r round(t.desc.duration$mean,0)` minutes, SD =
`r (round(t.desc.duration$sd,0))`.


STUDY 2, PROLIFIC Across the PROLIFIC sample (S2), responses from (n = `r p.desc.duration$n` )
participants ranged from `r round(p.desc.duration$min,0)` to
`r round(p.desc.duration$max,0)` minutes, with a mean response time of
`r round(p.desc.duration$mean,0)` minutes, SD =
`r (round(p.desc.duration$sd,0))`.


Across the combined sample, responses from (n = `r a.desc.duration$n` )
participants ranged from `r round(a.desc.duration$min,0)` to
`r round(a.desc.duration$max,0)` minutes, with a mean response time of
`r round(a.desc.duration$mean,0)` minutes, SD =
`r (round(a.desc.duration$sd,0))`.

```{r demo-cleanup}
rm(df, a.desc.duration, t.desc.duration, p.desc.duration )
```

## (5.1.4) Participants

```{r demo-sample-size}

df <- df_participants

## FOR DESCRIPTIVES PARAGRAPH

# #TUMBLR
df.t <- df %>% filter(Distribution == "TUMBLR")
desc.gender.t <- table(df.t$D_gender) %>% prop.table()
names(desc.gender.t) <- levels(df.t$D_gender)
t_participants <- nrow(df.t)


# #PROLIFIC
df.p <- df %>% filter(Distribution == "PROLIFIC")
desc.gender.p <- table(df.p$D_gender) %>% prop.table()
names(desc.gender.p) <- levels(df.p$D_gender)
p_participants <- nrow(df.p)



```

**As Reported in Section 5.1.4 Participants :**

Combined, a total of `r p_participants + t_participants` participants
were recruited from US-located English speaking users of TUMBLR (n =
`r t_participants`) and PROLIFIC (n = `r p_participants`).

`r p_participants` individuals from PROLIFIC participated in Study 2, (
`r round(desc.gender.p["Female"],2)*100`% Female,# 
`r round(desc.gender.p["Male"],2)*100`% Male,
`r round(desc.gender.p["Non-binary / third gender"],2)*100`%
Non-binary, `r round(desc.gender.p["Prefer not to say"],2)*100` %
Prefer Not to Say,
`r round(desc.gender.p["Prefer to self-describe"],2)*100`% Prefer to
Self Describe).


`r t_participants` individuals from Tumblr participated in Study 2, (
`r round(desc.gender.t["Female"],2)*100`% Female,
`r round(desc.gender.t["Male"],2)*100`% Male,
`r round(desc.gender.t["Non-binary / third gender"],2)*100`%
Non-binary, `r round(desc.gender.t["Prefer to self-describe"],2)*100`%
Prefer to Self Describe,
`r round(desc.gender.t["Prefer not to say"],2)*100`% Prefer Not to
Say. Other).


```{r demo-sample-cleanup}
rm(df, df.p, desc.gender.p, p_participants, df.t, desc.gender.t, t_participants)
```

## (5.1.4) Participants per Block

**As Reported in Section 5.1.4 Participants, there were \~ 53
participants per stimulus block**

```{r participant-block}

df <- df_participants
addmargins(table(df$Assigned.Block, df$Distribution))

```

## (FIG 5) Survey Question Distributions

**As Reported in Figure 5, descriptive statistics for in-scope survey
questions.**

```{r sparktable}

# # library(tinytable)
# # library(webshot2)

#### CUSTOM HORIZONTAL STACKED BARPLOT
g <- function(d, ...){

  p <- d$pal %>% unique
  ggplot(d, aes(x="", fill=value)) +
    geom_bar(stat="count", position = "stack") +
    scale_fill_manual(values=my_colors[[p]]) +
    coord_flip() + theme_void() + easy_remove_axes() + easy_remove_legend()
}


## SETUP LIST OF NUMERIC DATAFRAMES
all_q <- c("MAKER_CONF", "AGE_CONF", "GENDER_CONF", ref_sd_questions)

# ## SETUP NUMERIC DATAFRAME
df_num <- df_graphs %>% select(all_of(all_q))

## CALC MEANS
### MEANS
m <- sapply(df_num, FUN=mean)
m <- round(m,1)
m <- paste0("M=",m)
sd <- sapply(df_num, FUN=sd)
sd <- round(sd,1)
sd <- paste0("SD=",sd)
stat <- paste0(m," ",sd)


### CREATE LIST OF CATEGORICAL DATAFRAMES
id = df_graphs %>% select(MAKER_ID) %>%
  pivot_longer(cols=1)%>% mutate(pal="reds") %>% as.data.frame()
age = df_graphs %>% select(MAKER_AGE) %>%
  pivot_longer(cols=1)%>% mutate(pal="lightblues") %>% as.data.frame()
gender = df_graphs %>% select(MAKER_GENDER) %>%
  pivot_longer(cols=1)%>% mutate(pal="smallgreens") %>% as.data.frame()

df_cat <- list()
df_cat[["MAKER_ID"]] <- id
df_cat[["MAKER_AGE"]] <- age
df_cat[["MAKER_GENDER"]] <- gender

## CALC CAT PROPORTIONS
n <- nrow(id)
m_id <- table(id) %>% as.data.frame() %>% mutate(prop = round(Freq/n, 2)*100) %>% map_df(rev) #reverse reading order
stat_id <- paste0(m_id$value, "(", m_id$prop,"%)") %>%  unlist() %>% paste0(collapse=''," ")

n <- nrow(age)
m_age <- table(age) %>% as.data.frame() %>% mutate(prop = round(Freq/n, 2)*100)%>% map_df(rev)
stat_age <- paste0(m_age$value, "(", m_age$prop,"%)") %>%  unlist() %>% paste0(collapse=''," ")

n <- nrow(gender)
m_gender <- table(gender) %>% as.data.frame() %>% mutate(prop = round(Freq/n, 2)*100)%>% map_df(rev)
stat_gender <- paste0(m_gender$value, "(", m_gender$prop,"%)")%>%  unlist() %>% paste0(collapse=''," ")

## SETUP QUESTIONS
questions <- c(ref_cat_questions, "MAKER_CONF", "AGE_CONF", "GENDER_CONF", ref_sd_questions) 


#### SETUP TABLE
tab <- data.frame(
  VARIABLE = questions,
  DISTRIBUTION = "",
  STATISTICS = c(stat_id, stat_age, stat_gender, stat)
)

### RENDER TABLE
t <- tinytable::tt(tab, theme = "void") %>%
  plot_tt(j=2, i= 1:3, fun=g, data = df_cat, height = 1.5) %>%
  plot_tt(j=2, i= 4:17, fun="density", data = df_num, color="darkgrey") %>%
  style_tt(j=2, align="c")

t
if(GRAPH_SAVE){
  save_tt(t, output="figs/fig_5_descriptives.png", overwrite = TRUE)
}
```

# BLOCK 2 DATA

## (5.4) Design Features Index Social Attributions

**As Reported in Section 5.4, here we visualize the semantic
differential scale survey questions for each stimulus in randomization
block #2**


### BLOCK 2 GRAPHS
```{r plot_halfeye_sds_BLOCK2, warning=FALSE}


#DEFINE BLOCK 2 STIMULI
stimuli <- c("B2-1" ,"B2-2", "B2-3", "B2-4")
graphs <- list()

## LOOP THROUGH EACH STIMULUS IN LIST
i = 0

for (s in stimuli){
  i = i+1
  
  # setup titles 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME)  ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)

  # setup dataframe
  df <- df_sd_questions_long %>% select(1:8, STIMULUS, QUESTION, STIMULUS_CATEGORY, value) %>% filter(STIMULUS == s)
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
               category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
  (g <- d %>%
      ggplot(aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 90, y= ref_sd_questions,size = 8, vjust=-2) +
  labs (title = title, y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
)
  
  graphs[[i]] <- g

  if(GRAPH_SAVE == TRUE){ 
  ggsave(plot = g, path="figs/", filename =paste0("fig_7_BLOCK_2",s,"_ggdist.png"), units = c("in"), width = 10, height = 14,bg='#ffffff'   )
  }


} ## END LOOP 

graphs
```


### BLOCK 1 GRAPHS
```{r plot_halfeye_sds_BLOCK1, warning=FALSE}


#DEFINE BLOCK 1 STIMULI
stimuli <- c("B1-1" ,"B1-2", "B1-3", "B1-4")
graphs <- list()

## LOOP THROUGH EACH STIMULUS IN LIST
i = 0

for (s in stimuli){
  i = i+1
  
  # setup titles 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME)  ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)

  # setup dataframe
  df <- df_sd_questions_long %>% select(1:8, STIMULUS, QUESTION, STIMULUS_CATEGORY, value) %>% filter(STIMULUS == s)
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
               category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
  (g <- d %>%
      ggplot(aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 90, y= ref_sd_questions,size = 8, vjust=-2) +
  labs (title = title, y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
)
  
  graphs[[i]] <- g

  if(GRAPH_SAVE == TRUE){ 
  ggsave(plot = g, path="figs/", filename =paste0("BLOCK_1_",s,"_ggdist.png"), units = c("in"), width = 10, height = 14,bg='#ffffff'   )
  }


} ## END LOOP 

graphs
```

# PREDICTING TRUST

## (5.5) Social Inferences & Trust: Makers Matter

**As reported in Section 5.5**

What predicts CHART-TRUST? Recent work in psychology (Lin & Thorton,
2021) suggests that beauty is a strong predictor of trust. However, from
our free response data, we have reason to believe the relationship is
not this simple. For example, some participants explained that very
aesthetically pleasing images were likely meant to be persuasive and thus were
less trustworthy. Similarly, we observed that participants frequently
talked about a maker's data competency in relation to their
trustworthiness. On this basis, we expect that in predicting
`CHART_TRUST`: (1) there will be a significant interaction between
`CHART_BEAUTY` and `CHART_INTENT`, and (2) that `MAKER_DATA`
(competency) will also be a significant predictor.

We test this hypothesis by fitting a series of linear mixed effects
models, with `PID` (participant unique identifier) as a random intercept
to account for repeated measures. All continuous measures were
originally taken on a (0-100) scale. In these models, all continuous
predictors are first z-scored. We compare model fit via ChiSquared
difference tests and likelihood ratio tests (for nested models).

#### Setup Data

```{r hypo-trust_beauty_intent-data}

df <- df_graphs %>%
  ## FILTER OUT B0-0 COMMON STIMULUS (so cells can be balanced)
  # filter(STIMULUS != "B0-0") %>% 
  select(PID, STIMULUS,STIMULUS_CATEGORY, MAKER_ID, MAKER_TRUST, CHART_TRUST, CHART_BEAUTY, CHART_INTENT, MAKER_DATA) %>% 
  mutate(
    TRUST_Z = datawizard::standardise(CHART_TRUST),
    BEAUTY_Z = datawizard::standardise(CHART_BEAUTY),
    INTENT_Z = datawizard::standardise(CHART_INTENT),
    DATA_Z = datawizard::standardise(MAKER_DATA)
  ) %>% 
  droplevels()
```

#### M1 \| TRUST \~ BEAUTY

We begin by fitting a linear mixed effects, model predicting
`CHART_TRUST` by `CHART_BEAUTY` to see whether our data support the
claims made by Lin & Thorton, 2021.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

```{r, m1}

################## FIT MODEL
f.B <-  "TRUST ~ BEAUTY + (1|PID)"
mm.B <- lmer(TRUST_Z ~ BEAUTY_Z + (1|PID), data = df)
summary(mm.B)
car::Anova(mm.B, type=2)
performance(mm.B)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.B, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.B, type = "pred", terms = "BEAUTY_Z") +  theme_minimal()
(g <- (e+p) + plot_annotation(title = f.B))

```

A model predicting `CHART-TRUST` by `CHART_BEAUTY` explains 30% variance
in `CHART_TRUST`, with 22% variance explained by a significant main
effect of `CHART_BEAUTY` ($t(1554) = 21.59, p <
.001$). The model coefficient indicates that for every 1 standard
deviation increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average
by 0.47 SD.

**Model 1 supports the argument of Lin & Thorton (2021) that graphs
judged to be more attractive are also judged as more trustworthy.**

#### M2 \| TRUST \~ BEAUTY + INTENT

Here we add a main effect term `CHART_INTENT` as a predictor to the
previous model and compare fit with Model 1, to determine whether a
social attribution (in this case inference about the chart's intent) is
also predictive of `CHART_TRUST`.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

-   (`CHART_INTENT` 0 = to *inform* , 100 = *persuade*)

```{r m2}

################## FIT MODEL
f.BI <-  "TRUST ~ BEAUTY + INTENT + (1|PID)"
mm.BI <- lmer(TRUST_Z ~ BEAUTY_Z + INTENT_Z + (1|PID), data = df)
summary(mm.BI)
car::Anova(mm.BI, type=2)

################## COMPARE MODEL
compare_performance(mm.BI, mm.B, rank = TRUE)
anova(mm.BI, mm.B)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.BI, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.BI, type = "pred", terms = c("BEAUTY_Z", "INTENT_Z")) + theme_minimal()
(g <- (e+p) + plot_annotation(title = f.B, caption="low intent = inform, high intent = persuade"))

```

A model predicting `CHART-TRUST` by a linear combination of
`CHART_BEAUTY` and `CHART_INTENT` explains 49% variance in
`CHART_TRUST`, with 41% variance explained by fixed effects alone:

1.  A significant main effect of `CHART_BEAUTY`
    ($t(1532) = 22.04, p <.001$), and

2.  A significant main effect of `CHART_INTENT`
    ($t(1581) = -22.83, p <.001$).

    The model coefficients indicates that for every 1 standard deviation
    increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average by
    0.42 SD (more beauty corresponds to more trust). For every 1
    standard deviation increase in `CHART_INTENT`, (where LOW values
    correspond to intent to INFORM and high values correspond to intent
    to PERSUADE) `CHART-TRUST` decreases by 0.44 SD (more persuasive
    corresponds to less trust).

Further, model comparisons indicate that MODEL 2 (including
`CHART_INTENT`) is a significantly better fit to the data
($\chi^2(1) = 448 , p < 0.001$) than MODEL 1 including `CHART_BEAUTY` alone. 

**Model 2 supports our claim that social attributions (in this case, an
inference about the communicative intent of the chart) *also* predict
beauty, above and beyond the beauty-centric argument of Lin & Thorton
(2021) that graphs judged to be more attractive are also judged as more
trustworthy.**

#### M3 \| TRUST \~ BEAUTY X INTENT

Here we fit a model with `CHART_INTENT` as an **interaction** with
`CHART_BEAUTY`, and compare with the previous model (with the simple linear combination of the two predictors) 
to determine whether simply affecting `CHART_TRUST`, the social attribution of `CHART_INTENT` **moderates** the effect of
`CHART_BEAUTY` on `CHART_TRUST`.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

-   (`CHART_INTENT` 0 = to *inform* , 100 = *persuade*)

```{r m3}

################## FIT MODEL
f.BxI <-  "TRUST ~ BEAUTY X INTENT + (1|PID)"
mm.BxI <- lmer(TRUST_Z ~ BEAUTY_Z * INTENT_Z + (1|PID), data = df)
summary(mm.BxI)
car::Anova(mm.BxI, type=3)  #type 3 tests for interaction model

################## COMPARE MODEL
compare_performance(mm.BxI, mm.BI, rank = TRUE)
anova(mm.BxI, mm.BI)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.BxI, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.BxI, type = "int", terms = c("INTENT_Z","BEAUTY_Z"),mdrt.values = "all") + theme_minimal()
(g <- (e+p) + plot_annotation(title = f.BxI, caption="low intent = inform, high intent = persuade", subtitle = f.BxI))

```

A model predicting `CHART-TRUST` by a linear **interaction** of
`CHART_BEAUTY` and `CHART_INTENT` explains 51% variance in
`CHART_TRUST`, with 42% variance explained by fixed effects alone:

1.  A significant main effect of `CHART_BEAUTY`
    ($\chi^2(1) = 487, p <.001$)

2.  A significant main effect of `CHART_INTENT`
    ($\chi^2(1) = 486, p <.001$)

3.  A significant interaction between `CHART_BEAUTY` and `CHART_INTENT`
    ($\chi^2(1) = 49, p <.001$)

    The model coefficients indicates that for every 1 standard deviation
    increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average by
    0.41 SD (more beauty corresponds to more trust). For every 1
    standard deviation increase in `CHART_INTENT`, (where LOW values
    correspond to intent to INFORM and high values correspond to intent
    to PERSUADE) `CHART-TRUST` decreases on average by 0.42 SD (more
    persuasive corresponds to less trust). The significant interaction
    term indicates the difference in slope between the two main effects,
    that is to say, that the effect of `CHART_BEAUTY` on `CHART_TRUST`
    is **moderated** such that the effect of `CHART_BEAUTY` is
    *minimized* when `CHART_INTENT` is attributed as more informative
    (lower values of chart_intent) than persuasive (higher values of
    chart_intent)

Further, model comparisons indicate that MODEL 3 (an interaction rather
than MODEL 2 with a linear combination of `CHART_BEAUTY` and `CHART_INTENT`) is a
significantly better fit to the data ($\chi^2(1)=48.5 , p < 0.001$).

**Model 3 supports our claim that social attributions (in this case, an
inference about the communicative intent of the chart) *also* predict
beauty, and in fact can change (moderate) the effect of beauty on
trust.**

#### M4 \| TRUST \~ BEAUTY X INTENT + MAKER_DATA

Here we add `MAKER_DATA` competency to our previous model to determine
whether a viewer's inferences about the data analysis ability of the
chart's maker affect assesments of the chart's trustworthiness.

-   (`CHART_TRUST` 0 = not at all untrustworthy, 100 = very trustworthy)

-   (`CHART_BEAUTY` 0 = not at all aesthetically pleasing , 100 = very
    aesthetically pleasing)

-   (`CHART_INTENT` 0 = to *inform* , 100 = *persuade*)

-   (`MAKER_DATA` 0 = *professional* in data analysis , 100 =
    *layperson* in data analysis)

```{r, m4}

################## FIT MODEL
f.BxID <-  "TRUST ~ BEAUTY X INTENT + DATA (1|PID)"
mm.BxID <- lmer(TRUST_Z ~ BEAUTY_Z * INTENT_Z + DATA_Z + (1|PID), data = df)
summary(mm.BxID)
car::Anova(mm.BxID, type=3) #type 3 tests for interaction model

################## COMPARE MODEL
compare_performance(mm.BxID, mm.BxI, rank = TRUE)
anova(mm.BxID, mm.BxI)

################## PLOT MODEL
## PLOT MODEL COEFFICIENTS
e <- plot_model(mm.BxID, type = "est", show.intercept = TRUE) + labs(title = "Model Coefficients") + theme_minimal()
## PLOT MODEL PREDICTIONS
p <- plot_model(mm.BxID, type = "pred", terms = c("INTENT_Z", "BEAUTY_Z", "DATA_Z")) + theme_minimal()
(g <- (e/p) + plot_annotation(title = f.BxID, caption="low intent = inform, high intent = persuade; low data = professional, high data = layperson", subtitle = f.BxID))

if(GRAPH_SAVE){
 ggsave(g, scale =1, filename = "figs/fig_9_mm.BxID.png", width = 14, height = 6, dpi = 320, limitsize = FALSE,bg='#ffffff')
 tab_model(mm.BxID, file = "figs/fig_9_mm.BxID_table.html")
}


```

A model predicting `CHART-TRUST` by a linear **interaction** of
`CHART_BEAUTY` and `CHART_INTENT` as well as a main effect of
`MAKER_DATA` competency explains 54% variance in `CHART_TRUST`, with 45%
variance explained by fixed effects alone:

1.  A significant main effect of `CHART_BEAUTY`
    ($\chi^2(1) = 429, p <.001$)

2.  A significant main effect of `CHART_INTENT`
    ($\chi^2(1) = 354, p <.001$)

3.  A significant main effect of `MAKER_DATA`
    ($\chi^2(1) = 91, p <.001$)

4.  A significant interaction between `CHART_BEAUTY` and `CHART_INTENT`
    ($\chi^2(1) = 44, p <.001$)

    The model coefficients indicates that for every 1 standard deviation
    increase in `MAKER_DATA`, `CHART-TRUST` decreases on average by
    0.19 SD (less expertise/more layperson corresponds to lower trust). For every 1 standard deviation
    increase in `CHART-BEAUTY`, `CHART-TRUST` increases on average by
    0.38 SD (more beauty corresponds to more trust). For every 1
    standard deviation increase in `CHART_INTENT`, (where LOW values
    correspond to intent to INFORM and high values correspond to intent
    to PERSUADE) `CHART-TRUST` decreases on average by 0.37 SD (
    persuasive corresponds to less trust; informative corresponds to more trust). The significant interaction
    term indicates the difference in slope between the main effects for `CHART_BEAUTY` and `CHART_INTENT`,
    that is to say, that the effect of `CHART_BEAUTY` on `CHART_TRUST`
    is **moderated** such that the effect of `CHART_BEAUTY` is
    *minimized* when `CHART_INTENT` is attributed as more informative
    (lower values on chart_intent) than persuasive (higher values on
    chart_intent)

Further, model comparisons indicate that MODEL 4 (adding a simple main effect of `MAKER_DATA`) is a
significantly better fit to the data than MODEL 3 without the `MAKER_DATA` fixed effect ($\chi^2(1)=89.1 , p < 0.001$) . 

**Model 4 supports our claim that social attributions (in this case, _both_ an
inference about the communicative intent of the chart and inference about the data analysis skill of the maker) *also* predict
beauty, and in fact can change (in the case of intent, moderate) the effect of beauty on
trust.**


#### (FIG 9) Predicting Trust

**Here we produce the visualization and model parameters table reported in Figure 9.**

```{r best-fit-model}

################## PLOT MODEL
p + plot_annotation(title = f.BxID, caption="low intent = inform, high intent = persuade; low data = professional, high data = layperson", subtitle = f.BxID)

################## PRINT MODEL
tab_model(mm.BxID)

```

# ADDITIONAL BLOCKS

**In addition to the descriptive analysis of stimuli in Block 2 that is
reported in the manuscript, here we create visualize the semantic
differential scale for *each* stimulus in Study 2.**

## SD questions for each stimulus

```{r plot_halfeye_sdsplot_ALL, warning=FALSE}


#DEFINE STIMULI
df <- df_graphs
stimuli <- levels(df$STIMULUS)
graphs <- list()


## LOOP THROUGH EACH STIMULUS IN LIST
i = 0

for (s in stimuli){
  i = i+1
  
  # setup titles 
  title <- ref_stimuli %>% filter(ID == s) %>% select(NAME)  ##TODO IF NOT WORK ref_stim_id
  title <- paste(s,"|",title)

  # setup dataframe
  df <- df_sd_questions_long %>% select(1:8, STIMULUS, QUESTION, STIMULUS_CATEGORY, value) %>% filter(STIMULUS == s)
  d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
               category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(QUESTION) %>% 
    mutate(m=median(value)) ## calc median for printing on graph

  # GGDIST HALFEYE (raincloud doesn't work b/c long tails)
  (g <- d %>%
      ggplot(aes(y = fct_rev(QUESTION), x = value, fill=category)) +
    stat_halfeye(scale=0.8, density="bounded", point_interval = "median_qi", normalize="xy") +
    
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left), title = ""),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
  cowplot::draw_text(text = ref_sd_questions, x = 90, y= ref_sd_questions,size = 8, vjust=-2) +
  labs (title = title, y = "", caption = "(point is median)") +
  theme_minimal() + easy_remove_legend()
)

  graphs[[i]] <- g
  
  if(GRAPH_SAVE == TRUE){ 
  ggsave(plot = g, path="figs/other_blocks/", filename =paste0(s,"_ggdist.png"), units = c("in"), width = 10, height = 14,  bg='#ffffff'  )}
  

  
  
} ## END LOOP 

graphs
```

# SESSION

```{r session}
sessionInfo()
```
