---
title: "SUBMISSION 1006 — Study 3 Analysis"
author: "ANONYMIZED"
date: "2024-02-24"
output:
  html_document:
    theme: flatly
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#UTILITIES
library(Hmisc) # %nin% operator
library(psych) #describe()
library(tidyverse) #all the things
library(magrittr) #special pipes like %<>%
library(summarytools) #data quality
library(lubridate) #dealing with dates
library(tinytable) ##sparkline tables 
library(webshot2) ##saving sparkline tables

#EDA
library(qacBase)

#VIZ
library(kableExtra) #printing tables
library(ggformula) #regression syntax viz
# library(vcd) #mosaic plots
# library(vcdExtra) #mosaic plot helpers
library(ggstatsplot) #dummies
library(gghalves) #half boxplots 
library(GGally) #extends ggplot for EDA 
library(corrplot) #sophisticated correlation plots
library(ggeasy) #easy labelling
library(ggh4x) #guides [dual axes]
library(patchwork) #multi-plot layout
library(ggdist) #raincloud plots and other distributionals
library(ggridges) #ridge plots
library(viridis) #color palettes
library(RColorBrewer) #color palettes
library(plotly) # interactive graphs
library(paletteer) #more palettes
library(lessR) ##very pretty donuts 
library(ggsankey) ## ggplot2 sankey extension
library(interactions) ##easier regression ixn plots.srlsy
library(ggraph) ## node link diagrams
library(tidygraph)



#MODELLING
library(jtools) #Social Science regression utilities
library(easystats) #modelling helpers
library(see)
library(sjPlot)
library(lme4)
library(lmerTest) #for CIs in glmer
# library(mixed) ## utilities for glmers 
library(equatiomatic) ## extracting model formula
library(latex2exp) ## extracting and printing model formula

#STATISTICAL TESTS 
library(kSamples) #AD K-SAMPLE TEST (for distribution comparison)
library(rstatix) #FRIEDMAN'S TESTS and effect sizes 

#CONFIG
options(readr.show_col_types = FALSE) #don't show coltypes on read_csv
n_blocks = 6

## IMPORTANT 
GRAPH_SAVE = TRUE #set to true to generate all the SD graphs and save to folders 
source("graphing_functions.R") #import graphing palettes and custom functions
#factor order vectors moved to graphing file


```


**This notebook includes analysis and comparison of data collected in Study 4 (pre-post test design).**

# SETUP

*We start by importing data files previously wrangled in
`0_SUB1006_wrangling_S3.Rmd`.*

### Import References

```{r import-refs, message=FALSE, warning = FALSE}

############## IMPORT REFERENCE FILES
ref_stimuli <- readRDS("data/input/REFERENCE/ref_stimuli.rds")
ref_surveys <- readRDS("data/input/REFERENCE/ref_surveys.rds")
ref_labels <- readRDS("data/input/REFERENCE/ref_labels_S3.rds")
ref_labels_abs <- readRDS("data/input/REFERENCE/ref_labels_abs_S3.rds")

############## SETUP Graph Labels
ref_stim_id <- levels(ref_stimuli$ID)
ref_cat_questions <- c("ENCOUNTER","ID","AGE","GENDER")
ref_free_response <- c("EXPLAIN")
ref_conf_questions <- c("ID_CONF","AGE_CONF","GENDER_CONF")
ref_sd_questions <- rownames(ref_labels)
ref_sd_questions_abs <- rownames(ref_labels_abs)
  

# ref_blocks <- c("block1", "block2", "block3", "block4", "block5", "block6")
ref_blocks <- c(1,2,3,4,5,6)

```


### Import Data

```{r import-data}

############## IMPORT DATA FILES

# 1 row per participant — wide 
# df_data <- readRDS("data/output/df_data.rds")

# 1 row per participant — demographic
df_participants <- readRDS("data/output/Study_3/df_participants_S3.rds")

# 1 row per participant-graph 
df_graphs <- readRDS("data/output/Study_3/df_graphs_S3.rds")
# for modelling
df_graphs_z <- readRDS("data/output/Study_3/df_graphs_z_S3.rds")

# sd questions LONG (with pre/post in sep cols)
df_questions_long <- readRDS("data/output/Study_3/df_questions_long_S3.rds")
df_sd_questions_long <- readRDS("data/output/Study_3/df_sd_questions_long_S3.rds") #pre/post in sep rows as TIME
df_sd_questions_long_abs <-  readRDS("data/output/Study_3/df_sd_questions_long_abs_S3.rds")

df_questions <- readRDS("data/output/Study_3/df_questions_S3.rds") #pre/post in sep cols
df_sd_questions_abs <- readRDS("data/output/Study_3/df_sd_questions_abs_S3.rds") #pre/post in sep cols


```



# SAMPLE

```{r describe-sample}

print("df_participants")
table(df_participants$Assigned.Block, df_participants$Study)

```

# EXPLORATION


## RAW CONFIDENCE
```{r block1_confidence, message=FALSE, warning = FALSE}


### FILTER FOR ONLY SD QUESTIONS
df <- df_questions_long %>% 
  filter(QUESTION %in% ref_conf_questions) %>% 
  mutate(value = as.numeric(value)) %>% 
  droplevels()
# %>% filter(QUESTION %in% ref_sd_questions)



####### PRE/POST BY QUESTION AND STIMULUS  
(x <-
  df %>%   ggplot(aes(x = value, y = QUESTION, fill = TIME, color= TIME)) +
    geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE)+ 
  
    
    scale_fill_manual(values = my_palettes(name="blackgreen", direction = "1"))+
    scale_color_manual(values = my_palettes(name="blackgreen", direction = "1"))+
    facet_grid(.~STIMULUS)
)    

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_CONF_by_Stimulus_ridges.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}



#######PRE/POST BY QUESTION
(x <-
  df %>%   ggplot(aes(x = value, y = QUESTION, fill = TIME, color= TIME)) +
    geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE)+ 
    scale_fill_manual(values = my_palettes(name="blackgreen", direction = "1"))+
    scale_color_manual(values = my_palettes(name="blackgreen", direction = "1"))
)    

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_CONF_by_Question_ridges.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}




#######PRE/POST BY 
(x <-
  df %>%   ggplot(aes(x = value, y = TIME, fill = TIME, color= TIME)) +
    geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE)+ 
    scale_fill_manual(values = my_palettes(name="blackgreen", direction = "1"))+
    scale_color_manual(values = my_palettes(name="blackgreen", direction = "1"))
)    

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_CONF_by_Time_ridges.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}

```








## RAW PRE-POST SD Questions
```{r block1_sds_by_sample, message=FALSE, warning = FALSE}


### FILTER FOR ONLY SD QUESTIONS
df <- df_sd_questions_long 
# %>% filter(QUESTION %in% ref_sd_questions)


############## BLOCK 1 SDs by STIMULUS 
 df <- df %>% select(1:7, STIMULUS, QUESTION, TIME, value)  
 d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions),
          value = as.numeric(value)) %>%
    group_by(STIMULUS, QUESTION,TIME) %>% 
    mutate(m=median(value)) %>% droplevels() ## calc median for printing on graph
  
(x <-
    ggplot(d, aes(x = value, y = fct_rev(QUESTION), fill = TIME, color= TIME)) +
    # geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE) + 
    
    geom_density_ridges( 
              ## ridge geometry
              scale = 0.65, alpha = 0.25, quantile_lines = TRUE,  panel_scaling = FALSE,
              ## rug geometry
              jittered_points = TRUE, rel_min_height = .01,
              point_shape = "|", point_size = 3,
              position = position_points_jitter(height = 0)) +
    
    
    scale_fill_manual(values = my_palettes(name="blackgreen", direction = "1"))+
    scale_color_manual(values = my_palettes(name="blackgreen", direction = "1"))+
    facet_grid(.~STIMULUS) + 
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    # scale_x_continuous(limits = c(0,100))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
    labs (title = "Attitude Shift by Stimulus", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions, x = 100, y= ref_sd_questions,size = 8, vjust=-2, position=position_nudge(y=-.20))  + ##raw
    # cowplot::draw_text(text = ref_sd_questions, x = -4, y= ref_sd_questions,size = 10, vjust=-2) + ##z-score
    theme_minimal() 
  # + easy_remove_legend() 
)
  

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_B1_SDS_by_Stimulus_ridges.png"), units = c("in"), width = 10, height = 14,  bg='#ffffff'  )}
```





## ABS PRE-POST SD ABSOLUTE VALUES
```{r block1_sds_by_sample_ABS, message=FALSE, warning = FALSE}


### FILTER FOR ONLY SD QUESTIONS
df <- df_sd_questions_long_abs 
# %>% filter(QUESTION %in% ref_sd_questions)


############## BLOCK 1 SDs by STIMULUS 
 df <- df %>% select(1:7, STIMULUS, QUESTION, TIME, value)  
 d <- left_join( x = df, y = ref_labels_abs, 
                  by = c("QUESTION" = "ref_sd_questions_abs")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions),
          value = as.numeric(value)) %>%
    group_by(STIMULUS, QUESTION,TIME) %>% 
    mutate(m=median(value)) %>% droplevels() ## calc median for printing on graph
  
(x <-
    ggplot(d, aes(x = value, y = fct_rev(QUESTION), fill = TIME, color= TIME)) +
    # geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE) + 
    
    geom_density_ridges( 
              ## ridge geometry
              scale = 0.65, alpha = 0.25, quantile_lines = TRUE,  panel_scaling = FALSE,
              ## rug geometry
              jittered_points = TRUE, rel_min_height = .01,
              point_shape = "|", point_size = 3,
              position = position_points_jitter(height = 0)) +
    
    scale_x_continuous(limits = c(0,50))+
    scale_fill_manual(values = my_palettes(name="blackred", direction = "1"))+
    scale_color_manual(values = my_palettes(name="blackred", direction = "1"))+
    facet_grid(.~STIMULUS) + 
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    # scale_x_continuous(limits = c(0,100))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels_abs$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels_abs$right))
    ) +
    labs (title = "ABS VALUE Attitude Shift by Stimulus", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions_abs, x = 45, y= ref_sd_questions_abs,size = 8, vjust=-2, position=position_nudge(y=-.20))  + ##raw
  
    theme_minimal() 
  # + easy_remove_legend() 
)
  

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_B1_SDS_by_Stimulus_ridges_ABS.png"), units = c("in"), width = 10, height = 14,  bg='#ffffff'  )}
```






## RAW SHIFT SDs
```{r shift_sds, message=FALSE, warning = FALSE}


### FILTER FOR ONLY SD QUESTIONS
df <- df_questions %>% 
  filter(QUESTION %in% ref_sd_questions) %>% 
  droplevels() %>% 
  mutate(
    POST = as.numeric(POST),
    PRE = as.numeric(PRE),
    shift = POST - PRE
  )

############## BLOCK 1 SDs by SAMPLE
 df <- df %>% select(1:7, STIMULUS, QUESTION, shift)  
 d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(STIMULUS, QUESTION) %>% 
    mutate(m=median(shift)) %>% droplevels() ## calc median for printing on graph
  
(x <-
    ggplot(d, aes(x = shift, y = fct_rev(QUESTION), fill = category, color= category)) +
    # geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE) + 
    
    geom_density_ridges( 
              ## ridge geometry
              scale = 0.65, alpha = 0.25, quantile_lines = TRUE,  panel_scaling = FALSE,
              ## rug geometry
              jittered_points = TRUE, rel_min_height = .01,
              point_shape = "|", point_size = 3,
              position = position_points_jitter(height = 0)) +
    
    
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    facet_grid(.~STIMULUS) + 
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    # scale_x_continuous(limits = c(0,100))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
    labs (title = "RAW Attitude Shift by Stimulus", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions, x = 100, y= ref_sd_questions,size = 8, vjust=-2, position=position_nudge(y=-.20))  + ##raw
    # cowplot::draw_text(text = ref_sd_questions, x = -4, y= ref_sd_questions,size = 10, vjust=-2) + ##z-score
    theme_minimal() 
  # + easy_remove_legend() 
)
  

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_B1_SDS_by_Stimulus_ridges_SHIFT.png"), units = c("in"), width = 10, height = 14,  bg='#ffffff'  )}
```






## ABS SHIFT SDs
```{r shift_sds_abs, message=FALSE, warning = FALSE}


### FILTER FOR ONLY SD QUESTIONS
df <- df_sd_questions_abs%>% 
  filter(QUESTION %in% ref_sd_questions) %>% 
  droplevels() %>% 
  mutate(
    POST = as.numeric(POST),
    PRE = as.numeric(PRE),
    shift = POST - PRE
  )

############## BLOCK 1 SDs by SAMPLE
 df <- df %>% select(1:7, STIMULUS, QUESTION, shift)  
 d <- left_join( x = df, y = ref_labels, 
                  by = c("QUESTION" = "ref_sd_questions")) %>% 
        mutate(
          category=factor(category, levels=c("COMPETENCY","MAKER","CHART")),
          QUESTION = factor(QUESTION, levels=ref_sd_questions)) %>% 
    group_by(STIMULUS, QUESTION) %>% 
    mutate(m=median(shift)) %>% droplevels() ## calc median for printing on graph
  
(x <-
    ggplot(d, aes(x = shift, y = fct_rev(QUESTION), fill = category, color= category)) +
    # geom_density_ridges(scale = 0.75, quantile_lines = TRUE, alpha = 0.25, panel_scaling = FALSE) + 
    
    geom_density_ridges( 
              ## ridge geometry
              scale = 0.65, alpha = 0.25, quantile_lines = TRUE,  panel_scaling = FALSE,
              ## rug geometry
              jittered_points = TRUE, rel_min_height = .01,
              point_shape = "|", point_size = 3,
              position = position_points_jitter(height = 0)) +
    
    
    scale_fill_manual(values = my_palettes(name="greys", direction = "1"))+
    scale_color_manual(values = my_palettes(name="greys", direction = "1"))+
    facet_grid(.~STIMULUS) + 
    ## MEDIAN
    stat_summary(fun=median, geom="text", fontface = "bold", size= 2.2,
                vjust=+2, hjust = 0.50, aes(label=round(m, digits=0)))+
    stat_summary(fun=median, geom="point", size=2) +
    # scale_x_continuous(limits = c(0,100))+
    guides(
      y = guide_axis_manual(labels = rev(ref_labels$left)),
      y.sec = guide_axis_manual(labels = rev(ref_labels$right))
    ) +
    labs (title = "ABS Attitude Shift by Stimulus", y = "", caption = "(point is median)") +
    cowplot::draw_text(text = ref_sd_questions, x = 100, y= ref_sd_questions,size = 8, vjust=-2, position=position_nudge(y=-.20))  + ##raw
    # cowplot::draw_text(text = ref_sd_questions, x = -4, y= ref_sd_questions,size = 10, vjust=-2) + ##z-score
    theme_minimal() 
  # + easy_remove_legend() 
)
  

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_B1_SDS_by_Stimulus_ridges_ABS_SHIFT.png"), units = c("in"), width = 10, height = 14,  bg='#ffffff'  )}
```








## PRE-POST Categoricals

### ENCOUNTER
```{r SANKEY-ENCOUNTER}

### FILTER FOR ONLY GENDER QUESTION
df <- df_graphs %>% 
  select(PRE_ENCOUNTER, POST_ENCOUNTER, STIMULUS, PID) 

### {GGSANKEY} ################################

## REPEATED MEASURES
## SANKEY DIAGRAM
## MUST RESHAPE FOR SANKEY 
ds <- df %>% 
  ##custom from ggsankey
  make_long(PRE_ENCOUNTER, POST_ENCOUNTER, value=STIMULUS) %>% 
  mutate(
    node = factor(node, levels = rev(order_encounter)),
    next_node= factor(next_node, levels = rev(order_encounter)),
    match = ifelse(node==next_node, 1, 0.5), # try to highlight throughflows
  ) 

(S <- ggplot(ds, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = node
               ))+
  geom_sankey(width = 0.25, flow.alpha = 0.65, node.alpha = 1, node.color = "white") +
  geom_sankey_text(aes( x = as.numeric(x),  label = after_stat(freq)),
          size = 3, color = "white", fontface = "bold", check_overlap = TRUE) +
  scale_fill_manual(values = my_palettes(name="encounter", direction = "-1"), guide = guide_legend(reverse = TRUE)) +
  labs(title = "CHANGE in ENCOUNTER by STIMULUS", 
       x = "TIME", y = "(count)", fill = "AGE",
       caption = "") + 
  theme_minimal() + facet_grid(.~value)
)
#############################################


if(GRAPH_SAVE == TRUE) {
    ggsave(plot = S, path="figs/study3", filename =paste0("S3_ENCOUNTER_by_STIMLUS.png"), units = c("in"), width = 16, height = 8,  bg='#ffffff'  )
  }

```







### MAKER
```{r SANKEY-ID}

### FILTER FOR ONLY ID QUESTION
df <- df_graphs %>% 
  select(PRE_ID, POST_ID, STIMULUS, PID) 

### {GGSANKEY} ################################

## REPEATED MEASURES
## SANKEY DIAGRAM
## MUST RESHAPE FOR SANKEY 
ds <- df %>% 
  ##custom from ggsankey
  make_long(PRE_ID, POST_ID, value=STIMULUS) %>% 
  mutate(
    node = factor(node),
    next_node= factor(next_node),
    match = ifelse(node==next_node, 1, 0.5), # try to highlight throughflows
  ) 

(S <- ggplot(ds, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = node
               ))+
  geom_sankey(width = 0.25, flow.alpha = 0.65, node.alpha = 1, node.color = "white") +
  geom_sankey_text(aes( x = as.numeric(x),  label = after_stat(freq)),
          size = 3, color = "white", fontface = "bold", check_overlap = TRUE) +
  scale_fill_manual(values = my_palettes(name="reds", direction = "-1"), guide = guide_legend(reverse = TRUE)) +   
  # scale_fill_viridis(discrete=TRUE, option="viridis", drop = FALSE, alpha = 1) +
  labs(title = "CHANGE in MAKER ID by STIMULUS", 
       x = "TIME", y = "(count)", fill = "MAKER",
       caption = "") + 
  theme_minimal() + facet_grid(.~value)
)
#############################################

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = S, path="figs/study3", filename =paste0("S3_MAKER_by_STIMLUS.png"), units = c("in"), width = 16, height = 8,  bg='#ffffff'  )
  }
```

### AGE
```{r SANKEY-AGE}

### FILTER FOR ONLY AGE QUESTION
df <- df_graphs %>% 
  select(PRE_AGE, POST_AGE, STIMULUS, PID) 

### {GGSANKEY} ################################

## REPEATED MEASURES
## SANKEY DIAGRAM
## MUST RESHAPE FOR SANKEY 
ds <- df %>% 
  ##custom from ggsankey
  make_long(PRE_AGE, POST_AGE, value=STIMULUS) %>% 
  mutate(
    node = factor(node),
    next_node= factor(next_node),
    match = ifelse(node==next_node, 1, 0.5), # try to highlight throughflows
  ) 

(S <- ggplot(ds, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = node
               ))+
  geom_sankey(width = 0.25, flow.alpha = 0.65, node.alpha = 1, node.color = "white") +
  geom_sankey_text(aes( x = as.numeric(x),  label = after_stat(freq)),
          size = 3, color = "white", fontface = "bold", check_overlap = TRUE) +
  scale_fill_manual(values = my_palettes(name="lightblues", direction = "-1"), guide = guide_legend(reverse = TRUE)) +
  labs(title = "CHANGE in AGE by STIMULUS", 
       x = "TIME", y = "(count)", fill = "AGE",
       caption = "") + 
  theme_minimal() + facet_grid(.~value)
)
#############################################


if(GRAPH_SAVE == TRUE) {
    ggsave(plot = S, path="figs/study3", filename =paste0("S3_AGE_by_STIMLUS.png"), units = c("in"), width = 16, height = 8,  bg='#ffffff'  )
  }

```

### GENDER
```{r SANKEY-GENDER}

### FILTER FOR ONLY GENDER QUESTION
df <- df_graphs %>% 
  select(PRE_GENDER, POST_GENDER, STIMULUS, PID) 

### {GGSANKEY} ################################

## REPEATED MEASURES
## SANKEY DIAGRAM
## MUST RESHAPE FOR SANKEY 
ds <- df %>% 
  ##custom from ggsankey
  make_long(PRE_GENDER, POST_GENDER, value=STIMULUS) %>% 
  mutate(
    node = factor(node, levels = rev(order_gender)),
    next_node= factor(next_node, levels = rev(order_gender)),
    match = ifelse(node==next_node, 1, 0.5), # try to highlight throughflows
  ) 

(S <- ggplot(ds, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = node
               ))+
  geom_sankey(width = 0.25, flow.alpha = 0.65, node.alpha = 1, node.color = "white") +
  geom_sankey_text(aes( x = as.numeric(x),  label = after_stat(freq)),
          size = 3, color = "white", fontface = "bold", check_overlap = TRUE) +
  scale_fill_manual(values = my_palettes(name="smallgreens", direction = "-1"), guide = guide_legend(reverse = TRUE)) +
  labs(title = "CHANGE in GENDER by STIMULUS", 
       x = "TIME", y = "(count)", fill = "AGE",
       caption = "") + 
  theme_minimal() + facet_grid(.~value)
)
#############################################


if(GRAPH_SAVE == TRUE) {
    ggsave(plot = S, path="figs/study3", filename =paste0("S3_GENDER_by_STIMLUS.png"), units = c("in"), width = 16, height = 8,  bg='#ffffff'  )
  }

```



## CONFIDENCE and CATEGORICALS

### MAKER
```{r confidence-grid}

########### GRID OF SCATTERPLOTS
df <- df_graphs %>%
  filter(STIMULUS == "B1-3") %>% 
  select(STIMULUS, PRE_ID, POST_ID, PRE_ID_CONF, POST_ID_CONF) %>% 
  mutate(
    CHANGE = (PRE_ID != POST_ID)
  )


(x <- df %>% ggplot(aes(x=PRE_ID_CONF, y = POST_ID_CONF, color=CHANGE)) +
  geom_point() + 
  scale_x_continuous(limits = c(0,100))+
  scale_y_continuous(limits = c(0,100)) +
  facet_grid(POST_ID ~ PRE_ID) + 
  scale_color_manual(values = my_palettes(name="blackred", direction = "1")) + 
  labs( title = "Confidence in Maker ID", x = "Confidence (Pre)", y = "Confidence(Post)",
        subtitle =("ID_PRE in columns, ID_POST in rows")) + theme_clean()
)
if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_MATRIX_ID_Confidence_scatterplot.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}
```


```{r confidence-parallels}


### PARALLEL COORDINATES  ################################

# ### FILTER FOLKS WHO DID CHANGE
# ### FILTER FOR ONLY SD QUESTIONS
df <- df_graphs %>%
  select(PRE_ID, POST_ID, STIMULUS, PID, PRE_ID_CONF, POST_ID_CONF) %>%
  filter(STIMULUS == "B1-3") %>%
  mutate(
    CHANGE = (PRE_ID != POST_ID)
  ) 

unit_labeller <- function(string) {
  string=as.numeric(string)
  labeled_string <- order_maker[string]
  return(labeled_string)
}

(x <- df %>%  ggparcoord(
           columns = 5:6,
           scale = "globalminmax",
           groupColumn = "CHANGE") + 
           facet_grid(POST_ID~PRE_ID, labeller = labeller(POST_ID=unit_labeller, PRE_ID = unit_labeller)) +
  scale_y_continuous(limits = c(0,100))+
  scale_color_manual(values = my_palettes(name="blackred", direction = "1")) +
  labs( title = "Confidence in Maker ID", subtitle ="ID_PRE in columns, ID_POST in rows", x = "TIME", y = "CONFIDENCE") + theme_clean()
) 


if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_MATRIX_ID_Confidence_parallelcords.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}

```













 
 
 

### AGE
```{r confidence-grid-age}

########### GRID OF SCATTERPLOTS
df <- df_graphs %>%
  filter(STIMULUS == "B1-3") %>% 
  select(STIMULUS, PRE_AGE, POST_AGE, PRE_AGE_CONF, POST_AGE_CONF) %>% 
  mutate(
    CHANGE = (PRE_AGE != POST_AGE)
  )


(x <- df %>% ggplot(aes(x=PRE_AGE_CONF, y = POST_AGE_CONF, color=CHANGE)) +
  geom_point() + 
  scale_x_continuous(limits = c(0,100))+
  scale_y_continuous(limits = c(0,100)) +
  facet_grid(POST_AGE ~ PRE_AGE) + 
  scale_color_manual(values = my_palettes(name="blackred", direction = "1")) + 
  labs( title = "Confidence in Maker AGE", x = "Confidence (Pre)", y = "Confidence(Post)",
        subtitle =("PRE in columns, POST in rows")) + theme_clean()
)

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_MATRIX_AGE_Confidence_scatterplot.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}
```


```{r confidence-parallels-age}


### PARALLEL COORDINATES  ################################

# ### FILTER FOLKS WHO DID CHANGE
# ### FILTER FOR ONLY SD QUESTIONS
df <- df_graphs %>%
  select(PRE_AGE, POST_AGE, STIMULUS, PID, PRE_AGE_CONF, POST_AGE_CONF) %>%
  filter(STIMULUS == "B1-3") %>%
  mutate(
    CHANGE = (PRE_AGE != POST_AGE)
  ) 

unit_labeller <- function(string) {
  string=as.numeric(string)
  labeled_string <- order_age[string]
  return(labeled_string)
}

(x <- df %>%  ggparcoord(
           columns = 5:6,
           scale = "globalminmax",
           groupColumn = "CHANGE") + 
           facet_grid(POST_AGE~PRE_AGE, labeller = labeller(POST_AGE=unit_labeller, PRE_AGE = unit_labeller)) +
  scale_y_continuous(limits = c(0,100))+
  scale_color_manual(values = my_palettes(name="blackred", direction = "1")) +
  labs( title = "Confidence in Maker AGE", subtitle ="PRE in columns, POST in rows", x = "TIME", y = "CONFIDENCE") + theme_clean()
) 


if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_MATRIX_AGE_Confidence_parallelcords.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}

```














 
 
 




### GENDER
```{r confidence-grid-age}

########### GRID OF SCATTERPLOTS
df <- df_graphs %>%
  filter(STIMULUS == "B1-3") %>% 
  select(STIMULUS, PRE_GENDER, POST_GENDER, PRE_GENDER_CONF, POST_GENDER_CONF) %>% 
  mutate(
    CHANGE = (PRE_GENDER != POST_GENDER)
  )


(x <- df %>% ggplot(aes(x=PRE_GENDER_CONF, y = POST_GENDER_CONF, color=CHANGE)) +
  geom_point() + 
  scale_x_continuous(limits = c(0,100))+
  scale_y_continuous(limits = c(0,100)) +
  facet_grid(POST_GENDER ~ PRE_GENDER) + 
  scale_color_manual(values = my_palettes(name="blackred", direction = "1")) + 
  labs( title = "Confidence in Maker GENDERE", x = "Confidence (Pre)", y = "Confidence(Post)",
        subtitle =("PRE in columns, POST in rows")) + theme_clean()
)

if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_MATRIX_GENDER_Confidence_scatterplot.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}
```


```{r confidence-parallels-gender}


### PARALLEL COORDINATES  ################################

# ### FILTER FOLKS WHO DID CHANGE
# ### FILTER FOR ONLY SD QUESTIONS
df <- df_graphs %>%
  select(PRE_GENDER, POST_GENDER, STIMULUS, PID, PRE_GENDER_CONF, POST_GENDER_CONF) %>%
  filter(STIMULUS == "B1-3") %>%
  mutate(
    CHANGE = (PRE_GENDER != POST_GENDER)
  ) 

unit_labeller <- function(string) {
  string=as.numeric(string)
  labeled_string <- order_gender[string]
  return(labeled_string)
}

(x <- df %>%  ggparcoord(
           columns = 5:6,
           scale = "globalminmax",
           groupColumn = "CHANGE") + 
           facet_grid(POST_GENDER~PRE_GENDER, labeller = labeller(POST_GENDER=unit_labeller, PRE_GENDER = unit_labeller)) +
  scale_y_continuous(limits = c(0,100))+
  scale_color_manual(values = my_palettes(name="blackred", direction = "1")) +
  labs( title = "Confidence in Maker GENDER", subtitle ="PRE in columns, POST in rows", x = "TIME", y = "CONFIDENCE") + theme_clean()
) 


if(GRAPH_SAVE == TRUE) {
    ggsave(plot = x, path="figs/study3", filename =paste0("S3_MATRIX_GENDER_Confidence_parallelcords.png"), units = c("in"), width = 10, height = 10,  bg='#ffffff'  )}

```

# QUICK MODEL


## SIG CHANGES?

```{r anovas}

df <- df_sd_questions_long 
# %>% filter(QUESTION=="POLITICS")
# %>% filter(QUESTION=="POLITICS")

m1.aov <- aov(value ~ TIME*STIMULUS  + Error(PID), data = df)
summary(m1.aov)

# has the interaction.plot() function built-in, but it comes with a ton of parameters beginners can find confusing. The following list explains all the parameters you need to create an interaction plot:
# x.factor - A factor variable whose levels will be on the X-axis.
# trace.factor - The second-factor variable whose levels will be represented as traces (lines).
# response - A numeric response variable.
# fun - The function to compute the summary, e.g. median.
# ylab - Y-axis label of the plot.
# xlab - X-axis label of the plot.
# trace.label - Label for the legend.
# col - A vector of colors used for all traces.
# lyt - A type of the lines drawn.
# lwd - Width of the lines drawn.


with (df, { interaction.plot(  
                x.factor = STIMULUS,
                trace.factor = TIME,
                fun = median,
                response = value
              )})




###### THE REGRESSION WAY
df <- df_sd_questions_long %>% filter(QUESTION=="POLITICS")
m1 <- lmer( value ~ TIME*STIMULUS + (1|PID), data = df )
summary(m1)
anova(m1)


m1 <- lmer( value ~ STIMULUS*TIME + (1|PID), data = df )
plot_model(m1, type="int", terms = c("TIME","STIMULUS")) + coord_flip()


```

## BEAUTY TRUST

```{r trust-beauty}

df <- df_graphs_z %>% 
  mutate(
    shift_TRUST = POST_TRUST - PRE_TRUST,
    shift_BEAUTY = POST_BEAUTY - PRE_BEAUTY,
    shift_ALIGN = POST_ALIGN - PRE_ALIGN,
  )


m1 <- lmer(data = df, PRE_TRUST ~ PRE_BEAUTY + PRE_ALIGN + (1|PID))
summary(m1)
plot_model(m1)


m2 <- lmer(data = df, POST_TRUST ~ POST_BEAUTY + POST_ALIGN + (1|PID))
summary(m2)
plot_model(m2)

m3 <- lmer(data = df, shift_TRUST ~ shift_BEAUTY + shift_ALIGN + (1|PID))
summary(m3)
plot_model(m3)


```




